### 2024-07-10 Rmd/boostrap_0.1.Rmd
initiate package

---
title: "Bootstrap 0.1"
author: "Brett Stacy"
date: "2024-06-19"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(data.table)
library(tidytable)
library(purrr)
```

# Data

```{r}
DT = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
```

# Functions

Copied RSS function from Pcod script:

```{r}
rss2 = function(lengths_og, lengths_sim){
  # count the frequency of each observed length and assign them to a grid of length bins
  grid.temp = data.table(LENGTH = 1:141) # above there is the grid min and max = 1:141
  freqt = merge(grid.temp, lengths_og[,.(freq_og=.N),by=LENGTH], by="LENGTH", all.x = T) # table with length bins and frequency (number of fish) observed in each bin
  freqt = merge(freqt, lengths_sim[,.(freq_sim=.N),by=LENGTH], by="LENGTH", all.x = T) %>% # add resampled frequency to table %>% replace NAs with zero 
    replace(is.na(.), 0)

  freqt %>% mutate(prop_og = freq_og/sum(freq_og), .keep = "unused") %>% # make a proportions at length table including og and sim data.
    mutate(prop_sim = freq_sim/sum(freq_sim), .keep = "unused") -> propt

  # RSS 
  rss = sum(propt$prop_sim * (1 - propt$prop_sim)) / sum((propt$prop_sim - propt$prop_og)^2)

  return(rss)
}
```

Function for random sampling that can handle n=1 sample. This is important because there are for e.g. ~19 samples of length 1 in 2022.
```{r}
# consider not using ... because Ben never seems to
comp_sample = function(x, ...) x[sample.int(length(x), ...)]
```

# Bootstrap Serial

Year = 2022
Iters = 25
boot hauls iters
boot lengths once
serial

```{r}
iters = 25
subDT = DT[YEAR==2022]

# check: do any hauls have 1 length sample?
sum(subDT[,.N,by=HAUL_JOIN]$N==1) # 19 have 1

# boot hauls iters number of times
samp_func = function(x) sample(unique(x), size = length(unique(x)), replace = T)
booted.hauls = purrr::map(1:iters, ~samp_func(subDT$HAUL_JOIN))

# NO: we need to take the 1s out of the boostrapped hauls and store them, then put them directly back into the resampled length comps where their hauls were chosen in the haul resample
# haul.join.ones = subDT[,.N,by=HAUL_JOIN]$HAUL_JOIN[subDT[,.N,by=HAUL_JOIN]$N==1]
# booted.hauls[[1]][1]  # perhaps call them NAs for now

# for each set of booted hauls, boot the length comp samples once

samp_func2 = function(x2) {
  # purrr::map(x2, .f = function(x1) comp_sample(subDT[HAUL_JOIN == x1 , LENGTH], replace = T)) #!!!! NEED TO INCORPORATE SUM_FREQUENCY!!!!
  data.table::setkey(subDT, HAUL_JOIN) # setkey speeds it up 2x!
  purrr::map(x2, .f = function(x1) comp_sample(subDT[x1][["LENGTH"]], replace = T)) 
} 
tic()
booted.hauls %>%
  purrr::map(.f = samp_func2, .progress = T) -> booted.lengths # this gives a list of length() iters, each a list of length() unique hauls, each a numeric vector of length comps
toc()

# try it again in parallel using furrr
# first, change samp_func to use both x2 and DT, and change the way LENGTH is accessed because future() needs characters I think. 
samp_func3 = function(x2, DT) {
  data.table::setkey(DT, HAUL_JOIN)
  # purrr::map(.x = x2, .f = function(x1) comp_sample(DT[x1][["LENGTH"]], replace = T)) # without frequency (incorrect)
  purrr::map(.x = x2, .f = function(x1) comp_sample(DT[x1][["LENGTH"]] %>% rep(DT[x1][["SUM_FREQUENCY"]]), replace = T)) # with frequency (correct)
} 
# testing
# samp_func3(booted.hauls[[1]], DT = subDT)
tic()
booted.hauls %>%
  purrr::map(.f = function(x2, DT) samp_func3(x2 = x2, DT = subDT)) -> booted.lengths
  # purrr::map(.f = function(x2, DT = subDT) purrr::map(.x = x2, .f = function(x1) comp_sample(DT[x1][["LENGTH"]], replace = T))) -> booted.lengths # without the samp_func3 function for testing.
toc()
### key learnings
# 1. in samp_func3, setting the key sped things up. I think Ben speeds up by subsetting the DT, not sure which is faster
# 2. I had to include .f = function() in samp_func3 even though samp_func3 is already a function. Not sure why.

plan(multisession, workers = 14)

tic()
booted.hauls %>%
  furrr::future_map(.f = function(x2, DT) samp_func3(x2 = x2, DT = subDT), .options = furrr_options(seed = TRUE)) -> booted.lengths2 # 13 seconds. (3x faster)
toc()
```

## Take what I learned from above and make it better
```{r}

```

```{r}
# it would be great to name the list of hauls with the haul names. all the below map2 trials failed 
# purrr::map2(booted.hauls, booted.lengths, function(x,y) names(y)=x)
# purrr::map2(booted.hauls, booted.lengths, ~ .x)
# purrr::map2(booted.hauls, booted.lengths, ~ listr::list_rename(.y, .x))
# purrr::map2(booted.hauls, names(booted.lengths), ~ .y=.x)
# purrr::imap_chr(booted.hauls, booted.lengths, ~ paste0(.x))

for (i in 1:length(booted.lengths)) { # just hit it with a loop hammer
  names(booted.lengths[[i]]) = booted.hauls[[i]]
}

# testing
# x1 = booted.hauls[[1]][1]
# temp = subDT[HAUL_JOIN == x1 , LENGTH]
# sample(temp, replace = T)
# comp.sample(temp, replace = T)
# temp[sample.int(length(temp), replace = T)]

```

## Apply RSS to resampled legnth comps

Note that this is only practicing RSSing. This is NOT the correct method. The correct method expands the proportions to the fishery level, then RSSs that to each of the expanded bootstrapped versions.

```{r}

rss_length = function(lengths_og, lengths_sim){
  # count the frequency of each observed length and assign them to a grid of length bins
  grid.temp = tidytable::tidytable(LENGTH = 1:141) # above there is the grid min and max = 1:141
  freqt = merge(grid.temp, lengths_og[,.(freq_og=.N),by=LENGTH], by="LENGTH", all.x = T) # table with length bins and frequency (number of fish) observed in each bin
  freqt = merge(freqt, lengths_sim[,.(freq_sim=.N),by=LENGTH], by="LENGTH", all.x = T) %>% # add resampled frequency to table %>% replace NAs with zero 
    replace(is.na(.), 0)

  freqt %>% tidytable::mutate(prop_og = freq_og/sum(freq_og), .keep = "unused") %>% # make a proportions at length table including og and sim data.
    tidytable::mutate(prop_sim = freq_sim/sum(freq_sim), .keep = "unused") -> propt

  # RSS 
  rss = sum(propt$prop_sim * (1 - propt$prop_sim)) / sum((propt$prop_sim - propt$prop_og)^2)

  return(rss)
}

# testing
test.name = names(booted.lengths[[1]])[1]
lengths_og = tidytable::tidytable(subDT[HAUL_JOIN==test.name, .(LENGTH)])
lengths_sim = tidytable::tidytable(LENGTH = booted.lengths[[1]][[test.name]])
rss_length(lengths_og = lengths_og, lengths_sim = lengths_sim)

purrr::map()

```

### 2024-07-10 Rmd/boot_hauls_implications.Rmd
initiate package

---
title: "Booting Hauls Implications"
author: "Brett Stacy"
date: "2024-06-24"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

# Why do we boot hauls instead of just boot samples from every haul?

In surveyISS and the associated literature, hauls are resampled for a number of iterations. For each resampled haul, the length composition from that haul is resampled once. Howevewr, because the hauls are resampled with equal probability, I propose that as the iterations approach large numbers, this procedure is equivalent to resampling each of the samples an equal number of times. The number of times would be approximately equal to iterations/#hauls.

To test this, I will create an idealized situation with few hauls that have large differences in sample sizes. I will then resample by hauls and resample by samples and compare the difference in sample size as the number of iterations grows. If they converge, then I am right.

```{r}
iters = 10

DT = data.table(hauls = letters[1:3], sample_size = c(1, 100, 1000))

booted_hauls = purrr::map(1:iters, ~sample(DT$hauls, replace = T))

# associated sample sizes from one set of resampled hauls 
# booted_hauls[[1]] %>%
  # purrr::map_vec(.f=function(x) DT[hauls == x, sample_size])

# make the above into a function and add sum the sample size
total.sample.size = function(og.data, resample){
  resample %>%
    purrr::map_vec(.f = function(x) og.data[hauls == x, sample_size]) %>%
    sum() -> temp
    return(temp)
}
# total.sample.size(DT, booted_hauls[[1]])

# perform the function over all booted hauls. 
booted_hauls %>%
  purrr::map_vec(.f = function(x) total.sample.size(DT, x)) %>%
  sum() -> ss_boot_hauls

ss_boot_hauls

## Compare to just multiplying the sample sizes by the number of times their associated hauls were resampled
# count how many "a"s, "b"s, and "c"s there are in the resampled hauls
DT[, count_resampled_hauls := table(unlist(booted_hauls))]

DT[, sum(sample_size*count_resampled_hauls)]

DT

```

Conclusion: These numbers are exactly the same. This is because both methods are doing the same thing, just in a different way. The first one sums first by each resampled iteration, then sums over all iterations. The second sums over all iterations, then sums by the frequency of the haul in the resample.

## Compare to just multiplying sample size by number of bootstrap iterations.

```{r}

iters = 1000

## First calculate the sum of sample sizes from the bootstrap, using method 2 above (faster)
DT = data.table(hauls = letters[1:3], sample_size = c(1, 100, 1000))
booted_hauls = purrr::map(1:iters, ~sample(DT$hauls, replace = T))
# count how many "a"s, "b"s, and "c"s there are in the resampled hauls
DT[, count_resampled_hauls := table(unlist(booted_hauls))]
DT[, sum(sample_size*count_resampled_hauls)]

## Second simply multiply each sample size by iters and sum
sum(DT[, sample_size]*iters)

## Subtract the two
DT[, sum(sample_size*count_resampled_hauls)] - sum(DT[, sample_size]*iters)

```

## Do it a bunch of times and boxplot the result

```{r}
global.iters = 1000

DT = data.table(hauls = letters[1:3], sample_size = c(1, 100, 1000))

diff_methods = function(x){
  iters = 1000
  ## First calculate the sum of sample sizes from the bootstrap, using method 2 above (faster)

  booted_hauls = purrr::map(1:iters, ~sample(x$hauls, replace = T))
  # count how many "a"s, "b"s, and "c"s there are in the resampled hauls
  x[, count_resampled_hauls := table(unlist(booted_hauls))]
  method1 = x[, sum(sample_size*count_resampled_hauls)]
  ## Second simply multiply each sample size by iters and sum
  method2 = sum(x[, sample_size]*iters)
  ## Subtract the two
  return((method1 - method2)/method1)
}

purrr::map_vec(1:global.iters, ~diff_methods(DT)) -> methods_error

boxplot(methods_error)

```

Conclusion: The error between the two methods is zero, indicating there is no difference between methods and they provide the same information. The total sample size generated by bootstrapping for many iterations is equivalent to multiplying the sample sizes by the number of iterations and adding them up.

As suspected, sampling a vector where each element has the equal probability of being selected will result in the same number of each element being resampled.

This means that, for surveyISS purposes, each length composisiton sample could simply be resampled 500 times and provide the same answer as resampling the hauls 500 times.

### 2024-07-10 Rmd/furrr_example.Rmd
initiate package

---
title: "furrr example"
author: "Brett Stacy"
date: "2024-07-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
library(data.table)
library(tidytable)
library(purrr)
library(furrr) # also loads package "future" that includes functions for setting up parallel computing
library(tictoc)
```

# Data

Change the file directory to where you downloaded "y2_ebs_pcod_Brett.RDS"

```{r}
DT = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
```

# Quick furrr example

furrr contains all the purrr functions, but allows for parallelization. The most straightforward parallelization type is "multisession", where multiple virtual R sessions are initiated to carry out code evaluation in parallel. The number of sessions are user-defined and can be set as the number of cores you have (virtual or physical) minus 1 or 2 for overhead.

DISADVANTAGES:

  1. The user has to specify the number of workers (cores) to use based on the machine they are using. This will inevitably be clunky and the future use of furrr in a package should therefore be an optional switch, where the default is purrr.

  2. The speed gain is not necessarily a multiple of the number of workers you specify. There is overhead processing capacity required to transfer large data sets back and forth between the virtual R sessions, and your primary working session. This is relevant for our purposes and something to consider moving forward.

## Functions (I will improve the function names for the package, don't worry)
```{r}
# consider not using ... because Ben never seems to
comp_sample = function(x, ...) x[sample.int(length(x), ...)] # Function for random sampling length comps that can handle n=1 samples. This is important because base::sample does weird stuff when n=1 and there are for e.g., ~19 samples of length 1 in 2022.

samp_func = function(x) sample(unique(x), size = length(unique(x)), replace = T) # for resampling hauls

samp_func3 = function(x2, DT) { # for resampling length comps
  data.table::setkey(DT, HAUL_JOIN)
  purrr::map(.x = x2, .f = function(x1) comp_sample(DT[x1][["LENGTH"]] %>% rep(DT[x1][["SUM_FREQUENCY"]]), replace = T)) 
}

```

## Bootstrapping length comps

### Without furrr

```{r}
iters = 25
subDT = DT[YEAR==2022]

# boot hauls iters number of times
booted.hauls = purrr::map(1:iters, ~samp_func(subDT$HAUL_JOIN))

# for each set of booted hauls, boot the length comp samples once
# without furrr
tictoc::tic()
booted.hauls %>%
  purrr::map(.f = function(x2, DT) samp_func3(x2 = x2, DT = subDT)) -> booted.lengths
tictoc::toc()
```

### With furrr

```{r}
# with furrr
future::plan(multisession, workers = 14) # CHANGE THIS TO SUIT YOUR MACHINE AND NEEDS
tictoc::tic()
booted.hauls %>%
  furrr::future_map(.f = function(x2, DT) samp_func3(x2 = x2, DT = subDT), .options = furrr_options(seed = TRUE)) -> booted.lengths2 
tictoc::toc()
```
# Conclusion:

furrr speeds things up about 4-5x with 14 "workers". This is nice, but there is a workers/3 overhead time loss due to large data file transfers.

### 2024-07-10 Rmd/haul_size_effect.Rmd
initiate package

---
title: "Haul Size Effect"
author: "Brett Stacy"
date: "2024-06-19"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(data.table)
```

## What is the impact of scaling by haul size?

Haul size ranges a lot for EBS Pcod. We sample ~20 fish on every haul but only the samples from the larger hauls have a significant impact on the population proportions at length if we use haul size as an importance scaler.

load pcod data

illustrate range of haul sizes. plot probability haul sizes by groups (reasonable size classes).

Show that if we scale by haul size, how many samples have a miniscule impact on the length distribution

i.e., for hauls size max with 1% or less impact on length distribution, what is the percent samples in these hauls?

Load in pcod data

```{r}
DT = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
```

### Full data set

Plot histogram of haul size in numbers of fish

```{r}

haulDT = DT[!duplicated(HAUL_JOIN), -c("LENGTH", "SUM_FREQUENCY")][order(YAGMH_SNUM)] # condense to only unique hauls, get rid of sub-haul level data, order the DT by number of fish in hauls.

hist(haulDT$YAGMH_SNUM)

summary(haulDT$YAGMH_SNUM)

```

Sort the hauls by size, then find the haul that represents 1% of the total catch threshold

"the smallest 1% of hauls contain X% of length data"

```{r}

# plot(haulDT$YAGMH_SNUM[1:100000])

haulDT[,YAGMH_SNUM_CUMULATIVE := cumsum(YAGMH_SNUM)] # make a new vector of cumulative sum of catches in hauls

good.ind = which.min(abs(haulDT$YAGMH_SNUM_CUMULATIVE - .01*haulDT[.N, YAGMH_SNUM_CUMULATIVE])) # find which ordered haul represents the 1% threshold.
good.ind

# side quest: how many hauls have more samples than number of fish in the haul?
sum(haulDT$YAGMH_SNUM < haulDT$YAGMH_SFREQ)/haulDT[,.N] # less than .1%

haulDT[1:good.ind, sum(YAGMH_SFREQ)]/haulDT[, sum(YAGMH_SFREQ)] # find how many samples are in the 1% hauls

```

Conclusion:

-   The smallest 1% of hauls contain 7% of the length samples
-   The smallest 10% of hauls contain 30% of the length samples

Do it another way. This should be equivalent. Calculate the percentage of SNUM to the sum of SNUM, then scale it by the highest SNUM percentage (last in ordered DT)

```{r}

haulDT[,YAGMH_SNUM_PERCENT := YAGMH_SNUM/sum(YAGMH_SNUM)]
haulDT[,YAGMH_SNUM_PERCENT_SCALED := YAGMH_SNUM_PERCENT/max(YAGMH_SNUM_PERCENT)]

good.ind = which.min(abs(haulDT$YAGMH_SNUM_PERCENT_SCALED - .01))
good.ind

haulDT[1:good.ind, sum(YAGMH_SFREQ)]/haulDT[, sum(YAGMH_SFREQ)] # find how many samples are in the 1% hauls

```

Uh-oh. This gives a different answer. And I don't know which one (if any) are correct.

### One year of data

Now for one year, say 2022, find out how many times more influence 20 samples from a big haul have compared to 20 samples from a small haul. Perhaps use the 25% biggest haul and the 75% biggest haul. Is this the right way to do this? Just calculate the proportion of influence of each haul first maybe. then order them, or order them prior doesn't matter, then check the proportion of influence of the 25% largest haul and compare it to the 75% largest haul. Compare them by dividing their proportions.

#### Same analysis as above:
```{r}

haulDT2022 = haulDT[YEAR==2022]

good.ind = which.min(abs(haulDT2022$YAGMH_SNUM_CUMULATIVE - .01*haulDT2022[.N, YAGMH_SNUM_CUMULATIVE])) # find which ordered haul represents the 1% threshold.

haulDT2022[1:good.ind, sum(YAGMH_SFREQ)]/haulDT2022[, sum(YAGMH_SFREQ)]

```

6%
24%

#### Calculate proportions

```{r}

```

### 2024-07-10 Rmd/sample_scale_vs_scale_sample.Rmd
initiate package

---
title: "Sample scale vs scale sample"
author: "Brett Stacy"
date: "2024-06-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

# Can we scale a boostrap sample?

Can we take a boostrap sample of hauls, then scale it and it will equal the boostrapped scale?

## Bootstrap then scale

Bootstrap the hauls, then apply the scaling factors to

```{r}
iters = 10
haul_size = c(100, 100, 200, 300, 200, 100)
DT = data.table(hauls = letters[1:6], lengths = c(41:46))

r_hauls = purrr::map(1:iters, ~ sample(hauls, replace = T)) # resampled hauls

```

## Bootstrap the scale

### 2024-07-10 Rmd/sample_vs_rmultinomial.Rmd
initiate package

---
title: "sample() vs rmultinomial()"
author: "Brett Stacy"
date: "2024-06-18"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(data.table)
library(tidyverse)
```

## base::sample() vs base::rmultinomial()

This document compares the functions sample() and rmultinomial() for the purposes of bootstrapping. Both these functions use a random number generator and can produce a bootstrapped sample set from either a uniform or multinomial distribution. However, sample() cannot accept a single number, where rmultinomial() can. This is relevant to observer data where there exist single sample sizes for hauls in a non-trivial number of hauls. However, rmultinomial() cannot sample without replacement, where sample() can. This is relevant to situations where alternative sampling rates are investigated.

This document uses idealized simulated data.

Goals:

1.  Demonstrate that the following are equivalent:
    1.  sample()\*probs, sample(prob = probs), rmultinomial(prob = probs)

```{r, eval=T}

### SIDE QUEST ####
# is sampling from a multinomial with probabilities determined by frequency the same as sample()? if so, can we use the multinomial to resample considering weighitng?
# in other words, can we use the month weights to control which YAGM strata gets resampled more often?

iters = 10000
temp.lengths = c(44,45,46,46,46,47,47,48,49,50)
temp.lengthsDT = data.table(length = temp.lengths)
s.lengths = purrr::map(1:iters, ~sample(temp.lengths, replace = TRUE)) 
u.lengths = unique(temp.lengths)
n.lengths = temp.lengthsDT[, .N]
probs.lengths = tidytable::count(temp.lengthsDT, length)[,n/sum(n)] 
s.lengths2 = purrr::map(1:iters, ~sample(u.lengths, size = n.lengths, replace = TRUE, prob = probs.lengths))

## sample(n)
# I want to count how many times on average each number shows up in the sampled lengths
# old habits die hard, loop:
freq.list = list()
for (j in 1:length(unique(temp.lengths))) {
  freq.list[[j]] = rep(NA, iters)
  for (i in 1:iters) {
    freq.list[[j]][i] = sum(unique(temp.lengths)[j] == s.lengths[[i]])
  }
}

# lapply(freq.list, mean)

## sample(probs)
freq.list2 = list()
for (j in 1:length(unique(temp.lengths))) {
  freq.list2[[j]] = rep(NA, iters)
  for (i in 1:iters) {
    freq.list2[[j]][i] = sum(unique(temp.lengths)[j] == s.lengths2[[i]])
  }
}

# lapply(freq.list2, mean)

temp.freqDT = tidytable::count(temp.lengthsDT, length)[,setnames(.SD, "n", "true_frequency")] %>%
  mutate(true_prob = true_frequency/sum(true_frequency), sample_frequency = unlist(lapply(freq.list, mean)), sample_prob = unlist(lapply(freq.list2, mean)))
# tidytable::summarise(temp.lengthsDT, frequency = tidytable::n(), .by = length) # does the same thing as above but above is cleaner

## rmultinom(prob)
m.lengths = rmultinom(iters, temp.lengthsDT[,.N], prob = temp.freqDT$true_prob) # random multinomial based on the frequency of length l observed

temp.freqDT %>%
  mutate(rmultinom_prob = rowMeans(m.lengths)) %>%
  round(digits = 2) -> temp.freqDT

temp.freqDT
# great success! this shows that sample() is the same as rmultinomial(), one just uses frequency and the other probabilities
# this means that we can bootstrap the YAGM by weight for a particular year (YAGM/Y), then bootstrap the hauls (if any) in that YAGM, then lengths as usual.
# If there aren't any hauls in that YAGM, what happens?
### END SIDE QUEST ####

```

This demonstrates that using sample() with the vector of observations equals sample() with the probability of unique observations and using a sampling size equal to the number of observations. These are also equivalent to using rmultinom() in the same manner as the latter sample() method.

### 2024-07-10 Rmd/weighted_vs_unweighted_proportions.Rmd
initiate package

---
title: "Weighted vs Unweighted"
author: "Brett Stacy"
date: "2024-06-28"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Compare weighted vs unweighted proportions at length EBS Pcod

Let's take a look at how weighting (expanding) changes the unweighted (nominal) proportions at length.

## Load in necessary data

This data was saved from my version of the EBS Pcod expansion.

```{r}

y2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
y7 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y7_ebs_pcod_Brett.RDS")

library(tidyverse)
library(data.table)

```

## Calculate the nominal proportions at length

```{r}

y3<- y2[,c("YEAR","GEAR","AREA2","MONTH","CRUISE",
             "HAUL_JOIN", "LENGTH", "SUM_FREQUENCY", "YAGMH_SNUM", 
             "YAGMH_SFREQ","YAGM_SFREQ", "YG_SFREQ","Y_SFREQ","YAGM_TNUM","YG_TNUM","Y_TNUM","YAGMH_SNUM",
             "YAGM_SNUM","YG_SNUM","YG_SNUM","Y_SNUM","WEIGHT1","WEIGHT2","WEIGHT3","WEIGHT4")]     # get rid of some unneeded variables

  y3$WEIGHTX<-y3$WEIGHT1

  y4<-y3[YAGM_SFREQ>30][,list(WEIGHT=sum(WEIGHTX)),by=c("LENGTH","YEAR")]  ## setting minumal sample size to 30 lengths for Year, area, gear, month strata. # sample size here means haul numbers of fish, not observer sample number. this reduced nrow by about 1000. this line also creates a new variable WEIGHT, which is the sum of WEIGHTX across length and year. i.e., the weight of each length for every year.

  y5<-y4[,list(TWEIGHT=sum(WEIGHT)),by=c("YEAR")] # TWEIGHT is I think the total weight summed across length bins for every year. sum(TWEIGHT) = 1.9. Shouldn't this sum to 1??
  y5=merge(y4,y5) # merge the individual length weights with their respective year weights.
  y5$FREQ<-y5$WEIGHT/y5$TWEIGHT # RESULT! This is the preliminary proportions at length. They sum to 1 for every year. the FREQuency, or relative weight, between length bins to the total annual weight. 
  y6<-y5[,-c("WEIGHT","TWEIGHT")] # saving a version with just FREQ

  grid<-data.table::data.table(expand.grid(YEAR=unique(y5$YEAR),LENGTH=1:max(y5$LENGTH))) # make a grid for every year, have a length bin by centemeter from 1 to max length
  y7.nom<-merge(grid,y6,all.x=TRUE,by=c("YEAR","LENGTH")) # merge the grid with y6, which is the expanded frequency of proportions for each length bin observed for each year.
y7.nom[is.na(FREQ)]$FREQ <-0                                  # RESULT! ## this is the proportion at length for an aggregated-gear fishery. # The NAs are where there were no observations for that length bin in that year so call them zero. This is what must be input into the assessment model.

```

## Isolate the expanded proportions at length

```{r}
year = 2011

y7[YEAR==year, FREQ] %>% sum()

expanded = y7[YEAR==year, ]
nominal = y7.nom[YEAR==year, ]

```

## Density Plot

Don't use
```{r}
df2 <- data.frame(supp=rep(c("VC", "OJ"), each=3),
                dose=rep(c("D0.5", "D1", "D2"),2),
                len=c(6.8, 15, 33, 4.2, 10, 29.5))

ggplot(data=df2, aes(x=dose, y=len, fill=supp)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=len), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
  theme_minimal()

# mine
df = data.frame(type = rep(c("Nom", "Exp"), each = nrow(expanded)),
                bin = rep(expanded$LENGTH, 2),
                freq = c(nominal$FREQ, expanded$FREQ))

ggplot(data=df, aes(x=bin, y=freq, fill=type)) +
  geom_bar(stat="identity", position=position_dodge())+
  # geom_text(aes(label=freq), vjust=1.6, color="white",
  #           position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
  theme_minimal()
```

Use
```{r}
ggplot(data=df, aes(x=bin, y=freq, colour=type)) + 
  geom_line() +
  geom_area(aes(fill=type, group=type), alpha = 0.5, position = "identity")

```

## Explore 2011 difference

In 2011, there is a big hump in the expanded proportions that doesn't exist in the nominal proportions. Can I identify what data is contributing to this hump? It is between 40-55 cm length bins. Perhaps there are massive hauls that collect these length bins in a disproportionate quantity to the primary length bin (60-75).

```{r}
y2.2011 = y2[YEAR==2011,]

# find the obs with really high weight4
y2.2011$WEIGHT4 %>% plot

y2.2011$WEIGHT4 %>% max -> temp

y2.2011[WEIGHT4==temp, unique(YAGM_SNUM)]

y3 = y2.2011
y3$WEIGHTX<-y3$WEIGHT1*y3$WEIGHT2*y3$WEIGHT4

y3[, WEIGHTX] %>% plot
abline(h = .00003)

y3[WEIGHTX==max(WEIGHTX),]
```

```{r}
y3[WEIGHTX>.00003,] -> y3.biggest.weightx

## Plot the large values distribution compared to the nominal
  y4<-y3.biggest.weightx[YAGM_SFREQ>30][,list(WEIGHT=sum(WEIGHTX)),by=c("LENGTH","YEAR")]  ## setting minumal sample size to 30 lengths for Year, area, gear, month strata. # sample size here means haul numbers of fish, not observer sample number. this reduced nrow by about 1000. this line also creates a new variable WEIGHT, which is the sum of WEIGHTX across length and year. i.e., the weight of each length for every year.

  y5<-y4[,list(TWEIGHT=sum(WEIGHT)),by=c("YEAR")] # TWEIGHT is I think the total weight summed across length bins for every year. sum(TWEIGHT) = 1.9. Shouldn't this sum to 1??
  y5=merge(y4,y5) # merge the individual length weights with their respective year weights.
  y5$FREQ<-y5$WEIGHT/y5$TWEIGHT # RESULT! This is the preliminary proportions at length. They sum to 1 for every year. the FREQuency, or relative weight, between length bins to the total annual weight. 
  y6<-y5[,-c("WEIGHT","TWEIGHT")] # saving a version with just FREQ

  grid<-data.table::data.table(expand.grid(YEAR=unique(y5$YEAR),LENGTH=1:141)) # make a grid for every year, have a length bin by centemeter from 1 to max length
  y7.exp.2<-merge(grid,y6,all.x=TRUE,by=c("YEAR","LENGTH")) # merge the grid with y6, which is the expanded frequency of proportions for each length bin observed for each year.
y7.exp.2[is.na(FREQ)]$FREQ <-0                                  # RESULT! ## this is the proportion at length for an aggregated-gear fishery. # The NAs are where there were no observations for that length bin in that year so call them zero. This is what must be input into the assessment model.

df2 = df
df2[df2$type=="Exp", "freq"] = y7.exp.2$FREQ

ggplot(data=df2, aes(x=bin, y=freq, colour=type)) + 
  geom_line() +
  geom_area(aes(fill=type, group=type), alpha = 0.5, position = "identity")
```

Conclusion: these look like the culprits. The high WeightX values over .00003 have a high leverage on the proportions at length where all the WeightX values exceed the nominal proportions by a large degree. This occurs at 40-55cm.

Let's explore these observations

```{r}

summary(y3$WEIGHT1)
summary(y3.biggest.weightx$WEIGHT1) # higher median - 3x

summary(y3$WEIGHT2)
summary(y3.biggest.weightx$WEIGHT2) # way higher median - 80x

summary(y3$WEIGHT4)
summary(y3.biggest.weightx$WEIGHT4) # same median

# so weight2 has the highest leverage by far.

```

## check other combinations of weights to see where the highest are.

```{r}

y3$WEIGHTX.1.2 = y3$WEIGHT1*y3$WEIGHT2
y3[, WEIGHTX.1.2] %>% plot
y3$WEIGHTX.1.4 = y3$WEIGHT1*y3$WEIGHT4
y3[, WEIGHTX.1.4] %>% plot
y3$WEIGHTX.2.4 = y3$WEIGHT2*y3$WEIGHT4
y3[, WEIGHTX.2.4] %>% plot
# highest all in the same place

# lets plot the distribution of all these compared to nominal.
# make a function:

# Plot the large values distribution compared to the nominal

# testing
y3.subset = y3
weightx.name = "WEIGHTX"
comp_2_distributions = function(y3.subset, weightx.name){
  y4.intermediate<-y3.subset[YAGM_SFREQ>30]
  y4 = y4.intermediate[,list(WEIGHT=sum(.SD)), .SDcols = weightx.name, by=c("LENGTH","YEAR")]  ## setting minumal sample size to 30 lengths for Year, area, gear, month strata. # sample size here means haul numbers of fish, not observer sample number. this reduced nrow by about 1000. this line also creates a new variable WEIGHT, which is the sum of WEIGHTX across length and year. i.e., the weight of each length for every year.

  y5<-y4[,list(TWEIGHT=sum(WEIGHT)),by=c("YEAR")] # TWEIGHT is I think the total weight summed across length bins for every year. sum(TWEIGHT) = 1.9. Shouldn't this sum to 1??
  y5=merge(y4,y5) # merge the individual length weights with their respective year weights.
  y5$FREQ<-y5$WEIGHT/y5$TWEIGHT # RESULT! This is the preliminary proportions at length. They sum to 1 for every year. the FREQuency, or relative weight, between length bins to the total annual weight. 
  y6<-y5[,-c("WEIGHT","TWEIGHT")] # saving a version with just FREQ

  grid<-data.table::data.table(expand.grid(YEAR=unique(y5$YEAR),LENGTH=1:141)) # make a grid for every year, have a length bin by centemeter from 1 to max length
  y7.exp.2<-merge(grid,y6,all.x=TRUE,by=c("YEAR","LENGTH")) # merge the grid with y6, which is the expanded frequency of proportions for each length bin observed for each year.
y7.exp.2[is.na(FREQ)]$FREQ <-0                                  # RESULT! ## this is the proportion at length for an aggregated-gear fishery. # The NAs are where there were no observations for that length bin in that year so call them zero. This is what must be input into the assessment model.

df2 = df
df2[df2$type=="Exp", "freq"] = y7.exp.2$FREQ

gp = ggplot(data=df2, aes(x=bin, y=freq, colour=type)) + 
  geom_line() +
  geom_area(aes(fill=type, group=type), alpha = 0.5, position = "identity")

return(gp)
}

comp_2_distributions(y3, "WEIGHTX.1.2")
comp_2_distributions(y3, "WEIGHTX.1.4")
comp_2_distributions(y3, "WEIGHTX.2.4")
comp_2_distributions(y3, "WEIGHT2")

comp_2_distributions(y3, "WEIGHTX")

```

Conclusion: This shows that weight2 is largely responsible for the exaggerated hump around 40-55cm. This means that there were hauls that contributed a lot to the AGM group. This could mean that there were just few hauls in that group. This may be an important part of the data to represent with another hump because it could be capturing cohort detection better than just using the nominal data. Essentially, this area, gear, month group caught more fish in this length range than the average throughout the year.

# Inspect high leverage weightx more

```{r}
y3.biggest.weightx$AREA2 %>% unique
y3.biggest.weightx$GEAR %>% unique
y3.biggest.weightx$MONTH %>% unique
y3.biggest.weightx$LENGTH %>% summary

par(mfrow = c(2,1))
plot(y3.biggest.weightx$YAGMH_SNUM, type = "l")
plot(y3.biggest.weightx$YAGM_SNUM, type = "l")

par(mfrow = c(1,1))
boxplot(y3.biggest.weightx$LENGTH)

# what's special about the biggest one? 
y3.biggest.weightx[WEIGHTX==max(WEIGHTX), .(AREA2, GEAR, MONTH, YAGMH_SNUM, YAGM_SNUM, LENGTH)]
y3.biggest.weightx[WEIGHT2>.06, .(AREA2, GEAR, MONTH, YAGMH_SNUM, YAGM_SNUM, LENGTH, SUM_FREQUENCY)]
y3[WEIGHT2>.06, .(AREA2, GEAR, MONTH, YAGMH_SNUM, YAGM_SNUM, LENGTH, SUM_FREQUENCY)]

y3[AREA2==520 & GEAR=="TRW" & MONTH==3, .(AREA2, GEAR, MONTH, YAGMH_SNUM, YAGM_SNUM, LENGTH, SUM_FREQUENCY)]

```

Conclusion: I don't really know what's special about these area, gear, month combinations.

# Plot several years with large weightx leverage in the 40-55 range

include relative weight of weights1,2,4? can add as text on the plots.

```{r}
# function for calculating final proportions by year

comp_2_distributions2 = function(y2, y7.nom, year, weightx.name){
  y3 = y2[YEAR==year,]
  y3$WEIGHTX<-y3$WEIGHT1*y3$WEIGHT2*y3$WEIGHT4 
  y4.intermediate<-y3[YAGM_SFREQ>30]
  y4 = y4.intermediate[,list(WEIGHT=sum(.SD)), .SDcols = weightx.name, by=c("LENGTH","YEAR")]  ## setting minumal sample size to 30 lengths for Year, area, gear, month strata. # sample size here means haul numbers of fish, not observer sample number. this reduced nrow by about 1000. this line also creates a new variable WEIGHT, which is the sum of WEIGHTX across length and year. i.e., the weight of each length for every year.

  y5<-y4[,list(TWEIGHT=sum(WEIGHT)),by=c("YEAR")] # TWEIGHT is I think the total weight summed across length bins for every year. sum(TWEIGHT) = 1.9. Shouldn't this sum to 1??
  y5=merge(y4,y5) # merge the individual length weights with their respective year weights.
  y5$FREQ<-y5$WEIGHT/y5$TWEIGHT # RESULT! This is the preliminary proportions at length. They sum to 1 for every year. the FREQuency, or relative weight, between length bins to the total annual weight. 
  y6<-y5[,-c("WEIGHT","TWEIGHT")] # saving a version with just FREQ

  grid<-data.table::data.table(expand.grid(YEAR=unique(y5$YEAR),LENGTH=1:141)) # make a grid for every year, have a length bin by centemeter from 1 to max length
  y7.exp.2<-merge(grid,y6,all.x=TRUE,by=c("YEAR","LENGTH")) # merge the grid with y6, which is the expanded frequency of proportions for each length bin observed for each year.
y7.exp.2[is.na(FREQ)]$FREQ <-0                                  # RESULT! ## this is the proportion at length for an aggregated-gear fishery. # The NAs are where there were no observations for that length bin in that year so call them zero. This is what must be input into the assessment model.

expanded = y7.exp.2[YEAR==year, ]
nominal = y7.nom[YEAR==year, ]

df2 = data.frame(type = rep(c("Nominal", "Expanded"), each = nrow(grid)),
                length_bin = rep(expanded$LENGTH, 2),
                frequency = c(nominal$FREQ, expanded$FREQ))

gp = ggplot(data=df2, aes(x=length_bin, y=frequency, colour=type)) + 
  geom_line() +
  geom_area(aes(fill=type, group=type), alpha = 0.5, position = "identity") +
  ggtitle(year) +
  theme(legend.position = "inside") +
  theme(legend.position.inside = c(0.8, 0.8))

return(gp)
}

comp_2_distributions2(y2, y7.nom, 2009, "WEIGHTX")

purrr::map(2008:2011, ~comp_2_distributions2(y2, y7.nom, .x, "WEIGHTX"))

```

## Problem?

are hauls with more observations getting more weight in weight2?

For weight2 calculation, the number of fish from all hauls are added up, and the numbers from each haul are divided by the total. But the problem is, each length observation category lists the haul total in YAGMH. So the more observations, the greater the contribution to the total sum.

```{r}

y2.2011.hauls = y2.2011 %>%
  tidytable::distinct(HAUL_JOIN, .keep_all = T) %>%
  data.table()

y2.2011.hauls

# well, let's calculate the weights by unique hauls and compare it to what is already done.

y2[,sum(WEIGHT2), by=YAGM_SNUM] 
y2.2011[,sum(WEIGHT2), by=YAGM_SNUM] 
y2.2011.hauls[,sum(WEIGHT2), by=YAGM_SNUM]

# something is wrong here
y2.2011[AREA2==unique(AREA2)[1] & GEAR==unique(GEAR)[1] & MONTH==unique(MONTH)[1], YAGMH_SNUM] %>% sum()

y2.2011[1, YAGM_SNUM]

# I think if I for example added another observation to a haul, it would change the weight2, which is unintentional. It shouldn't change weight2.

x = c(3,3,3,4,4)

y = c(3,4)/7
y[1]/y[2]

z = x/sum(x)

z[1]/z[4]

```

Conclusion: I don't think there is a problem. Based on the pretend data above, the ratios of the proportions between distinct values are the same whether values are repeated or not. I think this means that the YAGMH values being repeated for all distinct length measurements in a haul isn't an issue.

### 2024-07-15 Rmd/boostrap_0.1.Rmd
some progress on bootstrap routine. create basic shell for some functions

@@
 library(purrr)
+library(tictoc)
+library(furrr)
 ```
@@
 
-## Take what I learned from above and make it better
-```{r}
-
-```
+## rename the booted length list
 

### 2024-07-15 R/boot_length.R

@@ -1,0 +1,49 @@
+#' Resample length frequency data w/replacement.
+#'
+#' @param lfreq_un expanded length frequency data (one row per sample)
+#'
+#' @return dataframe of resampled length-sex pairs by year, species, and haul
+#'
+#' @export
+#'
+boot_length <- function(lfreq_un) {
+
+  # combine sex-length to common id - bootstrap based on year, species, haul then split back apart
+  lfreq_un %>%
+    tidytable::mutate(sex_ln = paste0(sex, "-", length)) %>%
+    tidytable::mutate(sex_ln = sample(sex_ln, .N, replace = TRUE), .by= c(year, species_code, hauljoin)) %>%
+    tidytable::separate(sex_ln, c('sex', 'length'), sep = '-', convert = TRUE) -> .lfreq_un
+  # add combined sex resampled data
+  .lfreq_un %>%
+    tidytable::bind_rows(.lfreq_un %>%
+                           tidytable::mutate(sex = 0))
+
+}
+
+
+
+
+# mine
+samp_func3 = function(x2, DT) {
+  data.table::setkey(DT, HAUL_JOIN)
+  purrr::map(.x = x2, .f = function(x1) comp_sample(DT[x1][["LENGTH"]] %>% rep(DT[x1][["SUM_FREQUENCY"]]), replace = T)) # with frequency (correct)
+}
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-07-15 R/boot_trip.R

@@ -1,0 +1,18 @@
+#' Resample trips w/replacement.
+#'
+#' @param length_DT length frequency input data table
+#'
+#' @return length frequency data table including only resampled trips and associated data
+#'
+#' @export
+#'
+boot_trips = function(length_DT) { # based on surveyISS::boot_haul
+  length_DT %>%
+    tidytable::tidytable() %>%
+    tidytable::select(YEAR, CRUISE) %>% # change CRUISE to "Cruise, Permit, Trip_Seq" eventually somehow
+    tidytable::distinct() %>%
+    tidytable::mutate(CRUISE = base::sample(CRUISE, .N, replace = TRUE), .by = YEAR)
+}
+
+
+

### 2024-07-15 R/expand_length_props.R

@@ -1,0 +1,63 @@
+
+
+
+
+
+# expand_length_props = function(y2) - probably call "y2" whatever Ben calls it - the length frequency data.
+# this is the function that takes length frequency data and expands it into fished population proportions at length using the weightings
+# from the relevent data. The relevent data can be the og data or bootstrapped data.
+
+
+
+
+
+# TESTING
+length_DT = og_lf_data
+expand_length_props = function(length_DT) {
+
+
+  # Expansion copied from EBS Pcod code 2023 ----
+  y2 = length_DT
+
+  y3<- y2[,c("YEAR","GEAR","AREA2","MONTH","CRUISE",
+             "HAUL_JOIN", "LENGTH", "SUM_FREQUENCY", "YAGMH_SNUM",
+             "YAGMH_SFREQ","YAGM_SFREQ", "YG_SFREQ","Y_SFREQ","YAGM_TNUM","YG_TNUM","Y_TNUM","YAGMH_SNUM",
+             "YAGM_SNUM","YG_SNUM","YG_SNUM","Y_SNUM","WEIGHT1","WEIGHT2","WEIGHT3","WEIGHT4")]     # get rid of some unneeded variables
+
+  y3$WEIGHTX<-y3$WEIGHT1*y3$WEIGHT2*y3$WEIGHT4   ## weight of individual length sample for single fishery model. # multiply individual observation weight at haul level by weight of the haul by the weight of the year/area/gear/month. So this should give the weight each observation has, scaled by the haul weight and month/gear/year/area weight
+  # y3$WEIGHTX_GEAR<-y3$WEIGHT1*y3$WEIGHT2*y3$WEIGHT3 # similar to previous but including gear weights
+
+  y4<-y3[YAGM_SFREQ>30][,list(WEIGHT=sum(WEIGHTX)),by=c("LENGTH","YEAR")]  ## setting minumal sample size to 30 lengths for Year, area, gear, month strata. # sample size here means the number of samples taken by observers in the YAGM combination. this reduced nrow by about 1000. this line also creates a new variable WEIGHT, which is the sum of WEIGHTX across length and year. i.e., the weight of each length for every year.
+  # y4.1<-y3[YAGM_SFREQ>30][,list(WEIGHT_GEAR=sum(WEIGHTX_GEAR)),by=c("LENGTH","GEAR","YEAR")]  ## setting minimal sample size to 30 lengths for Year, area, gear, month strata. to be used in the multiple gear fisheries section below.
+
+
[…]

### 2024-08-02 Rmd/compare_output_pre_and_post_adding_strata.Rmd
clean some things up - rerun with trip_strata save Steve's y2 object to use in sql_downloads add section in sql_downloads to inspect and add trip_join eventually

---
title: "Compare output pre and post adding strata"
author: "Brett Stacy"
date: "2024-07-30"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

# Data

```{r}
out1 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_output_to_email_7_23_24.RDS")

out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_1000iters_output_7_30_24.RDS")

```

# Output

## Time series of sample size

```{r}

par(mfrow = c(3,1), mar = c(2, 4.5, .5, .5))
plot(out1$iss_length$YEAR, out1$iss_length$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3)

plot(out1$iss_length$YEAR, out1$iss_length$nhls, type = "l", ylab = "number of hauls", xlab = "", col = "black", cex.lab = 1.3)

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3) 
lines(out2$iss_length$YEAR, out2$iss_length$iss, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("without sampling strata", "with sampling strata"))

m1 = lm(out2$iss_length$nss ~ out2$iss_length$iss)
# summary(m1)

m2 = lm(out2$iss_length$nhls ~ out2$iss_length$iss)
# summary(m2)

```

## Boxplots of RSS

```{r}
df = data.frame(rss = out2$rss_length$rss, year = as.factor(out2$rss_length$YEAR))
# plot(df$year, df$rss, xaxt = "n", yaxt = "n", ylab = "", xlab = "")
plot(df$year, df$rss, ylab = "rss", cex.lab = 1.3)
```

## All together

```{r, fig.height=8}
# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(4,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
plot(out1$iss_length$YEAR, out1$iss_length$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")

plot(out1$iss_length$YEAR, out1$iss_length$nhls, type = "l", ylab = "number of hauls", xlab = "", col = "black", cex.lab = 1.3, xaxt = "n")

plot(df$year, df$rss, ylab = "RSS", cex.lab = 1.3, xaxt = "n")

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3) 
lines(out2$iss_length$YEAR, out2$iss_length$iss, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("without sampling strata", "with sampling strata"))

```

```{r from my phd, eval=F}
box.plot.status.proj2 = function(proj.raw, ...){
  sta_err = list()
  for(i in 1:length(proj.raw)){
    sta_err[[i]] = SSB.err.rel.proj(output = proj.raw[[i]], final.year.ind = grep("SSB", names(proj.raw[[i]]$M.TR.))[length(grep("SSB", names(proj.raw[[i]]$M.TR.)))])
  }

  # temp.ass.names = as.character(1:length(sta_err))
  # temp.ass.names = 1:length(sta_err)
  temp.ass.names = as.character(assessment_years)
  df = data.frame(error = c(unlist(sta_err)), type = as.factor(c(sapply(temp.ass.names, function(x) rep(x, 1000)))))

  # plot(df$type, df$error, ylim = c(-0.5, .5), xaxt = "n", yaxt = "n", ylab = "", xlab = "", ...)
  plot(df$type, df$error, xaxt = "n", yaxt = "n", ylab = "", xlab = "", ...)
  abline(h = 0, lwd = 0.5, lty = 2, col = "black")

  abline(v = 13, lty = 2, lwd = 0.5)

}

par(mfrow = c(2,3), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
  for (i in c(2,4,6)) {
    box.plot.status.proj2(out.projections.raw.I$`0.6`[[i]], ylim = c(-0.35, .8))
    text(2, .75, plot.letters[i/2], cex = subplot.letter.cex)
    if(i %in% c(1,2)) axis(side = 2, las = 2)
  }
  for (i in c(2,4,6)) {
    box.plot.status.proj2(out.projections.raw.R$`0.6`[[i]], ylim = c(-0.36, .12))
    text(2, .1, plot.letters[i/2+3], cex = subplot.letter.cex)
    if(i %in% c(2,4,6)) axis(side = 1, at = c(1, 7, 13, 19), labels = c(1996, 2002, 2008, 2014))
    if(i %in% c(1,2)) axis(side = 2, las = 2)
  }
mtext(text = expression(paste("SSB"["status"], " RE")), side = 2, outer = T, line = 2, las = 0, cex = 1.2)
```

### 2024-08-02 Rmd/steve_y2_object.Rmd
clean some things up - rerun with trip_strata save Steve's y2 object to use in sql_downloads add section in sql_downloads to inspect and add trip_join eventually

---
title: "Steve y2 data"
author: "Brett Stacy"
date: "2024-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Steve y2 object

```{r}
load("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Data/From Steve B/y2_data.RData")

# save as .RDS to load into run.r script
saveRDS(y2_nosex, "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve.RDS")

lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_ebs_pcod_Brett_TRIP_STRATA.RDS")

```

### 2024-08-02 run/run_the_thing.R

@@ -1,7 +1,7 @@
-iters = 2
+iters = 1000
 # lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
 # lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett_TRIP.RDS")
-lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett_TRIP_STRATA.RDS")
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_ebs_pcod_Brett_TRIP_STRATA2.RDS")
 yrs = NULL
 boot_thl = TRUE
 expand_by_sampling_strata = TRUE
@@ -16,6 +16,6 @@ fishery_iss(iters = iters,
 tictoc::toc()
 
 
-# saveRDS(.output, file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/ISS_output_to_email_7_23_24.RDS")
+saveRDS(.output, file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/ISS_1000iters_output_8_2_24.RDS")
 
 

### 2024-08-02 run/sql_downloads.R

@@ -38,7 +38,7 @@ sql_run <- function(database, query) {
 # # well that din't work because there are a bunch of trip_join values that are just "T"
 
 
-#### Take 2, manual trip join
+#### Take 2, manual trip join ----
 # let's try to make a unique trip join identifier using Jen's suggested combination of Cruise, Permit, and trip_seq
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
 lfreq2 = readLines('C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS/sql_files/test2.sql') # test2.sql includes Cruise, Permit, and trip_seq
@@ -65,25 +65,72 @@ saveRDS(new_lfreq_data2, file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHu
 
 
 
-#### Incorporate sampling strata column
+#### Incorporate sampling strata column ----
 # for use in bootstrapping within strata
-lfreq_data_trip = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett_TRIP.RDS")
+lfreq_data_trip = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_ebs_pcod_Brett_TRIP.RDS")
 sampling_strata = readLines('C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS/sql_files/sampling_strata.sql') # includes haul_join and sampling_strata
 
 temp_sampling_strata = sql_run(akfin, sampling_strata)
 joinDT_temp = data.table::setDT(temp_sampling_strata)
 
 # join it with the input data frame for baseISS
-new_lfreq_data3 = tidytable::left_join(lfreq_data, joinDT_temp) # this looks better
+new_lfreq_data3 = tidytable::left_join(lfreq_data_trip, joinDT_temp)
 
-# save the new data table with TRIP_JOIN added
-saveRDS(new_lfreq_data3, file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett_TRIP_STRATA.RDS")
[…]

### 2024-08-05 Rmd/compare_with_and_without_expansion.Rmd
run ISS without expansion. plot comparison in rmd

---
title: "Compare with and without expansion"
author: "Brett Stacy"
date: "2024-08-05"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# What impact does expanding have on ISS?

# Data

```{r}
out1 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_1000iters_output_8_2_24.RDS")

out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_10iters_output_2024-08-05.RDS")

```

## Compare

```{r, fig.height=4}
# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out2$iss_length$iss)*1.1)) 
lines(out2$iss_length$YEAR, out2$iss_length$iss, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("with expansion", "without expansion"))

```

### 2024-08-05 run/run_ISS_0.1.0.R

@@ -1,10 +1,9 @@
-iters = 1000
-# lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
-# lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett_TRIP.RDS")
+iters = 10
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_ebs_pcod_Brett_TRIP_STRATA2.RDS")
 yrs = NULL
 boot_thl = TRUE
 expand_by_sampling_strata = TRUE
+expand_using_weighting_factors = FALSE
 
 
 tictoc::tic()
@@ -12,10 +11,11 @@ fishery_iss(iters = iters,
             lfreq_data = lfreq_data,
             yrs = yrs,
             boot_thl = boot_thl,
-            expand_by_sampling_strata = expand_by_sampling_strata) -> .output
+            expand_by_sampling_strata = expand_by_sampling_strata,
+            expand_using_weighting_factors = expand_using_weighting_factors) -> .output
 tictoc::toc()
 
 
-saveRDS(.output, file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/ISS_1000iters_output_8_2_24.RDS")
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_", iters, "iters_output_", Sys.Date(), ".RDS"))
 
 

### 2024-08-05 Rmd/compare_output_pre_and_post_adding_strata.Rmd
update input file. results are the same as previous.

@@
 
-out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_1000iters_output_7_30_24.RDS")
+# out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_1000iters_output_7_30_24.RDS")
+out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_1000iters_output_8_2_24.RDS")
 

### 2024-08-12 Rmd/compare_with_and_without_expansion.Rmd
run and plot ISS using Steve's y2 object containing all the data for single sex. Use Cruise as placeholder for Trip for foreign data for now.

@@
 
-plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out2$iss_length$iss)*1.1)) 
+plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "Sample Size", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out2$iss_length$nss)*1.1)) 
 lines(out2$iss_length$YEAR, out2$iss_length$iss, col = "blue")
-legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("with expansion", "without expansion"))
+lines(out2$iss_length$YEAR, out2$iss_length$nss, col = "orange")
+legend("topright", lty = c(1,1,1), col = c("orange", "black", "blue"), legend = c("nominal", "with expansion", "without expansion"))
 

### 2024-08-12 Rmd/plot_output_steve_y2_object.Rmd
run and plot ISS using Steve's y2 object containing all the data for single sex. Use Cruise as placeholder for Trip for foreign data for now.

---
title: "Plot ISS Using Full Data Set"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidytable)
```

# First time plotting using full data set

# Data

```{r}
out1 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_300iters_output_2024-08-08.RDS")

out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_300iters_output_2024-08-09.RDS")
```

## ISS

```{r, fig.height=4}
# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3) 
legend("topright", lty = c(1), col = c("black"), legend = c("with expansion"))

```

## Compare to nss

```{r, fig.height=4}
# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "Sample Size", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out1$iss_length$nss)*1.1)) 
lines(out1$iss_length$YEAR, out1$iss_length$nss, col = "orange")
legend("topright", lty = c(1,1), col = c("orange", "black"), legend = c("nominal", "with expansion"))

```

## Compare to ISS from before

```{r, fig.height=4}
# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out1$iss_length$iss)*1.3), col = "blue") 
lines(out2$iss_length$YEAR, out2$iss_length$iss, col = "black")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("onboard domestic only", "after including port & foreign"))

```

## Compare to ISS from 2023 assessment

```{r, fig.height=4}
assessment_2023_iss = tidytable(year = 1977:2023,
                                iss = c(27,
                                45,
                                54,
                                54,
                                63,
                                31,
                                117,
                                140,
                                211,
                                216,
                                396,
                                401,
                                185,
                                189,
                                1565,
                                1543,
                                913,
                                1435,
                                1561,
                                2020,
                                2142,
                                2046,
                                2722,
                                2960,
                                3140,
                                3446,
                                4301,
                                3608,
                                3455,
                                2694,
                                2115,
                                2502,
                                2218,
                                1975,
                                2596,
                                2776,
                                3293,
                                3604,
                                3324,
                                2821,
                                2469,
                                1899,
                                1367,
                                1048,
                                859,
                                1160,
                                706))

par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out1$iss_length$iss)*1.1), col = "blue") 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "black")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("2023 assessment", "baseISS"))

```

### 2024-08-12 R/problem with internal mutate data.table.R

@@ -1,0 +1,10 @@
+# problem with := examined
+# simple example
+
+
+
+
+
+
+
+

### 2024-08-12 run/run_ISS_0.1.0.R

@@ -1,9 +1,9 @@
-iters = 10
+iters = 300
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_ebs_pcod_Brett_TRIP_STRATA2.RDS")
 yrs = NULL
 boot_thl = TRUE
 expand_by_sampling_strata = TRUE
-expand_using_weighting_factors = FALSE
+expand_using_weighting_factors = TRUE
 
 
 tictoc::tic()

### 2024-08-19 Rmd/compare_steve_y2_results_after_seperate_boot_switch.Rmd
cleanup

---
title: "Compare ISS before and after seperate boot"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidytable)
```

# What's Changed
I split the boot conditional statement into three seperate statements and coded them such that the user can turn all on or none on or any combination of the three on.

# Data

```{r}
out1 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_300iters_output_2024-08-08.RDS")

out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/separate_boot_switches_ISS_301iters_output_2024-08-13.RDS")
```

## Compare to ISS from before

```{r, fig.height=4}
par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, 1.2*max(out1$iss_length$iss)), col = "black") 
lines(out2$iss_length$YEAR, out2$iss_length$iss, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("before split boot", "after split boot"))

```

These are a bit different. BUT, this is expected because between these changes I also fixed a mistake where strata wasn't being incorporated as intended in the saved data file from sql_downloads. So now that it is, I would expect the ISS to be a bit different.

## Plot ISS and numnber of hauls

```{r, fig.height=4, dpi=600}
par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, 1.2*max(out1$iss_length$iss)), col = "black") 
lines(out1$iss_length$YEAR, out1$iss_length$nhls, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("Fishery ISS", "Number of Hauls"))

```

### 2024-08-27 Rmd/tidytable_left_join.Rmd
add age data frame processing. prepare for baseISS next.

---
title: "Tidy Table Practice"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Practice Tidytable left_join()

```{r}
library(tidytable)
```

Simple example from the help file. 
```{r}

df1 <- data.table(x = c("a", "a", "b", "c"), y = 1:4)
df2 <- data.table(x = c("a", "b"), z = 5:6)
df1
df2

df1 %>% left_join(df2)

```

The left_join found that the column x matched between df1 and df2. It kept all the columns in df1, but added the unshared column from df2, z, for the rows where the shared column, x, matched between df1 and df2. Where there was no match, it put an NA for column z in the new data.table.

Now let's see what happens when we add an additional shared column, w.

```{r}
df1 <- data.table(x = c("a", "a", "b", "c"), w = c("a", "a", "b", "c"), y = 1:4)
df2 <- data.table(x = c("a", "b"), w = c("a", "c"), z = 5:6)
df1
df2

df1 %>% left_join(df2)
```

This tries to match the row entries for columns x and w between df1 and df2. Where they match, the corresponding z value is included. Where they do not match, it puts an NA.

Now let's see what happens when there are multiple matches in the right data frame:
```{r}
df1 <- data.table(x = c("a", "a", "b", "c"), w = c("a", "a", "b", "c"), y = 1:4)
df2 <- data.table(x = c("a", "b"), w = c("a", "c"), z = 5:6)
df1
df2

df2 %>% left_join(df1)
```

It expands rows where there are multiple matches, while keeping all original row combinations of the left data frame. Where there is no match, it puts an NA for the unshared column from the right data frame.

Now what happens if there are multiple matches but the unshared column in the right data frame has two of the same exact row entries
```{r}
df1 <- data.table(x = c("a", "a", "b", "c"), w = c("a", "a", "b", "c"), y = c(1, 1, 3, 4))
df2 <- data.table(x = c("a", "b"), w = c("a", "c"), z = 5:6)
df1
df2

df2 %>% left_join(df1)
```
It does the same thing as before. It expands the rows by the number of matches.

### 2024-08-27 run/sql_downloads.R

@@ -348,7 +348,20 @@ new_lfreq_data3.2[, n_distinct(HAUL_JOIN)]
 lfreq_data_steve_sex[, n_distinct(HAUL_JOIN)]
 
 lfreq_data_steve_sex %>%
-  tidytable::left_join(new_lfreq_data3.2) -> new_lfreq_data3.3
+  tidytable::left_join(new_lfreq_data3.2 %>%
+                         tidytable::select(YEAR, HAUL_JOIN, TRIP_JOIN, SAMPLING_STRATA, SAMPLING_STRATA_NAME, SAMPLING_STRATA_DEPLOYMENT_CATEGORY, SAMPLING_STRATA_SELECTION_RATE) %>%
+                         tidytable::distinct())  -> new_lfreq_data3.3 # OK this works now
+
+unique(new_lfreq_data3.2$TRIP_JOIN)
+unique(new_lfreq_data3.3$TRIP_JOIN) # this is bad!!! FIX THIS! SOMETHING WENT WRONG WITH LEFT_JOIN ABOVE. I FIXED IT using the above select and distinct code.
+glimpse(new_lfreq_data3.2)
+glimpse(lfreq_data_steve_sex)
+glimpse(new_lfreq_data3.3)
+# identical(lfreq_data_steve_sex,
+#           new_lfreq_data3.3 %>%
+#             tidytable::select(-c(TRIP_JOIN, SAMPLING_STRATA, SAMPLING_STRATA_NAME, SAMPLING_STRATA_DEPLOYMENT_CATEGORY, SAMPLING_STRATA_SELECTION_RATE)))
+identical(unique(new_lfreq_data3.2$TRIP_JOIN), unique(new_lfreq_data3.3$TRIP_JOIN))
+
 
 # save the new data table with sex added
 saveRDS(new_lfreq_data3.3, file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_sex_ebs_pcod_Steve_TRIP_STRATA.RDS")
@@ -363,6 +376,116 @@ saveRDS(new_lfreq_data3.3, file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Git
 
 
 
+
+
+
+
+
+
+
+
+#### Age
+
+# read in the latest data join
[…]

### 2024-09-09 Rmd/post_stratify_sex_weighting_question.Rmd
get rid of deprecated length only scripts. Work on incorporating non-fake age resampling functionality. Initiate documenting WEIGHT1 questions for age.

---
title: "Should I re-calculate WEIGHT1 when post-stratifying by sex?"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidytable)
```

# Description
Sex is the only inter-haul characteristic (in length data) that can be post-stratified by. But does this mean that WEIGHT1 needs to be recalculated when sex is filtered by to post-stratify by it? WEIGHT1 = SUM_FREQUENCY/YAGMH_SFREQ. i.e., the number of fish of a particular length divided by the total number of fish lengthed in a haul.

Load a sex-differentiated input data frame:
```{r}
lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_sex_ebs_pcod_Steve_TRIP_STRATA.RDS")

```

Determine if SUM_FREQUENCY and YAGMH_SFREQ are sex-dependent. 
```{r}
lfreq_data[HAUL_JOIN=="H101530"] %>% 
  tidytable::glimpse()

lfreq_data[HAUL_JOIN=="H101530", .(SEX, LENGTH, YAGMH_SFREQ, SUM_FREQUENCY, WEIGHT1)]

lfreq_data[HAUL_JOIN=="H101530", sum(WEIGHT1)]

lfreq_data[HAUL_JOIN=="H101530", .(SEX, LENGTH, YAGMH_SFREQ, SUM_FREQUENCY, WEIGHT1, WEIGHT2, WEIGHT4)]

```

# Conclusion
Sex can only be post-stratified by if it is included as a column in the input data frame. In the case of EBS Pcod, the WEIGHT1 column is calculated as combined-sex (see above r code). So there are two important questions:

1. When a single sex is filtered, can we use the existing WEIGHT1 values?
2. When WEIGHT1 is recalculated in fishery_props.R, is using the existing YAGMH_SFREQ value appropriate? Because it will often be larger than if we recalculated it.

### 2024-09-09 run/sql_downloads.R

@@ -384,7 +384,7 @@ saveRDS(new_lfreq_data3.3, file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Git
 
 
 
-#### Age
+#### Age V1
 
 # read in the latest data join
 new_lfreq_data3.3 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_sex_ebs_pcod_Steve_TRIP_STRATA.RDS")
@@ -491,6 +491,64 @@ new_afreq_data1.0 %>%
 
 # save the new age data table
 saveRDS(new_afreq_data1.0, file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_age_sex_ebs_pcod_Steve_TRIP_STRATA_V1.RDS")
+# Note: this data frame only includes age data from haul_joins for which length data was used in the expansion.
+
+
+
+
+
+
+
+
+
+
+
+#### Age V2
+# add columns: SUM_FREQUENCY, WEIGHT1, YAGMH_SFREQ, YAGM_SFREQ, YAG_SFREQ, YG_SFREQ, Y_SFREQ,
+
+# read in the latest data join
+new_afreq_data1.0 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_age_sex_ebs_pcod_Steve_TRIP_STRATA_V1.RDS")
+new_afreq_data1.1 = new_afreq_data1.0
+
+new_afreq_data1.1[YEAR==2022,]
+
+new_afreq_data1.1[YEAR==2022, ] %>%
+  tidytable::count(HAUL_JOIN) %>%
+  print(n=400)
+
+new_afreq_data1.1[YEAR==2022 & HAUL_JOIN=="H25648004533000000049"] %>%
+  tidytable::glimpse()
+new_afreq_data1.1[YEAR==2022 & HAUL_JOIN=="H25648004533000000049", .(HAUL_JOIN, AGE, LENGTH)] %>%
+  tidytable::glimpse() # 3 ages in this haul, two are the same but the associated lengths are different.
+
+
+# Goal: Calculate WEIGHT1 ignoring length for now:
[…]

### 2024-09-09 README.Rmd
update documentation

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# baseISS

<!-- badges: start -->
<!-- badges: end -->

The goal of baseISS is to develop a preliminary method for calculating input sample size (ISS) for fishery-dependent composition data. This data includes length- and age-frequency data collected by the NORPAC observer program and excludes fishery-independent data from surveys. Fishery-dependent composition data represents an important element of the 26 statistical catch at age stock assessment models for Alaskan fisheries managed by the NOAA AFSC. The ISS determines the precision attached to this data type, and therefore regulates its leverage in assessment model outputs such as biomass predictions.

The structure and functionality of this package resembles surveyISS with some notable differences that accomodate the neuances of fishery-dependent data. These are covered in the next section, "Important Notes".

## Important Notes

### Input Data
The following conditions of an input data frame for any species must be met:
1. (length data) There exists a WEIGHT1 column that represents the haul-level proportions-at-length of the observed lengths. This is calculated by dividing the frequency of the observed length within a haul by the total number of fish lengthed in that haul. It should be a standard calculation that is exactly the same for every species.

### Current Functionality

### Developing Functionality

## Installation

You can install the development version of baseISS from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Brett-Stacy/baseISS")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(baseISS)
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

### 2024-09-10 README.Rmd
continue documentation

@@
 It should be a standard calculation that is exactly the same for every species.
+This convention...
+
+2. Length data be condensed with sum_frequency column.
+
+3. Age data include associated lengths.
+
+4. Age data flattened, no "sum_frequency" column.
 
 ### Current Functionality
+
+1.
+Length ISS must be a separate analysis to age ISS.
+Unlike surveyISS, this is necessary for several reasons: a.
+there will be many more hauls with lengths than ages, b.
+it is likely that the user options such as post_stratify will be different between length data and age data, c.
+NOTE ANOTHER ONE WHEN YOU REMEMBER.
 

### 2024-09-17 README.Rmd
investigate sample size for adding change_N functionality. Initiate test run script for adding functionality.

@@
 
-The structure and functionality of this package resembles surveyISS with some notable differences that accomodate the neuances of fishery-dependent data.
+The structure and functionality of this package resembles surveyISS with some notable differences that accommodate the nuances of fishery-dependent data.
 These are covered in the next section, "Important Notes".
@@
 It should be a standard calculation that is exactly the same for every species.
-This convention...
 
@@
 4. Age data flattened, no "sum_frequency" column.
+
+5.
+For EBS Pcod, age data has only been used when there exists alredy pre-processed length data associated with it.
+I.e., I matched the y2 length data object recieved from Steve with age data I downloaded when testing the baseISS functionality on age data.
+This was necessary becasue I needed quantities like YAGM_SNUM to perform the weighted expansion.
 
@@
 
+2.
+You can't chose the species from a big data set containing all the species.
+This is because data sets for each species should include unique columns necessary to apply their unique expansion methods.
+For EBS Pcod for example, these columns are only available after much pre-processing and calculating of the raw data.
+
 ### Developing Functionality
+
+- subsampling
 

### 2024-09-17 Rmd/does_subsampling_WOR_matter.Rmd
investigate sample size for adding change_N functionality. Initiate test run script for adding functionality.

---
title: "Does it matter if we subsample WR or WOR?"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidytable)
```

# Introduction
I can't wrap my head around the justification to subsample an existing sample WOR. Does it even matter which one we do? Do a simulation to test it empirically.

More considerations:
  - if we were taking a LARGER sample, say 125%, we would sample WR right? Test this too!
  - the principle is: whatever sample we take, we want it to be representative by proportion of the original sample.

# Special Note to remember
If the optimal sample size depends on the expansion method (or post-stratification for that matter) for one species, then I think the optimal sample size will have to be species specific. Because lots of species have different expansion methods, that arguably should remain different.

## WR vs WOR subsample lower
Make up some data. Sample the same size WR. Then do two things: 1. Subsample WR, 2. subsample WOR. Do these things many times, then summarize them and compare.

```{r}

x = c(rep(1, 70), rep(0, 30))

y1 = matrix(NA, nrow = 50, ncol = 100)
y2 = matrix(NA, nrow = 50, ncol = 100)
for(i in 1:100){
  temp = sample(x, 100, replace = TRUE)
  y1[,i] = sample(temp, 50, replace = FALSE)
  y2[,i] = sample(temp, 50, replace = TRUE)
}

colMeans(y1) %>% mean()
colMeans(y2) %>% mean()

```
  I'm getting the same result either WR or WOR.

## WR vs WOR subsample higher
same as above but subsample higher

```{r, eval=F}

x = c(rep(1, 70), rep(0, 30))

y1 = matrix(NA, nrow = 150, ncol = 100)
y2 = matrix(NA, nrow = 150, ncol = 100)
for(i in 1:100){
  temp = sample(x, 100, replace = TRUE)
  y1[,i] = sample(temp, 150, replace = FALSE)
  y2[,i] = sample(temp, 150, replace = TRUE)
}

colMeans(y1) %>% mean()
colMeans(y2) %>% mean()

```
This doesn't work! Because you can't take a sample from a population larger than the population WOR. This makes sense because once you have already chosen each element of a population and not replaced it, you will run out of elements to chose from once you reach the total number in the population.

# Conclusion
Just use WR in baseISS.

BUT, now the question is, do I subsample the samples or run the whole thing again with the different N? I think running the whole thing again is better because we further randomize the hauls chosen by re-randomize the trips and hauls. But perhaps it does not matter because on average, both sets of resampled trips/hauls should be equally representative at high enough iterations.

SO, figure out how to subsample after the fact like Ben and Pete do. Start with length.
option = years, proportion/value, type, grp? SHould I code in post-strata-specific subsampling?

### 2024-09-17 Rmd/haul_sample_size_investigation.Rmd
investigate sample size for adding change_N functionality. Initiate test run script for adding functionality.

---
title: "Inspect YAGMH_SFREQ"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidytable)
library(ggplot2)
```

```{r}
lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_sex_ebs_pcod_Steve_TRIP_STRATA.RDS")

```

# Introduction
We want to see how ISS changes when sample size is reduced or increased. The target sample size per haul has been 20 fish lengthed for some time now. Is that too many? Is that too few? Can baseISS be used as a framework to optimize sample size? Additionally, do adjustments to target sample size impact ISS differently when expansion method changes? I.e., is a change to sample size robust to expansion method applied? -Or- At what sample size does the expansion method not matter? Are we going to test this just for one or a couple years? Or for the whole time series?

## Inspect the distribution of a recent length composition data set
```{r}
lfreq_data[YEAR==2022, ] %>% 
  tidytable::distinct(HAUL_JOIN, .keep_all = TRUE) %>% 
  tidytable::select(YAGMH_SFREQ) -> temp

hist(temp$YAGMH_SFREQ)
summary(temp$YAGMH_SFREQ)

```
Looks pretty normal

## Average sample size 
```{r}
lfreq_data %>% 
  tidytable::distinct(HAUL_JOIN, .keep_all = TRUE) %>% 
  tidytable::summarize(avg_sample_N = mean(YAGMH_SFREQ), .by = YEAR) -> temp

plot(temp$YEAR, temp$avg_sample_N, type = "l")

plot(temp$YEAR[23:47], temp$avg_sample_N[23:47], type = "l")

```
Sample size varies quite a bit until 1999 when it levels out to about 20.

## Are they normal?
Are the ~20 sample size years normally distributed?

plot the boxplots over time

```{r}
lfreq_data %>% 
  tidytable::distinct(HAUL_JOIN, .keep_all = TRUE) -> temp
df = data.frame(sampl_N = temp$YAGMH_SFREQ, year = as.factor(temp$YEAR))
plot(df$year, df$sampl_N, ylab = "Haul Sample N", cex.lab = 1.3)

lfreq_data[YEAR %in% 1999:2023,] %>% 
  tidytable::distinct(HAUL_JOIN, .keep_all = TRUE) -> temp
df = data.frame(sampl_N = temp$YAGMH_SFREQ, year = as.factor(temp$YEAR))
plot(df$year, df$sampl_N, ylab = "Haul Sample N", cex.lab = 1.3)
plot(df$year, df$sampl_N, ylab = "Haul Sample N", cex.lab = 1.3, ylim = c(0, 100))
plot(df$year, df$sampl_N, ylab = "Haul Sample N", cex.lab = 1.3, ylim = c(18, 22))

temp %>% 
  tidytable::mutate(YEAR = factor(YEAR)) %>% 
  ggplot(aes(y=YAGMH_SFREQ, x=YEAR)) + 
  geom_violin() +
  ylim(18, 23)

# recent years wisker plot
temp %>% 
  tidytable::mutate(YEAR = factor(YEAR)) %>% 
  tidytable::mutate(sd_YAGMH_SFREQ = sd(YAGMH_SFREQ), .by = YEAR) %>% 
  tidytable::summarise(mean_YAGMH_SFREQ = mean(YAGMH_SFREQ), sd_YAGMH_SFREQ = unique(sd_YAGMH_SFREQ), .by = YEAR) %>% 
  ggplot(aes(x = YEAR, y = mean_YAGMH_SFREQ)) +
  geom_line(aes(group = 1)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = mean_YAGMH_SFREQ - sd_YAGMH_SFREQ, ymax = mean_YAGMH_SFREQ + sd_YAGMH_SFREQ), width = .2) +
  labs(y = "Haul Sample N (mean +- sd)", x = "Year")

# all years wisker plot mean
lfreq_data %>% 
  tidytable::distinct(HAUL_JOIN, .keep_all = TRUE) -> temp
temp %>% 
  tidytable::mutate(YEAR = factor(YEAR)) %>% 
  tidytable::mutate(sd_YAGMH_SFREQ = sd(YAGMH_SFREQ), .by = YEAR) %>% 
  tidytable::summarise(mean_YAGMH_SFREQ = mean(YAGMH_SFREQ), sd_YAGMH_SFREQ = unique(sd_YAGMH_SFREQ), .by = YEAR) %>% 
  ggplot(aes(x = YEAR, y = mean_YAGMH_SFREQ)) +
  geom_line(aes(group = 1)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = mean_YAGMH_SFREQ - sd_YAGMH_SFREQ, ymax = mean_YAGMH_SFREQ + sd_YAGMH_SFREQ), width = .2) +
  labs(y = "Haul Sample N (mean +- sd)", x = "Year")

# all years wisker plot mean + median
lfreq_data %>% 
  tidytable::distinct(HAUL_JOIN, .keep_all = TRUE) -> temp
temp %>% 
  tidytable::mutate(sd_YAGMH_SFREQ = sd(YAGMH_SFREQ), .by = YEAR) %>% 
  tidytable::summarise(mean_YAGMH_SFREQ = mean(YAGMH_SFREQ), sd_YAGMH_SFREQ = unique(sd_YAGMH_SFREQ), median_YAGMH_SFREQ = median(YAGMH_SFREQ), .by = YEAR) %>% 
  ggplot() +
  geom_line(aes(x = YEAR, y = mean_YAGMH_SFREQ), color = "blue") +
  geom_point(aes(x = YEAR, y = mean_YAGMH_SFREQ), size = 4) +
  geom_errorbar(aes(x = YEAR, y = mean_YAGMH_SFREQ, ymin = mean_YAGMH_SFREQ - sd_YAGMH_SFREQ, ymax = mean_YAGMH_SFREQ + sd_YAGMH_SFREQ), width = .2) +
  labs(y = "Haul Sample N (mean +- sd)", x = "Year") +
  geom_line(aes(x = YEAR, y = median_YAGMH_SFREQ), color = "red")

# recent years wisker plot mean + median
lfreq_data[YEAR %in% 1999:2023,] %>% 
  tidytable::distinct(HAUL_JOIN, .keep_all = TRUE) -> temp
temp %>% 
  tidytable::mutate(sd_YAGMH_SFREQ = sd(YAGMH_SFREQ), .by = YEAR) %>% 
  tidytable::summarise(mean_YAGMH_SFREQ = mean(YAGMH_SFREQ), sd_YAGMH_SFREQ = unique(sd_YAGMH_SFREQ), median_YAGMH_SFREQ = median(YAGMH_SFREQ), .by = YEAR) %>% 
  ggplot() +
  geom_line(aes(x = YEAR, y = mean_YAGMH_SFREQ), color = "blue") +
  geom_point(aes(x = YEAR, y = mean_YAGMH_SFREQ), size = 4) +
  geom_errorbar(aes(x = YEAR, y = mean_YAGMH_SFREQ, ymin = mean_YAGMH_SFREQ - sd_YAGMH_SFREQ, ymax = mean_YAGMH_SFREQ + sd_YAGMH_SFREQ), width = .2) +
  labs(y = "Haul Sample N (mean +- sd)", x = "Year") +
  geom_line(aes(x = YEAR, y = median_YAGMH_SFREQ), color = "red")

```

### 2024-09-17 Rmd/does_subsampling_WOR_matter.Rmd
change length N: establish option naming convention.

@@
 But perhaps it does not matter because on average, both sets of resampled trips/hauls should be equally representative at high enough iterations.
+in SWO, they subsample right after boot_length for every iteration.
+This means they take the same resampled hauls to subsample.
+I'm not sure why they do this instead of resample the hauls again.
+Is it just for speed optimization?
 
-SO, figure out how to subsample after the fact like Ben and Pete do. Start with length.
-option = years, proportion/value, type, grp? SHould I code in post-strata-specific subsampling?
+For now, I'm going to code it into the existing boot_length function and necessitate running the whole thing over again if we want to resample.
+One potential advantage of doing it this way is that, since the sampling rate varies wildly prior to 1999, the years for which subsampling is applied will probably not be the full data year span.
+Therefore, the existing yrs option in fishery_iss can be used to control years to apply subsamples to.
+I can consider doing it the other way in the future.
+Start with length.
+start with a fixed value, 10, just for 1999 and up I guess.
+Note that this cannot be applied when post_strata = "SEX" because the 20 fish target is sex-independent.
+
+Min/max problem: In SWO, the min(.N, samples) is taken.
+This is done instead of max() because they only considered reducing the sampling effort.
+I need to decide what to do with baseISS because I want to investigate greater-than sampling rates.
+Perhaps have a conditional statement that conditions on > or < the median YAGMH_SFREQ for the yrs spanned.
+
+option = years, proportion/value, type, grp? SHould I code in post-strata-specific subsampling? min/max stuff?

### 2024-09-17 R/fishery_iss.R

@@ -18,7 +18,7 @@
 #' @param boot.length Boolean. Resample lengths w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length
 #' @param boot.age Boolean. Resample ages w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-age
 #' @param expand.by.sampling.strata expand by observer sampling strata? If TRUE, then an additional weighting factor is calculated and applied to WEIGHT1 based on the number of fish caught in each sampling stratum.
-#' @param expand_using_weighting_factors expand using weighting factors? If TRUE, then then "WEIGHT2" and "WEIGHT4" are applied.
+#' @param expand_using_weighting_factors expand using weighting factors? If TRUE, then then "WEIGHT2" and "WEIGHT4" are applied. Consider improving/generalizing this by calling it expansion_weighting_factors = list(type = c("weight", "number"), factors = c("haul", "area", "month", "gear", etc.) to give the user the option of what aspects (columns) of the data to expand by and do it by weight of fish or number of fish in those categories.
 #'
 #' @return Dataframe of input sample size by year
 #'

### 2024-09-17 run/run_ISS_0.5.0.R

@@ -1,4 +1,5 @@
-# Change sample size option - option to reduce or increase the haul-level sample size
+# Change sample size option - option to reduce or increase the haul-level sample size. Length to start. Integrate the option into the boot_length function.
+# try 10 samples. only years 1999+. Do WR. Do conditional min or max based on median YAGMH_SFREQ over yrs.
 run_name = "haul_sample_size_change_V1"
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_sex_ebs_pcod_Steve_TRIP_STRATA.RDS")
@@ -9,11 +10,12 @@ library(baseISS)
 species_code = "202"
 area_code = "EBS"
 length_based = TRUE # TRUE for length
-iters = 10
+iters = 2
 freq_data = lfreq_data
-yrs = NULL
+yrs = 1999
 post_strata = NULL
-minimum_sample_size = NULL
+minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30) # throw minimum sample size back in because we are back to testing with length
+new_length_N = list(type = "fixed", amount = 10) # naming convention to allow type = "proportion" in the future.
 boot.trip = T
 boot.haul = T
 boot.length = T

### 2024-09-18 Rmd/does_subsampling_WOR_matter.Rmd
Implement new sample size functionality. test sample size=10 haul level, length, 1999-2023. Works.

@@
 Is it just for speed optimization?
+Is there a more substantial reason?
 
 For now, I'm going to code it into the existing boot_length function and necessitate running the whole thing over again if we want to resample.
-One potential advantage of doing it this way is that, since the sampling rate varies wildly prior to 1999, the years for which subsampling is applied will probably not be the full data year span.
+One potential advantage of doing it this way is that, since the sampling rate varies wildly prior to 1999, the years for which subsampling is desired to be applied will probably not be the full data year span.
 Therefore, the existing yrs option in fishery_iss can be used to control years to apply subsamples to.
@@
 I need to decide what to do with baseISS because I want to investigate greater-than sampling rates.
-Perhaps have a conditional statement that conditions on > or < the median YAGMH_SFREQ for the yrs spanned.
+I think this should be the lesser-than number in either case relative to the mean of the median YAGMH_SFREQ for the yrs spanned.
+Code it this way for now but continue to think about it.
 

### 2024-09-18 Rmd/haul_sample_size_investigation.Rmd
Implement new sample size functionality. test sample size=10 haul level, length, 1999-2023. Works.

@@
 ```
+
+## Check out YAGMH_SFREQ 1999-2023 in more detail
+
+```{r}
+lfreq_data[YEAR%in%c(1999:2023),] %>% tidytable::distinct(HAUL_JOIN, .keep_all = T) %>% tidytable::select(YAGMH_SFREQ)->temp
+
+hist(temp$YAGMH_SFREQ)
+summary(temp$YAGMH_SFREQ) # 540 is max!!!
+
+((temp$YAGMH_SFREQ>20) %>% sum)/nrow(temp)
+((temp$YAGMH_SFREQ>25) %>% sum)/nrow(temp) # about 2% over 20
+
+plot(temp$YAGMH_SFREQ[temp$YAGMH_SFREQ>25])
+plot(temp$YAGMH_SFREQ[temp$YAGMH_SFREQ>25], ylim = c(20, 100))
+
+```

### 2024-09-18 R/fishery_iss.R

@@ -12,7 +12,8 @@
 #' @param freq_data length or age frequency input data frame
 #' @param yrs any year filter >= (default = NULL)
 #' @param post_strata list(strata = character string, nested = Boolean) if NULL, then no post stratification. The first element of post_strata is a character string with name(s) of post strata type. Accepted types are "GEAR", etc. These must be column name(s) in the data frame where each row has an entry and there are no NAs. The second element in post_strata allows for nested post-strata (e.g., "GEAR", "SEX") that are in order of the desired nested hierarchy, then the final results will be a nested list in order of the listed post-strata as well. Perhaps there should be an error message for attempts with strata names that are not in freq_data or it does exist, but there are NAs in it.
-#' @param minimum_sample_size list(resolution = character string, size = integer) if NULL, then no minimum sample size. The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
+#' @param minimum_sample_size list(resolution = character string, size = integer). If NULL, then no minimum sample size. If not NULL, The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
+#' @param new_length_N list(type = character, amount = numeric). If NULL, then the number of length samples resampled in a haul equals the number actually sampled. If not NULL, then the haul-level number of samples is changed by type (acceptable entries are "fixed", or "proportion") at an amount (acceptable entries are an integer number or proportion). The amount can be less than or greater than the true N. Note that if it is either less than or greater than, the minimum of the two is chosen for N (this is still under consideration and may change in the future). The true N is taken to be... DOES THIS ONLY MATTER IF WE NEED A THRESHOLD TO DECIDE WHEN TO TAKE THE MAX?? The samples are still drawn with replacement. Warning: cannot do this if post_strata = "SEX"
 #' @param boot.trip Boolean. Resample trips w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length or -age
[…]

### 2024-09-18 R/fishery_props.R

@@ -66,7 +66,7 @@ fishery_props <- function(length_based,
   # randomize lengths if boot.length == true ----
   if(base::isTRUE(boot.length)) {
     .freq %>%
-      boot_length() -> .freq
+      boot_length(new_length_N = new_length_N) -> .freq
   }
 
   # randomize ages if boot.age == true ----

### 2024-09-18 run/run_ISS_0.5.0.R

@@ -1,5 +1,5 @@
 # Change sample size option - option to reduce or increase the haul-level sample size. Length to start. Integrate the option into the boot_length function.
-# try 10 samples. only years 1999+. Do WR. Do conditional min or max based on median YAGMH_SFREQ over yrs.
+# try 10 samples. only years 1999+. Do WR. Do not do conditional min or max based on median YAGMH_SFREQ over yrs, just do min for now, assuming this is what will apply when greater than median sample size will be tested.
 run_name = "haul_sample_size_change_V1"
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_sex_ebs_pcod_Steve_TRIP_STRATA.RDS")
@@ -32,6 +32,8 @@ fishery_iss(species_code = species_code,
             freq_data = freq_data,
             yrs = yrs,
             post_strata = post_strata,
+            minimum_sample_size = minimum_sample_size,
+            new_length_N = new_length_N,
             boot.trip = boot.trip,
             boot.haul = boot.haul,
             boot.length = boot.length,

### 2024-09-20 Rmd/Inspect_Outputs/change_sample_size_1.0.Rmd
run 100 iters of N=10, .N, 30 length per haul. Tested - works. Plot in Rmd shows results.

---
title: "Inspect Different Length Sample Size impact on ISS 1.0"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidytable)
library(ggplot2)
```

# Data Generated With:
C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS/run/run_ISS_0.5.1.R

```{r}

# speed: this took 1000 seconds
out.10 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2_N_samples_10_ISS_100iters_output_2024-09-19.RDS")

# speed: this took 1000 seconds
out.N = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2_N_samples_.N_ISS_100iters_output_2024-09-19.RDS")

# speed: this took 1300 seconds
out.30 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2_N_samples_30_ISS_100iters_output_2024-09-19.RDS")

```

# Introduction
Plot the ISS resulting from three levels of haul-level sample size:
1. min(.N, 10)
2. .N
3. min(.N, 30)

ancillary details:
- sample WR
- years 1999-2023 (median = 20 fish per haul)
- fixed values, not proportions

## Compare

Plot
```{r}

plot(out.10$length$iss$YEAR, out.10$length$iss$iss, type = "l", ylab = "ISS", xlab = "Year", col = "blue", ylim = c(0, 11000))
lines(out.N$length$iss$YEAR, out.N$length$iss$iss, col = "black")
lines(out.30$length$iss$YEAR, out.30$length$iss$iss, col = "red")
legend("topright", legend = c(".N", "min(.N, 10)", "min(.N, 30)"), col = c("black", "blue", "red"), lty = c(1,1,1))

```

Stats
```{r}
(out.10$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% 
  plot(type = "l")

(out.10$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% mean
```

# Conclusion
.N and 30 were equivalent. 10 was an average of 46% of .N, so about half. Implying uncertainty decreases proportional to sample size.

Try a more advanced option for changing length N where a separate sample function is called as a condition in boot_length.

### 2024-09-20 run/run_ISS_0.5.0.R

@@ -10,7 +10,7 @@ library(baseISS)
 species_code = "202"
 area_code = "EBS"
 length_based = TRUE # TRUE for length
-iters = 2
+iters = 10
 freq_data = lfreq_data
 yrs = 1999
 post_strata = NULL

### 2024-09-20 run/run_ISS_0.5.1.R

@@ -1,0 +1,170 @@
+# Change sample size option - test with N=10, NULL, 30 and plot
+# also measure time difference and compare.
+run_name = "haul_sample_size_change_V2"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_sex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+########### 10 samples
+samples = 10
+
+species_code = "202"
+area_code = "EBS"
+length_based = TRUE # TRUE for length
+iters = 100
+freq_data = lfreq_data
+yrs = 1999
+post_strata = NULL
+minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30) # throw minimum sample size back in because we are back to testing with length
+new_length_N = list(type = "fixed", amount = samples) # naming convention to allow type = "proportion" in the future.
+boot.trip = T
+boot.haul = T
+boot.length = T
+boot.age = F
+expand.by.sampling.strata = TRUE
+expand_using_weighting_factors = TRUE
+
+
+tictoc::tic()
+fishery_iss(species_code = species_code,
+            area_code = area_code,
+            length_based = length_based,
+            iters = iters,
+            freq_data = freq_data,
+            yrs = yrs,
+            post_strata = post_strata,
+            minimum_sample_size = minimum_sample_size,
+            new_length_N = new_length_N,
+            boot.trip = boot.trip,
+            boot.haul = boot.haul,
+            boot.length = boot.length,
+            boot.age = boot.age,
+            expand.by.sampling.strata = expand.by.sampling.strata,
+            expand_using_weighting_factors = expand_using_weighting_factors) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/", run_name, "_N_samples_", samples, "_ISS_", iters, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+########### NULL samples
+samples = ".N"
+
+species_code = "202"
+area_code = "EBS"
+length_based = TRUE # TRUE for length
+iters = 100
+freq_data = lfreq_data
+yrs = 1999
+post_strata = NULL
[…]

### 2024-09-20 Rmd/Inspect_Outputs/change_sample_size_1.0.Rmd
document mistake: I coded the subsampling routine incorrectly. all 0.5._ scripts are invalid. see those scripts for details. Forward: code subsampling after boot_length instead of inside it.

@@
 ---
+
+IGNORE THIS SCRIPT!!
+THE RESULTS ARE INVALID!
+I DID NOT CODE THE SUBSAMPLING CORRECTLY, I DID NOT USE SIZE ARGUEMENT IN SAMPLE.INT LIKE I SHOULD HAVE.
+WHEN I TRIED TO USE IT, BOOT_LENGTH WOULD NOT WORK BECAUSE MUTATE CANNOT ACCEPT UNEQUAL LENGTH VECTORS TO WHAT IT IS ASKED TO REPLACE.
 
@@
 Try a more advanced option for changing length N where a separate sample function is called as a condition in boot_length.
+
+UPDATE: THIS OUTPUT IS INNACURATE! I DID NOT CODE THE SAMPLING ROUTINE CORRECTLY: IT DOES NOT SUBSAMPLE, RATHER IT TAKES .N IN BOTH CASES WHEN I INTENDED OTHERWISE.

### 2024-09-20 R/boot_length.R

@@ -20,7 +20,7 @@ boot_length = function(length_DT,
 }
 # for testing
 # length_DT = .freq
-
+tidytable::mutate(length_DT, LENGTH = generic_sample_change_length_N(LENGTH, new_length_N), .by = c(YEAR, HAUL_JOIN))
 
 
 

### 2024-09-20 R/generic_sample.R

@@ -10,7 +10,7 @@
 #'
 #' @export
 #'
-generic_sample = function(flex.vec, n.samples) flex.vec[base::sample.int(length(flex.vec), n = n.samples, replace = TRUE)]
+generic_sample = function(flex.vec, n.samples) flex.vec[base::sample.int(length(flex.vec), size = n.samples, replace = TRUE)]
 
 
 

### 2024-09-20 run/run_ISS_0.5.0.R

@@ -1,5 +1,9 @@
 # Change sample size option - option to reduce or increase the haul-level sample size. Length to start. Integrate the option into the boot_length function.
 # try 10 samples. only years 1999+. Do WR. Do not do conditional min or max based on median YAGMH_SFREQ over yrs, just do min for now, assuming this is what will apply when greater than median sample size will be tested.
+
+
+### IGNORE THIS SCRIPT!! THE RESULTS ARE INVALID! I DID NOT CODE THE SUBSAMPLING CORRECTLY, I DID NOT USE SIZE ARGUEMENT IN SAMPLE.INT LIKE I SHOULD HAVE. WHEN I TRIED TO USE IT, BOOT_LENGTH WOULD NOT WORK BECAUSE MUTATE CANNOT ACCEPT UNEQUAL LENGTH VECTORS TO WHAT IT IS ASKED TO REPLACE.
+
 run_name = "haul_sample_size_change_V1"
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_sex_ebs_pcod_Steve_TRIP_STRATA.RDS")

### 2024-09-20 run/run_ISS_0.5.1.R

@@ -1,5 +1,8 @@
 # Change sample size option - test with N=10, NULL, 30 and plot
 # also measure time difference and compare.
+
+### IGNORE THIS SCRIPT!! THE RESULTS ARE INVALID! I DID NOT CODE THE SUBSAMPLING CORRECTLY, I DID NOT USE SIZE ARGUEMENT IN SAMPLE.INT LIKE I SHOULD HAVE. WHEN I TRIED TO USE IT, BOOT_LENGTH WOULD NOT WORK BECAUSE MUTATE CANNOT ACCEPT UNEQUAL LENGTH VECTORS TO WHAT IT IS ASKED TO REPLACE.
+
 run_name = "haul_sample_size_change_V2"
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_sex_ebs_pcod_Steve_TRIP_STRATA.RDS")

### 2024-09-20 run/run_ISS_0.5.2.R

@@ -1,4 +1,7 @@
 # Change sample size option - building off 0.5.0. Change to seperate function in boot_length when changing length N.
+
+# UPDATE: THIS WILL NOT WORK. SKIP THIS VERSION. SAMPLING DIFFERENT THAN .N CANNOT BE MUTATED IN BOOT_LENGTH. THIS MEANS THE PREVIOUS 0.5._ ITERATIONS ARE INVALID AS WELL.
+
 run_name = "haul_sample_size_change_V3"
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_sex_ebs_pcod_Steve_TRIP_STRATA.RDS")

### 2024-09-23 Rmd/Inspect_Outputs/change_sample_size_2.0.Rmd
change syntax of change length N sample.int to address min() not activating problem. tested - works as expected.

---
title: "Inspect Different Length Sample Size impact on ISS 2.0"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidytable)
library(ggplot2)
```

# Data Generated With:
C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS/run/run_ISS_0.6.1.R

```{r}

# speed: this took ~1000 seconds
out.10 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.2_N_samples_10_ISS_100iters_output_2024-09-23.RDS")

# speed: this took ~1000 seconds
out.N = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.2_N_samples_.N_ISS_100iters_output_2024-09-23.RDS")

# speed: this took ~1000 seconds
out.30 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.2_N_samples_30_ISS_100iters_output_2024-09-23.RDS")

```

# Introduction
Plot the ISS resulting from three levels of haul-level sample size:
1. min(.N, 10)
2. .N
3. min(.N, 30)

ancillary details:
- sample WR
- years 1999-2023 (median = 20 fish per haul)
- fixed values, not proportions

## Compare

Plot
```{r}

plot(out.10$length$iss$YEAR, out.10$length$iss$iss, type = "l", ylab = "ISS", xlab = "Year", col = "blue", ylim = c(0, 11000))
lines(out.N$length$iss$YEAR, out.N$length$iss$iss, col = "black")
lines(out.30$length$iss$YEAR, out.30$length$iss$iss, col = "red")
legend("topright", legend = c(".N", "min(.N, 10)", "min(.N, 30)"), col = c("black", "blue", "red"), lty = c(1,1,1))

```

Stats
```{r}
# 10
(out.10$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% 
  plot(type = "l")
(out.10$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% mean

# 30
(out.30$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% 
  plot(type = "l")
(out.30$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% mean

```

# Conclusion
These results look expected.

### 2024-09-23 R/generic_sample_change_length_N.R

@@ -14,7 +14,7 @@ generic_sample_change_length_N = function(flex.vec,
                                           new_length_N = NULL)
   {
   # 0.5.0 case
-  flex.vec[base::sample.int(length(flex.vec), size = min(.N, new_length_N$amount), replace = TRUE)]
+  flex.vec[base::sample.int(length(flex.vec), size = min(length(flex.vec), new_length_N$amount), replace = TRUE)]
 
 }
 

### 2024-09-23 R/reboot_length_N.R

@@ -20,7 +20,7 @@ reboot_length_N = function(length_DT,
 
   .length_DT %>%
     tidytable::summarise(LENGTH = generic_sample_change_length_N(flex.vec = LENGTH,
-                                                      new_length_N = new_length_N), .by = c(YEAR, HAUL_JOIN)) %>%
+                                                                 new_length_N = new_length_N), .by = c(YEAR, HAUL_JOIN)) %>%
     tidytable::summarise(SUM_FREQUENCY = n(base::unique(LENGTH)), .by = c(YEAR, HAUL_JOIN, LENGTH)) %>%
     tidytable::mutate(YAGMH_SFREQ = base::sum(SUM_FREQUENCY), .by = c(YEAR, HAUL_JOIN)) %>%
     tidytable::left_join(.length_DT %>%

### 2024-09-23 run/run_ISS_0.6.1.R

@@ -1,0 +1,173 @@
+# Change sample size option - test with N=10, NULL, 30 and plot
+# also measure time difference and compare.
+
+### IGNORE THIS SCRIPT!! THE RESULTS ARE INVALID! I DID NOT CODE THE SUBSAMPLING CORRECTLY, I DID NOT USE SIZE ARGUEMENT IN SAMPLE.INT LIKE I SHOULD HAVE. WHEN I TRIED TO USE IT, BOOT_LENGTH WOULD NOT WORK BECAUSE MUTATE CANNOT ACCEPT UNEQUAL LENGTH VECTORS TO WHAT IT IS ASKED TO REPLACE.
+
+run_name = "haul_sample_size_change_V2.2"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+########### 10 samples
+samples = 10
+
+species_code = "202"
+area_code = "EBS"
+length_based = TRUE # TRUE for length
+iters = 100
+freq_data = lfreq_data
+yrs = 1999
+post_strata = NULL
+minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30) # throw minimum sample size back in because we are back to testing with length
+new_length_N = list(type = "fixed", amount = samples) # naming convention to allow type = "proportion" in the future.
+boot.trip = T
+boot.haul = T
+boot.length = T
+boot.age = F
+expand.by.sampling.strata = TRUE
+expand_using_weighting_factors = TRUE
+
+
+tictoc::tic()
+fishery_iss(species_code = species_code,
+            area_code = area_code,
+            length_based = length_based,
+            iters = iters,
+            freq_data = freq_data,
+            yrs = yrs,
+            post_strata = post_strata,
+            minimum_sample_size = minimum_sample_size,
+            new_length_N = new_length_N,
+            boot.trip = boot.trip,
+            boot.haul = boot.haul,
+            boot.length = boot.length,
+            boot.age = boot.age,
+            expand.by.sampling.strata = expand.by.sampling.strata,
+            expand_using_weighting_factors = expand_using_weighting_factors) -> .output
+tictoc::toc()
+.output
+
+
[…]

### 2024-09-24 Rmd/Inspect_Outputs/change_sample_size_2.1.Rmd
run with 100 iters; N=10,.N,30.

---
title: "Inspect Different Length Sample Size impact on ISS 2.1"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidytable)
library(ggplot2)
```

# Data Generated With:
C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS/run/run_ISS_0.6.1.R

```{r}

# speed: this took ~1000 seconds
out.10 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_10_ISS_100iters_output_2024-09-23.RDS")

# speed: this took ~1000 seconds
out.N = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_.N_ISS_100iters_output_2024-09-23.RDS")

# speed: this took ~1000 seconds
out.30 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_30_ISS_100iters_output_2024-09-23.RDS")

```

# Introduction
Plot the ISS resulting from three levels of haul-level sample size:
1. 10
2. length(flex.vec)
3. 30

ancillary details:
- sample WR
- years 1999-2023 (median = 20 fish per haul)
- fixed values, not proportions

## Compare

Plot
```{r}

plot(out.10$length$iss$YEAR, out.10$length$iss$iss, type = "l", ylab = "ISS", xlab = "Year", col = "blue", ylim = c(0, 11000))
lines(out.N$length$iss$YEAR, out.N$length$iss$iss, col = "black")
lines(out.30$length$iss$YEAR, out.30$length$iss$iss, col = "red")
legend("topright", legend = c(".N", "10", "30"), col = c("black", "blue", "red"), lty = c(1,1,1))

```

Stats
```{r}
# 10
(out.10$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% 
  plot(type = "l")
(out.10$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% mean

# 30
(out.30$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% 
  plot(type = "l")
(out.30$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% mean

```

# Conclusion
similar to last run.

### 2024-09-24 Rmd/Inspect_Outputs/change_sample_size_2.2.Rmd
inspect N=20. results as expected.

--- 2024-09-24 Rmd/Inspect_Outputs/change_sample_size_2.1.Rmd
@@
 ---
-title: "Inspect Different Length Sample Size impact on ISS 2.1"
+title: "Inspect Different Length Sample Size impact on ISS 2.2"
 author: "Brett Stacy"
@@
 
-# speed: this took ~1000 seconds
 out.10 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_10_ISS_100iters_output_2024-09-23.RDS")
 
-# speed: this took ~1000 seconds
 out.N = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_.N_ISS_100iters_output_2024-09-23.RDS")
 
-# speed: this took ~1000 seconds
+out.20 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.5_N_samples_20_ISS_100iters_output_2024-09-24.RDS")
+
 out.30 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_30_ISS_100iters_output_2024-09-23.RDS")
@@
 1. 10
-2. length(flex.vec)
+2. 20
 3. 30
@@
 # 30
+(out.20$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% 
+  plot(type = "l")
+(out.20$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% mean
+
+# 30
 (out.30$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% 
@@
 # Conclusion
-similar to last run.
+looks reasonable.

### 2024-09-24 run/run_ISS_0.6.4.R

@@ -1,0 +1,76 @@
+# Change sample size option - same as previous version but only fixed 20
+
+
+run_name = "haul_sample_size_change_V2.5"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+########### 20 samples
+samples = 20
+
+species_code = "202"
+area_code = "EBS"
+length_based = TRUE # TRUE for length
+iters = 100
+freq_data = lfreq_data
+yrs = 1999
+post_strata = NULL
+minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30) # throw minimum sample size back in because we are back to testing with length
+new_length_N = list(type = "value", bound = NULL, amount = samples)
+boot.trip = T
+boot.haul = T
+boot.length = T
+boot.age = F
+expand.by.sampling.strata = TRUE
+expand_using_weighting_factors = TRUE
+
+
+tictoc::tic()
+fishery_iss(species_code = species_code,
+            area_code = area_code,
+            length_based = length_based,
+            iters = iters,
+            freq_data = freq_data,
+            yrs = yrs,
+            post_strata = post_strata,
+            minimum_sample_size = minimum_sample_size,
+            new_length_N = new_length_N,
+            boot.trip = boot.trip,
+            boot.haul = boot.haul,
+            boot.length = boot.length,
+            boot.age = boot.age,
+            expand.by.sampling.strata = expand.by.sampling.strata,
+            expand_using_weighting_factors = expand_using_weighting_factors) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/", run_name, "_N_samples_", samples, "_ISS_", iters, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-09-25 Rmd/Inspect_Outputs/inspect_normality_1.0.Rmd
attempt to show mean of multinomial samples approaches normal distribution. Failed - did not understand fully - give up.

---
title: "Inspect Normality of Simulations"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidytable)
library(ggplot2)
library(ggpubr)
```

# Data Generated With:
C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS/run/run_ISS_0.7.0.R

```{r}

out = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ouput_all_sims_V1_ISS_1000iters_output_2024-09-24.RDS")

```

# Introduction
I ran 1000 iterations, saving the simulated output, in order to inspect the normality of the simulated proportions at length. This has the potential to verify/justify the normal variance approximation assumption.

## 2022, length 60

Plot
```{r}

out$length$sim_props[YEAR==2022 & LENGTH==60,]$sim_FREQ %>% 
  hist()
out$length$sim_props[YEAR==2022 & LENGTH==60,]$sim_FREQ %>% 
  shapiro.test()
out$length$sim_props[YEAR==2022 & LENGTH==60,]$sim_FREQ %>% 
  shapiro.test() -> temp
temp$p.value
```

## 2022, length ALL

I DON'T THINK THE BELOW IS CORRECT. BASED ON THE KAHN ACADEMY VIDEO OF THE CLT I SHOULD BE TAKING THE MEAN OF EVERY SAMPLE OF THE DISTRIBUTION THEN TESTING THE NORMALITY OF ALL THOSE MEANS.

```{r}

out$length$sim_props[YEAR==2022, ] %>% 
  tidytable::filter(sim_FREQ %>% 
                      unique() %>% 
                      length() != 1, .by = LENGTH) %>% 
  tidytable::summarise(p.val = shapiro.test(sim_FREQ)$p.value, .by = LENGTH) %>% 
  tidytable::filter(p.val > 0.05)

```

## 2022, length ALL, take 2

take the mean of the distributions and test them for normality. I'm still not sure if this is correct because I'm taking the mean of the probabilities, not the lengths. But the probabilities are what we are applying the assumption of normality to to justify the variance approximation right?

```{r}

out$length$sim_props[YEAR==2022, ] %>% 
  tidytable::filter(sim_FREQ > 0) %>% 
  tidytable::summarise(mean.sim_FREQ = mean(sim_FREQ), .by = sim) %>% 
  tidytable::summarise(p.val = shapiro.test(mean.sim_FREQ)$p.value)

out$length$sim_props[YEAR==2022, ] %>% 
  tidytable::filter(sim_FREQ > 0) %>% 
  tidytable::summarise(mean.sim_FREQ = mean(sim_FREQ), .by = sim) %>% 
  tidytable::select(mean.sim_FREQ) %>% 
  unlist() -> temp

  hist(temp)

```

# Conclusion
not normally distributed. I don't think dealing with proportions is appropriate. See below simulation.

# simulated experiment

make up some multinomial data and see if it is approximately normal.

```{r}

# mean from samples
n.samples = 10

x = rmultinom(1000, n.samples, prob = c(.1, 0, .5, .3, 0, .1))
tf = function(x) sum(x*1:6)/n.samples
apply(x, 2, tf) -> temp1
temp1 %>% shapiro.test()

# mean from proportions
tf2 = function(x) mean(x/sum(x))
apply(x, 2, tf2) -> temp2
# temp2 %>% shapiro.test()

# plots
hist(temp1)
# hist(temp2)
ggqqplot(temp1)

```

## with normal distribution

```{r}
# mean from samples
iterations = 10
n.samples = 100

x = matrix(NA, nrow = n.samples, ncol = iterations)
for (i in 1:iterations) {
  x[,i] = rnorm(n.samples, 6, 2)
}
apply(x, 2, mean) -> temp1
temp1 %>% shapiro.test()

# plots
# library(ggpubr)
ggqqplot(temp1)
```

# Conclusion again
give up on this. I don't fully understand what is theoretically meant to be normally distributed. Is the sampling distribution of the sample mean meant to be normally distributed? Wouldn't that mean that I have to calculate the mean for each length (np) then check if all those for all lengths and iterations are normally distributed? I don't know. Or perhaps I have to do the above for the variance?

### 2024-10-10 Rmd/Inspect_Outputs/3x3_grid_sample_size_expansion_1.0.Rmd
add runs and rmd inspections and clean up

---
title: "Inspect 3x3 V1"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, results = "hide", fig.width = 8.5, fig.height = 5, dpi = 600)
library(tidytable)
library(data.table)
library(reshape2)
library(ggplot2)
library(knitr)
opts_knit$set(eval.after = "fig.cap")
```

# Introduction
3x3 grid: sample size 10, 20, 30 fixed X expansion none, haul only, haul+month.

## Data 
```{r}
out = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/3x3_grid_V1_ISS_200_iters_2024-10-09.RDS")

out2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/3x3_grid_V2_ISS_200_iters_2024-10-10.RDS")

year = out$samples_10$expansion_NULL$length$iss$YEAR

samples_global = c(10, 20, 30)
expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))

```

## Plot ISS
```{r}

df = tidytable(year = year,
                N10_Enull = out$samples_10$expansion_NULL$length$iss$iss,
                N10_Eh = out$samples_10$expansion_haul_numbers$length$iss$iss,
                N10_Ehm = out$samples_10$expansion_haul_month_numbers$length$iss$iss,
                N20_Enull = out$samples_20$expansion_NULL$length$iss$iss,
                N20_Eh = out$samples_20$expansion_haul_numbers$length$iss$iss,
                N20_Ehm = out$samples_20$expansion_haul_month_numbers$length$iss$iss,
                N30_Enull = out$samples_30$expansion_NULL$length$iss$iss,
                N30_Eh = out$samples_30$expansion_haul_numbers$length$iss$iss,
                N30_Ehm = out$samples_30$expansion_haul_month_numbers$length$iss$iss)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  labs(x = "Year", y = "ISS") +
  geom_point()

```

## Plot ISS V2
```{r}

df = tidytable(year = year,
               N10_Enull = out$samples_10$expansion_NULL$length$iss$iss,
               N20_Enull = out$samples_20$expansion_NULL$length$iss$iss,
               N30_Enull = out$samples_30$expansion_NULL$length$iss$iss,
               N10_Eh = out$samples_10$expansion_haul_numbers$length$iss$iss,
               N20_Eh = out$samples_20$expansion_haul_numbers$length$iss$iss,
               N30_Eh = out$samples_30$expansion_haul_numbers$length$iss$iss,
               N10_Ehm = out$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N20_Ehm = out$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N30_Ehm = out$samples_30$expansion_haul_month_numbers$length$iss$iss,)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  labs(x = "Year", y = "ISS") +
  geom_point()

```

### 2024-10-10 R/fishery_iss.R

@@ -82,7 +82,15 @@ fishery_iss <- function(species_code,
                               length_based = length_based,
                               iters = iters,
                               freq_data = freq_data,
-                              post_strata = post_strata)
+                              post_strata = post_strata,
+                              minimum_sample_size = minimum_sample_size,
+                              new_length_N = new_length_N,
+                              boot.trip = boot.trip,
+                              boot.haul = boot.haul,
+                              boot.length = boot.length,
+                              boot.age = boot.age,
+                              expand.by.sampling.strata = expand.by.sampling.strata,
+                              expansion_factors = expansion_factors)
 
   }else { # do not post-stratify
 

### 2024-10-10 run/run_ISS_0.10.0.R

@@ -1,0 +1,103 @@
+# 3x3 Grid. 10, 20, 30 length samples per haul X none, haul_only, haul_YAGM weighting factors.
+
+rm(list = ls())
+run_name = "3x3_grid_V1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+# species_code = "202"
+# area_code = "EBS"
+# length_based = TRUE # TRUE for length
+# iters = 2
+# freq_data = lfreq_data
+# yrs = 1999
+# post_strata = list(strata = "GEAR", nested = FALSE)
+# minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30) # throw minimum sample size back in because we are back to testing with length
+# new_length_N = list(type = "value", bound = NULL, amount = 20)
+# boot.trip = T
+# boot.haul = T
+# boot.length = T
+# boot.age = F
+# expand.by.sampling.strata = TRUE
+# expansion_factors = c("haul_numbers", "month_numbers")
+
+### Global
+iters_global = 200
+samples_global = c(10, 20, 30)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# ## 10, none
+# samples = 10
+# expansion = "NULL"
+#
+# tictoc::tic()
+# fishery_iss(species_code = "202",
+#             area_code = "EBS",
+#             length_based = TRUE,
+#             iters = iters_global,
+#             freq_data = lfreq_data,
+#             yrs = 1999,
+#             post_strata = NULL,
+#             minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+#             new_length_N = list(type = "value", bound = NULL, amount = samples),
+#             boot.trip = TRUE,
+#             boot.haul = TRUE,
+#             boot.length = TRUE,
+#             boot.age = FALSE,
+#             expand.by.sampling.strata = TRUE,
+#             expansion_factors = NULL) -> .output
+# tictoc::toc()
+# .output
+#
+#
[…]

### 2024-10-10 run/run_ISS_0.9.0.R

@@ -1,4 +1,4 @@
-# Fix mistake. fix all instances where I mistakenly relied on global environment definition of function arguements.
+# Fix mistake. fix all instances where I mistakenly relied on global environment definition of function arguements. tested - works.
 
 rm(list = ls())
 run_name = "fix_mistake_arguement_definitions_V1"

### 2024-10-15 Rmd/Inspect_Outputs/3x3_grid_sample_size_expansion_1.0.Rmd
implement max_length functionality to define the maximum length bin desired in the output. tested - works.

@@
 # Introduction
-3x3 grid: sample size 10, 20, 30 fixed X expansion none, haul only, haul+month.
+3x3 grid: sample size 10, 20, 30 fixed X expansion none, haul only, haul+month. For both with and without expand by sampling strata.
 
@@
 ## Plot ISS
-```{r}
+```{r, eval=F}
 
@@
 df = tidytable(year = year,
-               N10_Enull = out$samples_10$expansion_NULL$length$iss$iss,
-               N20_Enull = out$samples_20$expansion_NULL$length$iss$iss,
-               N30_Enull = out$samples_30$expansion_NULL$length$iss$iss,
-               N10_Eh = out$samples_10$expansion_haul_numbers$length$iss$iss,
-               N20_Eh = out$samples_20$expansion_haul_numbers$length$iss$iss,
-               N30_Eh = out$samples_30$expansion_haul_numbers$length$iss$iss,
-               N10_Ehm = out$samples_10$expansion_haul_month_numbers$length$iss$iss,
-               N20_Ehm = out$samples_20$expansion_haul_month_numbers$length$iss$iss,
-               N30_Ehm = out$samples_30$expansion_haul_month_numbers$length$iss$iss,)
+               N10_Enone = out$samples_10$expansion_NULL$length$iss$iss,
+               N20_Enone = out$samples_20$expansion_NULL$length$iss$iss,
+               N30_Enone = out$samples_30$expansion_NULL$length$iss$iss,
+               N10_Emedium = out$samples_10$expansion_haul_numbers$length$iss$iss,
+               N20_Emedium = out$samples_20$expansion_haul_numbers$length$iss$iss,
+               N30_Emedium = out$samples_30$expansion_haul_numbers$length$iss$iss,
+               N10_Efull = out$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N20_Efull = out$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N30_Efull = out$samples_30$expansion_haul_month_numbers$length$iss$iss,)
 
@@
 ```
+
+## Plot ISS V2.2
+```{r}
+
+df = tidytable(year = year,
+               N10_Enull = out2$samples_10$expansion_NULL$length$iss$iss,
+               N20_Enull = out2$samples_20$expansion_NULL$length$iss$iss,
+               N30_Enull = out2$samples_30$expansion_NULL$length$iss$iss,
+               N10_Eh = out2$samples_10$expansion_haul_numbers$length$iss$iss,
+               N20_Eh = out2$samples_20$expansion_haul_numbers$length$iss$iss,
+               N30_Eh = out2$samples_30$expansion_haul_numbers$length$iss$iss,
+               N10_Ehm = out2$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N20_Ehm = out2$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N30_Ehm = out2$samples_30$expansion_haul_month_numbers$length$iss$iss,)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+  geom_line() +
+  labs(x = "Year", y = "ISS") +
+  geom_point()
+
+```

### 2024-10-15 R/administrate_iss.R

@@ -7,6 +7,7 @@
 #' @param freq_data length or age frequency input data frame
 #' @param minimum_sample_size list(resolution = character string, size = integer). If NULL, then no minimum sample size. If not NULL, The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
 #' @param new_length_N list(type = character ("value", or "proportion"), bound = NULL or character ("minimum", or "maximum") amount = numeric). If NULL, then the number of length samples resampled in a haul equals the number actually sampled. If not NULL, then the haul-level number of samples is changed by type (acceptable entries are "fixed", or "proportion") at an amount (acceptable entries are an integer number or proportion). The amount can be less than or greater than the true N. Note that if it is either less than or greater than, the minimum of the two is chosen for N (this is still under consideration and may change in the future). The true N is taken to be... DOES THIS ONLY MATTER IF WE NEED A THRESHOLD TO DECIDE WHEN TO TAKE THE MAX?? The samples are still drawn with replacement. Warning: cannot do this if post_strata = "SEX"
+#' @param max_length integer or "data_derived" (default). Provides the maximum length bin to record proportions-at-length. Integer values must be equal to or greater than the maximum length observed in the data (this will be changed once a plus-group option is coded in the future). "data_derived" forces the maximum length to be calculated from the data.
 #' @param boot.trip Boolean. Resample trips w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length or -age
 #' @param boot.haul Boolean. Resample hauls w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length or -age
 #' @param boot.length Boolean. Resample lengths w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length
@@ -25,6 +26,7 @@ administrate_iss = function(species_code,
                             freq_data,
                             minimum_sample_size = NULL,
                             new_length_N = NULL,
+                            max_length,
                             boot.trip = FALSE,
                             boot.haul = FALSE,
                             boot.length = TRUE,
@@ -40,6 +42,7 @@ administrate_iss = function(species_code,
                            freq_data = freq_data,
                            minimum_sample_size = minimum_sample_size,
[…]

### 2024-10-15 R/expand_props.R

@@ -8,6 +8,7 @@
 #' @param length_based Boolean. If TRUE, then calculate length iss. if FALSE, then calculate age iss.
 #' @param freq_data length or age frequency input data frame
 #' @param minimum_sample_size list(resolution = character string, size = integer). If NULL, then no minimum sample size. If not NULL, The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
+#' @param max_length integer or "data_derived" (default). Provides the maximum length bin to record proportions-at-length. Integer values must be equal to or greater than the maximum length observed in the data (this will be changed once a plus-group option is coded in the future). "data_derived" forces the maximum length to be calculated from the data.
 #' @param boot.length Boolean. Resample lengths w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length. In this function, this activates a switch to calculate SUM_FREQUENCY for og_props.
 #' @param expand.by.sampling.strata MAKE THIS GENERIC IN FUTURE. expand by observer sampling strata? If TRUE, then an additional weighting factor is calculated and applied to WEIGHT1 based on the number of fish caught in each sampling stratum.
 #' @param expansion_factors expansion weighting factors to apply to the proportions. If NULL, then no expansion factors are applied. Otherwise, the conditional options coded in expand_props.R are "haul_numbers" or "haul_numbers" and "month_numbers". Consider improving/generalizing this by calling it expansion_weighting_factors = list(type = c("weight", "number"), factors = c("haul", "area", "month", "gear", etc.) to give the user the option of what aspects (columns) of the data to expand by and do it by weight of fish or number of fish in those categories.
@@ -19,6 +20,7 @@ expand_props = function(species_code,
                         length_based = TRUE,
                         freq_data,
                         minimum_sample_size = NULL,
+                        max_length,
                         boot.length = FALSE,
                         expand.by.sampling.strata = FALSE,
                         expansion_factors)
@@ -89,7 +91,13 @@ expand_props = function(species_code,
[…]

### 2024-10-15 R/fishery_iss.R

@@ -14,6 +14,7 @@
 #' @param post_strata list(strata = character string, nested = Boolean) if NULL, then no post stratification. The first element of post_strata is a character string with name(s) of post strata type. Accepted types are "GEAR", etc. These must be column name(s) in the data frame where each row has an entry and there are no NAs. The second element in post_strata allows for nested post-strata (e.g., "GEAR", "SEX") that are in order of the desired nested hierarchy, then the final results will be a nested list in order of the listed post-strata as well. Perhaps there should be an error message for attempts with strata names that are not in freq_data or it does exist, but there are NAs in it.
 #' @param minimum_sample_size list(resolution = character string, size = integer). If NULL, then no minimum sample size. If not NULL, The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
 #' @param new_length_N list(type = character ("value", or "proportion"), bound = NULL or character ("minimum", or "maximum") amount = numeric). If NULL, then the number of length samples resampled in a haul equals the number actually sampled. If not NULL, then the haul-level number of samples is changed by type (acceptable entries are "fixed", or "proportion") at an amount (acceptable entries are an integer number or proportion). The amount can be less than or greater than the true N. Note that if it is either less than or greater than, the minimum of the two is chosen for N (this is still under consideration and may change in the future). The true N is taken to be... DOES THIS ONLY MATTER IF WE NEED A THRESHOLD TO DECIDE WHEN TO TAKE THE MAX?? The samples are still drawn with replacement. Warning: cannot do this if post_strata = "SEX"
+#' @param max_length integer or "data_derived" (default). Provides the maximum length bin to record proportions-at-length. Integer values must be equal to or greater than the maximum length observed in the data (this will be changed once a plus-group option is coded in the future). "data_derived" forces the maximum length to be calculated from the data.
 #' @param boot.trip Boolean. Resample trips w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length or -age
 #' @param boot.haul Boolean. Resample hauls w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length or -age
[…]

### 2024-10-15 R/fishery_props.R

@@ -9,6 +9,7 @@
 #' @param freq_data length or age frequency input data frame
 #' @param minimum_sample_size list(resolution = character string, size = integer). If NULL, then no minimum sample size. If not NULL, The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
 #' @param new_length_N list(type = character ("value", or "proportion"), bound = NULL or character ("minimum", or "maximum") amount = numeric). If NULL, then the number of length samples resampled in a haul equals the number actually sampled. If not NULL, then the haul-level number of samples is changed by type (acceptable entries are "fixed", or "proportion") at an amount (acceptable entries are an integer number or proportion). The amount can be less than or greater than the true N. Note that if it is either less than or greater than, the minimum of the two is chosen for N (this is still under consideration and may change in the future). The true N is taken to be... DOES THIS ONLY MATTER IF WE NEED A THRESHOLD TO DECIDE WHEN TO TAKE THE MAX?? The samples are still drawn with replacement. Warning: cannot do this if post_strata = "SEX"
+#' @param max_length integer or "data_derived" (default). Provides the maximum length bin to record proportions-at-length. Integer values must be equal to or greater than the maximum length observed in the data (this will be changed once a plus-group option is coded in the future). "data_derived" forces the maximum length to be calculated from the data.
 #' @param boot.trip Boolean. Resample trips w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length or -age
 #' @param boot.haul Boolean. Resample hauls w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length or -age
 #' @param boot.length Boolean. Resample lengths w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length
@@ -25,7 +26,8 @@ fishery_props <- function(species_code,
                           length_based = TRUE,
                           freq_data,
                           minimum_sample_size = NULL,
-                          new_length_N = new_length_N,
+                          new_length_N,
+                          max_length,
                           boot.trip = FALSE,
                           boot.haul = FALSE,
                           boot.length = FALSE,
@@ -113,6 +115,7 @@ fishery_props <- function(species_code,
                       length_based = length_based,
                       freq_data = .freq,
[…]

### 2024-10-15 R/post_stratify.R

@@ -11,6 +11,7 @@
 #' @param post_strata list(strata = character string, nested = Boolean) if NULL, then no post stratification. The first element of post_strata is a character string with name(s) of post strata type. Accepted types are "GEAR", etc. These must be column name(s) in the data frame where each row has an entry and there are no NAs. The second element in post_strata allows for nested post-strata (e.g., "GEAR", "SEX") that are in order of the desired nested hierarchy, then the final results will be a nested list in order of the listed post-strata as well. Perhaps there should be an error message for attempts with strata names that are not in freq_data or it does exist, but there are NAs in it.
 #' @param minimum_sample_size list(resolution = character string, size = integer). If NULL, then no minimum sample size. If not NULL, The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
 #' @param new_length_N list(type = character ("value", or "proportion"), bound = NULL or character ("minimum", or "maximum") amount = numeric). If NULL, then the number of length samples resampled in a haul equals the number actually sampled. If not NULL, then the haul-level number of samples is changed by type (acceptable entries are "fixed", or "proportion") at an amount (acceptable entries are an integer number or proportion). The amount can be less than or greater than the true N. Note that if it is either less than or greater than, the minimum of the two is chosen for N (this is still under consideration and may change in the future). The true N is taken to be... DOES THIS ONLY MATTER IF WE NEED A THRESHOLD TO DECIDE WHEN TO TAKE THE MAX?? The samples are still drawn with replacement. Warning: cannot do this if post_strata = "SEX"
+#' @param max_length integer or "data_derived" (default). Provides the maximum length bin to record proportions-at-length. Integer values must be equal to or greater than the maximum length observed in the data (this will be changed once a plus-group option is coded in the future). "data_derived" forces the maximum length to be calculated from the data.
 #' @param boot.trip Boolean. Resample trips w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length or -age
 #' @param boot.haul Boolean. Resample hauls w/replacement? (default = FALSE). FALSE to all three boots will return og proportions-at-length or -age
[…]

### 2024-12-10 Rmd/paper_plots/paper_plots_1.1.Rmd
paper runs and plots first commit

---
title: "Paper Plots V1"
author: "Brett Stacy"
date: "2024-11-25"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, results = "hide", fig.width = 8.5, fig.height = 5, dpi = 600)
library(tidytable)
library(data.table)
library(reshape2)
library(ggplot2)
library(knitr)
opts_knit$set(eval.after = "fig.cap")
options(scipen = 5)
```

# Introduction
Plots for paper:

1. Time series of new ISS vs old. Accompanied by number of hauls, nominal sample size, and possibly RSS boxplots. RSS boxplots may help justify focusing in on 20 sample size meidan for later plots to get an apples to apples, granular test of impact of sample size and expansion complexity.

2. ISS full, ISS without expansion, ISS without sampling strata, ISS without either.

3. 3x3 grid: sample size 10, 20, 30 fixed X expansion none, haul only, haul+month. With sampling strata.

3.supp.1: same as above but without sampling strata. 
3.supp.2: same as above but without bootstrapping trip. 
3.supp.3: same as above but without either.

## Plot 1.1
```{r}
out_1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.1_ISS_100iters_output_2024-11-25.RDS")

out_2.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.1_ISS_100iters_output_2024-11-25.RDS")

out_3.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_3.1_ISS_100iters_output_2024-11-26.RDS")

out_4.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_4.1_ISS_100iters_output_2024-11-26.RDS")

out_5.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_5.1_ISS_100iters_output_2024-11-26.RDS")

out_6.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_6.1_ISS_100iters_output_2024-11-26.RDS")
out_7.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_7.1_ISS_100iters_output_2024-11-26.RDS")
out_8.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_8.1_ISS_100iters_output_2024-11-26.RDS")
out_9.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_9.1_ISS_100iters_output_2024-12-04.RDS")
out_10.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_10.1_ISS_100iters_output_2024-12-04.RDS")
out_11.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_11.1_ISS_100iters_output_2024-12-04.RDS")

assessment_2023_iss = tidytable(year = 1977:2023,
                                iss = c(27,
                                45,
                                54,
                                54,
                                63,
                                31,
                                117,
                                140,
                                211,
                                216,
                                396,
                                401,
                                185,
                                189,
                                1565,
                                1543,
                                913,
                                1435,
                                1561,
                                2020,
                                2142,
                                2046,
                                2722,
                                2960,
                                3140,
                                3446,
                                4301,
                                3608,
                                3455,
                                2694,
                                2115,
                                2502,
                                2218,
                                1975,
                                2596,
                                2776,
                                3293,
                                3604,
                                3324,
                                2821,
                                2469,
                                1899,
                                1367,
                                1048,
                                859,
                                1160,
                                706))
```

### baseISS with assessment ISS

```{r}
par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out_1.1$length$iss$iss)*1.1), col = "blue") 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "black")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("2023 assessment", "baseISS"))

```

### All together 4 panel

```{r, fig.height=8}
df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(4,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n") 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("2023 assessment", "baseISS"))

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, type = "l", ylab = "number of hauls", xlab = "", col = "black", cex.lab = 1.3, xaxt = "n")

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")

plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3, xlab = "year")

```

### All together 3 panel

```{r, fig.height=8}
df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000)) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("2023 assessment", "baseISS", "number of hauls"))

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")

plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3, xlab = "year")

```

#### Inspect R-squared
Fit models to number of hauls.

```{r}
# baseISS ~ # hauls
fit1 = lm(out_1.1$length$iss$iss ~ out_1.1$length$iss$nhls)
summary(fit1)

# assessment ISS ~ # hauls
fit2 = lm(assessment_2023_iss$iss ~ out_1.1$length$iss$nhls)
summary(fit2)

# baseISS ~ assessment ISS
fit3 = lm(out_1.1$length$iss$iss ~ assessment_2023_iss$iss)
summary(fit3)

```

## Plot 2.1 
Deconstruct the contributors to baseISS

### All together 1

Subtracting things from baseISS

```{r, fig.height=8}

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(5,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "baseISS", xaxt = "n") 
plot(out_2.1$length$iss$YEAR, out_2.1$length$iss$iss, type = "l", ylab = "baseISS - E", xaxt = "n") 
plot(out_3.1$length$iss$YEAR, out_3.1$length$iss$iss, type = "l", ylab = "baseISS - SS", xaxt = "n") 
plot(out_4.1$length$iss$YEAR, out_4.1$length$iss$iss, type = "l", ylab = "baseISS - (E,SS)", xaxt = "n") 
plot(out_5.1$length$iss$YEAR, out_5.1$length$iss$iss, type = "l", ylab = "baseISS - (E,SS,Bs)", cex.lab = 1.3, xlab = "year") 
```

### All together 2

Adding things to baseISS

```{r, fig.height=6}
par(mfrow = c(1,1))

plot(out_5.1$length$iss$YEAR, out_5.1$length$iss$iss, type = "l", ylab = "ISS", cex.lab = 1.3, col = "black")
lines(out_6.1$length$iss$YEAR, out_6.1$length$iss$iss, type = "l", col = "blue") 
lines(out_7.1$length$iss$YEAR, out_7.1$length$iss$iss, type = "l", col = "orange") 
lines(out_8.1$length$iss$YEAR, out_8.1$length$iss$iss, type = "l", col = "green") 
lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", col = "red")

legend("topleft", legend = c("-E,SS,Bs", "-SS,Bs", "-Bs", "-SS", "-0"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
```

#### sub range 1
```{r, fig.height=6}
sub_range = out_5.1$length$iss$YEAR %in% 1999:2023

par(mfrow = c(1,1))
plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000))
lines(out_6.1$length$iss$YEAR[sub_range], out_6.1$length$iss$iss[sub_range], type = "l", col = "blue") 
lines(out_7.1$length$iss$YEAR[sub_range], out_7.1$length$iss$iss[sub_range], type = "l", col = "orange") 
lines(out_8.1$length$iss$YEAR[sub_range], out_8.1$length$iss$iss[sub_range], type = "l", col = "green") 
lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")

legend("topright", legend = c("boot length", "boot length and expand", "boot length, expand, sampling strata weighting", "boot length, expand, boot trip+haul", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
```

#### reorder long
```{r, fig.height=6}
sub_range = out_5.1$length$iss$YEAR %in% 1977:2023

par(mfrow = c(1,1))
plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
lines(out_4.1$length$iss$YEAR[sub_range], out_4.1$length$iss$iss[sub_range], type = "l", col = "orange") 
lines(out_2.1$length$iss$YEAR[sub_range], out_2.1$length$iss$iss[sub_range], type = "l", col = "green")
# lines(out_8.1$length$iss$YEAR[sub_range], out_8.1$length$iss$iss[sub_range], type = "l", col = "green") 
lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")

legend("topright", legend = c("boot length", "boot length, haul", "boot all", "boot all, sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
```

#### reorder short
```{r, fig.height=6}
sub_range = out_5.1$length$iss$YEAR %in% 1998:2023

par(mfrow = c(1,1))
plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
lines(out_4.1$length$iss$YEAR[sub_range], out_4.1$length$iss$iss[sub_range], type = "l", col = "orange") 
lines(out_2.1$length$iss$YEAR[sub_range], out_2.1$length$iss$iss[sub_range], type = "l", col = "green")
# lines(out_8.1$length$iss$YEAR[sub_range], out_8.1$length$iss$iss[sub_range], type = "l", col = "green") 
lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")

legend("topright", legend = c("boot length", "boot length, haul", "boot all", "boot all, sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
```

#### reorder short 2
```{r, fig.height=6}
sub_range = out_5.1$length$iss$YEAR %in% 1998:2023

par(mfrow = c(1,1))
plot(out_10.1$length$iss$YEAR[sub_range], out_10.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
lines(out_11.1$length$iss$YEAR[sub_range], out_11.1$length$iss$iss[sub_range], type = "l", col = "blue")

lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")

legend("topright", legend = c("boot.length", "boot.length + boot.haul", "boot.length + boot.haul + boot.trip"), lty = c(1,1,1), col = c("black", "blue", "red"))
```

## Plot 3.1

3x3 grid.

### Data
```{r}
out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.1.1_ISS_200_iters_2024-11-27.RDS")

out_2.2.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.2.1_ISS_200_iters_2024-12-02.RDS")

year = out_2.1.1$samples_10$expansion_NULL$length$iss$YEAR

samples_global = c(10, 20, 30)
expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))

```

### With sampling strata
```{r}

df = tidytable(year = year,
               N10_Enone = out_2.1.1$samples_10$expansion_NULL$length$iss$iss,
               N20_Enone = out_2.1.1$samples_20$expansion_NULL$length$iss$iss,
               N30_Enone = out_2.1.1$samples_30$expansion_NULL$length$iss$iss,
               N10_Emedium = out_2.1.1$samples_10$expansion_haul_numbers$length$iss$iss,
               N20_Emedium = out_2.1.1$samples_20$expansion_haul_numbers$length$iss$iss,
               N30_Emedium = out_2.1.1$samples_30$expansion_haul_numbers$length$iss$iss,
               N10_Efull = out_2.1.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N20_Efull = out_2.1.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N30_Efull = out_2.1.1$samples_30$expansion_haul_month_numbers$length$iss$iss,)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  labs(x = "Year", y = "ISS") +
  geom_point()

```

### Without sampling strata
```{r}

df = tidytable(year = year,
               N10_Enone = out_2.2.1$samples_10$expansion_NULL$length$iss$iss,
               N20_Enone = out_2.2.1$samples_20$expansion_NULL$length$iss$iss,
               N30_Enone = out_2.2.1$samples_30$expansion_NULL$length$iss$iss,
               N10_Emedium = out_2.2.1$samples_10$expansion_haul_numbers$length$iss$iss,
               N20_Emedium = out_2.2.1$samples_20$expansion_haul_numbers$length$iss$iss,
               N30_Emedium = out_2.2.1$samples_30$expansion_haul_numbers$length$iss$iss,
               N10_Efull = out_2.2.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N20_Efull = out_2.2.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N30_Efull = out_2.2.1$samples_30$expansion_haul_month_numbers$length$iss$iss,)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  labs(x = "Year", y = "ISS") +
  geom_point()

```

### 2024-12-10 run/paper_runs/paper_scenario_10.1.R

@@ -1,0 +1,57 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_10.1"
+iterations = 100
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = FALSE,
+            boot.haul = FALSE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = TRUE,
+            expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-10 run/paper_runs/paper_scenario_2.1.1.R

@@ -1,0 +1,60 @@
+
+rm(list = ls())
+run_name = "paper_scenario_2.1.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 200
+samples_global = c(10, 20, 30)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(expansion_global)){
+
+    samples = samples_global[i]
+    expansion = expansion_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_length_N = list(type = "value", bound = NULL, amount = samples),
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = expansion) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("expansion_", expansion_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2024-12-10 run/paper_runs/paper_scenario_3.1.R

@@ -1,0 +1,57 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_3.1"
+iterations = 100
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-10 run/paper_runs/paper_scenario_6.1.R

@@ -1,0 +1,57 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_6.1"
+iterations = 100
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = FALSE,
+            boot.haul = FALSE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-10 run/paper_runs/paper_scenario_8.1.R

@@ -1,0 +1,57 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_8.1"
+iterations = 100
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-10 run/paper_runs/paper_scenario_9.1.R

@@ -1,0 +1,57 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_9.1"
+iterations = 100
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = FALSE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = NULL) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-11 Rmd/paper_plots/paper_plots_1.1.Rmd
initiate change haul amount capability. Tested-works.

@@
 out_11.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_11.1_ISS_100iters_output_2024-12-04.RDS")
+out_12.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_12.1_ISS_100iters_output_2024-12-10.RDS")
+out_13.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_13.1_ISS_100iters_output_2024-12-10.RDS")
+out_14.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_14.1_ISS_100iters_output_2024-12-10.RDS")
+out_15.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_15.1_ISS_100iters_output_2024-12-10.RDS")
+out_16.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_16.1_ISS_100iters_output_2024-12-11.RDS")
+out_17.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_17.1_ISS_100iters_output_2024-12-11.RDS")
 
@@
 
+#### reorder short with half trips and half hauls
+```{r, fig.height=6}
+sub_range = out_5.1$length$iss$YEAR %in% 1998:2023
+
+par(mfrow = c(1,1))
+plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
+lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
+lines(out_4.1$length$iss$YEAR[sub_range], out_4.1$length$iss$iss[sub_range], type = "l", col = "orange") 
+lines(out_12.1$length$iss$YEAR[sub_range], out_12.1$length$iss$iss[sub_range], type = "l", col = "purple")
+lines(out_13.1$length$iss$YEAR[sub_range], out_13.1$length$iss$iss[sub_range], type = "l", col = "brown")
+lines(out_2.1$length$iss$YEAR[sub_range], out_2.1$length$iss$iss[sub_range], type = "l", col = "green")
+lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")
+
+legend("topright", legend = c("boot length", "boot length, haul", "boot all", "boot all, half trips", "boot all, half hauls", "boot all, sampling strata weighting", "full"), lty = c(1,1,1,1,1,1,1), col = c("black", "blue", "orange","purple", "brown", "green", "red"))
+```
+
 #### reorder short 2
@@
 legend("topright", legend = c("boot.length", "boot.length + boot.haul", "boot.length + boot.haul + boot.trip"), lty = c(1,1,1), col = c("black", "blue", "red"))
+```
+
+#### Full, half trip, half haul
+```{r, fig.height=6}
+sub_range = out_5.1$length$iss$YEAR %in% 1998:2023
+
+par(mfrow = c(1,1))
+plot(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
+lines(out_14.1$length$iss$YEAR[sub_range], out_14.1$length$iss$iss[sub_range], type = "l", col = "blue")
+
+lines(out_15.1$length$iss$YEAR[sub_range], out_15.1$length$iss$iss[sub_range], type = "l", col = "red")
+
+legend("topright", legend = c("Full", "Half Trip", "Half Haul"), lty = c(1,1,1), col = c("black", "blue", "red"))
+```
+
+#### Full, 1.5 trip, 1.5 haul
+```{r, fig.height=6}
+sub_range = out_5.1$length$iss$YEAR %in% 1998:2023
+
+par(mfrow = c(1,1))
+plot(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
+lines(out_16.1$length$iss$YEAR[sub_range], out_16.1$length$iss$iss[sub_range], type = "l", col = "blue")
+
+lines(out_17.1$length$iss$YEAR[sub_range], out_17.1$length$iss$iss[sub_range], type = "l", col = "red")
+
+legend("topright", legend = c("Full", "1.5 Trip", "1.5 Haul"), lty = c(1,1,1), col = c("black", "blue", "red"))
 ```

### 2024-12-11 R/administrate_iss.R

@@ -9,6 +9,7 @@
 #' @param plus_len If set at a value, computes length expansion with a plus-length group (default = FALSE)
 #' @param minimum_sample_size list(resolution = character string, size = integer). If NULL, then no minimum sample size. If not NULL, The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
 #' @param new_trip_N list(type = character ("value", or "proportion"), amount = numeric). If NULL, then the number of trips resampled equals the number actually sampled. If not NULL, then the number of trips is changed by type (acceptable entries are "value", or "proportion") at an amount (acceptable entries are a proportion). E.g., new_trip_N = list(type = "proportion", amount = .50). Only proportion is coded so far as this makes the most sense.
+#' @param new_haul_N list(type = character ("value", or "proportion"), amount = numeric). If NULL, then the number of hauls resampled equals the number actually sampled. If not NULL, then the number of hauls is changed by type (acceptable entries are "value", or "proportion") at an amount (acceptable entries are a proportion). E.g., new_haul_N = list(type = "proportion", amount = .50). Only proportion is coded so far as this makes the most sense.
 #' @param new_length_N list(type = character ("value", or "proportion"), bound = NULL or character ("minimum", or "maximum") amount = numeric). If NULL, then the number of length samples resampled in a haul equals the number actually sampled. If not NULL, then the haul-level number of samples is changed by type (acceptable entries are "value", or "proportion") at an amount (acceptable entries are an integer number or proportion). E.g., new_length_N = list(type = "value", bound = NULL, amount = 20). The amount can be less than or greater than the true N. Note that if it is either less than or greater than, the minimum of the two is chosen for N (this is still under consideration and may change in the future). The true N is taken to be... DOES THIS ONLY MATTER IF WE NEED A THRESHOLD TO DECIDE WHEN TO TAKE THE MAX?? The samples are still drawn with replacement. Warning: cannot do this if post_strata = "SEX"
 #' @param max_length integer or "data_derived" (default). Provides the maximum length bin to record proportions-at-length. Integer values must be equal to or greater than the maximum length observed in the data (this will be changed once a plus-group option is coded in the future). "data_derived" forces the maximum length to be calculated from the data.
[…]

### 2024-12-11 R/boot_haul.R

@@ -1,20 +1,32 @@
-#' Resample hauls w/replacement.
+#' Resample hauls w/replacement, changing the number of hauls if desired
 #'
 #' @param freq_data length or age frequency input data frame. Can be the output object from boot_trip() if boot.trip == true
+#' @param new_haul_N user-defined sample size adjustment options defined in fishery_iss()
 #'
-#' @return length frequency data table including resampled hauls as HAUL_JOIN and associated data
+#' @return frequency data table including resampled hauls as HAUL_JOIN and associated data
 #'
 #' @export
 #'
-boot_haul = function(freq_data) { # based on surveyISS::boot_haul
+boot_haul = function(freq_data,  # based on surveyISS::boot_haul
+                     new_haul_N = NULL)
+{
+
   freq_data %>%
     tidytable::select(YEAR, TRIP_JOIN, HAUL_JOIN) %>%
-    tidytable::distinct() %>%
-    tidytable::mutate(HAUL_JOIN = generic_sample(HAUL_JOIN, n.samples = .N), .by = c(YEAR, TRIP_JOIN))
+    tidytable::distinct() -> .condensed.haul
+  if(base::is.null(new_haul_N)){
+    .condensed.haul %>%
+      tidytable::mutate(HAUL_JOIN = generic_sample(HAUL_JOIN,
+                                                   n.samples = .N),
+                        .by = c(YEAR, TRIP_JOIN)) -> .resampled.haul
+  }else {
+    .condensed.haul %>%
+      tidytable::summarise(HAUL_JOIN = generic_sample_change_haul_N(flex.vec = HAUL_JOIN,
+                                                                    new_haul_N = new_haul_N,
+                                                                    vec_length = .N),
+                           .by = c(YEAR, TRIP_JOIN)) -> .resampled.haul
+  }
+
+  return(.resampled.haul)
+
 }
-
-
-
-
-
-

### 2024-12-11 R/fishery_props.R

@@ -11,6 +11,7 @@
 #' @param plus_len If set at a value, computes length expansion with a plus-length group (default = FALSE)
 #' @param minimum_sample_size list(resolution = character string, size = integer). If NULL, then no minimum sample size. If not NULL, The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
 #' @param new_trip_N list(type = character ("value", or "proportion"), amount = numeric). If NULL, then the number of trips resampled equals the number actually sampled. If not NULL, then the number of trips is changed by type (acceptable entries are "value", or "proportion") at an amount (acceptable entries are a proportion). E.g., new_trip_N = list(type = "proportion", amount = .50). Only proportion is coded so far as this makes the most sense.
+#' @param new_haul_N list(type = character ("value", or "proportion"), amount = numeric). If NULL, then the number of hauls resampled equals the number actually sampled. If not NULL, then the number of hauls is changed by type (acceptable entries are "value", or "proportion") at an amount (acceptable entries are a proportion). E.g., new_haul_N = list(type = "proportion", amount = .50). Only proportion is coded so far as this makes the most sense.
 #' @param new_length_N list(type = character ("value", or "proportion"), bound = NULL or character ("minimum", or "maximum") amount = numeric). If NULL, then the number of length samples resampled in a haul equals the number actually sampled. If not NULL, then the haul-level number of samples is changed by type (acceptable entries are "value", or "proportion") at an amount (acceptable entries are an integer number or proportion). E.g., new_length_N = list(type = "value", bound = NULL, amount = 20). The amount can be less than or greater than the true N. Note that if it is either less than or greater than, the minimum of the two is chosen for N (this is still under consideration and may change in the future). The true N is taken to be... DOES THIS ONLY MATTER IF WE NEED A THRESHOLD TO DECIDE WHEN TO TAKE THE MAX?? The samples are still drawn with replacement. Warning: cannot do this if post_strata = "SEX"
[…]

### 2024-12-11 R/post_stratify.R

@@ -13,6 +13,7 @@
 #' @param post_strata list(strata = character string, nested = Boolean) if NULL, then no post stratification. The first element of post_strata is a character string with name(s) of post strata type. Accepted types are "GEAR", etc. These must be column name(s) in the data frame where each row has an entry and there are no NAs. The second element in post_strata allows for nested post-strata (e.g., "GEAR", "SEX") that are in order of the desired nested hierarchy, then the final results will be a nested list in order of the listed post-strata as well. Perhaps there should be an error message for attempts with strata names that are not in freq_data or it does exist, but there are NAs in it.
 #' @param minimum_sample_size list(resolution = character string, size = integer). If NULL, then no minimum sample size. If not NULL, The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
 #' @param new_trip_N list(type = character ("value", or "proportion"), amount = numeric). If NULL, then the number of trips resampled equals the number actually sampled. If not NULL, then the number of trips is changed by type (acceptable entries are "value", or "proportion") at an amount (acceptable entries are a proportion). E.g., new_trip_N = list(type = "proportion", amount = .50). Only proportion is coded so far as this makes the most sense.
+#' @param new_haul_N list(type = character ("value", or "proportion"), amount = numeric). If NULL, then the number of hauls resampled equals the number actually sampled. If not NULL, then the number of hauls is changed by type (acceptable entries are "value", or "proportion") at an amount (acceptable entries are a proportion). E.g., new_haul_N = list(type = "proportion", amount = .50). Only proportion is coded so far as this makes the most sense.
[…]

### 2024-12-11 run/paper_runs/paper_scenario_12.1.R

@@ -1,0 +1,58 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_12.1"
+iterations = 100
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = list(type = "proportion", amount = 0.50),
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = NULL) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-11 run/paper_runs/paper_scenario_13.1.R

@@ -1,0 +1,59 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_13.1"
+iterations = 100
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = list(type = "proportion", amount = 0.50),
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = NULL) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-11 run/paper_runs/paper_scenario_14.1.R

@@ -1,0 +1,59 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_14.1"
+iterations = 100
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = list(type = "proportion", amount = 0.50),
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = TRUE,
+            expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-11 run/paper_runs/paper_scenario_15.1.R

@@ -1,0 +1,59 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_15.1"
+iterations = 100
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = list(type = "proportion", amount = 0.50),
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = TRUE,
+            expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-11 run/paper_runs/paper_scenario_16.1.R

@@ -1,0 +1,59 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_16.1"
+iterations = 100
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = list(type = "proportion", amount = 1.50),
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = TRUE,
+            expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-11 run/run_ISS_0.16.0.R

@@ -1,0 +1,59 @@
+# reboot haul option - proportion only
+
+rm(list = ls())
+run_name = "reboot_haul_V1"
+iterations = 1
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = 1,
+            freq_data = lfreq_data,
+            yrs = 1999,
+            bin = c(5, 10, 20, 35, 60),
+            plus_len = NULL,
+            post_strata = list(strata = "GEAR", nested = FALSE),
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = list(type = "proportion", amount = .50),
+            new_length_N = list(type = "value", bound = NULL, amount = 20),
+            max_length = "data_derived",
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = TRUE,
+            expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2024-12-18 Rmd/paper_plots/paper_plots_1.1.Rmd
run Trip and Haul number variation scenarios and plot.

@@
 # par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
-par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
+# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
+par(mfrow = c(3,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
 plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000)) 
@@
 lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
-legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("2023 assessment", "baseISS", "number of hauls"))
+legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))
 
@@
 
-plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3, xlab = "year")
+plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3)
 
@@
 #### reorder long
+
+\newpage
+
 ```{r, fig.height=6}
@@
 par(mfrow = c(1,1))
-plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
+plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISSB", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
 lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
@@
 
-legend("topright", legend = c("boot length", "boot length, haul", "boot all", "boot all, sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
+legend("topleft", legend = c("boot length", "boot length + boot haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
 ```
 
+\newpage
+
 #### reorder short
+
+\newpage
+
 ```{r, fig.height=6}
-sub_range = out_5.1$length$iss$YEAR %in% 1998:2023
+sub_range = out_5.1$length$iss$YEAR %in% 1999:2023
 
 par(mfrow = c(1,1))
-plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
+plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISSB", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "")
 lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
@@
 
-legend("topright", legend = c("boot length", "boot length, haul", "boot all", "boot all, sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
+legend("topright", legend = c("boot length", "boot length + boot haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
 ```
+
+\newpage
 
@@
 
+## Plot 7x2 Grid Haul and Trip numbers
+
+### Trip Change
+```{r}
+
+out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.1_ISS_200_iters_2024-12-12.RDS")
+
+year = out_18.1$proportion_0.25$type_trip$length$iss$YEAR
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+type_global = list("trip", "haul")
+type_names_global = c("trip", "haul")
+
+df = tidytable(year = year,
+               N_0.25 = out_18.1$proportion_0.25$type_trip$length$iss$iss,
+               N_0.50 = out_18.1$proportion_0.5$type_trip$length$iss$iss,
+               N_0.75 = out_18.1$proportion_0.75$type_trip$length$iss$iss,
+               N_1.00 = out_1.1$length$iss$iss,
+               N_1.25 = out_18.1$proportion_1.25$type_trip$length$iss$iss,
+               N_1.50 = out_18.1$proportion_1.5$type_trip$length$iss$iss,
+               N_1.75 = out_18.1$proportion_1.75$type_trip$length$iss$iss,
+               N_2.00 = out_18.1$proportion_2$type_trip$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+  geom_line() +
+  labs(x = "Year", y = "ISS") +
+  geom_point() +
+  ylim(0, 17000) +
+  xlim(1998, 2023)
+
+```
+
+### Boxplots
+REMEMBER! these are the full year range, may want to narrow it to recent range.
+```{r}
+df2 %>% 
+  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_1.00"]) - ISS,
+                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_1.00"])/df2$ISS[df2$scenario=="N_1.00"],
+                    type = "trip",
+                    .by = scenario) -> df3.1
+
+# plot(df3$scenario, df3$ISS.diff)
+plot(df3.1$scenario, df3.1$ISS.error)
+abline(h = c(-.1,.1), lty = "dashed")
+
+```
+
+### Haul Change
+```{r}
+
+out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.1_ISS_200_iters_2024-12-12.RDS")
+
+year = out_18.1$proportion_0.25$type_trip$length$iss$YEAR
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+type_global = list("trip", "haul")
+type_names_global = c("trip", "haul")
+
+df = tidytable(year = year,
+               N_0.25 = out_18.1$proportion_0.25$type_haul$length$iss$iss,
+               N_0.50 = out_18.1$proportion_0.5$type_haul$length$iss$iss,
+               N_0.75 = out_18.1$proportion_0.75$type_haul$length$iss$iss,
+               N_1.00 = out_1.1$length$iss$iss,
+               N_1.25 = out_18.1$proportion_1.25$type_haul$length$iss$iss,
+               N_1.50 = out_18.1$proportion_1.5$type_haul$length$iss$iss,
+               N_1.75 = out_18.1$proportion_1.75$type_haul$length$iss$iss,
+               N_2.00 = out_18.1$proportion_2$type_haul$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+  geom_line() +
+  labs(x = "Year", y = "ISS") +
+  geom_point() +
+  ylim(0, 17000) +
+  xlim(1998, 2023)
+
+```
+
+### Boxplots
+```{r}
+df2 %>% 
+  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_1.00"]) - ISS,
+                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_1.00"])/df2$ISS[df2$scenario=="N_1.00"],
+                    type = "haul",
+                    .by = scenario) -> df3.2
+
+# plot(df3$scenario, df3$ISS.diff)
+plot(df3.2$scenario, df3.2$ISS.error)
+abline(h = c(-.1,.1), lty = "dashed")
+
+```
+
+### Boxplots Together 1977-2023
+```{r, fig.width=8}
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) -> df4
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.9))
+
+```
+
+### Boxplots Together 1999-2023
+```{r}
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::filter(year %in% 1999:2023) -> df4
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error)) +
+  geom_boxplot(aes(fill = type))
+
+```
+
 ## Plot 3.1
@@
 ### With sampling strata
-```{r}
-
+```{r, fig.width=9, fig.height=5}
 df = tidytable(year = year,
@@
   geom_line() +
-  labs(x = "Year", y = "ISS") +
-  geom_point()
+  labs(x = "", y = "ISSB") +
+  geom_point() + 
+  theme_classic() +
+  theme(legend.position = c(0.84, 0.8),
+        axis.title.x = element_blank())
+```
+
+```{r, fig.width=9, fig.height=5}
+# stats
+((df$N10_Enone - df$N20_Enone)/df$N20_Enone) %>%
+  mean()
+
+((df$N10_Emedium - df$N20_Emedium)/df$N20_Emedium) %>%
+  mean()
+
+((df$N10_Efull - df$N20_Efull)/df$N20_Efull) %>%
+  mean()
+(-.02 - .12 - .08)/3
+
+((df$N30_Enone - df$N20_Enone)/df$N20_Enone) %>%
+  mean()
+
+((df$N30_Emedium - df$N20_Emedium)/df$N20_Emedium) %>%
+  mean()
+
+((df$N30_Efull - df$N20_Efull)/df$N20_Efull) %>%
+  mean()
+
+(.03 + .04 +.03)/3
 
@@
 ```
+
+## Plot 4.1 Trip and Haul x .5, 1.5
+
+2x3 grid.
+
+### Data
+```{r}
+out_19.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_19.1_ISS_200_iters_2024-12-17.RDS")
+
+out_20.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_20.1_ISS_200_iters_2024-12-17.RDS")
+
+year = out_19.1$proportion_0.5$expansion_NULL$length$iss$YEAR
+
+proportion_global = c(0.50, 1.50)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+samples_global = c(10, 20, 30)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+```
+
+COME BACK TO THIS! NEED TO RERUN WITH REGULAR HAUL AND TRIP NUMBERS!
+### With sampling strata
+```{r, fig.width=9, fig.height=5}
+df = tidytable(year = year,
+               N0.5_Enone = out_19.1$proportion_0.5$expansion_NULL$length$iss$iss,
+               N1.0_Enone = out_2.1.1$samples_20$expansion_NULL$length$iss$iss,
+               N30_Enone = out_2.1.1$samples_30$expansion_NULL$length$iss$iss,
+               N10_Emedium = out_2.1.1$samples_10$expansion_haul_numbers$length$iss$iss,
+               N20_Emedium = out_2.1.1$samples_20$expansion_haul_numbers$length$iss$iss,
+               N30_Emedium = out_2.1.1$samples_30$expansion_haul_numbers$length$iss$iss,
+               N10_Efull = out_2.1.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N20_Efull = out_2.1.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N30_Efull = out_2.1.1$samples_30$expansion_haul_month_numbers$length$iss$iss,)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+  geom_line() +
+  labs(x = "", y = "ISSB") +
+  geom_point() + 
+  theme_classic() +
+  theme(legend.position = c(0.84, 0.8),
+        axis.title.x = element_blank())
+```

### 2024-12-18 run/paper_runs/paper_scenario_18.1.R

@@ -1,0 +1,63 @@
+
+rm(list = ls())
+run_name = "paper_scenario_18.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 200
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+type_global = list("trip", "haul")
+type_names_global = c("trip", "haul")
+
+
+# Loop All
+out = list()
+for(i in 1:length(proportion_global)){
+  out[[paste0("proportion_", proportion_global)[i]]] = list()
+  for(j in 1:length(type_global)){
+
+    .proportion = proportion_global[i]
+    .type = type_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = NULL,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = if(.type=="trip") {list(type = "proportion", amount = .proportion)} else{NULL},
+                new_haul_N = if(.type=="haul") {list(type = "proportion", amount = .proportion)} else{NULL},
+                new_length_N = NULL,
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+    tictoc::toc()
+    out[[paste0("proportion_", proportion_global)[i]]][[paste0("type_", type_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2024-12-18 run/paper_runs/paper_scenario_19.1.R

@@ -1,0 +1,63 @@
+
+rm(list = ls())
+run_name = "paper_scenario_19.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 200
+proportion_global = c(0.50, 1.00, 1.50)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# Loop All
+out = list()
+for(i in 1:length(proportion_global)){
+  out[[paste0("proportion_", proportion_global)[i]]] = list()
+  for(j in 1:length(expansion_global)){
+
+    .proportion = proportion_global[i]
+    expansion = expansion_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = NULL,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = list(type = "proportion", amount = .proportion),
+                new_haul_N = NULL,
+                new_length_N = NULL,
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = expansion) -> .output
+    tictoc::toc()
+    out[[paste0("proportion_", proportion_global)[i]]][[paste0("expansion_", expansion_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2024-12-18 run/paper_runs/paper_scenario_20.1.R

@@ -1,0 +1,63 @@
+
+rm(list = ls())
+run_name = "paper_scenario_20.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 200
+proportion_global = c(0.50, 1.00, 1.50)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# Loop All
+out = list()
+for(i in 1:length(proportion_global)){
+  out[[paste0("proportion_", proportion_global)[i]]] = list()
+  for(j in 1:length(expansion_global)){
+
+    .proportion = proportion_global[i]
+    expansion = expansion_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = NULL,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N = list(type = "proportion", amount = .proportion),
+                new_length_N = NULL,
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = expansion) -> .output
+    tictoc::toc()
+    out[[paste0("proportion_", proportion_global)[i]]][[paste0("expansion_", expansion_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-01-22 Rmd/paper_plots/paper_plots_1.1.Rmd
add more grid scenarios

@@
 library(knitr)
+library(stringr)
+library(patchwork)
 opts_knit$set(eval.after = "fig.cap")
@@
 out_1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.1_ISS_100iters_output_2024-11-25.RDS")
+
+out_1.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.2_ISS_1iters_output_2025-01-10.RDS")
 
@@
 
+### All together TRIPS TOO 4 panel
+
+```{r, fig.height=8}
+df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))
+
+# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
+par(mfrow = c(4,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
+plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n") 
+lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
+legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("2023 assessment", "baseISS"))
+
+plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, type = "l", ylab = "number of hauls", xlab = "", col = "black", cex.lab = 1.3, xaxt = "n")
+
+plot(out_1.2$length$iss$YEAR, out_1.2$length$iss$ntps, ylim = c(0, 1000), ylab = "Number of Trips", type = "l", cex.lab = 1.3, xaxt = "n", xlab = "")
+
+plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", cex.lab = 1.3, xlab = "year")
+
+```
+
+### All together TRIPS TOO 3 panel
+
+```{r, fig.height=8}
+df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))
+
+# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
+# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
+par(mfrow = c(3,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
+plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000)) 
+lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
+lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
+lines(out_1.2$length$iss$YEAR, out_1.2$length$iss$ntps, col = "green")
+legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))
+
+plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")
+
+plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3)
+
+```
+
 #### Inspect R-squared
@@
 
-### Boxplots
+### Boxplots Haul and Trip
 ```{r}
@@
 df4 %>% 
-  ggplot(aes(x = scenario, y = ISS.error)) +
-  geom_boxplot(aes(fill = type)) +
-  labs(x = "Scenario", y = "ISSB") +
-  theme_classic() +
-  theme(legend.position = c(0.5, 0.9))
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.9)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
 
@@
 df4 %>% 
-  ggplot(aes(x = scenario, y = ISS.error)) +
-  geom_boxplot(aes(fill = type))
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.9)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120))
+
+```
+
+### Boxplots samples
+
+### Validate N=20 assumption
+is assuming n=20 when the median is 20 for 1999-2023 valid to make a valid control? How well do they match?
+```{r}
+
+out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_22.1_ISS_200_iters_2024-12-25.RDS")
+
+plot(out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss, ylim = c(0, 13000))
+lines(out_1.1$length$iss$iss[out_1.1$length$iss$YEAR %in% 1999:2023], col = "blue")
+
+```
+
+### Boxplots Together 1977-2023
+```{r}
+
+out_21.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_21.1_ISS_200_iters_2024-12-23.RDS")
+
+year = out_21.1$samples_1$length$iss$YEAR
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+type_global = list("trip", "haul")
+type_names_global = c("trip", "haul")
+
+df = tidytable(year = year,
+               N_1 = out_21.1$samples_1$length$iss$iss,
+               N_5 = out_21.1$samples_5$length$iss$iss,
+               N_10 = out_21.1$samples_10$length$iss$iss,
+               N_15 = out_21.1$samples_15$length$iss$iss,
+               N_20 = out_21.1$samples_20$length$iss$iss,
+               N_25 = out_21.1$samples_25$length$iss$iss,
+               N_30 = out_21.1$samples_30$length$iss$iss,
+               N_35 = out_21.1$samples_35$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+  geom_line() +
+  labs(x = "Year", y = "ISS") +
+  geom_point() +
+  ylim(0, 17000)
+
+df2 %>% 
+  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_20"]) - ISS,
+                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_20"])/df2$ISS[df2$scenario=="N_20"],
+                    type = "sample",
+                    .by = scenario) %>% 
+  tidytable::filter(year %in% 1999:2023)-> df3.2
+
+# plot(df3$scenario, df3$ISS.diff)
+plot(df3.2$scenario, df3.2$ISS.error)
+abline(h = c(-.1,.1), lty = "dashed")
+
+df3.2 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+```
+
+### Samples VS Expantion. Boxplots Together 1999-2023
+```{r, fig.width=8}
+
+out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_22.1_ISS_200_iters_2024-12-25.RDS")
+
+year = out_22.1$samples_1$expansion_NULL$length$iss$YEAR
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+df = tidytable(year = year,
+               N1_Enone = out_22.1$samples_1$expansion_NULL$length$iss$iss,
+               N5_Enone = out_22.1$samples_5$expansion_NULL$length$iss$iss,
+               N10_Enone = out_22.1$samples_10$expansion_NULL$length$iss$iss,
+               N15_Enone = out_22.1$samples_15$expansion_NULL$length$iss$iss,
+               N20_Enone = out_22.1$samples_20$expansion_NULL$length$iss$iss,
+               N25_Enone = out_22.1$samples_25$expansion_NULL$length$iss$iss,
+               N30_Enone = out_22.1$samples_30$expansion_NULL$length$iss$iss,
+               N35_Enone = out_22.1$samples_35$expansion_NULL$length$iss$iss,
+               N1_Emedium = out_22.1$samples_1$expansion_haul_numbers$length$iss$iss,
+               N5_Emedium = out_22.1$samples_5$expansion_haul_numbers$length$iss$iss,
+               N10_Emedium = out_22.1$samples_10$expansion_haul_numbers$length$iss$iss,
+               N15_Emedium = out_22.1$samples_15$expansion_haul_numbers$length$iss$iss,
+               N20_Emedium = out_22.1$samples_20$expansion_haul_numbers$length$iss$iss,
+               N25_Emedium = out_22.1$samples_25$expansion_haul_numbers$length$iss$iss,
+               N30_Emedium = out_22.1$samples_30$expansion_haul_numbers$length$iss$iss,
+               N35_Emedium = out_22.1$samples_35$expansion_haul_numbers$length$iss$iss,
+               N1_Efull = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_Efull = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_Efull = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_Efull = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_Efull = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_Efull = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_Efull = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_Efull = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2[grep("Enone", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Enone"])/df2$ISS[df2$scenario=="N20_Enone"],
+                    type = "Enone",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1
+
+df2[grep("Emedium", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Emedium"])/df2$ISS[df2$scenario=="N20_Emedium"],
+                    type = "Emedium",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -9)) -> df3.2
+
+df2[grep("Efull", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
+                    type = "Efull",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+
+```
+
+### Samples VS Expantion TAKE 2: relative to unbiased control. Boxplots Together 1999-2023
+```{r, fig.width=8}
+
+out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_22.1_ISS_200_iters_2024-12-25.RDS")
+
+year = out_22.1$samples_1$expansion_NULL$length$iss$YEAR
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+df = tidytable(year = year,
+               N1_Enone = out_22.1$samples_1$expansion_NULL$length$iss$iss,
+               N5_Enone = out_22.1$samples_5$expansion_NULL$length$iss$iss,
+               N10_Enone = out_22.1$samples_10$expansion_NULL$length$iss$iss,
+               N15_Enone = out_22.1$samples_15$expansion_NULL$length$iss$iss,
+               N20_Enone = out_22.1$samples_20$expansion_NULL$length$iss$iss,
+               N25_Enone = out_22.1$samples_25$expansion_NULL$length$iss$iss,
+               N30_Enone = out_22.1$samples_30$expansion_NULL$length$iss$iss,
+               N35_Enone = out_22.1$samples_35$expansion_NULL$length$iss$iss,
+               N1_Emedium = out_22.1$samples_1$expansion_haul_numbers$length$iss$iss,
+               N5_Emedium = out_22.1$samples_5$expansion_haul_numbers$length$iss$iss,
+               N10_Emedium = out_22.1$samples_10$expansion_haul_numbers$length$iss$iss,
+               N15_Emedium = out_22.1$samples_15$expansion_haul_numbers$length$iss$iss,
+               N20_Emedium = out_22.1$samples_20$expansion_haul_numbers$length$iss$iss,
+               N25_Emedium = out_22.1$samples_25$expansion_haul_numbers$length$iss$iss,
+               N30_Emedium = out_22.1$samples_30$expansion_haul_numbers$length$iss$iss,
+               N35_Emedium = out_22.1$samples_35$expansion_haul_numbers$length$iss$iss,
+               N1_Efull = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_Efull = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_Efull = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_Efull = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_Efull = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_Efull = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_Efull = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_Efull = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2 %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
+                    .by = scenario)
+
+df2[grep("Enone", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
+                    type = "Enone",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1
+
+df2[grep("Emedium", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
+                    type = "Emedium",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -9)) -> df3.2
+
+df2[grep("Efull", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
+                    type = "Efull",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+
+```
+
+### Samples VS Haul. Boxplots Together 1999-2023
+```{r, fig.width=8}
+
+out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.1_ISS_200_iters_2025-01-02.RDS")
+
+year = out_24.1$samples_1$trip_0.25$length$iss$YEAR
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+
+df = tidytable(year = year,
+               N1_H0.75 = out_24.1$samples_1$trip_0.75$length$iss$iss,
+               N5_H0.75 = out_24.1$samples_5$trip_0.75$length$iss$iss,
+               N10_H0.75 = out_24.1$samples_10$trip_0.75$length$iss$iss,
+               N15_H0.75 = out_24.1$samples_15$trip_0.75$length$iss$iss,
+               N20_H0.75 = out_24.1$samples_20$trip_0.75$length$iss$iss,
+               N25_H0.75 = out_24.1$samples_25$trip_0.75$length$iss$iss,
+               N30_H0.75 = out_24.1$samples_30$trip_0.75$length$iss$iss,
+               N35_H0.75 = out_24.1$samples_35$trip_0.75$length$iss$iss,
+               N1_H1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_H1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_H1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_H1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_H1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_H1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_H1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_H1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss,
+               N1_H1.25 = out_24.1$samples_1$trip_1.25$length$iss$iss,
+               N5_H1.25 = out_24.1$samples_5$trip_1.25$length$iss$iss,
+               N10_H1.25 = out_24.1$samples_10$trip_1.25$length$iss$iss,
+               N15_H1.25 = out_24.1$samples_15$trip_1.25$length$iss$iss,
+               N20_H1.25 = out_24.1$samples_20$trip_1.25$length$iss$iss,
+               N25_H1.25 = out_24.1$samples_25$trip_1.25$length$iss$iss,
+               N30_H1.25 = out_24.1$samples_30$trip_1.25$length$iss$iss,
+               N35_H1.25 = out_24.1$samples_35$trip_1.25$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2[grep("H0.75", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H0.75"])/df2$ISS[df2$scenario=="N20_H0.75"],
+                    type = "H0.75",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1
+
+df2[grep("H1.0", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "H1.0",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2
+
+df2[grep("H1.25", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.25"])/df2$ISS[df2$scenario=="N20_H1.25"],
+                    type = "H1.25",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+
+```
+
+### Samples VS Haul. Boxplots Together 1999-2023. sub-sample range
+```{r, fig.width=8}
+
+out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.1_ISS_200_iters_2025-01-02.RDS")
+
+year = out_24.1$samples_1$trip_0.25$length$iss$YEAR
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+
+df = tidytable(year = year,
+               N1_H0.5 = out_24.1$samples_1$trip_0.5$length$iss$iss,
+               N5_H0.5 = out_24.1$samples_5$trip_0.5$length$iss$iss,
+               N10_H0.5 = out_24.1$samples_10$trip_0.5$length$iss$iss,
+               N15_H0.5 = out_24.1$samples_15$trip_0.5$length$iss$iss,
+               N20_H0.5 = out_24.1$samples_20$trip_0.5$length$iss$iss,
+               N25_H0.5 = out_24.1$samples_25$trip_0.5$length$iss$iss,
+               N30_H0.5 = out_24.1$samples_30$trip_0.5$length$iss$iss,
+               N35_H0.5 = out_24.1$samples_35$trip_0.5$length$iss$iss,
+               N1_H0.75 = out_24.1$samples_1$trip_0.75$length$iss$iss,
+               N5_H0.75 = out_24.1$samples_5$trip_0.75$length$iss$iss,
+               N10_H0.75 = out_24.1$samples_10$trip_0.75$length$iss$iss,
+               N15_H0.75 = out_24.1$samples_15$trip_0.75$length$iss$iss,
+               N20_H0.75 = out_24.1$samples_20$trip_0.75$length$iss$iss,
+               N25_H0.75 = out_24.1$samples_25$trip_0.75$length$iss$iss,
+               N30_H0.75 = out_24.1$samples_30$trip_0.75$length$iss$iss,
+               N35_H0.75 = out_24.1$samples_35$trip_0.75$length$iss$iss,
+               N1_H1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_H1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_H1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_H1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_H1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_H1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_H1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_H1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss,
+               N1_H1.25 = out_24.1$samples_1$trip_1.25$length$iss$iss,
+               N5_H1.25 = out_24.1$samples_5$trip_1.25$length$iss$iss,
+               N10_H1.25 = out_24.1$samples_10$trip_1.25$length$iss$iss,
+               N15_H1.25 = out_24.1$samples_15$trip_1.25$length$iss$iss,
+               N20_H1.25 = out_24.1$samples_20$trip_1.25$length$iss$iss,
+               N25_H1.25 = out_24.1$samples_25$trip_1.25$length$iss$iss,
+               N30_H1.25 = out_24.1$samples_30$trip_1.25$length$iss$iss,
+               N35_H1.25 = out_24.1$samples_35$trip_1.25$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2[grep("H0.5", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H0.5"])/df2$ISS[df2$scenario=="N20_H0.5"],
+                    type = "0.5",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.01
+
+df2[grep("H0.75", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H0.75"])/df2$ISS[df2$scenario=="N20_H0.75"],
+                    type = "0.75",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1
+
+df2[grep("H1.0", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "1.0",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2
+
+df2[grep("H1.25", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.25"])/df2$ISS[df2$scenario=="N20_H1.25"],
+                    type = "1.25",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3
+
+df3.01 %>% 
+  tidytable::bind_rows(df3.1) %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.1.a
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+df4 %>% 
+  tidytable::filter(scenario %in% c("N5", "N10", "N15")) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+
+```
+
+### Samples VS Haul TAKE 2: relative to unbiased control. Boxplots Together 1999-2023. sub-sample range
+```{r, fig.width=8}
+
+out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.1_ISS_200_iters_2025-01-02.RDS")
+
+year = out_24.1$samples_1$trip_0.25$length$iss$YEAR
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+
+df = tidytable(year = year,
+               N1_H0.5 = out_24.1$samples_1$trip_0.5$length$iss$iss,
+               N5_H0.5 = out_24.1$samples_5$trip_0.5$length$iss$iss,
+               N10_H0.5 = out_24.1$samples_10$trip_0.5$length$iss$iss,
+               N15_H0.5 = out_24.1$samples_15$trip_0.5$length$iss$iss,
+               N20_H0.5 = out_24.1$samples_20$trip_0.5$length$iss$iss,
+               N25_H0.5 = out_24.1$samples_25$trip_0.5$length$iss$iss,
+               N30_H0.5 = out_24.1$samples_30$trip_0.5$length$iss$iss,
+               N35_H0.5 = out_24.1$samples_35$trip_0.5$length$iss$iss,
+               N1_H0.75 = out_24.1$samples_1$trip_0.75$length$iss$iss,
+               N5_H0.75 = out_24.1$samples_5$trip_0.75$length$iss$iss,
+               N10_H0.75 = out_24.1$samples_10$trip_0.75$length$iss$iss,
+               N15_H0.75 = out_24.1$samples_15$trip_0.75$length$iss$iss,
+               N20_H0.75 = out_24.1$samples_20$trip_0.75$length$iss$iss,
+               N25_H0.75 = out_24.1$samples_25$trip_0.75$length$iss$iss,
+               N30_H0.75 = out_24.1$samples_30$trip_0.75$length$iss$iss,
+               N35_H0.75 = out_24.1$samples_35$trip_0.75$length$iss$iss,
+               N1_H1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_H1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_H1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_H1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_H1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_H1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_H1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_H1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss,
+               N1_H1.25 = out_24.1$samples_1$trip_1.25$length$iss$iss,
+               N5_H1.25 = out_24.1$samples_5$trip_1.25$length$iss$iss,
+               N10_H1.25 = out_24.1$samples_10$trip_1.25$length$iss$iss,
+               N15_H1.25 = out_24.1$samples_15$trip_1.25$length$iss$iss,
+               N20_H1.25 = out_24.1$samples_20$trip_1.25$length$iss$iss,
+               N25_H1.25 = out_24.1$samples_25$trip_1.25$length$iss$iss,
+               N30_H1.25 = out_24.1$samples_30$trip_1.25$length$iss$iss,
+               N35_H1.25 = out_24.1$samples_35$trip_1.25$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2[grep("H0.5", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "0.5",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.01
+
+df2[grep("H0.75", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "0.75",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1
+
+df2[grep("H1.0", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "1.0",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2
+
+df2[grep("H1.25", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "1.25",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3
+
+df3.01 %>% 
+  tidytable::bind_rows(df3.1) %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.1.b
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+df4 %>% 
+  tidytable::filter(scenario %in% c("N5", "N10", "N15")) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+
+```
+
+### Samples VS Trip. Boxplots Together 1999-2023
+```{r, fig.width=8}
+
+out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_23.1_ISS_200_iters_2024-12-31.RDS")
+
+year = out_23.1$samples_1$trip_0.25$length$iss$YEAR
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+
+df = tidytable(year = year,
+               N1_H0.5 = out_23.1$samples_1$trip_0.5$length$iss$iss,
+               N5_H0.5 = out_23.1$samples_5$trip_0.5$length$iss$iss,
+               N10_H0.5 = out_23.1$samples_10$trip_0.5$length$iss$iss,
+               N15_H0.5 = out_23.1$samples_15$trip_0.5$length$iss$iss,
+               N20_H0.5 = out_23.1$samples_20$trip_0.5$length$iss$iss,
+               N25_H0.5 = out_23.1$samples_25$trip_0.5$length$iss$iss,
+               N30_H0.5 = out_23.1$samples_30$trip_0.5$length$iss$iss,
+               N35_H0.5 = out_23.1$samples_35$trip_0.5$length$iss$iss,
+               N1_H0.75 = out_23.1$samples_1$trip_0.75$length$iss$iss,
+               N5_H0.75 = out_23.1$samples_5$trip_0.75$length$iss$iss,
+               N10_H0.75 = out_23.1$samples_10$trip_0.75$length$iss$iss,
+               N15_H0.75 = out_23.1$samples_15$trip_0.75$length$iss$iss,
+               N20_H0.75 = out_23.1$samples_20$trip_0.75$length$iss$iss,
+               N25_H0.75 = out_23.1$samples_25$trip_0.75$length$iss$iss,
+               N30_H0.75 = out_23.1$samples_30$trip_0.75$length$iss$iss,
+               N35_H0.75 = out_23.1$samples_35$trip_0.75$length$iss$iss,
+               N1_H1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_H1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_H1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_H1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_H1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_H1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_H1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_H1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss,
+               N1_H1.25 = out_23.1$samples_1$trip_1.25$length$iss$iss,
+               N5_H1.25 = out_23.1$samples_5$trip_1.25$length$iss$iss,
+               N10_H1.25 = out_23.1$samples_10$trip_1.25$length$iss$iss,
+               N15_H1.25 = out_23.1$samples_15$trip_1.25$length$iss$iss,
+               N20_H1.25 = out_23.1$samples_20$trip_1.25$length$iss$iss,
+               N25_H1.25 = out_23.1$samples_25$trip_1.25$length$iss$iss,
+               N30_H1.25 = out_23.1$samples_30$trip_1.25$length$iss$iss,
+               N35_H1.25 = out_23.1$samples_35$trip_1.25$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2[grep("H0.5", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H0.5"])/df2$ISS[df2$scenario=="N20_H0.5"],
+                    type = "0.5",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.01
+
+df2[grep("H0.75", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H0.75"])/df2$ISS[df2$scenario=="N20_H0.75"],
+                    type = "0.75",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1
+
+df2[grep("H1.0", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "1.0",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2
+
+df2[grep("H1.25", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.25"])/df2$ISS[df2$scenario=="N20_H1.25"],
+                    type = "1.25",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3
+
+df3.01 %>% 
+  tidytable::bind_rows(df3.1) %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.2.a
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+df4 %>% 
+  tidytable::filter(scenario %in% c("N5", "N10", "N15")) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+
+```
+
+### Samples VS Trip TAKE 2: relative to unbiased control. Boxplots Together 1999-2023
+```{r, fig.width=8}
+
+out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_23.1_ISS_200_iters_2024-12-31.RDS")
+
+year = out_23.1$samples_1$trip_0.25$length$iss$YEAR
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+
+df = tidytable(year = year,
+               N1_H0.5 = out_23.1$samples_1$trip_0.5$length$iss$iss,
+               N5_H0.5 = out_23.1$samples_5$trip_0.5$length$iss$iss,
+               N10_H0.5 = out_23.1$samples_10$trip_0.5$length$iss$iss,
+               N15_H0.5 = out_23.1$samples_15$trip_0.5$length$iss$iss,
+               N20_H0.5 = out_23.1$samples_20$trip_0.5$length$iss$iss,
+               N25_H0.5 = out_23.1$samples_25$trip_0.5$length$iss$iss,
+               N30_H0.5 = out_23.1$samples_30$trip_0.5$length$iss$iss,
+               N35_H0.5 = out_23.1$samples_35$trip_0.5$length$iss$iss,
+               N1_H0.75 = out_23.1$samples_1$trip_0.75$length$iss$iss,
+               N5_H0.75 = out_23.1$samples_5$trip_0.75$length$iss$iss,
+               N10_H0.75 = out_23.1$samples_10$trip_0.75$length$iss$iss,
+               N15_H0.75 = out_23.1$samples_15$trip_0.75$length$iss$iss,
+               N20_H0.75 = out_23.1$samples_20$trip_0.75$length$iss$iss,
+               N25_H0.75 = out_23.1$samples_25$trip_0.75$length$iss$iss,
+               N30_H0.75 = out_23.1$samples_30$trip_0.75$length$iss$iss,
+               N35_H0.75 = out_23.1$samples_35$trip_0.75$length$iss$iss,
+               N1_H1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_H1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_H1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_H1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_H1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_H1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_H1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_H1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss,
+               N1_H1.25 = out_23.1$samples_1$trip_1.25$length$iss$iss,
+               N5_H1.25 = out_23.1$samples_5$trip_1.25$length$iss$iss,
+               N10_H1.25 = out_23.1$samples_10$trip_1.25$length$iss$iss,
+               N15_H1.25 = out_23.1$samples_15$trip_1.25$length$iss$iss,
+               N20_H1.25 = out_23.1$samples_20$trip_1.25$length$iss$iss,
+               N25_H1.25 = out_23.1$samples_25$trip_1.25$length$iss$iss,
+               N30_H1.25 = out_23.1$samples_30$trip_1.25$length$iss$iss,
+               N35_H1.25 = out_23.1$samples_35$trip_1.25$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2[grep("H0.5", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "0.5",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.01
+
+df2[grep("H0.75", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "0.75",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1
+
+df2[grep("H1.0", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "1.0",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2
+
+df2[grep("H1.25", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "1.25",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3
+
+df3.01 %>% 
+  tidytable::bind_rows(df3.1) %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.2.b
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+df4 %>% 
+  tidytable::filter(scenario %in% c("N5", "N10", "N15")) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+
+```
+
+### Samples VS Trip/Haul. Boxplots Together 1999-2023
+```{r, fig.width=8}
+
+out_25.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_25.1_ISS_200_iters_2025-01-03.RDS")
+
+year = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$YEAR
+
+df = tidytable(year = year,
+               N1_H0.5_T0.5 = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$iss,
+               N5_H0.5_T0.5 = out_25.1$samples_5$haul_0.5_trip_0.5$length$iss$iss,
+               N10_H0.5_T0.5 = out_25.1$samples_10$haul_0.5_trip_0.5$length$iss$iss,
+               N15_H0.5_T0.5 = out_25.1$samples_15$haul_0.5_trip_0.5$length$iss$iss,
+               N20_H0.5_T0.5 = out_25.1$samples_20$haul_0.5_trip_0.5$length$iss$iss,
+               N25_H0.5_T0.5 = out_25.1$samples_25$haul_0.5_trip_0.5$length$iss$iss,
+               N30_H0.5_T0.5 = out_25.1$samples_30$haul_0.5_trip_0.5$length$iss$iss,
+               N35_H0.5_T0.5 = out_25.1$samples_35$haul_0.5_trip_0.5$length$iss$iss,
+
+               N1_H0.5_T0.75 = out_25.1$samples_1$haul_0.5_trip_0.75$length$iss$iss,
+               N5_H0.5_T0.75 = out_25.1$samples_5$haul_0.5_trip_0.75$length$iss$iss,
+               N10_H0.5_T0.75 = out_25.1$samples_10$haul_0.5_trip_0.75$length$iss$iss,
+               N15_H0.5_T0.75 = out_25.1$samples_15$haul_0.5_trip_0.75$length$iss$iss,
+               N20_H0.5_T0.75 = out_25.1$samples_20$haul_0.5_trip_0.75$length$iss$iss,
+               N25_H0.5_T0.75 = out_25.1$samples_25$haul_0.5_trip_0.75$length$iss$iss,
+               N30_H0.5_T0.75 = out_25.1$samples_30$haul_0.5_trip_0.75$length$iss$iss,
+               N35_H0.5_T0.75 = out_25.1$samples_35$haul_0.5_trip_0.75$length$iss$iss,
+
+               N1_H0.75_T0.5 = out_25.1$samples_1$haul_0.75_trip_0.5$length$iss$iss,
+               N5_H0.75_T0.5 = out_25.1$samples_5$haul_0.75_trip_0.5$length$iss$iss,
+               N10_H0.75_T0.5 = out_25.1$samples_10$haul_0.75_trip_0.5$length$iss$iss,
+               N15_H0.75_T0.5 = out_25.1$samples_15$haul_0.75_trip_0.5$length$iss$iss,
+               N20_H0.75_T0.5 = out_25.1$samples_20$haul_0.75_trip_0.5$length$iss$iss,
+               N25_H0.75_T0.5 = out_25.1$samples_25$haul_0.75_trip_0.5$length$iss$iss,
+               N30_H0.75_T0.5 = out_25.1$samples_30$haul_0.75_trip_0.5$length$iss$iss,
+               N35_H0.75_T0.5 = out_25.1$samples_35$haul_0.75_trip_0.5$length$iss$iss,
+
+               N1_H0.75_T0.75 = out_25.1$samples_1$haul_0.75_trip_0.75$length$iss$iss,
+               N5_H0.75_T0.75 = out_25.1$samples_5$haul_0.75_trip_0.75$length$iss$iss,
+               N10_H0.75_T0.75 = out_25.1$samples_10$haul_0.75_trip_0.75$length$iss$iss,
+               N15_H0.75_T0.75 = out_25.1$samples_15$haul_0.75_trip_0.75$length$iss$iss,
+               N20_H0.75_T0.75 = out_25.1$samples_20$haul_0.75_trip_0.75$length$iss$iss,
+               N25_H0.75_T0.75 = out_25.1$samples_25$haul_0.75_trip_0.75$length$iss$iss,
+               N30_H0.75_T0.75 = out_25.1$samples_30$haul_0.75_trip_0.75$length$iss$iss,
+               N35_H0.75_T0.75 = out_25.1$samples_35$haul_0.75_trip_0.75$length$iss$iss,
+
+               N1_H1.25_T0.5 = out_25.1$samples_1$haul_1.25_trip_0.5$length$iss$iss,
+               N5_H1.25_T0.5 = out_25.1$samples_5$haul_1.25_trip_0.5$length$iss$iss,
+               N10_H1.25_T0.5 = out_25.1$samples_10$haul_1.25_trip_0.5$length$iss$iss,
+               N15_H1.25_T0.5 = out_25.1$samples_15$haul_1.25_trip_0.5$length$iss$iss,
+               N20_H1.25_T0.5 = out_25.1$samples_20$haul_1.25_trip_0.5$length$iss$iss,
+               N25_H1.25_T0.5 = out_25.1$samples_25$haul_1.25_trip_0.5$length$iss$iss,
+               N30_H1.25_T0.5 = out_25.1$samples_30$haul_1.25_trip_0.5$length$iss$iss,
+               N35_H1.25_T0.5 = out_25.1$samples_35$haul_1.25_trip_0.5$length$iss$iss,
+
+               N1_H1.25_T0.75 = out_25.1$samples_1$haul_1.25_trip_0.75$length$iss$iss,
+               N5_H1.25_T0.75 = out_25.1$samples_5$haul_1.25_trip_0.75$length$iss$iss,
+               N10_H1.25_T0.75 = out_25.1$samples_10$haul_1.25_trip_0.75$length$iss$iss,
+               N15_H1.25_T0.75 = out_25.1$samples_15$haul_1.25_trip_0.75$length$iss$iss,
+               N20_H1.25_T0.75 = out_25.1$samples_20$haul_1.25_trip_0.75$length$iss$iss,
+               N25_H1.25_T0.75 = out_25.1$samples_25$haul_1.25_trip_0.75$length$iss$iss,
+               N30_H1.25_T0.75 = out_25.1$samples_30$haul_1.25_trip_0.75$length$iss$iss,
+               N35_H1.25_T0.75 = out_25.1$samples_35$haul_1.25_trip_0.75$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+scenario_names = c("H0.5_T0.5", "H0.5_T0.75", "H0.75_T0.5", "H0.75_T0.75", "H1.25_T0.5", "H1.25_T0.75")
+
+## 1
+df2[grep(scenario_names[1], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario==paste("N20", scenario_names[1], sep = "_")])/df2$ISS[df2$scenario==paste("N20", scenario_names[1], sep = "_")],
+                    type = scenario_names[1],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[1])+2))) -> df3.1
+
+## 2
+df2[grep(scenario_names[2], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario==paste("N20", scenario_names[2], sep = "_")])/df2$ISS[df2$scenario==paste("N20", scenario_names[2], sep = "_")],
+                    type = scenario_names[2],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[2])+2))) -> df3.2
+
+## 3
+df2[grep(scenario_names[3], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario==paste("N20", scenario_names[3], sep = "_")])/df2$ISS[df2$scenario==paste("N20", scenario_names[3], sep = "_")],
+                    type = scenario_names[3],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[3])+2))) -> df3.3
+
+## 4
+df2[grep(scenario_names[4], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario==paste("N20", scenario_names[4], sep = "_")])/df2$ISS[df2$scenario==paste("N20", scenario_names[4], sep = "_")],
+                    type = scenario_names[4],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[4])+2))) -> df3.4
+
+## 5
+df2[grep(scenario_names[5], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario==paste("N20", scenario_names[5], sep = "_")])/df2$ISS[df2$scenario==paste("N20", scenario_names[5], sep = "_")],
+                    type = scenario_names[5],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[5])+2))) -> df3.5
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::bind_rows(df3.4) %>% 
+  tidytable::bind_rows(df3.5) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.3.a
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+df4 %>% 
+  tidytable::filter(scenario %in% c("N5", "N10", "N15")) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+
+```
+
+### Samples VS Trip/Haul TAKE 2: relative to unbiased control. Boxplots Together 1999-2023
+```{r, fig.width=8}
+
+out_25.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_25.1_ISS_200_iters_2025-01-03.RDS")
+
+year = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$YEAR
+
+df = tidytable(year = year,
+               N1_H0.5_T0.5 = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$iss,
+               N5_H0.5_T0.5 = out_25.1$samples_5$haul_0.5_trip_0.5$length$iss$iss,
+               N10_H0.5_T0.5 = out_25.1$samples_10$haul_0.5_trip_0.5$length$iss$iss,
+               N15_H0.5_T0.5 = out_25.1$samples_15$haul_0.5_trip_0.5$length$iss$iss,
+               N20_H0.5_T0.5 = out_25.1$samples_20$haul_0.5_trip_0.5$length$iss$iss,
+               N25_H0.5_T0.5 = out_25.1$samples_25$haul_0.5_trip_0.5$length$iss$iss,
+               N30_H0.5_T0.5 = out_25.1$samples_30$haul_0.5_trip_0.5$length$iss$iss,
+               N35_H0.5_T0.5 = out_25.1$samples_35$haul_0.5_trip_0.5$length$iss$iss,
+
+               N1_H0.5_T0.75 = out_25.1$samples_1$haul_0.5_trip_0.75$length$iss$iss,
+               N5_H0.5_T0.75 = out_25.1$samples_5$haul_0.5_trip_0.75$length$iss$iss,
+               N10_H0.5_T0.75 = out_25.1$samples_10$haul_0.5_trip_0.75$length$iss$iss,
+               N15_H0.5_T0.75 = out_25.1$samples_15$haul_0.5_trip_0.75$length$iss$iss,
+               N20_H0.5_T0.75 = out_25.1$samples_20$haul_0.5_trip_0.75$length$iss$iss,
+               N25_H0.5_T0.75 = out_25.1$samples_25$haul_0.5_trip_0.75$length$iss$iss,
+               N30_H0.5_T0.75 = out_25.1$samples_30$haul_0.5_trip_0.75$length$iss$iss,
+               N35_H0.5_T0.75 = out_25.1$samples_35$haul_0.5_trip_0.75$length$iss$iss,
+
+               N1_H0.75_T0.5 = out_25.1$samples_1$haul_0.75_trip_0.5$length$iss$iss,
+               N5_H0.75_T0.5 = out_25.1$samples_5$haul_0.75_trip_0.5$length$iss$iss,
+               N10_H0.75_T0.5 = out_25.1$samples_10$haul_0.75_trip_0.5$length$iss$iss,
+               N15_H0.75_T0.5 = out_25.1$samples_15$haul_0.75_trip_0.5$length$iss$iss,
+               N20_H0.75_T0.5 = out_25.1$samples_20$haul_0.75_trip_0.5$length$iss$iss,
+               N25_H0.75_T0.5 = out_25.1$samples_25$haul_0.75_trip_0.5$length$iss$iss,
+               N30_H0.75_T0.5 = out_25.1$samples_30$haul_0.75_trip_0.5$length$iss$iss,
+               N35_H0.75_T0.5 = out_25.1$samples_35$haul_0.75_trip_0.5$length$iss$iss,
+
+               N1_H0.75_T0.75 = out_25.1$samples_1$haul_0.75_trip_0.75$length$iss$iss,
+               N5_H0.75_T0.75 = out_25.1$samples_5$haul_0.75_trip_0.75$length$iss$iss,
+               N10_H0.75_T0.75 = out_25.1$samples_10$haul_0.75_trip_0.75$length$iss$iss,
+               N15_H0.75_T0.75 = out_25.1$samples_15$haul_0.75_trip_0.75$length$iss$iss,
+               N20_H0.75_T0.75 = out_25.1$samples_20$haul_0.75_trip_0.75$length$iss$iss,
+               N25_H0.75_T0.75 = out_25.1$samples_25$haul_0.75_trip_0.75$length$iss$iss,
+               N30_H0.75_T0.75 = out_25.1$samples_30$haul_0.75_trip_0.75$length$iss$iss,
+               N35_H0.75_T0.75 = out_25.1$samples_35$haul_0.75_trip_0.75$length$iss$iss,
+
+               N1_H1.25_T0.5 = out_25.1$samples_1$haul_1.25_trip_0.5$length$iss$iss,
+               N5_H1.25_T0.5 = out_25.1$samples_5$haul_1.25_trip_0.5$length$iss$iss,
+               N10_H1.25_T0.5 = out_25.1$samples_10$haul_1.25_trip_0.5$length$iss$iss,
+               N15_H1.25_T0.5 = out_25.1$samples_15$haul_1.25_trip_0.5$length$iss$iss,
+               N20_H1.25_T0.5 = out_25.1$samples_20$haul_1.25_trip_0.5$length$iss$iss,
+               N25_H1.25_T0.5 = out_25.1$samples_25$haul_1.25_trip_0.5$length$iss$iss,
+               N30_H1.25_T0.5 = out_25.1$samples_30$haul_1.25_trip_0.5$length$iss$iss,
+               N35_H1.25_T0.5 = out_25.1$samples_35$haul_1.25_trip_0.5$length$iss$iss,
+
+               N1_H1.25_T0.75 = out_25.1$samples_1$haul_1.25_trip_0.75$length$iss$iss,
+               N5_H1.25_T0.75 = out_25.1$samples_5$haul_1.25_trip_0.75$length$iss$iss,
+               N10_H1.25_T0.75 = out_25.1$samples_10$haul_1.25_trip_0.75$length$iss$iss,
+               N15_H1.25_T0.75 = out_25.1$samples_15$haul_1.25_trip_0.75$length$iss$iss,
+               N20_H1.25_T0.75 = out_25.1$samples_20$haul_1.25_trip_0.75$length$iss$iss,
+               N25_H1.25_T0.75 = out_25.1$samples_25$haul_1.25_trip_0.75$length$iss$iss,
+               N30_H1.25_T0.75 = out_25.1$samples_30$haul_1.25_trip_0.75$length$iss$iss,
+               N35_H1.25_T0.75 = out_25.1$samples_35$haul_1.25_trip_0.75$length$iss$iss,
+
+               N1_H1.0_T1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_H1.0_T1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_H1.0_T1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_H1.0_T1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_H1.0_T1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_H1.0_T1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_H1.0_T1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_H1.0_T1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+scenario_names = c("H0.5_T0.5", "H0.5_T0.75", "H0.75_T0.5", "H0.75_T0.75", "H1.25_T0.5", "H1.25_T0.75", "H1.0_T1.0")
+scenario_names.short = c("0.5/0.5", "0.5/0.75", "0.75/0.5", "0.75/0.75", "1.25/0.5", "1.25/0.75", "1.0/1.0")
+
+## 1
+df2[grep(scenario_names[1], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[1],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[1])+2))) -> df3.1
+
+## 2
+df2[grep(scenario_names[2], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[2],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[2])+2))) -> df3.2
+
+## 3
+df2[grep(scenario_names[3], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[3],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[3])+2))) -> df3.3
+
+## 4
+df2[grep(scenario_names[4], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[4],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[4])+2))) -> df3.4
+
+## 5
+df2[grep(scenario_names[5], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[5],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[5])+2))) -> df3.5
+
+## 6
+df2[grep(scenario_names[6], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[6],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[6])+2))) -> df3.6
+
+## 7
+df2[grep(scenario_names[7], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[7],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[7])+2))) -> df3.7
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::bind_rows(df3.4) %>% 
+  tidytable::bind_rows(df3.5) %>% 
+  tidytable::bind_rows(df3.6) %>% 
+  tidytable::bind_rows(df3.7) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.3.b
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+df4 %>% 
+  tidytable::filter(scenario %in% c("N5", "N10", "N15")) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+
+```
+
+# Figure 7 Boxplots
+Trip and Haul over sample size.
+Trip first Haul second.
+1999-2023.
+Plot A includes scenarios relative to themselves at different sample sizes
+Plot B includes scenarios relative to the standard scenario at different sample sizes.
+
+```{r}
+df4.2.a %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.9)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120))
+
+df4.global = list(df4.2.a, df4.2.b, df4.1.a, df4.1.b, df4.3.a, df4.3.b)
+df4.global[[1]] %>% tidytable::mutate(label1 = "Trip", label2 = "A") %>% 
+  tidytable::bind_rows(df4.global[[2]] %>% tidytable::mutate(label1 = "Trip", label2 = "B")) %>% 
+  tidytable::bind_rows(df4.global[[3]] %>% tidytable::mutate(label1 = "Haul", label2 = "A")) %>% 
+  tidytable::bind_rows(df4.global[[4]] %>% tidytable::mutate(label1 = "Haul", label2 = "B")) %>% 
+  tidytable::bind_rows(df4.global[[5]] %>% tidytable::mutate(label1 = "Trip/Haul", label2 = "A")) %>% 
+  tidytable::bind_rows(df4.global[[6]] %>% tidytable::mutate(label1 = "Trip/Haul", label2 = "B")) -> df4.global2
+
+df4.global2 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  # theme(legend.position = c(0.5, 0.9)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20)) + 
+  facet_grid(label1 ~ label2)
+
+# only 3: relative to standard, get rid of 0.5 trip and haul, and mayhaps some trip/haul combos
+
+df4.global[[1]] %>% tidytable::mutate(label1 = "Trip", label2 = "A") %>% 
+  tidytable::bind_rows(df4.global[[3]] %>% tidytable::mutate(label1 = "Haul", label2 = "A")) %>% 
+  tidytable::bind_rows(df4.global[[5]] %>% tidytable::mutate(label1 = "Trip/Haul", label2 = "A")) -> df4.global2
+
+df4.global2 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.9)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20)) + 
+  facet_grid(rows = vars(label1))
+```
+
+## Take Two
+
+```{r, fig.height=12}
+p1 = df4.2.a %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.3)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20)) +
+  guides(fill=guide_legend(title="Trips"))
+
+p2 = df4.1.a %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.3)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20)) +
+  guides(fill=guide_legend(title="Hauls"))
+
+p3 = df4.3.a %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Number of Samples", y = "ISSB % Difference") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.3)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20)) +
+  guides(fill=guide_legend(title="Hauls/Trips"))
+
+p1 + p2 + p3 + plot_layout(ncol = 1)
+
+```
+
+```{r, fig.height=12}
+p1 = df4.2.b %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.3)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20)) +
+  guides(fill=guide_legend(title="Trips"))
+
+p2 = df4.1.b %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.3)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20)) +
+  guides(fill=guide_legend(title="Hauls"))
+
+p3 = df4.3.b %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Number of Samples", y = "ISSB % Difference") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.3)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20)) +
+  guides(fill=guide_legend(title="Hauls/Trips"))
+
+p1 + p2 + p3 + plot_layout(ncol = 1)
+
+```
+
+```{r, fig.height=12, fig.width=10}
+p1 = df4.2.b %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "A") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Trips",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))
+
+p2 = df4.1.b %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "B") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Hauls",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))
+
+p3 = df4.3.b %>% 
+  tidytable::mutate(scenario = factor(str_sub(scenario, start = 2, end = -1))) %>% 
+  tidytable::filter(type %in% scenario_names.short[c(2,4,5,6,7)]) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Samples per Haul", y = "ISSB % Difference", tag = "C") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Hauls/Trips",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))
+
+p1 + plot_spacer() + p2 + plot_spacer() + p3 + plot_layout(ncol = 1,
+                           heights = c(6, -.5, 6, -.5, 6))
 
@@
 ```{r}
-out_19.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_19.1_ISS_200_iters_2024-12-17.RDS")
-
-out_20.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_20.1_ISS_200_iters_2024-12-17.RDS")
+out_19.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_19.1_ISS_200_iters_2024-12-18.RDS")
+
+out_20.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_20.1_ISS_200_iters_2024-12-19.RDS")
 
@@
 
-proportion_global = c(0.50, 1.50)
-expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
-expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
-
-samples_global = c(10, 20, 30)
-expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
-expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
-
-```
-
-COME BACK TO THIS! NEED TO RERUN WITH REGULAR HAUL AND TRIP NUMBERS!
-### With sampling strata
+```
+
+### Trip
+
 ```{r, fig.width=9, fig.height=5}
@@
                N0.5_Enone = out_19.1$proportion_0.5$expansion_NULL$length$iss$iss,
-               N1.0_Enone = out_2.1.1$samples_20$expansion_NULL$length$iss$iss,
-               N30_Enone = out_2.1.1$samples_30$expansion_NULL$length$iss$iss,
-               N10_Emedium = out_2.1.1$samples_10$expansion_haul_numbers$length$iss$iss,
-               N20_Emedium = out_2.1.1$samples_20$expansion_haul_numbers$length$iss$iss,
-               N30_Emedium = out_2.1.1$samples_30$expansion_haul_numbers$length$iss$iss,
-               N10_Efull = out_2.1.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
-               N20_Efull = out_2.1.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
-               N30_Efull = out_2.1.1$samples_30$expansion_haul_month_numbers$length$iss$iss,)
+               N1.0_Enone = out_19.1$proportion_1$expansion_NULL$length$iss$iss,
+               N1.5_Enone = out_19.1$proportion_1.5$expansion_NULL$length$iss$iss,
+               N0.5_Emedium = out_19.1$proportion_0.5$expansion_haul_numbers$length$iss$iss,
+               N1.0_Emedium = out_19.1$proportion_1$expansion_haul_numbers$length$iss$iss,
+               N1.5_Emedium = out_19.1$proportion_1.5$expansion_haul_numbers$length$iss$iss,
+               N0.5_Efull = out_19.1$proportion_0.5$expansion_haul_month_numbers$length$iss$iss,
+               N1.0_Efull = out_19.1$proportion_1$expansion_haul_month_numbers$length$iss$iss,
+               N1.5_Efull = out_19.1$proportion_1.5$expansion_haul_month_numbers$length$iss$iss,)
 
@@
 ```
+
+### Haul
+
+```{r, fig.width=9, fig.height=5}
+df = tidytable(year = year,
+               N0.5_Enone = out_20.1$proportion_0.5$expansion_NULL$length$iss$iss,
+               N1.0_Enone = out_20.1$proportion_1$expansion_NULL$length$iss$iss,
+               N1.5_Enone = out_20.1$proportion_1.5$expansion_NULL$length$iss$iss,
+               N0.5_Emedium = out_20.1$proportion_0.5$expansion_haul_numbers$length$iss$iss,
+               N1.0_Emedium = out_20.1$proportion_1$expansion_haul_numbers$length$iss$iss,
+               N1.5_Emedium = out_20.1$proportion_1.5$expansion_haul_numbers$length$iss$iss,
+               N0.5_Efull = out_20.1$proportion_0.5$expansion_haul_month_numbers$length$iss$iss,
+               N1.0_Efull = out_20.1$proportion_1$expansion_haul_month_numbers$length$iss$iss,
+               N1.5_Efull = out_20.1$proportion_1.5$expansion_haul_month_numbers$length$iss$iss,)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+  geom_line() +
+  labs(x = "", y = "ISSB") +
+  geom_point() + 
+  theme_classic() +
+  theme(legend.position = c(0.84, 0.8),
+        axis.title.x = element_blank())
+```
+
+## Correlation Plots
+
+Can I calculate the intra-haul correlation between samples and plot that against sample size for average over the sampling years?
+
+I would have to sample with replacement lengths at every sample size and save them then corr() them, or save the corr() for every iteration, or save the average corr() over all iterations - then I could average over years to come up with either a boxplot or line plot.
+
+```{r}
+
+```

### 2025-01-22 run/paper_runs/paper_scenario_22.1.R

@@ -1,0 +1,63 @@
+
+rm(list = ls())
+run_name = "paper_scenario_22.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 200
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(expansion_global)){
+
+    samples = samples_global[i]
+    expansion = expansion_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = NULL, amount = samples),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = expansion) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("expansion_", expansion_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-01-22 run/paper_runs/paper_scenario_24.1.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_24.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 200
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N =list(type = "proportion", amount = .proportion),
+                new_length_N = list(type = "value", bound = NULL, amount = samples),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("trip_", proportion_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-01-22 run/paper_runs/paper_scenario_25.1.R

@@ -1,0 +1,66 @@
+
+rm(list = ls())
+run_name = "paper_scenario_25.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 200
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+# proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+proportion_global = list(haul = c(.5, .5, .75, .75, 1.25, 1.25), trip = c(.5, .75, .5, .75, .5, .75))
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global$haul)){
+
+    samples = samples_global[i]
+    .proportion_haul = proportion_global$haul[j]
+    .proportion_trip = proportion_global$trip[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = list(type = "proportion", amount = .proportion_trip),
+                new_haul_N = list(type = "proportion", amount = .proportion_haul),
+                new_length_N = list(type = "value", bound = NULL, amount = samples),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0(paste0("haul_", proportion_global$haul)[j], "_", paste0("trip_", proportion_global$trip)[j])]] = .output
+
+  }
+}
+
[…]

### 2025-02-08 Rmd/paper_plots/paper_plots_1.1.Rmd
run some updated scenarios

@@
 
-out_2.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.1_ISS_100iters_output_2024-11-25.RDS")
+out_1.3 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.3_ISS_100iters_output_2025-01-22.RDS")
+
+out_1.4 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.4_ISS_1000iters_output_2025-01-23.RDS")
+
+out_2.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.2_ISS_500iters_output_2025-01-28.RDS")
 
@@
 
-out_4.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_4.1_ISS_100iters_output_2024-11-26.RDS")
-
-out_5.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_5.1_ISS_100iters_output_2024-11-26.RDS")
+out_4.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_4.2_ISS_500iters_output_2025-01-28.RDS")
+
+out_5.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_5.2_ISS_500iters_output_2025-01-27.RDS")
 
@@
 out_8.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_8.1_ISS_100iters_output_2024-11-26.RDS")
-out_9.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_9.1_ISS_100iters_output_2024-12-04.RDS")
+out_9.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_9.2_ISS_500iters_output_2025-01-27.RDS")
 out_10.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_10.1_ISS_100iters_output_2024-12-04.RDS")
@@
 
+### * All together 2 panel
+
+```{r, fig.height=6}
+df = data.frame(rss = out_1.4$length$rss$rss, year = as.factor(out_1.4$length$rss$YEAR))
+
+# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
+# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
+par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
+plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
+lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
+lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "red")
+legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))
+
+plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3)
+
+```
+
 ### All together TRIPS TOO 4 panel
@@
 
+### All together TRIPS TOO 4 panel sample rate by HAUL on bottom
+
+```{r, fig.height=8}
+df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))
+
+# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
+# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
+par(mfrow = c(4,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
+plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000)) 
+lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
+lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
+# lines(out_1.2$length$iss$YEAR, out_1.2$length$iss$ntps, col = "green")
+legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))
+
+plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$ntps, type = "l", ylab = "number of trips", xlab = "", cex.lab = 1.3, xaxt = "n")
+plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")
+
+# plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3)
+out_1.4$length$freq_data_frame %>% 
+  tidytable::summarise(samples_per_haul = unique(YAGMH_SFREQ), .by = c(YEAR, HAUL_JOIN)) %>% 
+  tidytable::mutate(YEAR = as.factor(YEAR)) -> df.SpH
+
+df.SpH %>% 
+  tidytable::summarise(samples_per_haul_median = median(samples_per_haul), .by = c(YEAR)) %>% 
+  tidytable::mutate(YEAR = as.numeric(as.character(YEAR))) -> df.SpH.median
+
+# boxplot
+# plot(df.SpH$YEAR, df.SpH$samples_per_haul, ylab = "Samples per Haul", cex.lab = 1.3, ylim = c(0, 400))
+
+# median
+plot(df.SpH.median$YEAR, df.SpH.median$samples_per_haul_median, type = "l", ylab = "Haul sample rate", cex.lab = 1.3)
+
+```
+
+\newpage
+
+### 1999 and 2000 histograms
+```{r, fig.height=8, fig.width=9}
+# out_1.4$length$og_props %>% 
+#   tidytable::filter(YEAR %in% 1999:2000) %>% 
+#   tidytable::mutate(YEAR = as.factor(YEAR)) -> props.sub
+# 
+# ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = YEAR)) +
+#   geom_line() +
+#   geom_area(aes(fill = YEAR, group = YEAR), alpha = 0.5, position = "identity") +
+#   theme_classic() +
+#   theme(legend.position = c(0.8, 0.8)) +
+#   scale_x_continuous(limits = c(25, 110)) +
+#   labs(x = "Length", y = "Frequency")
+
+out_1.4$length$og_props %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
+  geom_line() +
+  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  scale_x_continuous(limits = c(22, 108),
+                     n.breaks = 9) +
+  labs(x = "Length (cm)", y = "Frequency", tag = "A") +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  scale_y_continuous(limits = c(0, .04), expand = c(0, 0))
+
+# now do RSS
+out_1.4$length$rss %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+# violin plot
+p2 = ggplot(props.sub, aes(x = rss, y = Year, fill = Year)) +
+  geom_violin() +
+  theme_classic() +
+  stat_summary(fun.y = median, geom = "point", color = "black") +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Year", tag = "B")
+
+p1 / p2
+```
+
+\newpage
+
+#### * Histograms
+
+\newpage
+
+```{r, fig.height=8, fig.width=9}
+# 
+# 
+# ggplot(props.sub, aes(rss, fill = YEAR)) +
+#   geom_histogram(binwidth = 500)
+# 
+# ggplot(props.sub, aes(rss, colour = YEAR)) +
+#   geom_histogram(aes(fill = YEAR, group = YEAR), alpha = 0.5)
+#
+
+p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "B") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_1.4$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 300), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000))
+
+p1 / p3
+
+# +
+#   scale_x_continuous(limits = c(22, 108)) +
+#   labs(x = "Length", y = "Frequency")
+
+```
+
+The comparison shows that fish in 2003 were less similar in length compared to 2004.
+2003 corresponds to a higher ISS even though the sample rate was the same and the number of hauls and nominal sample size were comparable.
+More of the fish sampled in 2003 were required for characterizing the underlying multinomial sampling distribution compared to 2004 because more lengths were represented at a higher rate in 2003 (shorter, wider distribution).
+This is reflected in the RSS (ref figure).
+
+### Simulate Multinomials
+```{r}
+
+# rmultinom(1, size = 20, prob = out_1.4$length$og_props[YEAR==2003, c(og_FREQ)])[,1] %>% 
+#   hist()
+
+multinom_var = function(n, p) n*p*(1-p)
+
+multinom_var(30, c(.3,.35)) %>% sum()
+multinom_var(60, c(.3,.35)) %>% sum()
+
+```
+
+### Plot new number of hauls vs old
+
+```{r, eval=F}
+
+plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
+lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "blue")
+
+plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, col = "red")
+lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, col = "blue")
+
+plot(out_1.2$length$iss$YEAR, out_1.2$length$iss$ntps, col = "red")
+lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$ntps, col = "blue")
+
+out_1.2$length$iss$ntps-out_1.4$length$iss$ntps
+
+```
+
+###
+
 #### Inspect R-squared
@@
 
-#### reorder long
+#### * reorder long
 
@@
 
-```{r, fig.height=6}
+```{r, fig.height=5.5}
 sub_range = out_5.1$length$iss$YEAR %in% 1977:2023
@@
 # lines(out_8.1$length$iss$YEAR[sub_range], out_8.1$length$iss$iss[sub_range], type = "l", col = "green") 
-lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")
-
-legend("topleft", legend = c("boot length", "boot length + boot haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
+lines(out_1.4$length$iss$YEAR[sub_range], out_1.4$length$iss$iss[sub_range], type = "l", col = "red")
+
+legend("topleft", legend = c("boot length", "boot length + boot haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"), bty = "n")
 ```
@@
 \newpage
+
+##### * Inspect 2000, 2001 for expansion drop
+```{r}
+out_1.4$length$freq_data_frame %>% 
+  tidytable::filter(YEAR %in% 2000:2001) %>% 
+  tidytable::summarise(YAGMH = unique(YAGMH_SNUM), .by = YEAR) %>% 
+  tidytable::mutate(YEAR = as.factor(YEAR)) -> temp1
+
+ggplot(data = temp1, aes(x = YAGMH, colour = YEAR)) +
+  geom_histogram(aes(fill = YEAR, group = YEAR), alpha = 0.5, position = "identity") +
+  theme_classic()
+
+out_1.4$length$freq_data_frame %>% 
+  tidytable::filter(YEAR %in% 2000:2001) %>% 
+  tidytable::summarise(YAGM = unique(YAGM_SNUM), .by = YEAR) %>% 
+  tidytable::mutate(YEAR = as.factor(YEAR)) -> temp2
+
+ggplot(data = temp2, aes(x = YAGM, colour = YEAR)) +
+  geom_histogram(aes(fill = YEAR, group = YEAR), alpha = 0.5, position = "identity") +
+  theme_classic()
+
+# inspect huge weighted YAGM over 30,000,000
+out_1.4$length$freq_data_frame %>% 
+  tidytable::filter(YAGM_SNUM>10000000, YEAR%in%2000:2001) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> temp3
+
+temp3 %>% 
+  ggplot(aes(x = LENGTH, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  scale_x_continuous(limits = c(30, 115))
+
+# maybe gear is responsible: check big AGM category to see if many more fish were caught with trawl net in 2000?
+
+# wait, it should be the combined weight right? so which WEIGHT is that from the expansion? Is it saved in the output?
+
+```
 
@@
 
-out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.1_ISS_200_iters_2024-12-12.RDS")
+# out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.1_ISS_200_iters_2024-12-12.RDS")
+out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.2_ISS_200_iters_2025-02-01.RDS")
 
@@
                N_0.75 = out_18.1$proportion_0.75$type_trip$length$iss$iss,
-               N_1.00 = out_1.1$length$iss$iss,
+               N_1.00 = out_1.4$length$iss$iss,
                N_1.25 = out_18.1$proportion_1.25$type_trip$length$iss$iss,
@@
 df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+df2.trip = df2
 
@@
                N_0.75 = out_18.1$proportion_0.75$type_haul$length$iss$iss,
-               N_1.00 = out_1.1$length$iss$iss,
+               N_1.00 = out_1.4$length$iss$iss,
                N_1.25 = out_18.1$proportion_1.25$type_haul$length$iss$iss,
@@
 df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+df2.haul = df2
 
@@
 
-### Boxplots Together 1977-2023
+### * Boxplots Together 1977-2023
 ```{r, fig.width=8}
@@
   geom_boxplot(aes(fill = type)) +
-  labs(x = "Scenario", y = "ISSB % Error") +
+  labs(x = "Proportional Change", y = "ISSB % Difference") +
   theme_classic() +
@@
   geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
-  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120))
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120)) +
+  scale_x_discrete(labels = c("0.25", "0.50", "0.75", "1.00", "1.25", "1.50", "1.75", "2.00"))
 
@@
 df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.9)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120))
+
+```
+
+#### Boxplots Together 1999-2023 TAKE TWO. fix mistake? NO ITS THE SAME AS ABOVE
+```{r}
+df2.trip %>% 
+  tidytable::filter(year %in% 1999:2023) -> df2.trip
+df2.trip %>% 
+  tidytable::mutate(ISS.diff = (df2.trip$ISS[df2.trip$scenario=="N_1.00"]) - ISS,
+                    ISS.error = (ISS - df2.trip$ISS[df2.trip$scenario=="N_1.00"])/df2.trip$ISS[df2.trip$scenario=="N_1.00"],
+                    type = "trip",
+                    .by = scenario) -> df3.1.trip
+df2.haul %>% 
+  tidytable::filter(year %in% 1999:2023) -> df2.haul
+df2.haul %>% 
+  tidytable::mutate(ISS.diff = (df2.haul$ISS[df2.haul$scenario=="N_1.00"]) - ISS,
+                    ISS.error = (ISS - df2.haul$ISS[df2.haul$scenario=="N_1.00"])/df2.haul$ISS[df2.haul$scenario=="N_1.00"],
+                    type = "haul",
+                    .by = scenario) -> df3.2.haul
+df3.1.trip %>% 
+  tidytable::bind_rows(df3.2.haul) -> df4.2
+
+df4.2 %>% 
   ggplot(aes(x = scenario, y = ISS.error*100)) +
@@
 
-### Samples VS Expantion. Boxplots Together 1999-2023
+### * Samples VS Expantion. Boxplots Together 1999-2023
 ```{r, fig.width=8}
 
-out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_22.1_ISS_200_iters_2024-12-25.RDS")
+# out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_22.1_ISS_200_iters_2024-12-25.RDS")
+out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_22.2_ISS_500_iters_2025-02-01.RDS")
 
@@
   geom_boxplot(aes(fill = type)) +
-  labs(x = "Scenario", y = "ISSB % Error") +
+  labs(x = "Samples per Haul", y = "ISSB % Difference") +
   theme_classic() +
@@
   geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
-  scale_y_continuous(breaks = seq(-100, 120, by = 10))
+  scale_y_continuous(breaks = seq(-100, 120, by = 10)) +
+  scale_x_discrete(labels = c("1", "5", "10", "15", "20", "25", "30", "35"))
 
@@
 
+## * 3 Panel
+
 ```{r, fig.height=12, fig.width=10}
@@
 
-### With sampling strata
+### * With sampling strata
 ```{r, fig.width=9, fig.height=5}

### 2025-02-08 Rmd/paper_plots/paper_plots_1.2.Rmd
run some updated scenarios

--- 2024-12-18 Rmd/paper_plots/paper_plots_1.1.Rmd
@@
 
-1.
-Time series of new ISS vs old.
-Accompanied by number of hauls, nominal sample size, and possibly RSS boxplots.
-RSS boxplots may help justify focusing in on 20 sample size meidan for later plots to get an apples to apples, granular test of impact of sample size and expansion complexity.
+## Data
+```{r}
 
-2. ISS full, ISS without expansion, ISS without sampling strata, ISS without either.
+out_1.4 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.4_ISS_1000iters_output_2025-01-23.RDS")
 
-3. 3x3 grid: sample size 10, 20, 30 fixed X expansion none, haul only, haul+month. With sampling strata.
+out_5.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_5.2_ISS_500iters_output_2025-01-27.RDS")
 
-3.supp.1: same as above but without sampling strata. 
-3.supp.2: same as above but without bootstrapping trip. 
-3.supp.3: same as above but without either.
+out_9.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_9.2_ISS_500iters_output_2025-01-27.RDS")
 
-## Plot 1.1
-```{r}
-out_1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.1_ISS_100iters_output_2024-11-25.RDS")
+out_4.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_4.2_ISS_500iters_output_2025-01-28.RDS")
 
-out_2.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.1_ISS_100iters_output_2024-11-25.RDS")
-
-out_3.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_3.1_ISS_100iters_output_2024-11-26.RDS")
-
-out_4.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_4.1_ISS_100iters_output_2024-11-26.RDS")
-
-out_5.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_5.1_ISS_100iters_output_2024-11-26.RDS")
-
-out_6.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_6.1_ISS_100iters_output_2024-11-26.RDS")
-out_7.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_7.1_ISS_100iters_output_2024-11-26.RDS")
-out_8.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_8.1_ISS_100iters_output_2024-11-26.RDS")
-out_9.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_9.1_ISS_100iters_output_2024-12-04.RDS")
-out_10.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_10.1_ISS_100iters_output_2024-12-04.RDS")
-out_11.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_11.1_ISS_100iters_output_2024-12-04.RDS")
-out_12.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_12.1_ISS_100iters_output_2024-12-10.RDS")
-out_13.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_13.1_ISS_100iters_output_2024-12-10.RDS")
-out_14.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_14.1_ISS_100iters_output_2024-12-10.RDS")
-out_15.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_15.1_ISS_100iters_output_2024-12-10.RDS")
-out_16.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_16.1_ISS_100iters_output_2024-12-11.RDS")
-out_17.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_17.1_ISS_100iters_output_2024-12-11.RDS")
+out_2.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.2_ISS_500iters_output_2025-01-28.RDS")
 
@@
 
-### baseISS with assessment ISS
+## ISSB Results 
+### * Time series 2 panel
 
-```{r}
-par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
-plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out_1.1$length$iss$iss)*1.1), col = "blue") 
-lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "black")
-legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("2023 assessment", "baseISS"))
-
-```
-
-### All together 4 panel
-
-```{r, fig.height=8}
-df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))
-
-# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
-par(mfrow = c(4,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
-plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n") 
-lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
-legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("2023 assessment", "baseISS"))
-
-plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, type = "l", ylab = "number of hauls", xlab = "", col = "black", cex.lab = 1.3, xaxt = "n")
-
-plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")
-
-plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3, xlab = "year")
-
-```
-
-### All together 3 panel
-
-```{r, fig.height=8}
-df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))
+```{r, fig.height=6}
+df = data.frame(rss = out_1.4$length$rss$rss, year = as.factor(out_1.4$length$rss$YEAR))
 
@@
 # par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
-par(mfrow = c(3,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
-plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000)) 
+par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
+plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
 lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
-lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
+lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "red")
 legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))
 
-plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")
+plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3)
 
-plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3)
-
-```
-
-#### Inspect R-squared
-Fit models to number of hauls.
-
-```{r}
-# baseISS ~ # hauls
-fit1 = lm(out_1.1$length$iss$iss ~ out_1.1$length$iss$nhls)
-summary(fit1)
-
-# assessment ISS ~ # hauls
-fit2 = lm(assessment_2023_iss$iss ~ out_1.1$length$iss$nhls)
-summary(fit2)
-
-# baseISS ~ assessment ISS
-fit3 = lm(out_1.1$length$iss$iss ~ assessment_2023_iss$iss)
-summary(fit3)
-
-```
-
-## Plot 2.1 
-Deconstruct the contributors to baseISS
-
-### All together 1
-
-Subtracting things from baseISS
-
-```{r, fig.height=8}
-
-# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
-par(mfrow = c(5,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
-plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "baseISS", xaxt = "n") 
-plot(out_2.1$length$iss$YEAR, out_2.1$length$iss$iss, type = "l", ylab = "baseISS - E", xaxt = "n") 
-plot(out_3.1$length$iss$YEAR, out_3.1$length$iss$iss, type = "l", ylab = "baseISS - SS", xaxt = "n") 
-plot(out_4.1$length$iss$YEAR, out_4.1$length$iss$iss, type = "l", ylab = "baseISS - (E,SS)", xaxt = "n") 
-plot(out_5.1$length$iss$YEAR, out_5.1$length$iss$iss, type = "l", ylab = "baseISS - (E,SS,Bs)", cex.lab = 1.3, xlab = "year") 
-```
-
-### All together 2
-
-Adding things to baseISS
-
-```{r, fig.height=6}
-par(mfrow = c(1,1))
-
-plot(out_5.1$length$iss$YEAR, out_5.1$length$iss$iss, type = "l", ylab = "ISS", cex.lab = 1.3, col = "black")
-lines(out_6.1$length$iss$YEAR, out_6.1$length$iss$iss, type = "l", col = "blue") 
-lines(out_7.1$length$iss$YEAR, out_7.1$length$iss$iss, type = "l", col = "orange") 
-lines(out_8.1$length$iss$YEAR, out_8.1$length$iss$iss, type = "l", col = "green") 
-lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", col = "red")
-
-legend("topleft", legend = c("-E,SS,Bs", "-SS,Bs", "-Bs", "-SS", "-0"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
-```
-
-#### sub range 1
-```{r, fig.height=6}
-sub_range = out_5.1$length$iss$YEAR %in% 1999:2023
-
-par(mfrow = c(1,1))
-plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000))
-lines(out_6.1$length$iss$YEAR[sub_range], out_6.1$length$iss$iss[sub_range], type = "l", col = "blue") 
-lines(out_7.1$length$iss$YEAR[sub_range], out_7.1$length$iss$iss[sub_range], type = "l", col = "orange") 
-lines(out_8.1$length$iss$YEAR[sub_range], out_8.1$length$iss$iss[sub_range], type = "l", col = "green") 
-lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")
-
-legend("topright", legend = c("boot length", "boot length and expand", "boot length, expand, sampling strata weighting", "boot length, expand, boot trip+haul", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
-```
-
-#### reorder long
-
-\newpage
-
-```{r, fig.height=6}
-sub_range = out_5.1$length$iss$YEAR %in% 1977:2023
-
-par(mfrow = c(1,1))
-plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISSB", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
-lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
-lines(out_4.1$length$iss$YEAR[sub_range], out_4.1$length$iss$iss[sub_range], type = "l", col = "orange") 
-lines(out_2.1$length$iss$YEAR[sub_range], out_2.1$length$iss$iss[sub_range], type = "l", col = "green")
-# lines(out_8.1$length$iss$YEAR[sub_range], out_8.1$length$iss$iss[sub_range], type = "l", col = "green") 
-lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")
-
-legend("topleft", legend = c("boot length", "boot length + boot haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
 ```
@@
 
-#### reorder short
+### * 2003 and 2004 histograms
+```{r, fig.height=8, fig.width=9}
+
+out_1.4$length$og_props %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
+  geom_line() +
+  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  scale_x_continuous(limits = c(22, 108),
+                     n.breaks = 9) +
+  labs(x = "Length (cm)", y = "Frequency", tag = "A") +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  scale_y_continuous(limits = c(0, .04), expand = c(0, 0))
+
+# now do RSS
+out_1.4$length$rss %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "B") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_1.4$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 300), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000))
+
+p1 / p3
+
+```
+
+The comparison shows that fish in 2003 were less similar in length compared to 2004.
+2003 corresponds to a higher ISS even though the sample rate was the same and the number of hauls and nominal sample size were comparable.
+More of the fish sampled in 2003 were required for characterizing the underlying multinomial sampling distribution compared to 2004 because more lengths were represented at a higher rate in 2003 (shorter, wider distribution).
+This is reflected in the RSS (ref figure).
+
+### * Time seris components
 
@@
 
-```{r, fig.height=6}
-sub_range = out_5.1$length$iss$YEAR %in% 1999:2023
+```{r, fig.height=5.5}
+sub_range = out_5.2$length$iss$YEAR %in% 1977:2023
 
 par(mfrow = c(1,1))
-plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISSB", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "")
-lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
-lines(out_4.1$length$iss$YEAR[sub_range], out_4.1$length$iss$iss[sub_range], type = "l", col = "orange") 
-lines(out_2.1$length$iss$YEAR[sub_range], out_2.1$length$iss$iss[sub_range], type = "l", col = "green")
-# lines(out_8.1$length$iss$YEAR[sub_range], out_8.1$length$iss$iss[sub_range], type = "l", col = "green") 
-lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")
+plot(out_5.2$length$iss$YEAR[sub_range], out_5.2$length$iss$iss[sub_range], type = "l", ylab = "ISSB", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
+lines(out_9.2$length$iss$YEAR[sub_range], out_9.2$length$iss$iss[sub_range], type = "l", col = "blue") 
+lines(out_4.2$length$iss$YEAR[sub_range], out_4.2$length$iss$iss[sub_range], type = "l", col = "orange") 
+lines(out_2.2$length$iss$YEAR[sub_range], out_2.2$length$iss$iss[sub_range], type = "l", col = "green")
+lines(out_1.4$length$iss$YEAR[sub_range], out_1.4$length$iss$iss[sub_range], type = "l", col = "red")
 
-legend("topright", legend = c("boot length", "boot length + boot haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
+legend("topleft", legend = c("boot length", "boot length + haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"), bty = "n")
 ```
@@
 
-#### reorder short with half trips and half hauls
-```{r, fig.height=6}
-sub_range = out_5.1$length$iss$YEAR %in% 1998:2023
-
-par(mfrow = c(1,1))
-plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
-lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
-lines(out_4.1$length$iss$YEAR[sub_range], out_4.1$length$iss$iss[sub_range], type = "l", col = "orange") 
-lines(out_12.1$length$iss$YEAR[sub_range], out_12.1$length$iss$iss[sub_range], type = "l", col = "purple")
-lines(out_13.1$length$iss$YEAR[sub_range], out_13.1$length$iss$iss[sub_range], type = "l", col = "brown")
-lines(out_2.1$length$iss$YEAR[sub_range], out_2.1$length$iss$iss[sub_range], type = "l", col = "green")
-lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")
-
-legend("topright", legend = c("boot length", "boot length, haul", "boot all", "boot all, half trips", "boot all, half hauls", "boot all, sampling strata weighting", "full"), lty = c(1,1,1,1,1,1,1), col = c("black", "blue", "orange","purple", "brown", "green", "red"))
-```
-
-#### reorder short 2
-```{r, fig.height=6}
-sub_range = out_5.1$length$iss$YEAR %in% 1998:2023
-
-par(mfrow = c(1,1))
-plot(out_10.1$length$iss$YEAR[sub_range], out_10.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
-lines(out_11.1$length$iss$YEAR[sub_range], out_11.1$length$iss$iss[sub_range], type = "l", col = "blue")
-
-lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")
-
-legend("topright", legend = c("boot.length", "boot.length + boot.haul", "boot.length + boot.haul + boot.trip"), lty = c(1,1,1), col = c("black", "blue", "red"))
-```
-
-#### Full, half trip, half haul
-```{r, fig.height=6}
-sub_range = out_5.1$length$iss$YEAR %in% 1998:2023
-
-par(mfrow = c(1,1))
-plot(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
-lines(out_14.1$length$iss$YEAR[sub_range], out_14.1$length$iss$iss[sub_range], type = "l", col = "blue")
-
-lines(out_15.1$length$iss$YEAR[sub_range], out_15.1$length$iss$iss[sub_range], type = "l", col = "red")
-
-legend("topright", legend = c("Full", "Half Trip", "Half Haul"), lty = c(1,1,1), col = c("black", "blue", "red"))
-```
-
-#### Full, 1.5 trip, 1.5 haul
-```{r, fig.height=6}
-sub_range = out_5.1$length$iss$YEAR %in% 1998:2023
-
-par(mfrow = c(1,1))
-plot(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
-lines(out_16.1$length$iss$YEAR[sub_range], out_16.1$length$iss$iss[sub_range], type = "l", col = "blue")
-
-lines(out_17.1$length$iss$YEAR[sub_range], out_17.1$length$iss$iss[sub_range], type = "l", col = "red")
-
-legend("topright", legend = c("Full", "1.5 Trip", "1.5 Haul"), lty = c(1,1,1), col = c("black", "blue", "red"))
-```
-
-## Plot 7x2 Grid Haul and Trip numbers
-
-### Trip Change
-```{r}
-
-out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.1_ISS_200_iters_2024-12-12.RDS")
-
-year = out_18.1$proportion_0.25$type_trip$length$iss$YEAR
-proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
-type_global = list("trip", "haul")
-type_names_global = c("trip", "haul")
-
-df = tidytable(year = year,
-               N_0.25 = out_18.1$proportion_0.25$type_trip$length$iss$iss,
-               N_0.50 = out_18.1$proportion_0.5$type_trip$length$iss$iss,
-               N_0.75 = out_18.1$proportion_0.75$type_trip$length$iss$iss,
-               N_1.00 = out_1.1$length$iss$iss,
-               N_1.25 = out_18.1$proportion_1.25$type_trip$length$iss$iss,
-               N_1.50 = out_18.1$proportion_1.5$type_trip$length$iss$iss,
-               N_1.75 = out_18.1$proportion_1.75$type_trip$length$iss$iss,
-               N_2.00 = out_18.1$proportion_2$type_trip$length$iss$iss)
-
-df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
-
-ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
-  geom_line() +
-  labs(x = "Year", y = "ISS") +
-  geom_point() +
-  ylim(0, 17000) +
-  xlim(1998, 2023)
-
-```
-
-### Boxplots
-REMEMBER! these are the full year range, may want to narrow it to recent range.
-```{r}
-df2 %>% 
-  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_1.00"]) - ISS,
-                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_1.00"])/df2$ISS[df2$scenario=="N_1.00"],
-                    type = "trip",
-                    .by = scenario) -> df3.1
-
-# plot(df3$scenario, df3$ISS.diff)
-plot(df3.1$scenario, df3.1$ISS.error)
-abline(h = c(-.1,.1), lty = "dashed")
-
-```
-
-### Haul Change
-```{r}
-
-out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.1_ISS_200_iters_2024-12-12.RDS")
-
-year = out_18.1$proportion_0.25$type_trip$length$iss$YEAR
-proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
-type_global = list("trip", "haul")
-type_names_global = c("trip", "haul")
-
-df = tidytable(year = year,
-               N_0.25 = out_18.1$proportion_0.25$type_haul$length$iss$iss,
-               N_0.50 = out_18.1$proportion_0.5$type_haul$length$iss$iss,
-               N_0.75 = out_18.1$proportion_0.75$type_haul$length$iss$iss,
-               N_1.00 = out_1.1$length$iss$iss,
-               N_1.25 = out_18.1$proportion_1.25$type_haul$length$iss$iss,
-               N_1.50 = out_18.1$proportion_1.5$type_haul$length$iss$iss,
-               N_1.75 = out_18.1$proportion_1.75$type_haul$length$iss$iss,
-               N_2.00 = out_18.1$proportion_2$type_haul$length$iss$iss)
-
-df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
-
-ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
-  geom_line() +
-  labs(x = "Year", y = "ISS") +
-  geom_point() +
-  ylim(0, 17000) +
-  xlim(1998, 2023)
-
-```
-
-### Boxplots
-```{r}
-df2 %>% 
-  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_1.00"]) - ISS,
-                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_1.00"])/df2$ISS[df2$scenario=="N_1.00"],
-                    type = "haul",
-                    .by = scenario) -> df3.2
-
-# plot(df3$scenario, df3$ISS.diff)
-plot(df3.2$scenario, df3.2$ISS.error)
-abline(h = c(-.1,.1), lty = "dashed")
-
-```
-
-### Boxplots Together 1977-2023
-```{r, fig.width=8}
-
-df3.1 %>% 
-  tidytable::bind_rows(df3.2) -> df4
-
-df4 %>% 
-  ggplot(aes(x = scenario, y = ISS.error)) +
-  geom_boxplot(aes(fill = type)) +
-  labs(x = "Scenario", y = "ISSB") +
-  theme_classic() +
-  theme(legend.position = c(0.5, 0.9))
-
-```
-
-### Boxplots Together 1999-2023
-```{r}
-
-df3.1 %>% 
-  tidytable::bind_rows(df3.2) %>% 
-  tidytable::filter(year %in% 1999:2023) -> df4
-
-df4 %>% 
-  ggplot(aes(x = scenario, y = ISS.error)) +
-  geom_boxplot(aes(fill = type))
-
-```
-
-## Plot 3.1
-
-3x3 grid.
-
-### Data
-```{r}
-out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.1.1_ISS_200_iters_2024-11-27.RDS")
-
-out_2.2.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.2.1_ISS_200_iters_2024-12-02.RDS")
+## Optimize Sampling
+### * Time series Expansion X Samples 10, 20, 30
+```{r, fig.width=9, fig.height=5}
+out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.1.2_ISS_500_iters_2025-01-28.RDS")
 
@@
 
-samples_global = c(10, 20, 30)
-expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
-expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
-
-```
-
-### With sampling strata
-```{r, fig.width=9, fig.height=5}
 df = tidytable(year = year,
@@
 
-```{r, fig.width=9, fig.height=5}
-# stats
-((df$N10_Enone - df$N20_Enone)/df$N20_Enone) %>%
-  mean()
+### * Samples VS Expantion. Boxplots Together 1999-2023
+```{r, fig.width=8}
 
-((df$N10_Emedium - df$N20_Emedium)/df$N20_Emedium) %>%
-  mean()
+out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_22.2_ISS_500_iters_2025-02-01.RDS")
 
-((df$N10_Efull - df$N20_Efull)/df$N20_Efull) %>%
-  mean()
-(-.02 - .12 - .08)/3
+year = out_22.1$samples_1$expansion_NULL$length$iss$YEAR
 
-((df$N30_Enone - df$N20_Enone)/df$N20_Enone) %>%
-  mean()
+df = tidytable(year = year,
+               N1_Enone = out_22.1$samples_1$expansion_NULL$length$iss$iss,
+               N5_Enone = out_22.1$samples_5$expansion_NULL$length$iss$iss,
+               N10_Enone = out_22.1$samples_10$expansion_NULL$length$iss$iss,
+               N15_Enone = out_22.1$samples_15$expansion_NULL$length$iss$iss,
+               N20_Enone = out_22.1$samples_20$expansion_NULL$length$iss$iss,
+               N25_Enone = out_22.1$samples_25$expansion_NULL$length$iss$iss,
+               N30_Enone = out_22.1$samples_30$expansion_NULL$length$iss$iss,
+               N35_Enone = out_22.1$samples_35$expansion_NULL$length$iss$iss,
+               N1_Emedium = out_22.1$samples_1$expansion_haul_numbers$length$iss$iss,
+               N5_Emedium = out_22.1$samples_5$expansion_haul_numbers$length$iss$iss,
+               N10_Emedium = out_22.1$samples_10$expansion_haul_numbers$length$iss$iss,
+               N15_Emedium = out_22.1$samples_15$expansion_haul_numbers$length$iss$iss,
+               N20_Emedium = out_22.1$samples_20$expansion_haul_numbers$length$iss$iss,
+               N25_Emedium = out_22.1$samples_25$expansion_haul_numbers$length$iss$iss,
+               N30_Emedium = out_22.1$samples_30$expansion_haul_numbers$length$iss$iss,
+               N35_Emedium = out_22.1$samples_35$expansion_haul_numbers$length$iss$iss,
+               N1_Efull = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_Efull = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_Efull = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_Efull = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_Efull = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_Efull = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_Efull = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_Efull = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss)
 
-((df$N30_Emedium - df$N20_Emedium)/df$N20_Emedium) %>%
-  mean()
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
 
-((df$N30_Efull - df$N20_Efull)/df$N20_Efull) %>%
-  mean()
+df2[grep("Enone", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Enone"])/df2$ISS[df2$scenario=="N20_Enone"],
+                    type = "Enone",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1
 
-(.03 + .04 +.03)/3
+df2[grep("Emedium", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Emedium"])/df2$ISS[df2$scenario=="N20_Emedium"],
+                    type = "Emedium",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -9)) -> df3.2
+
+df2[grep("Efull", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
+                    type = "Efull",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.0
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Samples per Haul", y = "ISSB % Difference") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.2)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10)) +
+  scale_x_discrete(labels = c("1", "5", "10", "15", "20", "25", "30", "35"))
+
+# Stats
+df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
+df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median
 
@@
 
-### Without sampling strata
-```{r}
+### DATA: Samples VS Haul 
+```{r, fig.width=8}
+
+out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.2_ISS_200_iters_2025-02-03.RDS")
+
+year = out_24.1$samples_1$trip_0.25$length$iss$YEAR
 
 df = tidytable(year = year,
-               N10_Enone = out_2.2.1$samples_10$expansion_NULL$length$iss$iss,
-               N20_Enone = out_2.2.1$samples_20$expansion_NULL$length$iss$iss,
-               N30_Enone = out_2.2.1$samples_30$expansion_NULL$length$iss$iss,
-               N10_Emedium = out_2.2.1$samples_10$expansion_haul_numbers$length$iss$iss,
-               N20_Emedium = out_2.2.1$samples_20$expansion_haul_numbers$length$iss$iss,
-               N30_Emedium = out_2.2.1$samples_30$expansion_haul_numbers$length$iss$iss,
-               N10_Efull = out_2.2.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
-               N20_Efull = out_2.2.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
-               N30_Efull = out_2.2.1$samples_30$expansion_haul_month_numbers$length$iss$iss,)
+               N1_H0.5 = out_24.1$samples_1$trip_0.5$length$iss$iss,
+               N5_H0.5 = out_24.1$samples_5$trip_0.5$length$iss$iss,
+               N10_H0.5 = out_24.1$samples_10$trip_0.5$length$iss$iss,
+               N15_H0.5 = out_24.1$samples_15$trip_0.5$length$iss$iss,
+               N20_H0.5 = out_24.1$samples_20$trip_0.5$length$iss$iss,
+               N25_H0.5 = out_24.1$samples_25$trip_0.5$length$iss$iss,
+               N30_H0.5 = out_24.1$samples_30$trip_0.5$length$iss$iss,
+               N35_H0.5 = out_24.1$samples_35$trip_0.5$length$iss$iss,
+               N1_H0.75 = out_24.1$samples_1$trip_0.75$length$iss$iss,
+               N5_H0.75 = out_24.1$samples_5$trip_0.75$length$iss$iss,
+               N10_H0.75 = out_24.1$samples_10$trip_0.75$length$iss$iss,
+               N15_H0.75 = out_24.1$samples_15$trip_0.75$length$iss$iss,
+               N20_H0.75 = out_24.1$samples_20$trip_0.75$length$iss$iss,
+               N25_H0.75 = out_24.1$samples_25$trip_0.75$length$iss$iss,
+               N30_H0.75 = out_24.1$samples_30$trip_0.75$length$iss$iss,
+               N35_H0.75 = out_24.1$samples_35$trip_0.75$length$iss$iss,
+               N1_H1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_H1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_H1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_H1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_H1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_H1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_H1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_H1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss,
+               N1_H1.25 = out_24.1$samples_1$trip_1.25$length$iss$iss,
+               N5_H1.25 = out_24.1$samples_5$trip_1.25$length$iss$iss,
+               N10_H1.25 = out_24.1$samples_10$trip_1.25$length$iss$iss,
+               N15_H1.25 = out_24.1$samples_15$trip_1.25$length$iss$iss,
+               N20_H1.25 = out_24.1$samples_20$trip_1.25$length$iss$iss,
+               N25_H1.25 = out_24.1$samples_25$trip_1.25$length$iss$iss,
+               N30_H1.25 = out_24.1$samples_30$trip_1.25$length$iss$iss,
+               N35_H1.25 = out_24.1$samples_35$trip_1.25$length$iss$iss)
 
@@
 
-ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
-  geom_line() +
-  labs(x = "Year", y = "ISS") +
-  geom_point()
+df2[grep("H0.5", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "0.5",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.01
+
+df2[grep("H0.75", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "0.75",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1
+
+df2[grep("H1.0", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "1.0",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2
+
+df2[grep("H1.25", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "1.25",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3
+
+df3.01 %>% 
+  tidytable::bind_rows(df3.1) %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.1.b
 
@@
 
-## Plot 4.1 Trip and Haul x .5, 1.5
+### DATA: Samples VS Trip
+```{r, fig.width=8}
 
-2x3 grid.
+out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_23.1_ISS_200_iters_2024-12-31.RDS")
 
-### Data
-```{r}
-out_19.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_19.1_ISS_200_iters_2024-12-17.RDS")
+year = out_23.1$samples_1$trip_0.25$length$iss$YEAR
 
-out_20.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_20.1_ISS_200_iters_2024-12-17.RDS")
+df = tidytable(year = year,
+               N1_H0.5 = out_23.1$samples_1$trip_0.5$length$iss$iss,
+               N5_H0.5 = out_23.1$samples_5$trip_0.5$length$iss$iss,
+               N10_H0.5 = out_23.1$samples_10$trip_0.5$length$iss$iss,
+               N15_H0.5 = out_23.1$samples_15$trip_0.5$length$iss$iss,
+               N20_H0.5 = out_23.1$samples_20$trip_0.5$length$iss$iss,
+               N25_H0.5 = out_23.1$samples_25$trip_0.5$length$iss$iss,
+               N30_H0.5 = out_23.1$samples_30$trip_0.5$length$iss$iss,
+               N35_H0.5 = out_23.1$samples_35$trip_0.5$length$iss$iss,
+               N1_H0.75 = out_23.1$samples_1$trip_0.75$length$iss$iss,
+               N5_H0.75 = out_23.1$samples_5$trip_0.75$length$iss$iss,
+               N10_H0.75 = out_23.1$samples_10$trip_0.75$length$iss$iss,
+               N15_H0.75 = out_23.1$samples_15$trip_0.75$length$iss$iss,
+               N20_H0.75 = out_23.1$samples_20$trip_0.75$length$iss$iss,
+               N25_H0.75 = out_23.1$samples_25$trip_0.75$length$iss$iss,
+               N30_H0.75 = out_23.1$samples_30$trip_0.75$length$iss$iss,
+               N35_H0.75 = out_23.1$samples_35$trip_0.75$length$iss$iss,
+               N1_H1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_H1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_H1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_H1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_H1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_H1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_H1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_H1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss,
+               N1_H1.25 = out_23.1$samples_1$trip_1.25$length$iss$iss,
+               N5_H1.25 = out_23.1$samples_5$trip_1.25$length$iss$iss,
+               N10_H1.25 = out_23.1$samples_10$trip_1.25$length$iss$iss,
+               N15_H1.25 = out_23.1$samples_15$trip_1.25$length$iss$iss,
+               N20_H1.25 = out_23.1$samples_20$trip_1.25$length$iss$iss,
+               N25_H1.25 = out_23.1$samples_25$trip_1.25$length$iss$iss,
+               N30_H1.25 = out_23.1$samples_30$trip_1.25$length$iss$iss,
+               N35_H1.25 = out_23.1$samples_35$trip_1.25$length$iss$iss)
 
-year = out_19.1$proportion_0.5$expansion_NULL$length$iss$YEAR
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
 
-proportion_global = c(0.50, 1.50)
-expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
-expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+df2[grep("H0.5", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "0.5",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.01
 
-samples_global = c(10, 20, 30)
-expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
-expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+df2[grep("H0.75", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "0.75",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1
+
+df2[grep("H1.0", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "1.0",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2
+
+df2[grep("H1.25", scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
+                    type = "1.25",
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3
+
+df3.01 %>% 
+  tidytable::bind_rows(df3.1) %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.2.b
 
@@
 
-COME BACK TO THIS! NEED TO RERUN WITH REGULAR HAUL AND TRIP NUMBERS!
-### With sampling strata
-```{r, fig.width=9, fig.height=5}
+### DATA: Samples VS Trip/Haul
+```{r, fig.width=8}
+
+out_25.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_25.1_ISS_200_iters_2025-01-03.RDS")
+
+year = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$YEAR
+
 df = tidytable(year = year,
-               N0.5_Enone = out_19.1$proportion_0.5$expansion_NULL$length$iss$iss,
-               N1.0_Enone = out_2.1.1$samples_20$expansion_NULL$length$iss$iss,
-               N30_Enone = out_2.1.1$samples_30$expansion_NULL$length$iss$iss,
-               N10_Emedium = out_2.1.1$samples_10$expansion_haul_numbers$length$iss$iss,
-               N20_Emedium = out_2.1.1$samples_20$expansion_haul_numbers$length$iss$iss,
-               N30_Emedium = out_2.1.1$samples_30$expansion_haul_numbers$length$iss$iss,
-               N10_Efull = out_2.1.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
-               N20_Efull = out_2.1.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
-               N30_Efull = out_2.1.1$samples_30$expansion_haul_month_numbers$length$iss$iss,)
+               N1_H0.5_T0.5 = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$iss,
+               N5_H0.5_T0.5 = out_25.1$samples_5$haul_0.5_trip_0.5$length$iss$iss,
+               N10_H0.5_T0.5 = out_25.1$samples_10$haul_0.5_trip_0.5$length$iss$iss,
+               N15_H0.5_T0.5 = out_25.1$samples_15$haul_0.5_trip_0.5$length$iss$iss,
+               N20_H0.5_T0.5 = out_25.1$samples_20$haul_0.5_trip_0.5$length$iss$iss,
+               N25_H0.5_T0.5 = out_25.1$samples_25$haul_0.5_trip_0.5$length$iss$iss,
+               N30_H0.5_T0.5 = out_25.1$samples_30$haul_0.5_trip_0.5$length$iss$iss,
+               N35_H0.5_T0.5 = out_25.1$samples_35$haul_0.5_trip_0.5$length$iss$iss,
+
+               N1_H0.5_T0.75 = out_25.1$samples_1$haul_0.5_trip_0.75$length$iss$iss,
+               N5_H0.5_T0.75 = out_25.1$samples_5$haul_0.5_trip_0.75$length$iss$iss,
+               N10_H0.5_T0.75 = out_25.1$samples_10$haul_0.5_trip_0.75$length$iss$iss,
+               N15_H0.5_T0.75 = out_25.1$samples_15$haul_0.5_trip_0.75$length$iss$iss,
+               N20_H0.5_T0.75 = out_25.1$samples_20$haul_0.5_trip_0.75$length$iss$iss,
+               N25_H0.5_T0.75 = out_25.1$samples_25$haul_0.5_trip_0.75$length$iss$iss,
+               N30_H0.5_T0.75 = out_25.1$samples_30$haul_0.5_trip_0.75$length$iss$iss,
+               N35_H0.5_T0.75 = out_25.1$samples_35$haul_0.5_trip_0.75$length$iss$iss,
+
+               N1_H0.75_T0.5 = out_25.1$samples_1$haul_0.75_trip_0.5$length$iss$iss,
+               N5_H0.75_T0.5 = out_25.1$samples_5$haul_0.75_trip_0.5$length$iss$iss,
+               N10_H0.75_T0.5 = out_25.1$samples_10$haul_0.75_trip_0.5$length$iss$iss,
+               N15_H0.75_T0.5 = out_25.1$samples_15$haul_0.75_trip_0.5$length$iss$iss,
+               N20_H0.75_T0.5 = out_25.1$samples_20$haul_0.75_trip_0.5$length$iss$iss,
+               N25_H0.75_T0.5 = out_25.1$samples_25$haul_0.75_trip_0.5$length$iss$iss,
+               N30_H0.75_T0.5 = out_25.1$samples_30$haul_0.75_trip_0.5$length$iss$iss,
+               N35_H0.75_T0.5 = out_25.1$samples_35$haul_0.75_trip_0.5$length$iss$iss,
+
+               N1_H0.75_T0.75 = out_25.1$samples_1$haul_0.75_trip_0.75$length$iss$iss,
+               N5_H0.75_T0.75 = out_25.1$samples_5$haul_0.75_trip_0.75$length$iss$iss,
+               N10_H0.75_T0.75 = out_25.1$samples_10$haul_0.75_trip_0.75$length$iss$iss,
+               N15_H0.75_T0.75 = out_25.1$samples_15$haul_0.75_trip_0.75$length$iss$iss,
+               N20_H0.75_T0.75 = out_25.1$samples_20$haul_0.75_trip_0.75$length$iss$iss,
+               N25_H0.75_T0.75 = out_25.1$samples_25$haul_0.75_trip_0.75$length$iss$iss,
+               N30_H0.75_T0.75 = out_25.1$samples_30$haul_0.75_trip_0.75$length$iss$iss,
+               N35_H0.75_T0.75 = out_25.1$samples_35$haul_0.75_trip_0.75$length$iss$iss,
+
+               N1_H1.25_T0.5 = out_25.1$samples_1$haul_1.25_trip_0.5$length$iss$iss,
+               N5_H1.25_T0.5 = out_25.1$samples_5$haul_1.25_trip_0.5$length$iss$iss,
+               N10_H1.25_T0.5 = out_25.1$samples_10$haul_1.25_trip_0.5$length$iss$iss,
+               N15_H1.25_T0.5 = out_25.1$samples_15$haul_1.25_trip_0.5$length$iss$iss,
+               N20_H1.25_T0.5 = out_25.1$samples_20$haul_1.25_trip_0.5$length$iss$iss,
+               N25_H1.25_T0.5 = out_25.1$samples_25$haul_1.25_trip_0.5$length$iss$iss,
+               N30_H1.25_T0.5 = out_25.1$samples_30$haul_1.25_trip_0.5$length$iss$iss,
+               N35_H1.25_T0.5 = out_25.1$samples_35$haul_1.25_trip_0.5$length$iss$iss,
+
+               N1_H1.25_T0.75 = out_25.1$samples_1$haul_1.25_trip_0.75$length$iss$iss,
+               N5_H1.25_T0.75 = out_25.1$samples_5$haul_1.25_trip_0.75$length$iss$iss,
+               N10_H1.25_T0.75 = out_25.1$samples_10$haul_1.25_trip_0.75$length$iss$iss,
+               N15_H1.25_T0.75 = out_25.1$samples_15$haul_1.25_trip_0.75$length$iss$iss,
+               N20_H1.25_T0.75 = out_25.1$samples_20$haul_1.25_trip_0.75$length$iss$iss,
+               N25_H1.25_T0.75 = out_25.1$samples_25$haul_1.25_trip_0.75$length$iss$iss,
+               N30_H1.25_T0.75 = out_25.1$samples_30$haul_1.25_trip_0.75$length$iss$iss,
+               N35_H1.25_T0.75 = out_25.1$samples_35$haul_1.25_trip_0.75$length$iss$iss,
+
+               N1_H1.0_T1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
+               N5_H1.0_T1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
+               N10_H1.0_T1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
+               N15_H1.0_T1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
+               N20_H1.0_T1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
+               N25_H1.0_T1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
+               N30_H1.0_T1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
+               N35_H1.0_T1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss)
 
@@
 
-ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
-  geom_line() +
-  labs(x = "", y = "ISSB") +
-  geom_point() + 
+scenario_names = c("H0.5_T0.5", "H0.5_T0.75", "H0.75_T0.5", "H0.75_T0.75", "H1.25_T0.5", "H1.25_T0.75", "H1.0_T1.0")
+scenario_names.short = c("0.5/0.5", "0.5/0.75", "0.75/0.5", "0.75/0.75", "1.25/0.5", "1.25/0.75", "1.0/1.0")
+
+## 1
+df2[grep(scenario_names[1], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[1],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[1])+2))) -> df3.1
+
+## 2
+df2[grep(scenario_names[2], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[2],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[2])+2))) -> df3.2
+
+## 3
+df2[grep(scenario_names[3], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[3],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[3])+2))) -> df3.3
+
+## 4
+df2[grep(scenario_names[4], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[4],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[4])+2))) -> df3.4
+
+## 5
+df2[grep(scenario_names[5], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[5],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[5])+2))) -> df3.5
+
+## 6
+df2[grep(scenario_names[6], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[6],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[6])+2))) -> df3.6
+
+## 7
+df2[grep(scenario_names[7], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[7],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[7])+2))) -> df3.7
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::bind_rows(df3.4) %>% 
+  tidytable::bind_rows(df3.5) %>% 
+  tidytable::bind_rows(df3.6) %>% 
+  tidytable::bind_rows(df3.7) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.3.b
+
+```
+
+### * 3 Panel: Sample Size VS Haul, Trip, Haul/Trip
+
+```{r, fig.height=12, fig.width=10}
+p1 = df4.2.b %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "A") +
   theme_classic() +
-  theme(legend.position = c(0.84, 0.8),
-        axis.title.x = element_blank())
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Trips",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))
+
+p2 = df4.1.b %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "B") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Hauls",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))
+
+p3 = df4.3.b %>% 
+  tidytable::mutate(scenario = factor(str_sub(scenario, start = 2, end = -1))) %>% 
+  tidytable::filter(type %in% scenario_names.short[c(2,4,5,6,7)]) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Samples per Haul", y = "ISSB % Difference", tag = "C") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Hauls/Trips",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))
+
+p1 + plot_spacer() + p2 + plot_spacer() + p3 + plot_layout(ncol = 1,
+                           heights = c(6, -.5, 6, -.5, 6))
+
 ```
+
+### * 4 Panel: Sample Size VS Expansion, Haul, Trip, Haul/Trip 
+\newpage
+
+```{r, fig.height=14, fig.width=10}
+
+p0 = df4.0 %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>%
+  tidytable::mutate(type = str_sub(type, start = 2, end = -1)) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "A") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Expansion Complexity",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20))
+
+p1 = df4.2.b %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "B") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Proportion of Trips",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20))
+
+p2 = df4.1.b %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "C") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Proportion of Hauls",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20))
+
+p3 = df4.3.b %>% 
+  tidytable::mutate(scenario = factor(str_sub(scenario, start = 2, end = -1))) %>% 
+  tidytable::filter(type %in% scenario_names.short[c(2,4,5,6,7)]) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Samples per Haul", y = "ISSB % Difference", tag = "D") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Proportion of Hauls/Trips",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 20))
+
+p0 + plot_spacer() + p1 + plot_spacer() + p2 + plot_spacer() + p3 + plot_layout(ncol = 1,
+                           heights = c(6, -.7, 6, -.7, 6, -.7, 6))
+
+```
+
+## SUPPLEMENTARY MATERIAL
+### Plot 7x2 Grid Haul and Trip numbers
+
+CONSIDER MOVING THESE TO SUPPLEMENTARY MATERIAL AND TOTALLY FOCUSING ON 1999-2023 PERIOD.
+
+```{r}
+
+out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.2_ISS_200_iters_2025-02-01.RDS")
+
+year = out_18.1$proportion_0.25$type_trip$length$iss$YEAR
+
+# Trip
+df = tidytable(year = year,
+               N_0.25 = out_18.1$proportion_0.25$type_trip$length$iss$iss,
+               N_0.50 = out_18.1$proportion_0.5$type_trip$length$iss$iss,
+               N_0.75 = out_18.1$proportion_0.75$type_trip$length$iss$iss,
+               N_1.00 = out_1.4$length$iss$iss,
+               N_1.25 = out_18.1$proportion_1.25$type_trip$length$iss$iss,
+               N_1.50 = out_18.1$proportion_1.5$type_trip$length$iss$iss,
+               N_1.75 = out_18.1$proportion_1.75$type_trip$length$iss$iss,
+               N_2.00 = out_18.1$proportion_2$type_trip$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2 %>% 
+  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_1.00"]) - ISS,
+                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_1.00"])/df2$ISS[df2$scenario=="N_1.00"],
+                    type = "trip",
+                    .by = scenario) -> df3.1
+
+# Haul
+df = tidytable(year = year,
+               N_0.25 = out_18.1$proportion_0.25$type_haul$length$iss$iss,
+               N_0.50 = out_18.1$proportion_0.5$type_haul$length$iss$iss,
+               N_0.75 = out_18.1$proportion_0.75$type_haul$length$iss$iss,
+               N_1.00 = out_1.4$length$iss$iss,
+               N_1.25 = out_18.1$proportion_1.25$type_haul$length$iss$iss,
+               N_1.50 = out_18.1$proportion_1.5$type_haul$length$iss$iss,
+               N_1.75 = out_18.1$proportion_1.75$type_haul$length$iss$iss,
+               N_2.00 = out_18.1$proportion_2$type_haul$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2 %>% 
+  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_1.00"]) - ISS,
+                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_1.00"])/df2$ISS[df2$scenario=="N_1.00"],
+                    type = "haul",
+                    .by = scenario) -> df3.2
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) -> df4
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Proportional Change", y = "ISSB % Difference") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.9)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120)) +
+  scale_x_discrete(labels = c("0.25", "0.50", "0.75", "1.00", "1.25", "1.50", "1.75", "2.00"))
+
+```
+
+### Boxplots Together 1999-2023
+```{r}
+
+df4 %>%  
+  tidytable::filter(year %in% 1999:2023) -> df4.2
+
+df4.2 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Scenario", y = "ISSB % Error") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.9)) +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120))
+
+```

### 2025-02-08 Rmd/weighted_vs_unweighted_proportions.Rmd
run some updated scenarios

@@
 
-y2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
-y7 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y7_ebs_pcod_Brett.RDS")
+# y2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
+# y7 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y7_ebs_pcod_Brett.RDS")
+y2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_ebs_pcod_Brett.RDS")
+y7 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y7_ebs_pcod_Brett.RDS")
 
@@
 ```{r}
-ggplot(data=df, aes(x=bin, y=freq, colour=type)) + 
+df.temp = df
+df.temp$type[df.temp$type=="Nom"] = "Nominal"
+df.temp$type[df.temp$type=="Exp"] = "Expanded"
+df.temp %>% 
+  tidytable::rename("Composition" = type) -> df.temp
+
+ggplot(data=df.temp, aes(x=bin, y=freq, colour=Composition)) + 
   geom_line() +
-  geom_area(aes(fill=type, group=type), alpha = 0.5, position = "identity")
+  geom_area(aes(fill=Composition, group=Composition), alpha = 0.5, position = "identity") +
+  scale_x_continuous(limits = c(20, 110)) +
+  labs(x = "Length (cm)", y = "Frequency")
 

### 2025-02-08 run/paper_runs/paper_scenario_2.1.2.R

@@ -1,0 +1,63 @@
+
+rm(list = ls())
+run_name = "paper_scenario_2.1.2"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(10, 20, 30)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(expansion_global)){
+
+    samples = samples_global[i]
+    expansion = expansion_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = NULL, amount = samples),
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = expansion,
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("expansion_", expansion_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-02-08 run/paper_runs/paper_scenario_2.2.R

@@ -1,0 +1,60 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_2.2"
+iterations = 500
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = TRUE,
+            expansion_factors = NULL,
+            save_data_frame = FALSE) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2025-02-08 run/paper_runs/paper_scenario_22.2.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_22.2"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(expansion_global)){
+
+    samples = samples_global[i]
+    expansion = expansion_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = NULL, amount = samples),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = expansion,
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("expansion_", expansion_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-02-08 run/paper_runs/paper_scenario_23.2.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_23.2"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = list(type = "proportion", amount = .proportion),
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = NULL, amount = samples),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("trip_", proportion_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-02-08 run/paper_runs/paper_scenario_24.2.R

@@ -1,0 +1,65 @@
+
+rm(list = ls())
+run_name = "paper_scenario_24.2"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 200
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N =list(type = "proportion", amount = .proportion),
+                new_length_N = list(type = "value", bound = NULL, amount = samples),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("trip_", proportion_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-02-08 run/paper_runs/paper_scenario_4.2.R

@@ -1,0 +1,60 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_4.2"
+iterations = 500
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = NULL,
+            save_data_frame = FALSE) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2025-02-08 run/paper_runs/paper_scenario_9.2.R

@@ -1,0 +1,60 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_9.2"
+iterations = 500
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = FALSE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = NULL,
+            save_data_frame = FALSE) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2025-02-26 Rmd/paper_plots/paper_plots_1.2.Rmd
update paper plots and run 500 iters on remaining scenarios for paper

@@
 ---
-title: "Paper Plots V1"
+title: "Paper Plots V2"
 author: "Brett Stacy"
@@
                                 706))
+
+# survey vs observer length measurements
+obs_numbers = tidytable(year = 1982:2023,
+                        survey = c(10863,
+                        13143,
+                        12133,
+                        17150,
+                        15872,
+                        9483,
+                        6950,
+                        4246,
+                        5428,
+                        7069,
+                        10129,
+                        10500,
+                        12931,
+                        9820,
+                        9348,
+                        9591,
+                        9574,
+                        11183,
+                        12170,
+                        19078,
+                        12365,
+                        11835,
+                        10986,
+                        11753,
+                        12530,
+                        13441,
+                        15328,
+                        23737,
+                        21223,
+                        25150,
+                        30177,
+                        19902,
+                        29204,
+                        19880,
+                        19507,
+                        15020,
+                        8806,
+                        23408,
+                        0,
+                        17397,
+                        16677,
+                        19943),
+                        fishery = c(9658,
+                                    33200,
+                                    45635,
+                                    66940,
+                                    58257,
+                                    129226,
+                                    111065,
+                                    58625,
+                                    39698,
+                                    347227,
+                                    344923,
+                                    248967,
+                                    359147,
+                                    344794,
+                                    445217,
+                                    474908,
+                                    438746,
+                                    186233,
+                                    199708,
+                                    210419,
+                                    230802,
+                                    288854,
+                                    237487,
+                                    228664,
+                                    179782,
+                                    140663,
+                                    164860,
+                                    147875,
+                                    131514,
+                                    172269,
+                                    192273,
+                                    211962,
+                                    234476,
+                                    213888,
+                                    182980,
+                                    157482,
+                                    124004,
+                                    86800,
+                                    65301,
+                                    55858,
+                                    73025,
+                                    42942))
+
+obs_numbers %>% 
+  tidytable::summarise(sum(survey), sum(fishery))
+
 ```
@@
 lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "red")
-legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))
+legend(1977, 11000, lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n")
+text(1977, 14000, "A")
 
 plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3) 
+text(1977, 420000, "B")
+
+# averages
+out_1.4$length$iss$iss %>% mean()
+assessment_2023_iss$iss %>% mean()
 
@@
 legend("topleft", legend = c("boot length", "boot length + haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"), bty = "n")
+
+# not accounting for correlations exceed hauls?
+sum((out_5.2$length$iss$iss[sub_range]-out_1.4$length$iss$nhls) < 0)
+
 ```
@@
 
-out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.2_ISS_200_iters_2025-02-03.RDS")
+out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.3_ISS_500_iters_2025-02-11.RDS")
 
-year = out_24.1$samples_1$trip_0.25$length$iss$YEAR
+year = out_24.1$samples_1$trip_0.5$length$iss$YEAR
 
@@
 
-out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_23.1_ISS_200_iters_2024-12-31.RDS")
+out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_23.2_ISS_500_iters_2025-02-09.RDS")
 
-year = out_23.1$samples_1$trip_0.25$length$iss$YEAR
+year = out_23.1$samples_1$trip_0.5$length$iss$YEAR
 
@@
 
-out_25.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_25.1_ISS_200_iters_2025-01-03.RDS")
+# out_25.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_25.1_ISS_200_iters_2025-01-03.RDS")
+out_25.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_25.3.TAS_ISS_500_iters_2025-02-12.RDS")
 
-year = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$YEAR
+# year = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$YEAR
+year = out_25.1$samples_1$haul_0.5_trip_0.75$length$iss$YEAR
 
@@
 
-out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.2_ISS_200_iters_2025-02-01.RDS")
+out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.3.TAS_ISS_500_iters_2025-02-10.RDS")
 

### 2025-02-26 run/paper_runs/paper_scenario_18.3.TAS.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_18.2"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 200
+proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+type_global = list("trip", "haul")
+type_names_global = c("trip", "haul")
+
+
+# Loop All
+out = list()
+for(i in 1:length(proportion_global)){
+  out[[paste0("proportion_", proportion_global)[i]]] = list()
+  for(j in 1:length(type_global)){
+
+    .proportion = proportion_global[i]
+    .type = type_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = NULL,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = if(.type=="trip") {list(type = "proportion", amount = .proportion)} else{NULL},
+                new_haul_N = if(.type=="haul") {list(type = "proportion", amount = .proportion)} else{NULL},
+                new_length_N = NULL,
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("proportion_", proportion_global)[i]]][[paste0("type_", type_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-02-26 run/paper_runs/paper_scenario_24.3.R

@@ -1,0 +1,66 @@
+
+rm(list = ls())
+run_name = "paper_scenario_24.3"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+proportion_global = c(0.50, 0.75, 1.25)
+
+
+
+tictoc::tic()
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    # tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N =list(type = "proportion", amount = .proportion),
+                new_length_N = list(type = "value", bound = NULL, amount = samples),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    # tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("trip_", proportion_global)[j]]] = .output
+
+  }
+}
+tictoc::toc()
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-02-28 Rmd/paper_plots/paper_plots_1.3.Rmd
add paper plots version and min(20) scenarios

--- 2025-02-26 Rmd/paper_plots/paper_plots_1.2.Rmd
@@
 out_2.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.2_ISS_500iters_output_2025-01-28.RDS")
+
+# save out_1.4 for Steve to plug into the assessment
+out_1.4$length$iss %>% 
+  select(YEAR, iss) %>% 
+  write.csv(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/issb_v1_from_Brett_Stacy.csv", row.names = F)
 
@@
 ## Optimize Sampling
+
+### Min 20
+```{r, fig.width=9, fig.height=5}
+out_26.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_26.1_ISS_500iters_output_2025-02-27.RDS")
+
+year = out_26.1$length$iss$YEAR
+
+df = tidytable(year = year,
+               iss.base = out_1.4$length$iss$iss,
+               iss.20.min = out_26.1$length$iss$iss)
+
+df %>% 
+  tidytable::mutate(ISS.error = (iss.20.min - iss.base)/iss.base) %>% 
+  filter(year%in%1999:2023) %>% 
+  select(ISS.error) %>% 
+  boxplot()
+
+df %>% 
+  tidytable::mutate(ISS.error = (iss.20.min - iss.base)/iss.base) %>% 
+  filter(year%in%2023) %>% 
+  select(ISS.error) %>% 
+  boxplot()
+
+# df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+```
+
 ### * Time series Expansion X Samples 10, 20, 30

### 2025-02-28 run/Pollock/run_pollock_ISS_0.1.1.R

@@ -1,0 +1,89 @@
+# Pollock
+
+# test improved SQL download that converts things to characters for:
+# debriefed_length_mv (length data and strata),
+# debriefed_haul_mv (trip_seq for creating accurate trip_join). Note that the TRIP_JOIN in debriefed_haul_mv should NOT be used for trip_join in the ISS analysis. Therefore it should not be part of the .sql download.
+# debriefed_spcomp_mv (for extrapolated_numbers for expand.by.sampling.strata). extrapolated_weight can also be retrieved from debriefed_spcomp_mv
+
+
+rm(list = ls())
+run_name = "generic_201_V3"
+iterations = 100
+
+
+lfreq_data_201 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/species_201_generic_V2.RDS")
+spcomp_data_201 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/spcomp_generic_201_V2.RDS")
+haul_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/haul_generic_201.RDS")
+
+
+library(tidytable)
+library(baseISS)
+
+
+lfreq_data_201 %>%
+  glimpse()
+
+##### Standard Processing Steps ----
+
+# Filter out SEX for now and remove NAs for LENGTH and HAUL_JOIN
+lfreq_data_201 %>%
+  tidytable::mutate(SEX_KEY = NULL, SEX = NULL) %>%
+  tidytable::drop_na(LENGTH, HAUL_JOIN) -> lfreq_data_201_V2
+
+# Join with haul_mv to get trip join and spcomp_mv to get extrapolated numbers, also rename this to YAGMH_SNUM
+lfreq_data_201_V2 %>%
+  tidytable::left_join(haul_data) %>%
+  tidytable::mutate(TRIP_JOIN = paste(CRUISE, PERMIT, TRIP_SEQ, sep = "-")) %>%
+  tidytable::left_join(spcomp_data_201) -> lfreq_data_201_V3
+# tidytable::rename(YAGMH_SNUM = EXTRAPOLATED_NUMBER)
+
+
+lfreq_data_201_V3 %>%
+  glimpse()
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "201",
+            area_code = "unknown",
+            length_based = TRUE,
[…]

### 2025-02-28 run/Post_Stratified/run_post_strata_ISS_0.1.1.R

@@ -1,0 +1,59 @@
+# Run a post-stratified run for testing combine by post strata functionality
+
+rm(list = ls())
+run_name = "post_strata_0.1.1"
+iterations = 1
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = list(strata = "GEAR", nested = FALSE),
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = TRUE,
+            expansion_factors = c("haul_numbers", "month_numbers"),
+            save_data_frame = TRUE) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/Post Stratified/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2025-02-28 run/paper_runs/paper_scenario_26.1.R

@@ -1,0 +1,60 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_26.1"
+iterations = 500
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = list(type = "value", bound = "minimum", amount = 20),
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = TRUE,
+            expansion_factors = c("haul_numbers", "month_numbers"),
+            save_data_frame = TRUE) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2025-02-28 Rmd/paper_plots/paper_plots_1.3.Rmd
clean up change_length_N, git new scenarios, mark DEV combine post strata work to come back to later.

@@
 ```{r, fig.width=9, fig.height=5}
+
+## min(20, #samples) port and haul 1999-2023
+# with replacement
 out_26.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_26.1_ISS_500iters_output_2025-02-27.RDS")
@@
 
+# without replacement - THIS HAS MUCH SMALLER PERCENT DIFFERENCE! So use this in paper. 
+out_27.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_27.1_ISS_500iters_output_2025-02-28.RDS")
+
+year = out_27.1$length$iss$YEAR
+
+df = tidytable(year = year,
+               iss.base = out_1.4$length$iss$iss,
+               iss.20.min = out_27.1$length$iss$iss)
+
 df %>% 
   tidytable::mutate(ISS.error = (iss.20.min - iss.base)/iss.base) %>% 
-  filter(year%in%2023) %>% 
+  filter(year%in%1999:2023) %>% 
+  select(ISS.error) %>% 
+  boxplot()
+
+# without replacement - Hauls only 
+out_28.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_28.1_ISS_500iters_output_2025-02-28.RDS")
+
+year = out_28.1$length$iss$YEAR
+
+df = tidytable(year = year,
+               iss.base = out_1.4$length$iss$iss,
+               iss.20.min = out_28.1$length$iss$iss)
+
+df %>% 
+  tidytable::mutate(ISS.error = (iss.20.min - iss.base)/iss.base) %>% 
+  filter(year%in%1999:2023) %>% 
   select(ISS.error) %>% 

### 2025-02-28 R/combine_post_strata.R

@@ -3,12 +3,26 @@
 #' @description
 #' Combine the post-stratified ISS results by post-strata fish weight or numbers as weighted average. Includes evidence somewhere (DECIDE BEST PLACE) that states it was combined by post_strata and reports what the strata were and the method used to combine them.
 #'
-#' @param out_stats from fishery_iss()
+#' @param freq_data length or age frequency input data frame
+#' @param out_stats output object from fishery_iss()
 #'
 #' @return out_stats object to be returned by fishery_iss() that includes one vector of ISS based on the weighted average between post-strata
 #'
 #' @export
 #'
-combine_post_strata = function(out_stats){
+combine_post_strata = function(freq_data,
+                               out_stats){
+
+  # step 1: take out_stats and extract the ISS and proportions
+  # step 2: take freq_data and separate in the same way as post_stratify()
+  # step 3: add up weight or numbers from each unique haul_join in each strata, for each year. This can be a data frame with columns: year, "NAME1"_post_strata, "NAME2"_post_strata, etc. With totals in kg or numbers of fish and NAs where the post-strata was absent for that year.
+  # Absent post-strata years will have to be treated as a special case in the weighted average. Probably have a conditional statement asking for NAs?
+  # step 4: apply proportional weighting to the ISS and props from each strata and combine
+  # step 5: figure out what to do with the rest of the auxiliary data, e.g., RSS. Perhaps just add a list element to the existing out_stats that says: $combined_post_strata with a sublist that says $by that equals weight or numbers e.g., $by_weight.
+  # step 6: deal with column name discrepencies: EXTRAPOLATED_NUMBER is number of fish in haul for generic species download, but YAGMH_SNUM for EBS Pcod. There are different expand_by_sampling_strata functions because of this discrepency.
+  # step 7: deal with lack of haul weight in generic data download. this is EXTRAPOLATED_WEIGHT that is NOT currently in the .sql download generic but can be found in DEBRIEFED_SPCOMP_MV
+
+  return(out_stats)
+
 
 }

### 2025-02-28 R/fishery_iss.R

@@ -152,11 +152,12 @@ fishery_iss <- function(species_code,
   ### Include the function arguments in the output as a default
   out_stats$arguments = match.call()
 
-
-  ### Combine post strata by user-defined measurement (weight or numbers) if requested
-  if(!is.null(combine.post.strata) & post_strata$nested==FALSE){
-    out_stats = combine_post_strata(out_stats)
-  }
+  # DEV
+  # ### Combine post strata by user-defined measurement (weight or numbers) if requested. Keep nested out of this for now, too complicated. Also,
+  # if(!is.null(combine.post.strata) & post_strata$nested==FALSE){
+  #   out_stats = combine_post_strata(freq_data = freq_data,
+  #                                   out_stats = out_stats)
+  # }
 
 
 

### 2025-02-28 run/paper_runs/paper_scenario_29.1.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_29.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+proportion_global = seq(0.1, 0.9, by = .1)
+type_global = list("trip", "haul")
+type_names_global = c("trip", "haul")
+
+
+# Loop All
+out = list()
+for(i in 1:length(proportion_global)){
+  out[[paste0("proportion_", proportion_global)[i]]] = list()
+  for(j in 1:length(type_global)){
+
+    .proportion = proportion_global[i]
+    .type = type_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = NULL,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = if(.type=="trip") {list(type = "proportion", amount = .proportion)} else{NULL},
+                new_haul_N = if(.type=="haul") {list(type = "proportion", amount = .proportion)} else{NULL},
+                new_length_N = NULL,
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("proportion_", proportion_global)[i]]][[paste0("type_", type_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-02-28 run/paper_runs/paper_scenario_30.1.R

@@ -1,0 +1,59 @@
+
+rm(list = ls())
+run_name = "paper_scenario_30.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# Loop All
+out = list()
+  for(j in 1:length(expansion_global)){
+
+    expansion = expansion_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N = NULL,
+                new_length_N = NULL,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = expansion,
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("expansion_", expansion_names_global)[j]]] = .output
+
+  }
+
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-07 Rmd/paper_plots/paper_plots_1.3.Rmd
add scenarios

@@
 out_1.4 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.4_ISS_1000iters_output_2025-01-23.RDS")
+
+out_3.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.4_ISS_500iters_output_2025-03-06.RDS") ### mislabeled
 
@@
 lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "red")
-legend(1977, 11000, lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n")
+lines(out_3.2$length$iss$YEAR, out_3.2$length$iss$iss, col = "green")
+legend(1977, 11000, lty = c(1,1,1,1), col = c("black", "blue", "red", "green"), legend = c("ISSB", "ISSA", "number of hauls", "ISSB-noSS"), bty = "n")
 text(1977, 14000, "A")
@@
 
+ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+  geom_line() +
+  labs(x = "", y = "ISSB") +
+  geom_point() + 
+  theme_classic() +
+  theme(legend.position = c(0.84, 0.8),
+        axis.title.x = element_blank())
+```
+
+### * Time series Expansion NEW
+```{r, fig.width=9, fig.height=5}
+out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_30.1_ISS_500_iters_2025-03-01.RDS")
+
+year = out_2.1.1$expansion_NULL$length$iss$YEAR
+
+df = tidytable(year = year,
+               none = out_2.1.1$expansion_NULL$length$iss$iss,
+               medium = out_2.1.1$expansion_haul_numbers$length$iss$iss,
+               full = out_2.1.1$expansion_haul_month_numbers$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+# all years
+ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+  geom_line() +
+  labs(x = "", y = "ISSB") +
+  geom_point() + 
+  theme_classic() +
+  theme(legend.position = c(0.84, 0.8),
+        axis.title.x = element_blank())
+
+# 1999:2023
+df2 %>% 
+  filter(year%in%1999:2023) -> df2
 ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
@@
 
+\newpage
+
+### * DATA: NEW reduce samples
+```{r}
+out_31.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_31.1.TAS_ISS_500_iters_2025-03-02.RDS")
+
+year = out_31.1$samples_1$data_H_P$length$iss$YEAR
+
+### H_P ###################
+df = tidytable(year = year,
+               N1_HP = out_31.1$samples_1$data_H_P$length$iss$iss,
+               N5_HP = out_31.1$samples_5$data_H_P$length$iss$iss,
+               N10_HP = out_31.1$samples_10$data_H_P$length$iss$iss,
+               N15_HP = out_31.1$samples_15$data_H_P$length$iss$iss,
+               N20_HP = out_31.1$samples_20$data_H_P$length$iss$iss,
+
+               NN_HP = out_1.4$length$iss$iss[out_1.4$length$iss$YEAR%in%1999:2023])
+
+########## PROBLEM: these should be the same! I think the problem is that I ran it on TAS without updating baseISS from github.
+# (out_27.1$length$iss$iss[out_27.1$length$iss$YEAR%in%1999:2023]-out_31.1$samples_20$data_H_P$length$iss$iss) %>% boxplot()
+out_27.1$length$iss$iss[out_27.1$length$iss$YEAR%in%1999:2023]-out_31.1$samples_5$data_H_P$length$iss$iss
+# (df2[scenario=="full"]$ISS - out_1.4$length$iss$iss[out_1.4$length$iss$YEAR%in%1999:2023]) %>% boxplot()
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+scenario_names = c("N1_HP", "N5_HP", "N10_HP", "N15_HP", "N20_HP", "NN_HP")
+
+## 1
+df2 %>% 
+  tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="N20_HP"])/df2$ISS[df2$scenario=="N20_HP"],
+                    type = "relative_20",
+                    .by = scenario) -> df3.1
+## 2
+df2 %>% 
+  tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="NN_HP"])/df2$ISS[df2$scenario=="NN_HP"],
+                    type = "relative_N",
+                    .by = scenario) -> df3.2
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>%
+  tidytable::filter(scenario!="NN_HP") %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -4)) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.a
+
+### H ###################
+df = tidytable(year = year,
+               N1_H = out_31.1$samples_1$data_H$length$iss$iss,
+               N5_H = out_31.1$samples_5$data_H$length$iss$iss,
+               N10_H = out_31.1$samples_10$data_H$length$iss$iss,
+               N15_H = out_31.1$samples_15$data_H$length$iss$iss,
+               N20_H = out_31.1$samples_20$data_H$length$iss$iss,
+
+               NN_H = out_1.4$length$iss$iss[out_1.4$length$iss$YEAR%in%1999:2023])
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+scenario_names = c("N1_H", "N5_H", "N10_H", "N15_H", "N20_H", "NN_H")
+
+## 1
+df2 %>% 
+  tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="N20_H"])/df2$ISS[df2$scenario=="N20_H"],
+                    type = "relative_20",
+                    .by = scenario) -> df3.1
+## 2
+df2 %>% 
+  tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="NN_H"])/df2$ISS[df2$scenario=="NN_H"],
+                    type = "relative_N",
+                    .by = scenario) -> df3.2
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>%
+  tidytable::filter(scenario!="NN_H") %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -3)) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.b
+
+### H 20 only ###################
+out_32.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_32.1_ISS_500_iters_2025-03-03.RDS")
+
+year = out_32.1$samples_1$data_H_20$length$iss$YEAR
+
+df = tidytable(year = year,
+               N1_H20 = out_32.1$samples_1$data_H_20$length$iss$iss,
+               N5_H20 = out_32.1$samples_5$data_H_20$length$iss$iss,
+               N10_H20 = out_32.1$samples_10$data_H_20$length$iss$iss,
+               N15_H20 = out_32.1$samples_15$data_H_20$length$iss$iss,
+               N20_H20 = out_32.1$samples_20$data_H_20$length$iss$iss,
+
+               NN_HP = out_1.4$length$iss$iss[out_1.4$length$iss$YEAR%in%1999:2023])
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+## 1
+df2 %>% 
+  tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="N20_H20"])/df2$ISS[df2$scenario=="N20_H20"],
+                    type = "relative_H20",
+                    .by = scenario) -> df3.1
+## 2
+df2 %>% 
+  tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="NN_HP"])/df2$ISS[df2$scenario=="NN_HP"],
+                    type = "relative_N",
+                    .by = scenario) -> df3.2
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>%
+  tidytable::filter(scenario!="NN_HP") %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -5)) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.c
+
+# 
+# ### Port only ###################
+# out_36.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_36.1_ISS_500_iters_2025-03-06.RDS")
+# 
+# year = out_36.1$samples_1$data_P$length$iss$YEAR
+# 
+# # # manually insert a zero for samples=1 year 2021 because only one port sample in 2021
+# # out_36.1$samples_1$data_P$length$iss$iss[out_36.1$samples_1$data_P$length$iss$YEAR==2021] = 0
+# # 
+# 
+# 
+# df = tidytable(year = year,
+#                N1_P = out_36.1$samples_1$data_P$length$iss$iss,
+#                N5_P = out_36.1$samples_5$data_P$length$iss$iss,
+#                N10_P = out_36.1$samples_10$data_P$length$iss$iss,
+#                N15_P = out_36.1$samples_15$data_P$length$iss$iss,
+#                N20_P = out_36.1$samples_20$data_P$length$iss$iss,
+#                
+#                NN_P = out_36.1$samples_999$data_P$length$iss$iss)
+# 
+# 
+# df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+# 
+# 
+# 
+# ## 1
+# df2 %>% 
+#   tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="N20_H20"])/df2$ISS[df2$scenario=="N20_H20"],
+#                     type = "relative_H20",
+#                     .by = scenario) -> df3.1
+# ## 2
+# df2 %>% 
+#   tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="NN_HP"])/df2$ISS[df2$scenario=="NN_HP"],
+#                     type = "relative_N",
+#                     .by = scenario) -> df3.2
+# 
+# 
+# df3.1 %>% 
+#   tidytable::bind_rows(df3.2) %>%
+#   tidytable::filter(scenario!="NN_HP") %>% 
+#   tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -5)) %>%
+#   tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+# df4 -> df4.c
+#
+
+```
+
+\newpage
+
+```{r, fig.height=8}
+### plots
+
+p1 = df4.a %>%
+  ggplot(aes(x = scenario, y = ISS.error)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "A") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "haul and port data",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-80, 10))
+
+p2 = df4.b %>%
+  ggplot(aes(x = scenario, y = ISS.error)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Samples per Haul", y = "ISSB % Difference", tag = "B") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "haul only data",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-80, 10))
+
+p3 = df4.c %>%
+  ggplot(aes(x = scenario, y = ISS.error)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Samples per Haul", y = "ISSB % Difference", tag = "optional C") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "haul=20 only data",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-80, 10))
+
+p1 + plot_spacer() + p2 + plot_layout(ncol = 1,
+                           heights = c(6, -.5, 6))
+
+p3
+
+```
+
+\newpage
+
+for above.
+"the median percent difference in ISSB increased with increasing sample size using the full data set (A) and only the haul data (B) over the period 1999-2023.
+There was no appreciable change in the percent difference when only using the haul data.
+There was also very little difference comparing the percent difference relative to the baseline ISSB or relative to applying the sample reduction routine at a sampling rate of 20.
+This verifies that the results are comparable for the following scenarios: comparisons to the baseline or comparisons to just using hauls with a sampling rate that never exceeds 20.
+The most conservative scenario is assuming a future sampling where high sampling rates from port samples are not available and the haul sampling rate is allowed to be below 20 but not exceed it.
+Comparisons relative to this scenario are the most relevant, conservative, scenario available to evaluate the impact of reducing observer haul sampling rate on composition data precision for future years.
+If the sampling rate behavior continues on average at least as good as it has done for the period 1999:2023 (which it is scheduled to do), we can expect the loss of precision not to exceed these values.
+(Assuming fishing trip and haul characteristics are comparable on average, also likely expected).
+
+\newpage
+
+### NEW Haul and TRIP Decrease
+```{r, eval=F}
+out_29.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_29.1_ISS_500_iters_2025-03-02.RDS")
+
+year = out_29.1$proportion_0.1$type_trip$length$iss$YEAR
+
+# Trip
+df = tidytable(year = year,
+               N_0.1 = out_29.1$proportion_0.1$type_trip$length$iss$iss,
+               N_0.2 = out_29.1$proportion_0.2$type_trip$length$iss$iss,
+               N_0.3 = out_29.1$proportion_0.3$type_trip$length$iss$iss,
+               N_0.4 = out_29.1$proportion_0.4$type_trip$length$iss$iss,
+               N_0.5 = out_29.1$proportion_0.5$type_trip$length$iss$iss,
+               N_0.6 = out_29.1$proportion_0.6$type_trip$length$iss$iss,
+               N_0.7 = out_29.1$proportion_0.7$type_trip$length$iss$iss,
+               N_0.8 = out_29.1$proportion_0.8$type_trip$length$iss$iss,
+               N_0.9 = out_29.1$proportion_0.9$type_trip$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2 %>% 
+  tidytable::mutate(ISS.error = (ISS - out_1.4$length$iss$iss)/out_1.4$length$iss$iss,
+                    type = "trip",
+                    .by = scenario) -> df3.1
+
+# Haul
+df = tidytable(year = year,
+               N_0.1 = out_29.1$proportion_0.1$type_haul$length$iss$iss,
+               N_0.2 = out_29.1$proportion_0.2$type_haul$length$iss$iss,
+               N_0.3 = out_29.1$proportion_0.3$type_haul$length$iss$iss,
+               N_0.4 = out_29.1$proportion_0.4$type_haul$length$iss$iss,
+               N_0.5 = out_29.1$proportion_0.5$type_haul$length$iss$iss,
+               N_0.6 = out_29.1$proportion_0.6$type_haul$length$iss$iss,
+               N_0.7 = out_29.1$proportion_0.7$type_haul$length$iss$iss,
+               N_0.8 = out_29.1$proportion_0.8$type_haul$length$iss$iss,
+               N_0.9 = out_29.1$proportion_0.9$type_haul$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2 %>% 
+  tidytable::mutate(ISS.error = (ISS - out_1.4$length$iss$iss)/out_1.4$length$iss$iss,
+                    type = "haul",
+                    .by = scenario) -> df3.2
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) -> df4
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Proportional Change", y = "ISSB % Difference") +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.2)) +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 20, by = 10), limits = c(-100, 20)) +
+  scale_x_discrete(labels = c("0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.7", "0.8", "0.9"))
+
+```
+
+### NEW Haul and TRIP Decrease w/o replacement
+```{r}
+out_29.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_33.1.TAS_ISS_500_iters_2025-03-04.RDS")
+
+year = out_29.1$proportion_0.1$type_trip$length$iss$YEAR
+
+# Trip
+df = tidytable(year = year,
+               N_0.1 = out_29.1$proportion_0.1$type_trip$length$iss$iss,
+               N_0.2 = out_29.1$proportion_0.2$type_trip$length$iss$iss,
+               N_0.3 = out_29.1$proportion_0.3$type_trip$length$iss$iss,
+               N_0.4 = out_29.1$proportion_0.4$type_trip$length$iss$iss,
+               N_0.5 = out_29.1$proportion_0.5$type_trip$length$iss$iss,
+               N_0.6 = out_29.1$proportion_0.6$type_trip$length$iss$iss,
+               N_0.7 = out_29.1$proportion_0.7$type_trip$length$iss$iss,
+               N_0.8 = out_29.1$proportion_0.8$type_trip$length$iss$iss,
+               N_0.9 = out_29.1$proportion_0.9$type_trip$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2 %>% 
+  tidytable::mutate(ISS.error = (ISS - out_1.4$length$iss$iss)/out_1.4$length$iss$iss,
+                    type = "trip",
+                    .by = scenario) -> df3.1
+
+# Haul
+df = tidytable(year = year,
+               N_0.1 = out_29.1$proportion_0.1$type_haul$length$iss$iss,
+               N_0.2 = out_29.1$proportion_0.2$type_haul$length$iss$iss,
+               N_0.3 = out_29.1$proportion_0.3$type_haul$length$iss$iss,
+               N_0.4 = out_29.1$proportion_0.4$type_haul$length$iss$iss,
+               N_0.5 = out_29.1$proportion_0.5$type_haul$length$iss$iss,
+               N_0.6 = out_29.1$proportion_0.6$type_haul$length$iss$iss,
+               N_0.7 = out_29.1$proportion_0.7$type_haul$length$iss$iss,
+               N_0.8 = out_29.1$proportion_0.8$type_haul$length$iss$iss,
+               N_0.9 = out_29.1$proportion_0.9$type_haul$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+df2 %>% 
+  tidytable::mutate(ISS.error = (ISS - out_1.4$length$iss$iss)/out_1.4$length$iss$iss,
+                    type = "haul",
+                    .by = scenario) -> df3.2
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) -> df4
+
+df4 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Proportional Change", y = "ISSB % Difference") +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.2)) +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 20, by = 10), limits = c(-100, 20)) +
+  scale_x_discrete(labels = c("0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.7", "0.8", "0.9"))
+
+```
+
 ## SUPPLEMENTARY MATERIAL

### 2025-03-07 run/Pollock/run_pollock_ISS_0.2.1.R

@@ -1,0 +1,80 @@
+# Pollock
+
+# Test generic species data download function and run fishery_iss().
+
+rm(list = ls())
+run_name = "generic_201_0.2.1"
+iterations = 1
+species = 201
+
+
+
+library(tidytable)
+library(baseISS)
+
+
+##### Download Data ----
+lfreq_data_201 = download_akfin_data(akfin_credentials = list(uid="bstacy",pwd="Dasmanid78."),
+                                     species_code = species,
+                                     composition_type = "LENGTH",
+                                     save_file_path = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/Pollock/generic_201_0.2.1.RDS")
+
+
+##### Processing Steps ----
+
+# Remove sex and migrate port_join to haul_join where haul_join=NA.
+
+lfreq_data_201 %>%
+  tidytable::filter(is.na(HAUL_JOIN)) %>%
+  tidytable::mutate(HAUL_JOIN = PORT_JOIN) %>%
+  tidytable::bind_rows(lfreq_data_201 %>%
+                         tidytable::filter(!is.na(HAUL_JOIN))) %>%
+  tidytable::mutate(SEX_KEY = NULL, SEX = NULL) -> lfreq_data_201_v2
+
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = species,
+            area_code = "unknown",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data_201_v2,
+            yrs = 1999,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = NULL,
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = "data_derived",
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = TRUE,
+            expansion_factors = NULL,
+            save_data_frame = TRUE) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/Pollock/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2025-03-07 run/paper_runs/paper_scenario_32.1.R

@@ -1,6 +1,6 @@
 
 rm(list = ls())
-run_name = "paper_scenario_30.1"
+run_name = "paper_scenario_32.1"
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
 library(tidytable)
@@ -9,44 +9,65 @@ library(baseISS)
 
 ### Global
 iters_global = 500
-expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
-expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+samples_global = c(1, 5, 10, 15, 20)
+data_global = list("H_20")
+data_names_global = c("H_20")
 
 
 # Loop All
 out = list()
-  for(j in 1:length(expansion_global)){
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(data_global)){
 
-    expansion = expansion_global[[j]]
+    samples = samples_global[i]
+    .data = data_global[[j]]
+
+    if(.data=="H_P"){
+      .lfreq_data = lfreq_data
+    }else{
+      .lfreq_data = lfreq_data %>% tidytable::filter(substr(HAUL_JOIN, 1, 1)=="H",
+                                                     YAGMH_SFREQ==20)
+    }
 
     tictoc::tic()
     fishery_iss(species_code = "202",
                 area_code = "EBS",
                 length_based = TRUE,
                 iters = iters_global,
-                freq_data = lfreq_data,
-                yrs = NULL,
+                freq_data = .lfreq_data,
+                yrs = 1999,
                 bin = NULL,
                 plus_len = NULL,
                 post_strata = NULL,
                 minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
                 new_trip_N = NULL,
                 new_haul_N = NULL,
-                new_length_N = NULL,
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
                 boot.trip = TRUE,
                 boot.haul = TRUE,
                 boot.length = TRUE,
                 boot.age = FALSE,
                 expand.by.sampling.strata = TRUE,
[…]

### 2025-03-07 run/paper_runs/paper_scenario_33.1.R

@@ -1,6 +1,6 @@
 
 rm(list = ls())
-run_name = "paper_scenario_30.1"
+run_name = "paper_scenario_33.1"
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
 library(tidytable)
@@ -9,15 +9,19 @@ library(baseISS)
 
 ### Global
 iters_global = 500
-expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
-expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+proportion_global = seq(0.1, 0.9, by = .1)
+type_global = list("trip", "haul")
+type_names_global = c("trip", "haul")
 
 
 # Loop All
 out = list()
-  for(j in 1:length(expansion_global)){
+for(i in 1:length(proportion_global)){
+  out[[paste0("proportion_", proportion_global)[i]]] = list()
+  for(j in 1:length(type_global)){
 
-    expansion = expansion_global[[j]]
+    .proportion = proportion_global[i]
+    .type = type_global[[j]]
 
     tictoc::tic()
     fishery_iss(species_code = "202",
@@ -30,21 +34,22 @@ out = list()
                 plus_len = NULL,
                 post_strata = NULL,
                 minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
-                new_trip_N = NULL,
-                new_haul_N = NULL,
+                new_trip_N = if(.type=="trip") {list(type = "proportion", amount = .proportion, replace = FALSE)} else{NULL},
+                new_haul_N = if(.type=="haul") {list(type = "proportion", amount = .proportion, replace = FALSE)} else{NULL},
                 new_length_N = NULL,
+                max_length = 150,
                 boot.trip = TRUE,
                 boot.haul = TRUE,
                 boot.length = TRUE,
                 boot.age = FALSE,
                 expand.by.sampling.strata = TRUE,
-                expansion_factors = expansion,
+                expansion_factors = c("haul_numbers", "month_numbers"),
                 save_data_frame = FALSE) -> .output
     tictoc::toc()
-    out[[paste0("expansion_", expansion_names_global)[j]]] = .output
[…]

### 2025-03-07 run/paper_runs/paper_scenario_34.1.R

@@ -1,0 +1,60 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_34.1"
+iterations = 500
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+.lfreq_data = lfreq_data %>% tidytable::filter(substr(HAUL_JOIN, 1, 1)=="H")
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = .lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = TRUE,
+            expansion_factors = c("haul_numbers", "month_numbers"),
+            save_data_frame = TRUE) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2025-03-07 run/paper_runs/paper_scenario_35.1.R

@@ -1,52 +1,74 @@
 
 rm(list = ls())
-run_name = "paper_scenario_30.1"
+run_name = "paper_scenario_35.1"
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
 library(tidytable)
 library(baseISS)
 
+######### COME BACK TO THIS BECAUSE I WOULD HAVE TO CHNAGE CODE TO BE CONDITIONAL IN REBOOT LENGTH N ON PORT ONLY DATA
+
 
 ### Global
 iters_global = 500
-expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
-expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+samples_global = c(1, 5, 10, 15, 20)
+data_global = list("H_P", "H")
+data_names_global = c("H_P", "H")
 
 
 # Loop All
 out = list()
-  for(j in 1:length(expansion_global)){
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(data_global)){
 
-    expansion = expansion_global[[j]]
+    samples = samples_global[i]
+    .data = data_global[[j]]
+
+    if(.data=="H_P"){
+      .lfreq_data = lfreq_data
+    }else{
+      .lfreq_data = lfreq_data %>% tidytable::filter(substr(HAUL_JOIN, 1, 1)=="H")
+    }
 
     tictoc::tic()
     fishery_iss(species_code = "202",
                 area_code = "EBS",
                 length_based = TRUE,
                 iters = iters_global,
-                freq_data = lfreq_data,
-                yrs = NULL,
+                freq_data = .lfreq_data,
+                yrs = 1999,
                 bin = NULL,
                 plus_len = NULL,
                 post_strata = NULL,
                 minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
                 new_trip_N = NULL,
                 new_haul_N = NULL,
-                new_length_N = NULL,
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
                 boot.trip = TRUE,
                 boot.haul = TRUE,
                 boot.length = TRUE,
[…]

### 2025-03-07 run/paper_runs/paper_scenario_37.1.R

@@ -1,0 +1,60 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_37.1"
+iterations = 500
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = FALSE,
+            boot.haul = FALSE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = c("haul_numbers", "month_numbers"),
+            save_data_frame = TRUE) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2025-03-07 run/paper_runs/paper_scenario_37.2.R

@@ -1,0 +1,60 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_37.2"
+iterations = 500
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = FALSE,
+            boot.haul = TRUE,
+            boot.length = FALSE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = c("haul_numbers", "month_numbers"),
+            save_data_frame = TRUE) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2025-03-07 run/paper_runs/paper_scenario_37.3.R

@@ -1,0 +1,60 @@
+
+
+rm(list = ls())
+run_name = "paper_scenario_37.3"
+iterations = 500
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+
+
+tictoc::tic()
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = FALSE,
+            boot.length = FALSE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = c("haul_numbers", "month_numbers"),
+            save_data_frame = TRUE) -> .output
+tictoc::toc()
+.output
+
+
+saveRDS(.output, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iterations, "iters_output_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2025-03-21 README.Rmd
add runs and rmd inspections and clean up
commit namespace things

@@
 5.
-For EBS Pcod, age data has only been used when there exists alredy pre-processed length data associated with it.
+For EBS Pcod, age data has only been used when there exists already pre-processed length data associated with it.
 I.e., I matched the y2 length data object recieved from Steve with age data I downloaded when testing the baseISS functionality on age data.
@@
 
-- subsampling
+- subsampling length - done.
+
+- custom max length control - done.
+- plus group option - done.
+- different length bin size control - done.
+- different species - tested with Pollock only.
+- reboot_age.R
 

### 2025-03-31 README.Rmd
update documentation.

--- 2024-09-10 README.Rmd
@@
 
-The goal of baseISS is to develop a preliminary method for calculating input sample size (ISS) for fishery-dependent composition data.
+The goal of baseISS is to develop a preliminary bootstrap method for calculating input sample size (ISS) for fishery-dependent composition data.
 This data includes length- and age-frequency data collected by the NORPAC observer program and excludes fishery-independent data from surveys.
 Fishery-dependent composition data represents an important element of the 26 statistical catch at age stock assessment models for Alaskan fisheries managed by the NOAA AFSC.
-The ISS determines the precision attached to this data type, and therefore regulates its leverage in assessment model outputs such as biomass predictions.
+The ISS determines the precision attached to this data type, and therefore regulates (to a degree) its leverage in assessment model outputs such as biomass predictions.
 
-The structure and functionality of this package resembles surveyISS with some notable differences that accomodate the neuances of fishery-dependent data.
-These are covered in the next section, "Important Notes".
+The structure and functionality of this package resembles surveyISS with some notable differences that accommodate the nuances of fishery-dependent data.As of writing this, baseISS can perform the bootstrap ISS calculation for EBS Pcod length data, and has been successfully tested on EBS Pcod age data as well as Pollock length data.
 
-## Important Notes
+### Process Flow
+
+fishery_iss.R is the primary function that controls all other processes to calculate ISS.
+The descriptions of the function arguments in fishery_iss.R are the key resource for its capability.
+There are many options a user can toggle to suit their particular requirements, such as bootstrapping trips or hauls instead of length or age observations.
+
+This is an example of specifying fishery_iss.R for EBS Pcod:
+```{r, eval=F}
+
+fishery_iss(species_code = "202",
+            area_code = "EBS",
+            length_based = TRUE,
+            iters = iterations,
+            freq_data = lfreq_data,
+            yrs = NULL,
+            bin = NULL,
+            plus_len = NULL,
+            post_strata = NULL,
+            minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+            new_trip_N = NULL,
+            new_haul_N = NULL,
+            new_length_N = NULL,
+            max_length = 150,
+            boot.trip = TRUE,
+            boot.haul = TRUE,
+            boot.length = TRUE,
+            boot.age = FALSE,
+            expand.by.sampling.strata = FALSE,
+            expansion_factors = c("haul_numbers", "month_numbers"),
+            save_data_frame = TRUE) -> .output
+
+```
 
@@
 The following conditions of an input data frame for any species must be met:
-1.
-(length data) There exists a WEIGHT1 column that represents the haul-level proportions-at-length of the observed lengths.
-This is calculated by dividing the frequency of the observed length within a haul by the total number of fish lengthed in that haul.
-It should be a standard calculation that is exactly the same for every species.
-This convention...
 
-2. Length data be condensed with sum_frequency column.
+1. Age data include associated lengths.
 
-3. Age data include associated lengths.
+2.
+Age data needs to be flattened, meaning every observation has a row in the data frame whether it is identical to another or not.
+This ensures that the length measurement associated with the age measurement is preserved.
 
-4. Age data flattened, no "sum_frequency" column.
+3.
+For EBS Pcod, age data has only been used when there exists already pre-processed length data associated with it.
+I.e., I matched the y2 length data object received from Steve with age data I downloaded when testing the baseISS functionality on age data.
+This was necessary because I needed quantities like YAGM_SNUM to perform the weighted expansion.
 
@@
 Unlike surveyISS, this is necessary for several reasons: a.
-there will be many more hauls with lengths than ages, b.
-it is likely that the user options such as post_stratify will be different between length data and age data, c.
-NOTE ANOTHER ONE WHEN YOU REMEMBER.
+there will be many more hauls with lengths than ages for fishery-dependent data, b.
+it is likely that the user options such as post_stratify will be different between length data and age data, and these must be performed separately between length and age analyses.
+
+2.
+You can't chose the species from a big data set containing all the species like you can in surveyISS.
+This is because data sets for each species should include unique columns necessary to apply their unique expansion methods.
+For EBS Pcod for example, these columns are only available after much pre-processing of the raw data.
+The user can input a species-specific data frame into fishery_iss.R and run it according to their specifications.
+
+3.
+A user can add their species- and area-specific expansion routine to expand_props.R.
+As of writing this, the only official expansion routine coded is for EBS Pcod length data from the 2023 assessment.
+There are also placeholder expansion routines for age data for the EBS Pcod and length data for Pollock to test the generic functionality of baseISS.
 
 ### Developing Functionality
+- different species - tested with Pollock only. Need to re-test with pollock using generic data download.
+- reboot_age.R - needs developing
+- combine post-strata. needs developing.
 
-## Installation
+### Installation
 
@@
 
-## Example
-
-This is a basic example which shows you how to solve a common problem:
-
-```{r example}
-library(baseISS)
-## basic example code
-```
-
-What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:
-
-```{r cars}
-summary(cars)
-```
-
-You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.
-
-You can also embed plots, for example:
-
-```{r pressure, echo = FALSE}
-plot(pressure)
-```
-
-In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
+### Example
+Coming Soon...

### 2025-03-31 R/fishery_iss.R

@@ -14,7 +14,7 @@
 #' @param bin bin size (NULL = 1 cm), also can use custom length bins through defining vector of upper length bin limits, i.e., c(5, 10, 20, 35, 60), plus length group will automatically be populated and denoted with the largest defined bin + 1 (i.e., 61 for provided example)
 #' @param plus_len If set at a value other than NULL, computes length expansion with a plus-length group (default = FALSE)
 #' @param post_strata list(strata = character string, nested = Boolean) if NULL, then no post stratification. The first element of post_strata is a character string with name(s) of post strata type. Accepted types are "GEAR", etc. These must be column name(s) in the data frame where each row has an entry and there are no NAs. The second element in post_strata allows for nested post-strata (e.g., "GEAR", "SEX") that are in order of the desired nested hierarchy, then the final results will be a nested list in order of the listed post-strata as well. Perhaps there should be an error message for attempts with strata names that are not in freq_data or it does exist, but there are NAs in it.
-#' @param combine.post.strata list(strata = post_strata$strata, .by = either "weight" or "number") if NULL, then ISS between post strata is not combined into one. Otherwise, it is combined according to the strata defined in the post_strata arguement, and .by either weight or numbers by adding up the weight or numbers in each unique haul for every year and applying a weighted average to the ISS from that strata in addition to the proportions-at-age vector in the output.
+#' @param combine.post.strata Under development. Intention: list(strata = post_strata$strata, .by = either "weight" or "number") if NULL, then ISS between post strata is not combined into one. Otherwise, it is combined according to the strata defined in the post_strata arguement, and .by either weight or numbers by adding up the weight or numbers in each unique haul for every year and applying a weighted average to the ISS from that strata in addition to the proportions-at-age vector in the output.
 #' @param minimum_sample_size list(resolution = character string, size = integer). If NULL, then no minimum sample size. If not NULL, The sample size at the chosen resolution (must be column in freq_data, e.g., YAGM_SFREQ for EBS Pcod) for which to filter out data that does not meet the minimum sample size requested. Example: minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30). Note that this filters to keep only samples GREATER than 30 at the YAGM resolution.
[…]

### 2025-03-31 Rmd/paper_plots/paper_plots_1.3.Rmd
add paper runs and plots

@@
 
-out_3.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.4_ISS_500iters_output_2025-03-06.RDS") ### mislabeled
+out_3.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_3.2_ISS_500iters_output_2025-03-07.RDS") ### mislabeled
 
@@
 # par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
+par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
+plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
+lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
+lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "red")
+legend(1977, 11000, lty = c(1,1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n")
+text(1977, 14000, "A")
+
+plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3) 
+text(1977, 420000, "B")
+mtext("Year", side = 1, line = 2, cex = 2)
+
+# averages
+out_1.4$length$iss$iss %>% mean()
+assessment_2023_iss$iss %>% mean()
+
+```
+
+### * Time series 2 panel no-SS
+
+```{r, fig.height=6}
+df = data.frame(rss = out_1.4$length$rss$rss, year = as.factor(out_1.4$length$rss$YEAR))
+
+# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
+# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
 par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
@@
 
-\newpage
-
-### * 2003 and 2004 histograms
-```{r, fig.height=8, fig.width=9}
+## histogram test, which are similar? 
+provide a counter example to 2003:2004
+
+```{r}
 
 out_1.4$length$og_props %>% 
-  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::filter(YEAR %in% 1997:1998) %>% 
   tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
@@
 
+p1
+
+```
+
+\newpage
+
+### * 2003 and 2004 histograms
+```{r, fig.height=8, fig.width=9}
+out_1.4$length$og_props %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
+  geom_line() +
+  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  scale_x_continuous(limits = c(22, 108),
+                     n.breaks = 9) +
+  labs(x = "Length (cm)", y = "Frequency", tag = "A") +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  scale_y_continuous(limits = c(0, .04), expand = c(0, 0))
+
 # now do RSS
@@
 p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
-  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
   theme_classic() +
@@
         plot.tag = element_text(size = 14, face = "bold")) +
-  labs(x = "RSS", y = "Count", tag = "B") + 
+  labs(x = "RSS", y = "Count", tag = "F") + 
   geom_point(data = props.sub %>% 
@@
                tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
-  scale_y_continuous(limits = c(0, 300), expand = c(0, 0)) +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
   # scale_x_continuous(n.breaks = 8)
   scale_x_continuous(breaks = seq(0, 35000, by = 2500),
-                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000))
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))
+
+# now do RSS with boot_length only.
+out_5.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "B") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_5.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))
+
+# now do RSS with boot_length and boot_haul.
+out_9.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "C") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_9.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))
+
+# now do RSS with boot all.
+out_4.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "D") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_4.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))
+
+# now do RSS with boot all + SS
+out_2.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.5 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "E") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_2.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))
 
 p1 / p3
+p1 / p3 / p3.2
+```
+
+```{r, fig.height=10}
+p1 / p3.2 / p3.3 / p3.4 / p3.5 / p3
 
@@
 This is reflected in the RSS (ref figure).
+
+### with another year
+
+\newpage
+
+#### histograms
+```{r, fig.height=10}
+out_1.4$length$og_props %>% 
+  tidytable::filter(YEAR %in% 2021:2022) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
+  geom_line() +
+  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  scale_x_continuous(limits = c(22, 108),
+                     n.breaks = 9) +
+  labs(x = "Length (cm)", y = "Frequency", tag = "A") +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  scale_y_continuous(limits = c(0, .04), expand = c(0, 0))
+
+# now do RSS
+out_1.4$length$rss %>% 
+  tidytable::filter(YEAR %in% 2021:2022) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "F") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_1.4$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))
+
+# now do RSS with boot_length only.
+out_5.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2021:2022) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "B") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_5.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))
+
+# now do RSS with boot_length and boot_haul.
+out_9.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2021:2022) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "C") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_9.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))
+
+# now do RSS with boot all.
+out_4.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2021:2022) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "D") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_4.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))
+
+# now do RSS with boot all + SS
+out_2.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2021:2022) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.5 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "E") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_2.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))
+
+# p1 / p3
+# p1 / p3 / p3.2
+
+p1 / p3.2 / p3.3 / p3.4 / p3.5 / p3
+
+```
+
+### with another year
+
+\newpage
+
+#### histograms
+```{r, fig.height=10}
+out_1.4$length$og_props %>% 
+  tidytable::filter(YEAR %in% 1997:1998) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
+  geom_line() +
+  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  scale_x_continuous(limits = c(22, 108),
+                     n.breaks = 9) +
+  labs(x = "Length (cm)", y = "Frequency", tag = "A") +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  scale_y_continuous(limits = c(0, .04), expand = c(0, 0))
+
+# now do RSS
+out_1.4$length$rss %>% 
+  tidytable::filter(YEAR %in% 1997:1998) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 20) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "F") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_1.4$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 3000, by = 250),
+                     limits = c(0, 3000),
+                     expand = c(0, 0))
+
+# now do RSS with boot_length only.
+out_5.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 1997:1998) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 10) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "B") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_5.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 3000, by = 250),
+                     limits = c(0, 3000),
+                     expand = c(0, 0))
+
+# now do RSS with boot_length and boot_haul.
+out_9.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 1997:1998) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 10) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "C") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_9.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 3000, by = 250),
+                     limits = c(0, 3000),
+                     expand = c(0, 0))
+
+# now do RSS with boot all.
+out_4.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 1997:1998) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 10) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "D") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_4.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 3000, by = 250),
+                     limits = c(0, 3000),
+                     expand = c(0, 0))
+
+# now do RSS with boot all + SS
+out_2.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 1997:1998) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.5 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 10) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "E") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_2.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 3000, by = 250),
+                     limits = c(0, 3000),
+                     expand = c(0, 0))
+
+# p1 / p3
+# p1 / p3 / p3.2
+
+p1 / p3.2 / p3.3 / p3.4 / p3.5 / p3
+
+```
+
+# For presentation
+```{r, fig.height=10}
+out_1.4$length$og_props %>% 
+  tidytable::filter(YEAR %in% 1997) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
+  geom_line() +
+  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  scale_x_continuous(limits = c(22, 108),
+                     n.breaks = 9) +
+  labs(x = "Length Bin-b (cm)", y = "Proportion (P)", tag = "") +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  scale_y_continuous(limits = c(0, .032), expand = c(0, 0)) +
+  theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14,face="bold"))
+
+out_1.4$length$iss$nss[out_1.4$length$iss$YEAR==1997]
+```
 
@@
         axis.title.x = element_blank())
-
+```
+
+\newpage
+
+```{r, fig.width=9, fig.height=5}
 # 1999:2023
 df2 %>% 
-  filter(year%in%1999:2023) -> df2
-ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+  filter(year%in%1999:2023) %>% 
+ggplot(aes(x = year, y = ISS, group = scenario, colour = scenario)) +
   geom_line() +
-  labs(x = "", y = "ISSB") +
   geom_point() +
-  theme_classic() +
-  theme(legend.position = c(0.84, 0.8),
-        axis.title.x = element_blank())
+  scale_shape_manual(values = c(1,2,3)) +
+  labs(x = "Year", y = "ISSB", color = "Expansion Complexity") +
+  scale_color_manual(labels = c("None", "Medium: haul only", "Full: haul, area, gear, month"), values = c("blue", "red", "black")) +
+  geom_point() + 
+  theme_classic() + 
+  theme(legend.position = c(0.7, 0.9),
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12),
+        legend.text = element_text(size = 12),
+        legend.title = element_text(size = 14))
 ```
@@
 
-```{r, fig.height=8}
+```{r, fig.height=6}
 ### plots
@@
                              label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-80, 10))
+
+## for presentation
+df4.a %>%
+  filter(type=="relative_N") %>% 
+  ggplot(aes(x = scenario, y = ISS.error)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Adjusted Samples Per Haul", y = "ISSB % Difference", tag = "") +
+  theme_classic() +
+  theme(legend.position = c(3, 0.15),
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12),
+        legend.text = element_text(size = 12),
+        legend.title = element_text(size = 14)) + 
+  guides(fill = guide_legend(title = "relative to baseline")) +
   geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
@@
 ```
+
+# * Steve's data
+
+```{r}
+
+a.out = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/Derived_quants.csv")
+p.out = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/parameters.csv")
+
+a.out %>% glimpse()
+
+SSB.names = paste0("SSB_", 1977:2038)
+SPRratio.names = paste0("SPRratio_", 1977:2038)
+Bratio.names = paste0("Bratio_", 1977:2038)
+
+SSB = a.out %>% 
+  tidytable::filter(MODEL2 == "OM tuned", Label%in%SSB.names) %>% 
+  tidytable::bind_rows(a.out %>% 
+                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%SSB.names)) %>% 
+  tidytable::mutate(Year = as.numeric(substr(Label, 5, 8)))
+SPRratio = a.out %>% 
+  tidytable::filter(MODEL2 == "OM tuned", Label%in%SPRratio.names) %>% 
+  tidytable::bind_rows(a.out %>% 
+                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%SPRratio.names)) %>% 
+  tidytable::mutate(Year = as.numeric(substr(Label, 10, 13)))
+Bratio = a.out %>% 
+  tidytable::filter(MODEL2 == "OM tuned", Label%in%Bratio.names) %>% 
+  tidytable::bind_rows(a.out %>% 
+                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%Bratio.names)) %>% 
+  tidytable::mutate(Year = as.numeric(substr(Label, 8, 11)))
+
+SSB %>% 
+  tidytable::rename(Model_run = MODEL2) %>% 
+  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_run, linetype = Model_run)) +
+  geom_line() +
+  geom_ribbon(alpha = 0.5) +
+  xlab("Year") + 
+  ylab("SSB") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.85), 
+        legend.direction = "vertical", 
+        legend.box = "vertical") +
+  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
+  theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14,face="bold"))
+
+SPRratio %>% 
+  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = MODEL2, linetype = MODEL2)) +
+  geom_line() +
+  geom_ribbon(alpha = 0.5) +
+  xlab("Year") + 
+  ylab("SPRratio") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.3), 
+        legend.direction = "vertical", 
+        legend.box = "vertical") +
+  geom_vline(xintercept = 2023, linetype = "dashed", color = "black")
+Bratio %>% 
+  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = MODEL2, linetype = MODEL2)) +
+  geom_line() +
+  geom_ribbon(alpha = 0.5) +
+  xlab("Year") + 
+  ylab("Bratio") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.85), 
+        legend.direction = "vertical", 
+        legend.box = "vertical") +
+  geom_vline(xintercept = 2023, linetype = "dashed", color = "black")
+
+# Tables of parameters
+
+p.out %>% 
+  tidytable::filter(Label%in%c("VonBert_K_Fem_GP_1", "L_at_Amax_Fem_GP_1", "SR_LN(R0)"),
+                    MODEL2%in%c("OM tuned", "Fiss tuned")) %>% 
+  tidytable::mutate(StdDev = Parm_StDev) %>% 
+  tidytable::select(-Parm_StDev) %>% 
+  tidytable::bind_rows(a.out %>% 
+                         tidytable::filter(Label%in%c("SSB_2023", "SSB_2038", "Bratio_2023", "Bratio_2038", "SPRratio_2023", "SPRratio_2038"),
+                                           MODEL2%in%c("OM tuned", "Fiss tuned"))) %>% 
+  tidytable::select(-X, -MODEL, -HI, -LO) -> p.table
+
+require(xtable)
+age <- sample(c('30-50', '50-70', '70+'), 200, replace=T)
+sex <- sample(c('Male', 'Female'), 200, replace=T)
+val <- table(age, sex)
+val <- rbind(val, formatC(prop.table(val)*100, format='f', digits=1))
+val <- structure(val, dim=c(3, 4))
+val <- rbind(c('n', '%'), val)
+rownames(val) <- c('', sort(unique(age)))
+val <- xtable(val)
+
+addtorow <- list()
+addtorow$pos <- list(0)
+addtorow$command <- paste0(paste0('& \\multicolumn{2}{c}{', sort(unique(sex)), '}', collapse=''), '\\\\')
+
+print(val, add.to.row=addtorow, include.colnames=F)
+
+```

### 2025-03-31 Rmd/paper_plots/paper_plots_1.4.Rmd
add paper runs and plots

---
title: "Paper Plots V2"
author: "Brett Stacy"
date: "2024-11-25"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, results = "hide", fig.width = 8.5, fig.height = 5, dpi = 600)
library(tidytable)
library(data.table)
library(reshape2)
library(ggplot2)
library(knitr)
library(stringr)
library(patchwork)
opts_knit$set(eval.after = "fig.cap")
options(scipen = 5)
```

# Introduction
Plots for paper:

## Data
```{r}

out_1.4 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.4_ISS_1000iters_output_2025-01-23.RDS")

out_3.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_3.2_ISS_500iters_output_2025-03-07.RDS") ### mislabeled

out_5.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_5.2_ISS_500iters_output_2025-01-27.RDS")

out_9.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_9.2_ISS_500iters_output_2025-01-27.RDS")

out_4.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_4.2_ISS_500iters_output_2025-01-28.RDS")

out_2.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.2_ISS_500iters_output_2025-01-28.RDS")

out_31.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_31.1.TAS_ISS_500_iters_2025-03-02.RDS")

out_39.5 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_39.5_ISS_500_iters_2025-03-21.RDS")

# save out_1.4 for Steve to plug into the assessment
out_1.4$length$iss %>% 
  select(YEAR, iss) %>% 
  write.csv(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/issb_v1_from_Brett_Stacy.csv", row.names = F)

assessment_2023_iss = tidytable(year = 1977:2023,
                                iss = c(27,
                                45,
                                54,
                                54,
                                63,
                                31,
                                117,
                                140,
                                211,
                                216,
                                396,
                                401,
                                185,
                                189,
                                1565,
                                1543,
                                913,
                                1435,
                                1561,
                                2020,
                                2142,
                                2046,
                                2722,
                                2960,
                                3140,
                                3446,
                                4301,
                                3608,
                                3455,
                                2694,
                                2115,
                                2502,
                                2218,
                                1975,
                                2596,
                                2776,
                                3293,
                                3604,
                                3324,
                                2821,
                                2469,
                                1899,
                                1367,
                                1048,
                                859,
                                1160,
                                706))

# survey vs observer length measurements
obs_numbers = tidytable(year = 1982:2023,
                        survey = c(10863,
                        13143,
                        12133,
                        17150,
                        15872,
                        9483,
                        6950,
                        4246,
                        5428,
                        7069,
                        10129,
                        10500,
                        12931,
                        9820,
                        9348,
                        9591,
                        9574,
                        11183,
                        12170,
                        19078,
                        12365,
                        11835,
                        10986,
                        11753,
                        12530,
                        13441,
                        15328,
                        23737,
                        21223,
                        25150,
                        30177,
                        19902,
                        29204,
                        19880,
                        19507,
                        15020,
                        8806,
                        23408,
                        0,
                        17397,
                        16677,
                        19943),
                        fishery = c(9658,
                                    33200,
                                    45635,
                                    66940,
                                    58257,
                                    129226,
                                    111065,
                                    58625,
                                    39698,
                                    347227,
                                    344923,
                                    248967,
                                    359147,
                                    344794,
                                    445217,
                                    474908,
                                    438746,
                                    186233,
                                    199708,
                                    210419,
                                    230802,
                                    288854,
                                    237487,
                                    228664,
                                    179782,
                                    140663,
                                    164860,
                                    147875,
                                    131514,
                                    172269,
                                    192273,
                                    211962,
                                    234476,
                                    213888,
                                    182980,
                                    157482,
                                    124004,
                                    86800,
                                    65301,
                                    55858,
                                    73025,
                                    42942))

obs_numbers %>% 
  tidytable::summarise(sum(survey), sum(fishery))

obs_numbers %>% 
  tidytable::summarise(mean(survey), mean(fishery))

```

## ISSB Results 
### * Time series 2 panel

```{r, fig.height=6}
df = data.frame(rss = out_1.4$length$rss$rss, year = as.factor(out_1.4$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$iss, type = "o", pch = 19, ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue", type = "o", pch = 3)
lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "orange", type = "o", 5)
legend(1977, 11000, lty = c(1,1,1), col = c("black", "blue", "orange"), pch = c(19, 3, 5), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n")
text(1977, 14000, "A")

plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3) 
text(1977, 420000, "B")
mtext("Year", side = 1, line = 2, cex = 1.5)

# averages
out_1.4$length$iss$iss %>% mean()
assessment_2023_iss$iss %>% mean()

```

### * Time seris components

\newpage

```{r, fig.height=5.5}
sub_range = out_5.2$length$iss$YEAR %in% 1977:2023

par(mfrow = c(1,1))
plot(out_5.2$length$iss$YEAR[sub_range], out_5.2$length$iss$iss[sub_range], ylab = "ISSB", cex.lab = 1.3, col = "cyan", ylim = c(0, 25000), xlab = "Year", lwd = 2, type = "o", pch= 18)
lines(out_9.2$length$iss$YEAR[sub_range], out_9.2$length$iss$iss[sub_range], type = "o", pch = 15, col = "orange3", lwd = 2)
lines(out_4.2$length$iss$YEAR[sub_range], out_4.2$length$iss$iss[sub_range], type = "o", pch = 17, col = "magenta", lwd = 2)
lines(out_2.2$length$iss$YEAR[sub_range], out_2.2$length$iss$iss[sub_range], type = "o", pch = 23, col = "green", lwd = 2)
lines(out_1.4$length$iss$YEAR[sub_range], out_1.4$length$iss$iss[sub_range], type = "o", pch = 19, col = "black", lwd = 2, lty = 1)

# legend("topleft", title = "Component Case", legend = c("1", "2", "3", "4", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"), bty = "n")
legend("topleft", title = "Component Case", legend = c("1", "2", "3", "4", "full"), lty = c(1,1,1,1,1), pch = c(18, 15, 17, 23, 19), col = c("cyan", "orange3", "magenta", "green", "black"), bty = "n", lwd = rep(2, 5))

# not accounting for correlations exceed hauls?
sum((out_5.2$length$iss$iss[sub_range]-out_1.4$length$iss$nhls) < 0)

```

\newpage

#### * TOGETHER

\newpage

```{r, fig.height=8}
df = data.frame(rss = out_1.4$length$rss$rss, year = as.factor(out_1.4$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(3,1), mar = c(0,3.1,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$iss, type = "o", pch = 19, ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue", type = "o", pch = 3)
lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "orange", type = "o", 5)
legend(1977, 11000, lty = c(1,1,1), col = c("black", "blue", "orange"), pch = c(19, 3, 5), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n")
text(1977, 14000, "A")

plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xaxt = "n", cex.lab = 1.3) 
text(1977, 420000, "B")

plot(out_5.2$length$iss$YEAR[sub_range], out_5.2$length$iss$iss[sub_range], ylab = "ISSB", cex.lab = 1.3, col = "cyan", ylim = c(0, 25000), xlab = "Year", lwd = 1.5, type = "o", pch= 18)
lines(out_9.2$length$iss$YEAR[sub_range], out_9.2$length$iss$iss[sub_range], type = "o", pch = 15, col = "orange3", lwd = 1.5)
lines(out_4.2$length$iss$YEAR[sub_range], out_4.2$length$iss$iss[sub_range], type = "o", pch = 17, col = "magenta", lwd = 1.5)
lines(out_2.2$length$iss$YEAR[sub_range], out_2.2$length$iss$iss[sub_range], type = "o", pch = 23, col = "green", lwd = 1.5)
lines(out_1.4$length$iss$YEAR[sub_range], out_1.4$length$iss$iss[sub_range], type = "o", pch = 19, col = "black", lwd = 1.5, lty = 1)
legend(1977, 20000, title = "Component Case", legend = c("1", "2", "3", "4", "full"), lty = c(1,1,1,1,1), pch = c(18, 15, 17, 23, 19), col = c("cyan", "orange3", "magenta", "green", "black"), bty = "n", lwd = rep(1.5, 5))
text(1977, 23000, "C")

mtext("Year", side = 1, line = 2, cex = 1.3)

```

\newpage

* Samples VS Expantion. intra-relative

Make sure to say in the paper: Methods: Unlike changing the number of hauls or trips (static quality of the data), the stock assessor has discression over changing the expansion method. IF they change it, they will change it for past and present data, not change it based on blocks of time or something like that. SO, these scenarios demonstrate what we can expect to see in near future years IF we decrease the sample size, ASSUMING the expansion complexity will change. For example, IF the expansion complexity will change, what will be the expected loss of precision if we reduce the sample size from 20 to 10. REMEMBER, these scenarios are relative to the N=20 case for each expansion complexity case.

```{r, fig.width=8}

out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_38.2_ISS_500_iters_2025-03-20.RDS")

year = out_22.1$samples_1$expansion_NULL$length$iss$YEAR

df = tidytable(year = year,
               N1_Enone = out_22.1$samples_1$expansion_NULL$length$iss$iss,
               N5_Enone = out_22.1$samples_5$expansion_NULL$length$iss$iss,
               N10_Enone = out_22.1$samples_10$expansion_NULL$length$iss$iss,
               N15_Enone = out_22.1$samples_15$expansion_NULL$length$iss$iss,
               N20_Enone = out_22.1$samples_20$expansion_NULL$length$iss$iss,
               N1_Emedium = out_22.1$samples_1$expansion_haul_numbers$length$iss$iss,
               N5_Emedium = out_22.1$samples_5$expansion_haul_numbers$length$iss$iss,
               N10_Emedium = out_22.1$samples_10$expansion_haul_numbers$length$iss$iss,
               N15_Emedium = out_22.1$samples_15$expansion_haul_numbers$length$iss$iss,
               N20_Emedium = out_22.1$samples_20$expansion_haul_numbers$length$iss$iss,
               N1_Efull = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
               N5_Efull = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
               N10_Efull = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N15_Efull = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
               N20_Efull = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

df2[grep("Enone", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Enone"])/df2$ISS[df2$scenario=="N20_Enone"],
                    type = "Enone",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("Emedium", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Emedium"])/df2$ISS[df2$scenario=="N20_Emedium"],
                    type = "Emedium",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -9)) -> df3.2

df2[grep("Efull", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
                    type = "Efull",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.0

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Samples per Haul", y = "ISSB % Difference") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.2)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10)) +
  scale_x_discrete(labels = c("1", "5", "10", "15", "20"))

# Stats
df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median

```

### * Samples VS Expantion. inter-relative
DON'T SHOW THIS ONE BECAUSE IT IS LESS RELEVANT THAN THE ABOVE
```{r, fig.width=8, eval=F}

out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_38.2_ISS_500_iters_2025-03-20.RDS")

year = out_22.1$samples_1$expansion_NULL$length$iss$YEAR

df = tidytable(year = year,
               N1_Enone = out_22.1$samples_1$expansion_NULL$length$iss$iss,
               N5_Enone = out_22.1$samples_5$expansion_NULL$length$iss$iss,
               N10_Enone = out_22.1$samples_10$expansion_NULL$length$iss$iss,
               N15_Enone = out_22.1$samples_15$expansion_NULL$length$iss$iss,
               N20_Enone = out_22.1$samples_20$expansion_NULL$length$iss$iss,
               N1_Emedium = out_22.1$samples_1$expansion_haul_numbers$length$iss$iss,
               N5_Emedium = out_22.1$samples_5$expansion_haul_numbers$length$iss$iss,
               N10_Emedium = out_22.1$samples_10$expansion_haul_numbers$length$iss$iss,
               N15_Emedium = out_22.1$samples_15$expansion_haul_numbers$length$iss$iss,
               N20_Emedium = out_22.1$samples_20$expansion_haul_numbers$length$iss$iss,
               N1_Efull = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
               N5_Efull = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
               N10_Efull = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N15_Efull = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
               N20_Efull = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,

               NN = out_1.4$length$iss$iss[out_1.4$length$iss$YEAR%in%1999:2023])

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

df2[grep("Enone", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "Enone",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("Emedium", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "Emedium",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -9)) -> df3.2

df2[grep("Efull", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "Efull",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.0

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Samples per Haul", y = "ISSB % Difference") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.2)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10)) +
  scale_x_discrete(labels = c("1", "5", "10", "15", "20"))

# Stats
df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median

```

### DATA: Samples VS Haul 
```{r, fig.width=8}

out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_40.1_ISS_500_iters_2025-03-19.RDS")

year = out_24.1$samples_1$haul_0.25$length$iss$YEAR

df = tidytable(year = year,
               N1_H0.25 = out_24.1$samples_1$haul_0.25$length$iss$iss,
               N5_H0.25 = out_24.1$samples_5$haul_0.25$length$iss$iss,
               N10_H0.25 = out_24.1$samples_10$haul_0.25$length$iss$iss,
               N15_H0.25 = out_24.1$samples_15$haul_0.25$length$iss$iss,
               N20_H0.25 = out_24.1$samples_20$haul_0.25$length$iss$iss,
               N1_H0.5 = out_24.1$samples_1$haul_0.5$length$iss$iss,
               N5_H0.5 = out_24.1$samples_5$haul_0.5$length$iss$iss,
               N10_H0.5 = out_24.1$samples_10$haul_0.5$length$iss$iss,
               N15_H0.5 = out_24.1$samples_15$haul_0.5$length$iss$iss,
               N20_H0.5 = out_24.1$samples_20$haul_0.5$length$iss$iss,
               N1_H0.75 = out_24.1$samples_1$haul_0.75$length$iss$iss,
               N5_H0.75 = out_24.1$samples_5$haul_0.75$length$iss$iss,
               N10_H0.75 = out_24.1$samples_10$haul_0.75$length$iss$iss,
               N15_H0.75 = out_24.1$samples_15$haul_0.75$length$iss$iss,
               N20_H0.75 = out_24.1$samples_20$haul_0.75$length$iss$iss,
               N1_H1.0 = out_31.1$samples_1$data_H_P$length$iss$iss,
               N5_H1.0 = out_31.1$samples_5$data_H_P$length$iss$iss,
               N10_H1.0 = out_31.1$samples_10$data_H_P$length$iss$iss,
               N15_H1.0 = out_31.1$samples_15$data_H_P$length$iss$iss,
               N20_H1.0 = out_31.1$samples_20$data_H_P$length$iss$iss,

               NN = out_1.4$length$iss$iss[out_1.4$length$iss$YEAR%in%1999:2023])

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

df2[grep("H0.25", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "0.25",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("H0.5", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "0.5",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2

df2[grep("H0.75", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "0.75",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df2[grep("H1.0", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "1.0",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.4

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::bind_rows(df3.4) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.1.b

```

### DATA: Samples VS Haul. Replace=TRUE, including 1.0
```{r, fig.width=8}

out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_40.2_ISS_500_iters_2025-03-23.RDS")

year = out_24.1$samples_1$haul_0.25$length$iss$YEAR

df = tidytable(year = year,
               N1_H0.25 = out_24.1$samples_1$haul_0.25$length$iss$iss,
               N5_H0.25 = out_24.1$samples_5$haul_0.25$length$iss$iss,
               N10_H0.25 = out_24.1$samples_10$haul_0.25$length$iss$iss,
               N15_H0.25 = out_24.1$samples_15$haul_0.25$length$iss$iss,
               N20_H0.25 = out_24.1$samples_20$haul_0.25$length$iss$iss,
               N1_H0.5 = out_24.1$samples_1$haul_0.5$length$iss$iss,
               N5_H0.5 = out_24.1$samples_5$haul_0.5$length$iss$iss,
               N10_H0.5 = out_24.1$samples_10$haul_0.5$length$iss$iss,
               N15_H0.5 = out_24.1$samples_15$haul_0.5$length$iss$iss,
               N20_H0.5 = out_24.1$samples_20$haul_0.5$length$iss$iss,
               N1_H0.75 = out_24.1$samples_1$haul_0.75$length$iss$iss,
               N5_H0.75 = out_24.1$samples_5$haul_0.75$length$iss$iss,
               N10_H0.75 = out_24.1$samples_10$haul_0.75$length$iss$iss,
               N15_H0.75 = out_24.1$samples_15$haul_0.75$length$iss$iss,
               N20_H0.75 = out_24.1$samples_20$haul_0.75$length$iss$iss,
               N1_H1.0 = out_24.1$samples_1$haul_1$length$iss$iss,
               N5_H1.0 = out_24.1$samples_5$haul_1$length$iss$iss,
               N10_H1.0 = out_24.1$samples_10$haul_1$length$iss$iss,
               N15_H1.0 = out_24.1$samples_15$haul_1$length$iss$iss,
               N20_H1.0 = out_24.1$samples_20$haul_1$length$iss$iss,

               NN = out_1.4$length$iss$iss[out_1.4$length$iss$YEAR%in%1999:2023])

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

df2[grep("H0.25", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "0.25",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("H0.5", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "0.5",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2

df2[grep("H0.75", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "0.75",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df2[grep("H1.0", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "1.0",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.4

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::bind_rows(df3.4) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.1.b

```

### DATA: Samples VS Trip
```{r, fig.width=8}

out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_39.2_ISS_500_iters_2025-03-21.RDS")

year = out_23.1$samples_1$trip_0.25$length$iss$YEAR

df = tidytable(year = year,
               N1_T0.25 = out_23.1$samples_1$trip_0.25$length$iss$iss,
               N5_T0.25 = out_23.1$samples_5$trip_0.25$length$iss$iss,
               N10_T0.25 = out_23.1$samples_10$trip_0.25$length$iss$iss,
               N15_T0.25 = out_23.1$samples_15$trip_0.25$length$iss$iss,
               N20_T0.25 = out_23.1$samples_20$trip_0.25$length$iss$iss,
               N1_T0.5 = out_23.1$samples_1$trip_0.5$length$iss$iss,
               N5_T0.5 = out_23.1$samples_5$trip_0.5$length$iss$iss,
               N10_T0.5 = out_23.1$samples_10$trip_0.5$length$iss$iss,
               N15_T0.5 = out_23.1$samples_15$trip_0.5$length$iss$iss,
               N20_T0.5 = out_23.1$samples_20$trip_0.5$length$iss$iss,
               N1_T0.75 = out_23.1$samples_1$trip_0.75$length$iss$iss,
               N5_T0.75 = out_23.1$samples_5$trip_0.75$length$iss$iss,
               N10_T0.75 = out_23.1$samples_10$trip_0.75$length$iss$iss,
               N15_T0.75 = out_23.1$samples_15$trip_0.75$length$iss$iss,
               N20_T0.75 = out_23.1$samples_20$trip_0.75$length$iss$iss,
               N1_T1.0 = out_31.1$samples_1$data_H_P$length$iss$iss,
               N5_T1.0 = out_31.1$samples_5$data_H_P$length$iss$iss,
               N10_T1.0 = out_31.1$samples_10$data_H_P$length$iss$iss,
               N15_T1.0 = out_31.1$samples_15$data_H_P$length$iss$iss,
               N20_T1.0 = out_31.1$samples_20$data_H_P$length$iss$iss,

               NN = out_39.5$samples_20$trip_1$length$iss$iss) 
               # NN = out_1.4$length$iss$iss[out_1.4$length$iss$YEAR%in%1999:2023])

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

df2[grep("T0.25", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "0.25",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("T0.5", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "0.5",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2

df2[grep("T0.75", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "0.75",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df2[grep("T1.0", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "1.0",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.4

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::bind_rows(df3.4) %>%
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.1.a

```

### DATA: Samples VS Trip. Replace=TRUE, including 1.0
```{r, fig.width=8}

out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_39.6_ISS_500_iters_2025-03-23.RDS")

year = out_23.1$samples_1$trip_0.25$length$iss$YEAR

df = tidytable(year = year,
               N1_T0.25 = out_23.1$samples_1$trip_0.25$length$iss$iss,
               N5_T0.25 = out_23.1$samples_5$trip_0.25$length$iss$iss,
               N10_T0.25 = out_23.1$samples_10$trip_0.25$length$iss$iss,
               N15_T0.25 = out_23.1$samples_15$trip_0.25$length$iss$iss,
               N20_T0.25 = out_23.1$samples_20$trip_0.25$length$iss$iss,
               N1_T0.5 = out_23.1$samples_1$trip_0.5$length$iss$iss,
               N5_T0.5 = out_23.1$samples_5$trip_0.5$length$iss$iss,
               N10_T0.5 = out_23.1$samples_10$trip_0.5$length$iss$iss,
               N15_T0.5 = out_23.1$samples_15$trip_0.5$length$iss$iss,
               N20_T0.5 = out_23.1$samples_20$trip_0.5$length$iss$iss,
               N1_T0.75 = out_23.1$samples_1$trip_0.75$length$iss$iss,
               N5_T0.75 = out_23.1$samples_5$trip_0.75$length$iss$iss,
               N10_T0.75 = out_23.1$samples_10$trip_0.75$length$iss$iss,
               N15_T0.75 = out_23.1$samples_15$trip_0.75$length$iss$iss,
               N20_T0.75 = out_23.1$samples_20$trip_0.75$length$iss$iss,
               N1_T1.0 = out_23.1$samples_1$trip_1$length$iss$iss,
               N5_T1.0 = out_23.1$samples_5$trip_1$length$iss$iss,
               N10_T1.0 = out_23.1$samples_10$trip_1$length$iss$iss,
               N15_T1.0 = out_23.1$samples_15$trip_1$length$iss$iss,
               N20_T1.0 = out_23.1$samples_20$trip_1$length$iss$iss,

               NN = out_39.5$samples_20$trip_1$length$iss$iss) 
               # NN = out_1.4$length$iss$iss[out_1.4$length$iss$YEAR%in%1999:2023])

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

df2[grep("T0.25", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_T1.0"])/df2$ISS[df2$scenario=="N20_T1.0"],
                    type = "0.25",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("T0.5", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_T1.0"])/df2$ISS[df2$scenario=="N20_T1.0"],
                    type = "0.5",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2

df2[grep("T0.75", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_T1.0"])/df2$ISS[df2$scenario=="N20_T1.0"],
                    type = "0.75",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df2[grep("T1.0", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_T1.0"])/df2$ISS[df2$scenario=="N20_T1.0"],
                    type = "1.0",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.4

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::bind_rows(df3.4) %>%
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.1.a

```

### * 2 Panel: Sample Size VS Haul, Trip

```{r, fig.height=12, fig.width=10}
p1 = df4.1.a %>%
  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>%
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>%
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "", y = "ISSB % Difference", tag = "A") +
  theme_classic() +
  theme(legend.position = c(0.7, 0.15),
        legend.direction = "horizontal",
        legend.box = "horizontal",
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  guides(fill = guide_legend(title = "Trips",
                             title.position = "top",
                             title.hjust = 0.5,
                             label.position = "bottom"))  +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))

p2 = df4.1.b %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "", y = "ISSB % Difference", tag = "B") +
  theme_classic() +
  theme(legend.position = c(0.7, 0.15), 
        legend.direction = "horizontal", 
        legend.box = "horizontal",
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) + 
  guides(fill = guide_legend(title = "Hauls",
                             title.position = "top", 
                             title.hjust = 0.5,
                             label.position = "bottom"))  +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))

# p3 = df4.3.b %>% 
#   tidytable::mutate(scenario = factor(str_sub(scenario, start = 2, end = -1))) %>% 
#   tidytable::filter(type %in% scenario_names.short[c(2,4,5,6,7)]) %>%
#   tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
#   ggplot(aes(x = scenario, y = ISS.error*100)) +
#   geom_boxplot(aes(fill = type)) +
#   labs(x = "Samples per Haul", y = "ISSB % Difference", tag = "C") +
#   theme_classic() +
#   theme(legend.position = c(0.7, 0.15), 
#         legend.direction = "horizontal", 
#         legend.box = "horizontal",
#         plot.tag.position = c(0.1, 0.95),
#         plot.tag = element_text(size = 14, face = "bold")) + 
#   guides(fill = guide_legend(title = "Hauls/Trips",
#                              title.position = "top", 
#                              title.hjust = 0.5,
#                              label.position = "bottom"))  +
#   geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
#   geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
#   scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))

p1 + plot_spacer() + p2 + plot_layout(ncol = 1,
                           heights = c(6, -.5, 6))

```

### PROBLEM DATA: Samples VS Trip

replace=false for trips is problematic.

```{r, fig.width=8}

out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_39.3_ISS_10_iters_2025-03-21.RDS")

year = out_23.1$samples_1$trip_0.25$length$iss$YEAR

df = tidytable(year = year,
               N1_T0.25 = out_23.1$samples_1$trip_0.25$length$iss$iss,
               N5_T0.25 = out_23.1$samples_5$trip_0.25$length$iss$iss,
               N10_T0.25 = out_23.1$samples_10$trip_0.25$length$iss$iss,
               N15_T0.25 = out_23.1$samples_15$trip_0.25$length$iss$iss,
               N20_T0.25 = out_23.1$samples_20$trip_0.25$length$iss$iss,
               N1_T0.5 = out_23.1$samples_1$trip_0.5$length$iss$iss,
               N5_T0.5 = out_23.1$samples_5$trip_0.5$length$iss$iss,
               N10_T0.5 = out_23.1$samples_10$trip_0.5$length$iss$iss,
               N15_T0.5 = out_23.1$samples_15$trip_0.5$length$iss$iss,
               N20_T0.5 = out_23.1$samples_20$trip_0.5$length$iss$iss,
               N1_T0.75 = out_23.1$samples_1$trip_0.75$length$iss$iss,
               N5_T0.75 = out_23.1$samples_5$trip_0.75$length$iss$iss,
               N10_T0.75 = out_23.1$samples_10$trip_0.75$length$iss$iss,
               N15_T0.75 = out_23.1$samples_15$trip_0.75$length$iss$iss,
               N20_T0.75 = out_23.1$samples_20$trip_0.75$length$iss$iss,
               N1_T0.9 = out_23.1$samples_1$trip_0.9$length$iss$iss,
               N5_T0.9 = out_23.1$samples_5$trip_0.9$length$iss$iss,
               N10_T0.9 = out_23.1$samples_10$trip_0.9$length$iss$iss,
               N15_T0.9 = out_23.1$samples_15$trip_0.9$length$iss$iss,
               N20_T0.9 = out_23.1$samples_20$trip_0.9$length$iss$iss,
               N1_T1.0 = out_31.1$samples_1$data_H_P$length$iss$iss,
               N5_T1.0 = out_31.1$samples_5$data_H_P$length$iss$iss,
               N10_T1.0 = out_31.1$samples_10$data_H_P$length$iss$iss,
               N15_T1.0 = out_31.1$samples_15$data_H_P$length$iss$iss,
               N20_T1.0 = out_31.1$samples_20$data_H_P$length$iss$iss,

               NN = out_1.4$length$iss$iss[out_1.4$length$iss$YEAR%in%1999:2023])

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

df2[grep("T0.25", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "0.25",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("T0.5", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "0.5",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2

df2[grep("T0.75", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "0.75",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df2[grep("T1.0", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "1.0",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.4

df2[grep("T0.9", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="NN"])/df2$ISS[df2$scenario=="NN"],
                    type = "0.9",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.5

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::bind_rows(df3.5) %>% 
  tidytable::bind_rows(df3.4) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.1.a

```

### * 2 Panel: Sample Size VS Haul, Trip

```{r, fig.height=12, fig.width=10}
p1 = df4.1.a %>%
  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>%
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>%
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "", y = "ISSB % Difference", tag = "A") +
  theme_classic() +
  theme(legend.position = c(0.7, 0.15),
        legend.direction = "horizontal",
        legend.box = "horizontal",
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  guides(fill = guide_legend(title = "Trips",
                             title.position = "top",
                             title.hjust = 0.5,
                             label.position = "bottom"))  +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))

p2 = df4.1.b %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "", y = "ISSB % Difference", tag = "B") +
  theme_classic() +
  theme(legend.position = c(0.7, 0.15), 
        legend.direction = "horizontal", 
        legend.box = "horizontal",
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) + 
  guides(fill = guide_legend(title = "Hauls",
                             title.position = "top", 
                             title.hjust = 0.5,
                             label.position = "bottom"))  +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))

# p3 = df4.3.b %>% 
#   tidytable::mutate(scenario = factor(str_sub(scenario, start = 2, end = -1))) %>% 
#   tidytable::filter(type %in% scenario_names.short[c(2,4,5,6,7)]) %>%
#   tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
#   ggplot(aes(x = scenario, y = ISS.error*100)) +
#   geom_boxplot(aes(fill = type)) +
#   labs(x = "Samples per Haul", y = "ISSB % Difference", tag = "C") +
#   theme_classic() +
#   theme(legend.position = c(0.7, 0.15), 
#         legend.direction = "horizontal", 
#         legend.box = "horizontal",
#         plot.tag.position = c(0.1, 0.95),
#         plot.tag = element_text(size = 14, face = "bold")) + 
#   guides(fill = guide_legend(title = "Hauls/Trips",
#                              title.position = "top", 
#                              title.hjust = 0.5,
#                              label.position = "bottom"))  +
#   geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
#   geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
#   scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))

p1 + plot_spacer() + p2 + plot_layout(ncol = 1,
                           heights = c(6, -.5, 6))

```

### 2025-03-31 Rmd/paper_plots/paper_plots_1.5.Rmd
add paper runs and plots

---
title: "Paper Plots V5"
author: "Brett Stacy"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, results = "hide", fig.width = 8.5, fig.height = 5, dpi = 600)
library(tidytable)
library(data.table)
library(reshape2)
library(ggplot2)
library(knitr)
library(stringr)
library(patchwork)
library(viridis)
library(ggpattern)
opts_knit$set(eval.after = "fig.cap")
options(scipen = 5)
```

# Introduction
Plots for paper:

## Data
```{r}

out_1.4.old = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.4_ISS_1000iters_output_2025-01-23.RDS")

out_1.5 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.5_ISS_1000iters_output_2025-03-24.RDS")

# out_3.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_3.2_ISS_500iters_output_2025-03-07.RDS") ### mislabeled

out_5.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_41.1_ISS_500iters_output_2025-03-24.RDS")

out_9.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_42.1_ISS_500iters_output_2025-03-24.RDS")

out_4.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_43.1_ISS_500iters_output_2025-03-24.RDS")
# 
# out_31.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_31.1.TAS_ISS_500_iters_2025-03-02.RDS")
# 
# out_39.5 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_39.5_ISS_500_iters_2025-03-21.RDS")
#

out_37.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_37.2_ISS_500iters_output_2025-03-26.RDS")
out_37.3 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_37.3_ISS_500iters_output_2025-03-26.RDS")

# save out_1.5 for Steve to plug into the assessment
out_1.5$length$iss %>% 
  select(YEAR, iss) %>% 
  write.csv(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/issb_v1_from_Brett_Stacy.csv", row.names = F)

assessment_2023_iss = tidytable(year = 1977:2023,
                                iss = c(27,
                                45,
                                54,
                                54,
                                63,
                                31,
                                117,
                                140,
                                211,
                                216,
                                396,
                                401,
                                185,
                                189,
                                1565,
                                1543,
                                913,
                                1435,
                                1561,
                                2020,
                                2142,
                                2046,
                                2722,
                                2960,
                                3140,
                                3446,
                                4301,
                                3608,
                                3455,
                                2694,
                                2115,
                                2502,
                                2218,
                                1975,
                                2596,
                                2776,
                                3293,
                                3604,
                                3324,
                                2821,
                                2469,
                                1899,
                                1367,
                                1048,
                                859,
                                1160,
                                706))

# survey vs observer length measurements
obs_numbers = tidytable(year = 1982:2023,
                        survey = c(10863,
                        13143,
                        12133,
                        17150,
                        15872,
                        9483,
                        6950,
                        4246,
                        5428,
                        7069,
                        10129,
                        10500,
                        12931,
                        9820,
                        9348,
                        9591,
                        9574,
                        11183,
                        12170,
                        19078,
                        12365,
                        11835,
                        10986,
                        11753,
                        12530,
                        13441,
                        15328,
                        23737,
                        21223,
                        25150,
                        30177,
                        19902,
                        29204,
                        19880,
                        19507,
                        15020,
                        8806,
                        23408,
                        0,
                        17397,
                        16677,
                        19943),
                        fishery = c(9658,
                                    33200,
                                    45635,
                                    66940,
                                    58257,
                                    129226,
                                    111065,
                                    58625,
                                    39698,
                                    347227,
                                    344923,
                                    248967,
                                    359147,
                                    344794,
                                    445217,
                                    474908,
                                    438746,
                                    186233,
                                    199708,
                                    210419,
                                    230802,
                                    288854,
                                    237487,
                                    228664,
                                    179782,
                                    140663,
                                    164860,
                                    147875,
                                    131514,
                                    172269,
                                    192273,
                                    211962,
                                    234476,
                                    213888,
                                    182980,
                                    157482,
                                    124004,
                                    86800,
                                    65301,
                                    55858,
                                    73025,
                                    42942))

obs_numbers %>% 
  tidytable::summarise(sum(survey), sum(fishery))

obs_numbers %>% 
  tidytable::summarise(mean(survey), mean(fishery))

```

## ISSB Results 
### * Time series 2 panel

```{r, fig.height=6}
df = data.frame(rss = out_1.5$length$rss$rss, year = as.factor(out_1.5$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, type = "o", pch = 19, ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue", type = "o", pch = 3)
lines(out_1.5$length$iss$YEAR, out_1.5$length$iss$nhls, col = "orange", type = "o", pch = 5)
legend(1977, 11000, lty = c(1,1,1), col = c("black", "blue", "orange"), pch = c(19, 3, 5), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n")
text(1977, 14000, "A")

plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3) 
text(1977, 420000, "B")
mtext("Year", side = 1, line = 2, cex = 1.5)

# compare with and without SS
par(mfrow = c(1,1))
plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, type = "o", pch = 19, ylab = "ISSB", ylim = c(0, 15000), cex.lab = 1.3) 
lines(out_1.4.old$length$iss$YEAR, out_1.4.old$length$iss$iss, col = "blue", type = "o", pch = 5)
legend(1977, 11000, lty = c(1,1), col = c("black", "blue"), pch = c(19, 5), legend = c("Not including sampling strata weighting", "Including sampling strata weighting"), bty = "n")

# averages
out_1.5$length$iss$iss %>% mean()
assessment_2023_iss$iss %>% mean()

```

### * Time seris components

\newpage

```{r, fig.height=5.5}
sub_range = out_5.2$length$iss$YEAR %in% 1977:2023

par(mfrow = c(1,1))
plot(out_5.2$length$iss$YEAR[sub_range], out_5.2$length$iss$iss[sub_range], ylab = "ISSB", cex.lab = 1.3, col = "cyan", ylim = c(0, 25000), xlab = "Year", lwd = 2, type = "o", pch= 18)
lines(out_9.2$length$iss$YEAR[sub_range], out_9.2$length$iss$iss[sub_range], type = "o", pch = 15, col = "orange3", lwd = 2)
lines(out_4.2$length$iss$YEAR[sub_range], out_4.2$length$iss$iss[sub_range], type = "o", pch = 17, col = "magenta", lwd = 2)
lines(out_1.5$length$iss$YEAR[sub_range], out_1.5$length$iss$iss[sub_range], type = "o", pch = 19, col = "black", lwd = 2, lty = 1)

# legend("topleft", title = "Component Case", legend = c("1", "2", "3", "4", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"), bty = "n")
legend("topleft", title = "Component Case", legend = c("1", "2", "3", "full"), lty = c(1,1,1,1), pch = c(18, 15, 17, 19), col = c("cyan", "orange3", "magenta", "black"), bty = "n", lwd = rep(2, 4))

# not accounting for correlations exceed hauls?
sum((out_5.2$length$iss$iss[sub_range]-out_1.5$length$iss$nhls) < 0)

```

\newpage

#### * TOGETHER

\newpage

```{r, fig.height=8}
df = data.frame(rss = out_1.5$length$rss$rss, year = as.factor(out_1.5$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(3,1), mar = c(0,3.1,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, type = "o", pch = 19, ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.5, cex.axis = 1.3)
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue", type = "o", pch = 3)
lines(out_1.5$length$iss$YEAR, out_1.5$length$iss$nhls, col = "orange", type = "o", 5)
legend(1977, 11000, lty = c(1,1,1), col = c("black", "blue", "orange"), pch = c(19, 3, 5), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n", cex = 1.5)
text(1977, 14000, "A", cex = 1.5)

plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xaxt = "n", cex.lab = 1.5, cex.axis = 1.3)
text(1977, 420000, "B", cex = 1.5)

plot(out_5.2$length$iss$YEAR[sub_range], out_5.2$length$iss$iss[sub_range], ylab = "ISSB", cex.lab = 1.5, col = "cyan", ylim = c(0, 27000), xlab = "", xaxt = "n", lwd = 1.5, type = "o", pch= 18, cex.axis = 1.3)
axis(side = 1, at = seq(1980, 2020, by = 5), cex.axis = 1.3)
lines(out_9.2$length$iss$YEAR[sub_range], out_9.2$length$iss$iss[sub_range], type = "o", pch = 15, col = "orange3", lwd = 1.5)
lines(out_4.2$length$iss$YEAR[sub_range], out_4.2$length$iss$iss[sub_range], type = "o", pch = 17, col = "magenta", lwd = 1.5)
lines(out_1.5$length$iss$YEAR[sub_range], out_1.5$length$iss$iss[sub_range], type = "o", pch = 19, col = "black", lwd = 1.5, lty = 1)
legend(1977, 20000, title = "Scenario", legend = c("1", "2", "3", "Full"), lty = c(1,1,1,1), pch = c(18, 15, 17, 19), col = c("cyan", "orange3", "magenta", "black"), bty = "n", lwd = rep(1.5, 4), cex = 1.5)
text(1977, 23000, "C", cex = 1.5)

# mtext("Year", side = 1, line = 2, cex = 1.3)

```

\newpage

# * 2003 & 2004 Histograms

\newpage

```{r, fig.height=10}
out_1.5$length$og_props %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
  geom_line() +
  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
  # geom_area_pattern(aes(pattern = Year, y = og_FREQ, x = LENGTH), alpha = 0.5, position = "identity") +
  theme_classic() +
  scale_x_continuous(limits = c(22, 108),
                     n.breaks = 9) +
  labs(x = "Length (cm)", y = "Frequency", tag = "A") +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  scale_y_continuous(limits = c(0, .04), expand = c(0, 0)) +
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS
out_1.5$length$rss %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "E") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_1.5$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS with boot_length only.
out_5.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "B") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_5.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS with boot_length and boot_haul.
out_9.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "C") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_9.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# now do RSS with boot all.
out_4.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "D") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_4.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(2,2)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))+
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# # now do RSS with boot all + SS
# out_2.2$length$rss %>% 
#   tidytable::filter(YEAR %in% 2003:2004) %>% 
#   tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
# 
# p3.5 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
#   geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
#   theme_classic() +
#   theme(legend.position = c(0.8, 0.8),
#         plot.tag.position = c(0.1, 0.95),
#         plot.tag = element_text(size = 14, face = "bold")) +
#   labs(x = "RSS", y = "Count", tag = "E") + 
#   geom_point(data = props.sub %>% 
#                tidytable::left_join(out_2.2$length$iss %>% 
#                                       tidytable::select(YEAR, iss)) %>% 
#                tidytable::summarise(x = unique(iss), .by = Year) %>% 
#                # tidytable::summarise(x = median(rss), .by = Year) %>% 
#                tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
#   scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
#   # scale_x_continuous(n.breaks = 8)
#   scale_x_continuous(breaks = seq(0, 35000, by = 2500),
#                      labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
#                      limits = c(0, 35000),
#                      expand = c(0, 0))
# 
#

# 
# p1 / p3
# p1 / p3 / p3.2

p1 / p3.2 / p3.3 / p3.4 / p3

```

The comparison shows that fish in 2003 were less similar in length compared to 2004. 2003 corresponds to a higher ISS even though the sample rate was the same and the number of hauls and nominal sample size were comparable. More of the fish sampled in 2003 were required for characterizing the underlying multinomial sampling distribution compared to 2004 because more lengths were represented at a higher rate in 2003 (shorter, wider distribution). This is reflected in the RSS (ref figure).

# * Time series Expansion NEW
```{r, fig.width=9, fig.height=5}
out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_44.1_ISS_500_iters_2025-03-25.RDS")

year = out_2.1.1$expansion_NULL$length$iss$YEAR

df = tidytable(year = year,
               none = out_2.1.1$expansion_NULL$length$iss$iss,
               medium = out_2.1.1$expansion_haul_numbers$length$iss$iss,
               full = out_2.1.1$expansion_haul_month_numbers$length$iss$iss)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

# 
# # all years
# ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
#   geom_line() +
#   labs(x = "", y = "ISSB") +
#   geom_point() + 
#   theme_classic() +
#   theme(legend.position = c(0.84, 0.8),
#         axis.title.x = element_blank())

# 1999:2023
df2 %>% 
  filter(year%in%1999:2023) %>% 
ggplot(aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  geom_point() +
  scale_shape_manual(values = c(1,2,3)) +
  labs(x = "Year", y = "ISSB", color = "Expansion Complexity") +
  scale_color_manual(labels = c("None", "Medium: haul only", "Full: haul, area, gear, month"), values = c("blue", "red", "black")) +
  geom_point() + 
  theme_classic() + 
  theme(legend.position = c(0.7, 0.9),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14))
```

\newpage

# * Reduce Samples

```{r}
# out_31.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_31.1.TAS_ISS_500_iters_2025-03-02.RDS")
out_31.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_47.1_ISS_500_iters_2025-03-30.RDS")

year = out_31.1$samples_1$data_H_P$length$iss$YEAR

### H_P ###################
df = tidytable(year = year,
               N1_HP = out_31.1$samples_1$data_H_P$length$iss$iss,
               N5_HP = out_31.1$samples_5$data_H_P$length$iss$iss,
               N10_HP = out_31.1$samples_10$data_H_P$length$iss$iss,
               N15_HP = out_31.1$samples_15$data_H_P$length$iss$iss,
               N20_HP = out_31.1$samples_20$data_H_P$length$iss$iss,

               NN_HP = out_1.5$length$iss$iss[out_1.5$length$iss$YEAR%in%1999:2023])

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

scenario_names = c("N1_HP", "N5_HP", "N10_HP", "N15_HP", "N20_HP", "NN_HP")

## 1
df2 %>% 
  tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="N20_HP"])/df2$ISS[df2$scenario=="N20_HP"],
                    type = "relative_20",
                    .by = scenario) -> df3.1
## 2
df2 %>% 
  tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="NN_HP"])/df2$ISS[df2$scenario=="NN_HP"],
                    type = "relative_N",
                    .by = scenario) -> df3.2

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>%
  tidytable::filter(scenario!="NN_HP") %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -4)) %>%
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.a

### H ###################
df = tidytable(year = year,
               N1_H = out_31.1$samples_1$data_H$length$iss$iss,
               N5_H = out_31.1$samples_5$data_H$length$iss$iss,
               N10_H = out_31.1$samples_10$data_H$length$iss$iss,
               N15_H = out_31.1$samples_15$data_H$length$iss$iss,
               N20_H = out_31.1$samples_20$data_H$length$iss$iss,

               NN_H = out_1.5$length$iss$iss[out_1.5$length$iss$YEAR%in%1999:2023])

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

scenario_names = c("N1_H", "N5_H", "N10_H", "N15_H", "N20_H", "NN_H")

## 1
df2 %>% 
  tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="N20_H"])/df2$ISS[df2$scenario=="N20_H"],
                    type = "relative_20",
                    .by = scenario) -> df3.1
## 2
df2 %>% 
  tidytable::mutate(ISS.error = 100*(ISS - df2$ISS[df2$scenario=="NN_H"])/df2$ISS[df2$scenario=="NN_H"],
                    type = "relative_N",
                    .by = scenario) -> df3.2

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>%
  tidytable::filter(scenario!="NN_H") %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -3)) %>%
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.b

```

\newpage

```{r, fig.height=7}
### plots

p1 = df4.a %>%
  ggplot(aes(x = scenario, y = ISS.error)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "", y = "ISSB % Difference", tag = "A") +
  theme_classic() +
  theme(legend.position = c(0.7, 0.15), 
        legend.direction = "horizontal", 
        legend.box = "horizontal",
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) + 
  guides(fill = guide_legend(title = "haul and port data",
                             title.position = "top", 
                             title.hjust = 0.5,
                             label.position = "bottom"))  +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-80, 10))

## for presentation
p.p = df4.a %>%
  filter(type=="relative_N") %>% 
  ggplot(aes(x = scenario, y = ISS.error)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Adjusted Samples Per Haul", y = "ISSB % Difference", tag = "") +
  theme_classic() +
  theme(legend.position = c(3, 0.15),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14)) + 
  guides(fill = guide_legend(title = "relative to baseline")) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-80, 10))

p2 = df4.b %>%
  ggplot(aes(x = scenario, y = ISS.error)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Samples per Haul", y = "ISSB % Difference", tag = "B") +
  theme_classic() +
  theme(legend.position = c(0.7, 0.15), 
        legend.direction = "horizontal", 
        legend.box = "horizontal",
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) + 
  guides(fill = guide_legend(title = "haul only data",
                             title.position = "top", 
                             title.hjust = 0.5,
                             label.position = "bottom"))  +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-80, 10))

p1 + plot_spacer() + p2 + plot_layout(ncol = 1,
                           heights = c(6, -.5, 6))

```

\newpage

for above. "the median percent difference in ISSB increased with increasing sample size using the full data set (A) and only the haul data (B) over the period 1999-2023. There was no appreciable change in the percent difference when only using the haul data. There was also very little difference comparing the percent difference relative to the baseline ISSB or relative to applying the sample reduction routine at a sampling rate of 20. This verifies that the results are comparable for the following scenarios: comparisons to the baseline or comparisons to just using hauls with a sampling rate that never exceeds 20. The most conservative scenario is assuming a future sampling where high sampling rates from port samples are not available and the haul sampling rate is allowed to be below 20 but not exceed it. Comparisons relative to this scenario are the most relevant, conservative, scenario available to evaluate the impact of reducing observer haul sampling rate on composition data precision for future years. If the sampling rate behavior continues on average at least as good as it has done for the period 1999:2023 (which it is scheduled to do), we can expect the loss of precision not to exceed these values. (Assuming fishing trip and haul characteristics are comparable on average, also likely expected).

\newpage

# * Samples VS Expantion. intra-relative

Make sure to say in the paper: Methods: Unlike changing the number of hauls or trips (static quality of the data), the stock assessor has discression over changing the expansion method. IF they change it, they will change it for past and present data, not change it based on blocks of time or something like that. SO, these scenarios demonstrate what we can expect to see in near future years IF we decrease the sample size, ASSUMING the expansion complexity will change. For example, IF the expansion complexity will change, what will be the expected loss of precision if we reduce the sample size from 20 to 10. REMEMBER, these scenarios are relative to the N=20 case for each expansion complexity case.

```{r, fig.width=8}

out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_38.2_ISS_500_iters_2025-03-20.RDS")

year = out_22.1$samples_1$expansion_NULL$length$iss$YEAR

df = tidytable(year = year,
               N1_Enone = out_22.1$samples_1$expansion_NULL$length$iss$iss,
               N5_Enone = out_22.1$samples_5$expansion_NULL$length$iss$iss,
               N10_Enone = out_22.1$samples_10$expansion_NULL$length$iss$iss,
               N15_Enone = out_22.1$samples_15$expansion_NULL$length$iss$iss,
               N20_Enone = out_22.1$samples_20$expansion_NULL$length$iss$iss,
               N1_Emedium = out_22.1$samples_1$expansion_haul_numbers$length$iss$iss,
               N5_Emedium = out_22.1$samples_5$expansion_haul_numbers$length$iss$iss,
               N10_Emedium = out_22.1$samples_10$expansion_haul_numbers$length$iss$iss,
               N15_Emedium = out_22.1$samples_15$expansion_haul_numbers$length$iss$iss,
               N20_Emedium = out_22.1$samples_20$expansion_haul_numbers$length$iss$iss,
               N1_Efull = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
               N5_Efull = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
               N10_Efull = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N15_Efull = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
               N20_Efull = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

df2[grep("Enone", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Enone"])/df2$ISS[df2$scenario=="N20_Enone"],
                    type = "Enone",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("Emedium", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Emedium"])/df2$ISS[df2$scenario=="N20_Emedium"],
                    type = "Emedium",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -9)) -> df3.2

df2[grep("Efull", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
                    type = "Efull",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.0

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Samples per Haul", y = "ISSB % Difference") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.2)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10)) +
  scale_x_discrete(labels = c("1", "5", "10", "15", "20")) +
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# Stats
df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median

```

# * Haul and TRIP Decrease w/o replacement
```{r}
out_29.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_45.1_ISS_500_iters_2025-03-26.RDS")
out_48.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_48.1_ISS_500_iters_2025-03-27.RDS")
relative.trip = out_48.1$proportion_1$type_trip$length$iss$iss
relative.haul = out_48.1$proportion_1$type_haul$length$iss$iss

year = out_29.1$proportion_0.1$type_trip$length$iss$YEAR

# Trip
df = tidytable(year = year,
               N_0.1 = out_29.1$proportion_0.1$type_trip$length$iss$iss,
               N_0.2 = out_29.1$proportion_0.2$type_trip$length$iss$iss,
               N_0.3 = out_29.1$proportion_0.3$type_trip$length$iss$iss,
               N_0.4 = out_29.1$proportion_0.4$type_trip$length$iss$iss,
               N_0.5 = out_29.1$proportion_0.5$type_trip$length$iss$iss,
               N_0.6 = out_29.1$proportion_0.6$type_trip$length$iss$iss,
               N_0.7 = out_29.1$proportion_0.7$type_trip$length$iss$iss,
               N_0.8 = out_29.1$proportion_0.8$type_trip$length$iss$iss,
               N_0.9 = out_29.1$proportion_0.9$type_trip$length$iss$iss)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
# 
# df2 %>% 
#   tidytable::mutate(ISS.error = (ISS - out_1.5$length$iss$iss)/out_1.5$length$iss$iss,
#                     type = "trip",
#                     .by = scenario) -> df3.1
df2 %>% 
  tidytable::mutate(ISS.error = (ISS - relative.trip)/relative.trip,
                    type = "trip",
                    .by = scenario) -> df3.1

# Haul
df = tidytable(year = year,
               N_0.1 = out_29.1$proportion_0.1$type_haul$length$iss$iss,
               N_0.2 = out_29.1$proportion_0.2$type_haul$length$iss$iss,
               N_0.3 = out_29.1$proportion_0.3$type_haul$length$iss$iss,
               N_0.4 = out_29.1$proportion_0.4$type_haul$length$iss$iss,
               N_0.5 = out_29.1$proportion_0.5$type_haul$length$iss$iss,
               N_0.6 = out_29.1$proportion_0.6$type_haul$length$iss$iss,
               N_0.7 = out_29.1$proportion_0.7$type_haul$length$iss$iss,
               N_0.8 = out_29.1$proportion_0.8$type_haul$length$iss$iss,
               N_0.9 = out_29.1$proportion_0.9$type_haul$length$iss$iss)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

# 
# df2 %>% 
#   tidytable::mutate(ISS.error = (ISS - out_1.5$length$iss$iss)/out_1.5$length$iss$iss,
#                     type = "haul",
#                     .by = scenario) -> df3.2
df2 %>% 
  tidytable::mutate(ISS.error = (ISS - relative.haul)/relative.haul,
                    type = "haul",
                    .by = scenario) -> df3.2

df3.1 %>% 
  tidytable::bind_rows(df3.2) -> df4

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Proportional Change", y = "ISSB % Difference") +
  theme_classic() +
  theme(legend.position = c(0.8, 0.2)) +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 20, by = 10), limits = c(-100, 20)) +
  scale_x_discrete(labels = c("0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.7", "0.8", "0.9"))

```

# Samples VS Haul/Trip

### DATA: Samples VS Haul. Replace=TRUE, including 1.0
```{r, fig.width=8}

out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_40.3_ISS_500_iters_2025-03-25.RDS")

year = out_24.1$samples_1$haul_0.25$length$iss$YEAR

df = tidytable(year = year,
               N1_H0.25 = out_24.1$samples_1$haul_0.25$length$iss$iss,
               N5_H0.25 = out_24.1$samples_5$haul_0.25$length$iss$iss,
               N10_H0.25 = out_24.1$samples_10$haul_0.25$length$iss$iss,
               N15_H0.25 = out_24.1$samples_15$haul_0.25$length$iss$iss,
               N20_H0.25 = out_24.1$samples_20$haul_0.25$length$iss$iss,
               N1_H0.5 = out_24.1$samples_1$haul_0.5$length$iss$iss,
               N5_H0.5 = out_24.1$samples_5$haul_0.5$length$iss$iss,
               N10_H0.5 = out_24.1$samples_10$haul_0.5$length$iss$iss,
               N15_H0.5 = out_24.1$samples_15$haul_0.5$length$iss$iss,
               N20_H0.5 = out_24.1$samples_20$haul_0.5$length$iss$iss,
               N1_H0.75 = out_24.1$samples_1$haul_0.75$length$iss$iss,
               N5_H0.75 = out_24.1$samples_5$haul_0.75$length$iss$iss,
               N10_H0.75 = out_24.1$samples_10$haul_0.75$length$iss$iss,
               N15_H0.75 = out_24.1$samples_15$haul_0.75$length$iss$iss,
               N20_H0.75 = out_24.1$samples_20$haul_0.75$length$iss$iss,
               N1_H1.0 = out_24.1$samples_1$haul_1$length$iss$iss,
               N5_H1.0 = out_24.1$samples_5$haul_1$length$iss$iss,
               N10_H1.0 = out_24.1$samples_10$haul_1$length$iss$iss,
               N15_H1.0 = out_24.1$samples_15$haul_1$length$iss$iss,
               N20_H1.0 = out_24.1$samples_20$haul_1$length$iss$iss)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

df2[grep("H0.25", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "0.25",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("H0.5", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "0.5",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2

df2[grep("H0.75", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "0.75",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df2[grep("H1.0", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "1.0",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.4

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::bind_rows(df3.4) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.1.b

```

### DATA: Samples VS Trip. Replace=TRUE, including 1.0
```{r, fig.width=8}

out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_39.7_ISS_500_iters_2025-03-25.RDS")
# out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_39.8_ISS_500_iters_2025-03-27.RDS")

year = out_23.1$samples_1$trip_0.25$length$iss$YEAR

df = tidytable(year = year,
               N1_T0.25 = out_23.1$samples_1$trip_0.25$length$iss$iss,
               N5_T0.25 = out_23.1$samples_5$trip_0.25$length$iss$iss,
               N10_T0.25 = out_23.1$samples_10$trip_0.25$length$iss$iss,
               N15_T0.25 = out_23.1$samples_15$trip_0.25$length$iss$iss,
               N20_T0.25 = out_23.1$samples_20$trip_0.25$length$iss$iss,
               N1_T0.5 = out_23.1$samples_1$trip_0.5$length$iss$iss,
               N5_T0.5 = out_23.1$samples_5$trip_0.5$length$iss$iss,
               N10_T0.5 = out_23.1$samples_10$trip_0.5$length$iss$iss,
               N15_T0.5 = out_23.1$samples_15$trip_0.5$length$iss$iss,
               N20_T0.5 = out_23.1$samples_20$trip_0.5$length$iss$iss,
               N1_T0.75 = out_23.1$samples_1$trip_0.75$length$iss$iss,
               N5_T0.75 = out_23.1$samples_5$trip_0.75$length$iss$iss,
               N10_T0.75 = out_23.1$samples_10$trip_0.75$length$iss$iss,
               N15_T0.75 = out_23.1$samples_15$trip_0.75$length$iss$iss,
               N20_T0.75 = out_23.1$samples_20$trip_0.75$length$iss$iss,
               N1_T1.0 = out_23.1$samples_1$trip_1$length$iss$iss,
               N5_T1.0 = out_23.1$samples_5$trip_1$length$iss$iss,
               N10_T1.0 = out_23.1$samples_10$trip_1$length$iss$iss,
               N15_T1.0 = out_23.1$samples_15$trip_1$length$iss$iss,
               N20_T1.0 = out_23.1$samples_20$trip_1$length$iss$iss)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")

df2[grep("T0.25", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_T1.0"])/df2$ISS[df2$scenario=="N20_T1.0"],
                    type = "0.25",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("T0.5", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_T1.0"])/df2$ISS[df2$scenario=="N20_T1.0"],
                    type = "0.5",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2

df2[grep("T0.75", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_T1.0"])/df2$ISS[df2$scenario=="N20_T1.0"],
                    type = "0.75",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df2[grep("T1.0", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_T1.0"])/df2$ISS[df2$scenario=="N20_T1.0"],
                    type = "1.0",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.4

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::bind_rows(df3.4) %>%
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.1.a

```

### * 2 Panel: Sample Size VS Trip, Haul

```{r, fig.height=12, fig.width=10}
p1 = df4.1.a %>%
  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>%
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>%
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "", y = "ISSB % Difference", tag = "A") +
  theme_classic() +
  theme(legend.position = c(0.74, 0.15),
        legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.background = element_rect(fill = "transparent"),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  guides(fill = guide_legend(title = "Trips",
                             title.position = "top",
                             title.hjust = 0.5,
                             label.position = "bottom"))  +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
  scale_color_viridis_d() +
  scale_fill_viridis_d()

p2 = df4.1.b %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "", y = "ISSB % Difference", tag = "B") +
  theme_classic() +
  theme(legend.position = c(0.74, 0.15), 
        legend.direction = "horizontal", 
        legend.box = "horizontal",
        legend.background = element_rect(fill = "transparent"),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) + 
  guides(fill = guide_legend(title = "Hauls",
                             title.position = "top", 
                             title.hjust = 0.5,
                             label.position = "bottom"))  +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
  scale_color_viridis_d() +
  scale_fill_viridis_d()

# p3 = df4.3.b %>% 
#   tidytable::mutate(scenario = factor(str_sub(scenario, start = 2, end = -1))) %>% 
#   tidytable::filter(type %in% scenario_names.short[c(2,4,5,6,7)]) %>%
#   tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
#   ggplot(aes(x = scenario, y = ISS.error*100)) +
#   geom_boxplot(aes(fill = type)) +
#   labs(x = "Samples per Haul", y = "ISSB % Difference", tag = "C") +
#   theme_classic() +
#   theme(legend.position = c(0.7, 0.15), 
#         legend.direction = "horizontal", 
#         legend.box = "horizontal",
#         plot.tag.position = c(0.1, 0.95),
#         plot.tag = element_text(size = 14, face = "bold")) + 
#   guides(fill = guide_legend(title = "Hauls/Trips",
#                              title.position = "top", 
#                              title.hjust = 0.5,
#                              label.position = "bottom"))  +
#   geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
#   geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
#   scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-90, 30))

p1 + plot_spacer() + p2 + plot_layout(ncol = 1,
                           heights = c(6, -.5, 6))

```

# SCRATCH
## PLOT BOOT.HAUL AND BOOT.TRIP ONLY SCENARIOS?

```{r}

par(mfrow = c(1,1))
plot(out_37.2$length$iss$YEAR, out_37.2$length$iss$iss, col = "blue", type = "l")
lines(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss)
lines(out_37.3$length$iss$YEAR, out_37.3$length$iss$iss, col = "purple")

```

### 2025-03-31 Rmd/paper_plots/paper_plots_assessment_1.Rmd
add paper runs and plots

---
title: "EBS Pcod Fishery ISS Assesssment Results"
author: "Brett Stacy"
output: pdf_document
header-includes:
  - \usepackage{float}
  - \floatplacement{table}{H}
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, results = "hide", dpi = 600, fig.width = 8.5, fig.pos = "H")
library(tidytable)
library(data.table)
library(reshape2)
library(ggplot2)
library(knitr)
library(stringr)
library(patchwork)
library(xtable)
library(kableExtra)
library(gt)
library(tidyr)
library(dplyr)
options(scipen = 5)
```

# Introduction
This document summarizes the impact of our bootstrap fishery composition ISS results on the 2023 EBS Pacific cod stock assessment.

```{r}

out_1.4 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.4_ISS_1000iters_output_2025-01-23.RDS")

# save out_1.4 for Steve to plug into the assessment
out_1.4$length$iss %>% 
  select(YEAR, iss) %>% 
  write.csv(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/issb_v1_from_Brett_Stacy.csv", row.names = F)

assessment_2023_iss = tidytable(year = 1977:2023,
                                iss = c(27,
                                45,
                                54,
                                54,
                                63,
                                31,
                                117,
                                140,
                                211,
                                216,
                                396,
                                401,
                                185,
                                189,
                                1565,
                                1543,
                                913,
                                1435,
                                1561,
                                2020,
                                2142,
                                2046,
                                2722,
                                2960,
                                3140,
                                3446,
                                4301,
                                3608,
                                3455,
                                2694,
                                2115,
                                2502,
                                2218,
                                1975,
                                2596,
                                2776,
                                3293,
                                3604,
                                3324,
                                2821,
                                2469,
                                1899,
                                1367,
                                1048,
                                859,
                                1160,
                                706))

# survey vs observer length measurements
obs_numbers = tidytable(year = 1982:2023,
                        survey = c(10863,
                        13143,
                        12133,
                        17150,
                        15872,
                        9483,
                        6950,
                        4246,
                        5428,
                        7069,
                        10129,
                        10500,
                        12931,
                        9820,
                        9348,
                        9591,
                        9574,
                        11183,
                        12170,
                        19078,
                        12365,
                        11835,
                        10986,
                        11753,
                        12530,
                        13441,
                        15328,
                        23737,
                        21223,
                        25150,
                        30177,
                        19902,
                        29204,
                        19880,
                        19507,
                        15020,
                        8806,
                        23408,
                        0,
                        17397,
                        16677,
                        19943),
                        fishery = c(9658,
                                    33200,
                                    45635,
                                    66940,
                                    58257,
                                    129226,
                                    111065,
                                    58625,
                                    39698,
                                    347227,
                                    344923,
                                    248967,
                                    359147,
                                    344794,
                                    445217,
                                    474908,
                                    438746,
                                    186233,
                                    199708,
                                    210419,
                                    230802,
                                    288854,
                                    237487,
                                    228664,
                                    179782,
                                    140663,
                                    164860,
                                    147875,
                                    131514,
                                    172269,
                                    192273,
                                    211962,
                                    234476,
                                    213888,
                                    182980,
                                    157482,
                                    124004,
                                    86800,
                                    65301,
                                    55858,
                                    73025,
                                    42942))

obs_numbers %>% 
  tidytable::summarise(sum(survey), sum(fishery))

a.out = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/Derived_quants.csv")
p.out = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/parameters.csv")

```

# ISSB Results 
ISSB stands for the fishery input sample size by bootstrapping. ISSB is the time series output from our bootstrap analysis. ISSA stands for the fishery input sample size traditionally used in the assessment.

```{r, fig.height=6}
df = data.frame(rss = out_1.4$length$rss$rss, year = as.factor(out_1.4$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "red")
legend(1977, 11000, lty = c(1,1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n")
text(1977, 14000, "A")

plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3) 
text(1977, 420000, "B")
mtext("Year", side = 1, line = 2, cex = 2)

# averages
out_1.4$length$iss$iss %>% mean()
assessment_2023_iss$iss %>% mean()

```

\newpage

# EBS Pcod Assessment Impact

Steve B. ran the published 2023 stock assessment version with ISSB to see if it impacted the assessment outcomes. The below results are from stock assessment runs with Francis tuning, although Steve also produced runs without tuning.

## Tables of parameters

These tables include the point estimates and standard deviations (SD) of selected parameters and quantities with the original 2023 assessment configuration using ISSA and the modified using ISSB. Both the untuned and tuned results are shown. The values highlighted in grey are the only values exceeding an absolute percent difference of 10\%

\newpage

### Tuned

```{r, results="hide"}
p.out %>% 
  tidytable::filter(Label%in%c("VonBert_K_Fem_GP_1", "L_at_Amax_Fem_GP_1", "SR_LN(R0)"),
                    MODEL2%in%c("OM tuned", "Fiss tuned")) %>% 
  tidytable::mutate(StdDev = Parm_StDev) %>% 
  tidytable::select(-Parm_StDev) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(Label%in%c("SSB_2023", "SSB_2038", "Bratio_2023", "Bratio_2038", "SPRratio_2023", "SPRratio_2038"),
                                           MODEL2%in%c("OM tuned", "Fiss tuned"))) %>% 
  tidytable::select(-X, -MODEL, -HI, -LO) -> p.table

p.out %>% 
  tidytable::filter(Label%in%c("VonBert_K_Fem_GP_1", "L_at_Amax_Fem_GP_1", "SR_LN(R0)", "L_at_Amin_Fem_GP_1", "Richards_Fem_GP_1", "LnQ_base_Survey(2)", "Size_DblN_peak_Fishery(1)", "Size_DblN_ascend_se_Fishery(1)",
                               "Size_DblN_peak_Survey(2)", "Size_DblN_ascend_se_Survey(2)"),
                    MODEL2%in%c("OM tuned", "Fiss tuned")) %>% 
  tidytable::mutate(StdDev = Parm_StDev) %>% 
  tidytable::select(-Parm_StDev) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(Label%in%c("SSB_2023", "SSB_2038", "Bratio_2023", "Bratio_2038", "SPRratio_2023", "SPRratio_2038"),
                                           MODEL2%in%c("OM tuned", "Fiss tuned"))) %>% 
  tidytable::select(-X, -MODEL, -HI, -LO) -> p.table.full

# possible solution:
# cols_order <- unlist(lapply(c("a", "b", "c"), function(x) paste(x, c("Count", "Percent"), sep = "_")))
cols_order <- unlist(lapply(c("Value", "StdDev"), function(x) paste(x, c("OM tuned", "Fiss tuned"), sep = "_")))

data_wide <- p.table %>% 
        pivot_wider(names_from = "MODEL2", values_from = c(Value, StdDev), names_glue = "{.value}_{MODEL2}") %>% 
        # Reorder columns
        select(all_of(c("Label", cols_order)))

# percent difference?
data_wide %>% 
  tidytable::mutate(diff.val = 100*abs(`Value_OM tuned` - `Value_Fiss tuned`)/`Value_OM tuned`,
                    diff.sd = 100*abs(`StdDev_OM tuned` - `StdDev_Fiss tuned`)/`StdDev_OM tuned`)

data_wide %>% 
        gt(rowname_col = "Label") %>%
        tab_spanner_delim(delim = "_") %>% 
  fmt_number(decimals = 4) %>% 
  fmt_number(rows = c(4, 5),
             decimals = 0) %>% 
  fmt_number(rows = c(1,3),
             columns = c(2),
             decimals = 2)
```

```{r, results="hide"}
p.table %>% 
  tidytable::rename("Point Estimate" = Value, "SD" = StdDev) %>% 
  tidytable::mutate(MODEL2 = ifelse(MODEL2 == "OM tuned", "ISSA tuned", "ISSB tuned")) -> p.table2

cols_order <- unlist(lapply(c("Point Estimate", "SD"), function(x) paste(x, c("ISSA tuned", "ISSB tuned"), sep = "_")))

data_wide <- p.table2 %>% 
        pivot_wider(names_from = "MODEL2", values_from = c("Point Estimate", "SD"), names_glue = "{.value}_{MODEL2}") %>% 
        # Reorder columns
        select(all_of(c("Label", cols_order)))

data_wide %>% 
        gt(rowname_col = "Label") %>%
        tab_spanner_delim(delim = "_") %>% 
  fmt_number(decimals = 4) %>% 
  fmt_number(rows = c(4, 5),
             decimals = 0) %>% 
  fmt_number(rows = c(1,3),
             columns = c(2),
             decimals = 2) %>% 
  fmt_number(rows = c(1,3),
             columns = c(3),
             decimals = 2) %>% 
  tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(5),
      rows = c(5, 7, 9)))

```

```{r, results="show"}
p.table.full %>% 
  tidytable::rename("Point Estimate" = Value, "SD" = StdDev) %>% 
  tidytable::mutate(MODEL2 = ifelse(MODEL2 == "OM tuned", "ISSA tuned", "ISSB tuned")) -> p.table2

cols_order <- unlist(lapply(c("Point Estimate", "SD"), function(x) paste(x, c("ISSA tuned", "ISSB tuned"), sep = "_")))

data_wide <- p.table2 %>% 
        pivot_wider(names_from = "MODEL2", values_from = c("Point Estimate", "SD"), names_glue = "{.value}_{MODEL2}") %>% 
        # Reorder columns
        select(all_of(c("Label", cols_order)))

# # percent difference?
# data_wide %>% 
#   tidytable::mutate(diff.val = 100*abs((`Point Estimate_ISSA tuned` - `Point Estimate_ISSB tuned`)/`Point Estimate_ISSA tuned`),
#                     diff.sd = 100*abs((`SD_ISSA tuned` - `SD_ISSB tuned`)/`SD_ISSA tuned`))

data_wide %>% 
        gt(rowname_col = "Label") %>%
        tab_spanner_delim(delim = "_") %>% 
  fmt_number(decimals = 4) %>% 
  fmt_number(rows = c(11, 12),
             decimals = 0) %>% 
  fmt_number(rows = c(1,2,5,7,9),
             columns = c(2,3),
             decimals = 2) %>% 
  # tab_style(style = list(cell_fill("grey")),
  #           locations = cells_body(
  #     columns = c(5),
  #     rows = c(5, 7, 9)))
    tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(2,3),
      rows = c(6))) %>% 
  tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(4,5),
      rows = c(8,12,14,16))) -> tuned.table
tuned.table

```

<!-- \begin{table}[H] -->
<!-- \centering -->
<!-- ```{r, results='asis', echo=FALSE} -->
<!-- gt::as_latex(tuned.table) %>%  -->
<!--   cat(sep = "") -->

<!-- ``` -->
<!-- \end{table} -->

\newpage

### Tuned with added params

\newpage

```{r, results="hide"}

p.out %>% 
  tidytable::filter(Label%in%c("VonBert_K_Fem_GP_1", "L_at_Amax_Fem_GP_1", "SR_LN(R0)", "L_at_Amin_Fem_GP_1", "Richards_Fem_GP_1", "LnQ_base_Survey(2)", "Size_DblN_peak_Fishery(1)", "Size_DblN_ascend_se_Fishery(1)",
                               "Size_DblN_peak_Survey(2)", "Size_DblN_ascend_se_Survey(2)", "Size_DblN_peak_Fishery(1)_BLK4repl_1977", "Size_DblN_ascend_se_Fishery(1)_BLK4repl_1977"),
                    MODEL2%in%c("OM tuned", "Fiss tuned")) %>% 
  tidytable::mutate(StdDev = Parm_StDev) %>% 
  tidytable::select(-Parm_StDev) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(Label%in%c("SSB_2023", "SSB_2038", "Bratio_2023", "Bratio_2038", "SPRratio_2023", "SPRratio_2038"),
                                           MODEL2%in%c("OM tuned", "Fiss tuned"))) %>% 
  tidytable::select(-X, -MODEL, -HI, -LO) -> p.table.full

```

\blandscape

```{r, results="show"}
p.table.full %>% 
  tidytable::rename("Point Estimate" = Value, "SD" = StdDev) %>% 
  tidytable::mutate(MODEL2 = ifelse(MODEL2 == "OM tuned", "ISSA tuned", "ISSB tuned")) -> p.table2

cols_order <- unlist(lapply(c("Point Estimate", "SD"), function(x) paste(x, c("ISSA tuned", "ISSB tuned"), sep = "_")))

data_wide <- p.table2 %>% 
        pivot_wider(names_from = "MODEL2", values_from = c("Point Estimate", "SD"), names_glue = "{.value}_{MODEL2}") %>% 
        # Reorder columns
        select(all_of(c("Label", cols_order)))

# # percent difference?
# data_wide %>%
#   tidytable::mutate(diff.val = 100*abs((`Point Estimate_ISSA tuned` - `Point Estimate_ISSB tuned`)/`Point Estimate_ISSA tuned`),
#                     diff.sd = 100*abs((`SD_ISSA tuned` - `SD_ISSB tuned`)/`SD_ISSA tuned`))

data_wide %>% 
        gt(rowname_col = "Label") %>%
        tab_spanner_delim(delim = "_") %>% 
  fmt_number(decimals = 4) %>% 
  fmt_number(rows = c(11, 12)+2,
             decimals = 0) %>% 
  fmt_number(rows = c(1,2,5,7,9),
             columns = c(2,3),
             decimals = 2) %>% 
  # tab_style(style = list(cell_fill("grey")),
  #           locations = cells_body(
  #     columns = c(5),
  #     rows = c(5, 7, 9)))
  tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(2,3),
      rows = c(6))) %>% 
  tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(4,5),
      rows = c(8,11,12,14,16,18))) -> tuned.table
tuned.table

```

\elandscape

\newpage

### Untuned

```{r, results="hide"}

p.out %>% 
  tidytable::filter(Label%in%c("VonBert_K_Fem_GP_1", "L_at_Amax_Fem_GP_1", "SR_LN(R0)", "L_at_Amin_Fem_GP_1", "Richards_Fem_GP_1", "LnQ_base_Survey(2)", "Size_DblN_peak_Fishery(1)", "Size_DblN_ascend_se_Fishery(1)",
                               "Size_DblN_peak_Survey(2)", "Size_DblN_ascend_se_Survey(2)"),
                    MODEL2%in%c("OM untuned", "Fiss untuned")) %>% 
  tidytable::mutate(StdDev = Parm_StDev) %>% 
  tidytable::select(-Parm_StDev) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(Label%in%c("SSB_2023", "SSB_2038", "Bratio_2023", "Bratio_2038", "SPRratio_2023", "SPRratio_2038"),
                                           MODEL2%in%c("OM untuned", "Fiss untuned"))) %>% 
  tidytable::select(-X, -MODEL, -HI, -LO) -> p.table.full

```

```{r, results="show"}
p.table.full %>% 
  tidytable::rename("Point Estimate" = Value, "SD" = StdDev) %>% 
  tidytable::mutate(MODEL2 = ifelse(MODEL2 == "OM untuned", "ISSA untuned", "ISSB untuned")) -> p.table2

cols_order <- unlist(lapply(c("Point Estimate", "SD"), function(x) paste(x, c("ISSA untuned", "ISSB untuned"), sep = "_")))

data_wide <- p.table2 %>% 
        pivot_wider(names_from = "MODEL2", values_from = c("Point Estimate", "SD"), names_glue = "{.value}_{MODEL2}") %>% 
        # Reorder columns
        select(all_of(c("Label", cols_order)))

# # percent difference?
# data_wide %>% 
#   tidytable::mutate(diff.val = 100*abs((`Point Estimate_ISSA untuned` - `Point Estimate_ISSB untuned`)/`Point Estimate_ISSA untuned`),
#                     diff.sd = 100*abs((`SD_ISSA untuned` - `SD_ISSB untuned`)/`SD_ISSA untuned`)) 
# 
#

data_wide %>% 
        gt(rowname_col = "Label") %>%
        tab_spanner_delim(delim = "_") %>% 
  fmt_number(decimals = 4) %>% 
  fmt_number(rows = c(11, 12),
             decimals = 0) %>% 
  fmt_number(rows = c(1,2,5,7,9),
             columns = c(2,3),
             decimals = 2) %>% 
  # tab_style(style = list(cell_fill("grey")),
  #           locations = cells_body(
  #     columns = c(5),
  #     rows = c(5, 7, 9)))
    tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(2,3),
      rows = c(6))) %>% 
  tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(4,5),
      rows = c(7,14)))

```

\newpage

### Plots old

```{r}

a.out %>% glimpse()

SSB.names = paste0("SSB_", 1977:2038)
SPRratio.names = paste0("SPRratio_", 1977:2038)
Bratio.names = paste0("Bratio_", 1977:2038)

SSB = a.out %>% 
  tidytable::filter(MODEL2 == "OM tuned", Label%in%SSB.names) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%SSB.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 5, 8)))
SPRratio = a.out %>% 
  tidytable::filter(MODEL2 == "OM tuned", Label%in%SPRratio.names) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%SPRratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 10, 13)))
Bratio = a.out %>% 
  tidytable::filter(MODEL2 == "OM tuned", Label%in%Bratio.names) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%Bratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 8, 11)))

SSB %>% 
  tidytable::rename(Model_run = MODEL2) %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_run, linetype = Model_run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("SSB") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

SPRratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = MODEL2, linetype = MODEL2)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("SPRratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.3), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black")
Bratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = MODEL2, linetype = MODEL2)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("Bratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black")
```

<!-- # Scratch: percent differences of all params -->
<!-- ```{r} -->

<!-- p.out = tidytable(p.out) -->

<!-- p.out %>%  -->
<!--   filter(MODEL2=="OM tuned") %>%  -->
<!--   pull(Value) -> temp1 -->
<!-- p.out %>%  -->
<!--   filter(MODEL2=="Fiss tuned") %>%  -->
<!--   pull(Value) -> temp2 -->
<!-- p.out %>%  -->
<!--   filter(MODEL2=="OM tuned") %>%  -->
<!--   pull(Parm_StDev) -> temp1.2 -->
<!-- p.out %>%  -->
<!--   filter(MODEL2=="Fiss tuned") %>%  -->
<!--   pull(Parm_StDev) -> temp2.2 -->
<!-- p.error = tidytable(value = 100*abs((temp1-temp2)/temp1), -->
<!--                     SD = 100*abs((temp1.2-temp2.2)/temp1.2)) -->

<!-- barplot(p.error$value) -->

<!-- ``` -->

### Plots

\newpage

```{r, fig.height=10}
a.out %>% glimpse()

SSB.names = paste0("SSB_", 1977:2038)
SPRratio.names = paste0("SPRratio_", 1977:2038)
Bratio.names = paste0("Bratio_", 1977:2038)
rec.names = paste0("Recr_", 1977:2038)

a.out %>% 
  tidytable::mutate(MODEL2 = ifelse(MODEL2 == "OM tuned",
                                    "ISSA tuned",
                                    ifelse(MODEL2 == "OM untuned", 
                                           "ISSA untuned",
                                           ifelse(MODEL2 == "Fiss tuned", "ISSB tuned", "ISSB untuned")))) %>% 
  tidytable::rename(Model_Run = MODEL2) -> a.out.2

# tuned

SSB = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA tuned", Label%in%SSB.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB tuned", Label%in%SSB.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 5, 8)))

SPRratio = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA tuned", Label%in%SPRratio.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB tuned", Label%in%SPRratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 10, 13)))

Bratio = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA tuned", Label%in%Bratio.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB tuned", Label%in%Bratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 8, 11)))

Recruitment = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA tuned", Label%in%rec.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB tuned", Label%in%rec.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 6, 9)))

p1 = SSB %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("") + 
  ylab("SSB") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  geom_text(aes(x=2023, label="Assessment Year 2023", y=750000), colour="blue", angle=90, vjust = 1.2) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

p2 = SPRratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("") + 
  ylab("SPRratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.3), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

p3 = Bratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("Bratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  geom_hline(yintercept = .35, linetype = "dashed", color = "black") +
  geom_text(aes(x=1985, label="Management Target = 0.35", y=.38), colour="blue", angle=0) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

p1 + plot_spacer() + p2 + plot_spacer() + p3 + plot_layout(ncol = 1,
                           heights = c(6, -.5, 6, -.5, 6))
```

\newpage

```{r, fig.height=4}
p4 = Recruitment %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("Recruitment") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))
p4

```

\newpage

```{r, fig.height=10}
# untuned

SSB = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA untuned", Label%in%SSB.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB untuned", Label%in%SSB.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 5, 8)))

SPRratio = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA untuned", Label%in%SPRratio.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB untuned", Label%in%SPRratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 10, 13)))

Bratio = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA untuned", Label%in%Bratio.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB untuned", Label%in%Bratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 8, 11)))

p1 = SSB %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("") + 
  ylab("SSB") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  geom_text(aes(x=2023, label="Assessment Year 2023", y=750000), colour="blue", angle=90, vjust = 1.2) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

p2 = SPRratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("") + 
  ylab("SPRratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.3), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

p3 = Bratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("Bratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  geom_hline(yintercept = .35, linetype = "dashed", color = "black") +
  geom_text(aes(x=1985, label="Management Target = 0.35", y=.38), colour="blue", angle=0) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

p1 + plot_spacer() + p2 + plot_spacer() + p3 + plot_layout(ncol = 1,
                           heights = c(6, -.5, 6, -.5, 6))

```

\newpage

# M

```{r, fig.height=8}
profiles = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/Likelihoods_by_fleet.csv")

profiles %>%
  tidytable::filter(Label=="Length_like", variable=="Fishery") %>% 
  mutate(Model_Run = ifelse(MODEL=="Model_23.1.0.d_NEW_FISS_tuned", "ISSB", "ISSA")) -> profiles.2

profiles.2 %>% 
  ggplot(aes(x = M, y = Diff, group = Model_Run, color = Model_Run)) +
  geom_line() +
  geom_point() +
  geom_vline(xintercept = 0.3866, linetype = "dashed", color = "black") +
  geom_text(aes(x = 0.38, label = "Fixed M=0.3866", y = 1.5), colour="blue", angle=90, vjust = 1.2) +
  geom_hline(yintercept = 0) +
  labs(x = "M", y = "Change in -LL for Fishery Length Comps") +
  theme_classic() +
  theme(legend.position = c(.8, .8))

```

### 2025-03-31 run/paper_runs/paper_scenario_1.5.R

@@ -1,8 +1,8 @@
 
 
 rm(list = ls())
-run_name = "paper_scenario_37.2"
-iterations = 500
+run_name = "paper_scenario_1.5"
+iterations = 1000
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
 library(tidytable)
@@ -26,13 +26,13 @@ fishery_iss(species_code = "202",
             new_haul_N = NULL,
             new_length_N = NULL,
             max_length = 150,
-            boot.trip = FALSE,
+            boot.trip = TRUE,
             boot.haul = TRUE,
-            boot.length = FALSE,
+            boot.length = TRUE,
             boot.age = FALSE,
             expand.by.sampling.strata = FALSE,
             expansion_factors = c("haul_numbers", "month_numbers"),
-            save_data_frame = FALSE) -> .output
+            save_data_frame = TRUE) -> .output
 tictoc::toc()
 .output
 

### 2025-03-31 run/paper_runs/paper_scenario_38.1.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_38.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(expansion_global)){
+
+    samples = samples_global[i]
+    expansion = expansion_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = expansion,
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("expansion_", expansion_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-31 run/paper_runs/paper_scenario_38.2.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_38.2"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20, 999)
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(expansion_global)){
+
+    samples = samples_global[i]
+    expansion = expansion_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N = NULL,
+                new_length_N = if(samples==999) {NULL} else{list(type = "value", bound = "minimum", amount = samples, replace = FALSE)},
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = expansion,
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("expansion_", expansion_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-31 run/paper_runs/paper_scenario_39.1.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_39.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20)
+proportion_global = c(0.25, 0.50, 0.75)
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = list(type = "proportion", amount = .proportion),
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("trip_", proportion_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-31 run/paper_runs/paper_scenario_39.2.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_39.2"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20)
+proportion_global = c(0.25, 0.50, 0.75)
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = list(type = "proportion", amount = .proportion, replace=FALSE),
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("trip_", proportion_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-31 run/paper_runs/paper_scenario_39.3.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_39.3"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 10
+samples_global = c(1, 5, 10, 15, 20)
+proportion_global = c(0.25, 0.50, 0.75, 0.9, 1.0)
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = list(type = "proportion", amount = .proportion, replace=FALSE),
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("trip_", proportion_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-31 run/paper_runs/paper_scenario_39.6.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_39.6"
+
+lfreq_data = readRDS(file = '/Users/brettstacy/Documents/baseISS output/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS')
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20)
+proportion_global = c(0.25, 0.5, 0.75, 1.0)
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = list(type = "proportion", amount = .proportion, replace=TRUE),
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers")) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("trip_", proportion_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("/Users/brettstacy/Documents/baseISS output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-31 run/paper_runs/paper_scenario_39.7.R

@@ -1,0 +1,65 @@
+
+rm(list = ls())
+run_name = "paper_scenario_39.7"
+
+lfreq_data = readRDS(file = '/Users/brettstacy/Documents/baseISS output/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS')
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20)
+proportion_global = c(0.25, 0.5, 0.75, 1.0)
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = list(type = "proportion", amount = .proportion, replace=TRUE),
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = FALSE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("trip_", proportion_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("/Users/brettstacy/Documents/baseISS output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-31 run/paper_runs/paper_scenario_40.1.R

@@ -1,0 +1,66 @@
+
+rm(list = ls())
+run_name = "paper_scenario_40.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20)
+proportion_global = c(0.25, 0.50, 0.75)
+
+
+
+tictoc::tic()
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    # tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N =list(type = "proportion", amount = .proportion, replace = FALSE),
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    # tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("haul_", proportion_global)[j]]] = .output
+
+  }
+}
+tictoc::toc()
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-31 run/paper_runs/paper_scenario_41.1.R

@@ -1,7 +1,7 @@
 
 
 rm(list = ls())
-run_name = "paper_scenario_37.2"
+run_name = "paper_scenario_41.1"
 iterations = 500
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
@@ -27,11 +27,11 @@ fishery_iss(species_code = "202",
             new_length_N = NULL,
             max_length = 150,
             boot.trip = FALSE,
-            boot.haul = TRUE,
-            boot.length = FALSE,
+            boot.haul = FALSE,
+            boot.length = TRUE,
             boot.age = FALSE,
             expand.by.sampling.strata = FALSE,
-            expansion_factors = c("haul_numbers", "month_numbers"),
+            expansion_factors = NULL,
             save_data_frame = FALSE) -> .output
 tictoc::toc()
 .output

### 2025-03-31 run/paper_runs/paper_scenario_42.1.R

@@ -1,7 +1,7 @@
 
 
 rm(list = ls())
-run_name = "paper_scenario_37.2"
+run_name = "paper_scenario_42.1"
 iterations = 500
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
@@ -28,10 +28,10 @@ fishery_iss(species_code = "202",
             max_length = 150,
             boot.trip = FALSE,
             boot.haul = TRUE,
-            boot.length = FALSE,
+            boot.length = TRUE,
             boot.age = FALSE,
             expand.by.sampling.strata = FALSE,
-            expansion_factors = c("haul_numbers", "month_numbers"),
+            expansion_factors = NULL,
             save_data_frame = FALSE) -> .output
 tictoc::toc()
 .output

### 2025-03-31 run/paper_runs/paper_scenario_43.1.R

@@ -1,7 +1,7 @@
 
 
 rm(list = ls())
-run_name = "paper_scenario_37.2"
+run_name = "paper_scenario_43.1"
 iterations = 500
 
 lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
@@ -26,12 +26,12 @@ fishery_iss(species_code = "202",
             new_haul_N = NULL,
             new_length_N = NULL,
             max_length = 150,
-            boot.trip = FALSE,
+            boot.trip = TRUE,
             boot.haul = TRUE,
-            boot.length = FALSE,
+            boot.length = TRUE,
             boot.age = FALSE,
             expand.by.sampling.strata = FALSE,
-            expansion_factors = c("haul_numbers", "month_numbers"),
+            expansion_factors = NULL,
             save_data_frame = FALSE) -> .output
 tictoc::toc()
 .output

### 2025-03-31 run/paper_runs/paper_scenario_44.1.R

@@ -1,0 +1,60 @@
+
+rm(list = ls())
+run_name = "paper_scenario_44.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
+expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))
+
+
+# Loop All
+out = list()
+  for(j in 1:length(expansion_global)){
+
+    expansion = expansion_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = NULL,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N = NULL,
+                new_length_N = NULL,
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = FALSE,
+                expansion_factors = expansion,
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("expansion_", expansion_names_global)[j]]] = .output
+
+  }
+
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-31 run/paper_runs/paper_scenario_45.1.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_45.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+proportion_global = seq(0.1, 0.9, by = .1)
+type_global = list("trip", "haul")
+type_names_global = c("trip", "haul")
+
+
+# Loop All
+out = list()
+for(i in 1:length(proportion_global)){
+  out[[paste0("proportion_", proportion_global)[i]]] = list()
+  for(j in 1:length(type_global)){
+
+    .proportion = proportion_global[i]
+    .type = type_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = NULL,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = if(.type=="trip") {list(type = "proportion", amount = .proportion, replace = FALSE)} else{NULL},
+                new_haul_N = if(.type=="haul") {list(type = "proportion", amount = .proportion, replace = FALSE)} else{NULL},
+                new_length_N = NULL,
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = FALSE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("proportion_", proportion_global)[i]]][[paste0("type_", type_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-03-31 run/paper_runs/paper_scenario_47.1.R

@@ -1,0 +1,80 @@
+
+rm(list = ls())
+run_name = "paper_scenario_47.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20)
+data_global = list("H_P", "H")
+data_names_global = c("H_P", "H")
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(data_global)){
+
+    samples = samples_global[i]
+    .data = data_global[[j]]
+
+    if(.data=="H_P"){
+      .lfreq_data = lfreq_data
+    }else{
+      .lfreq_data = lfreq_data %>% tidytable::filter(substr(HAUL_JOIN, 1, 1)=="H")
+    }
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = .lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N = NULL,
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = FALSE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("data_", data_names_global)[j]]] = .output
+
+  }
+}
+
[…]

### 2025-03-31 run/paper_runs/paper_scenario_48.1.R

@@ -1,0 +1,64 @@
+
+rm(list = ls())
+run_name = "paper_scenario_48.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+proportion_global = 1.0
+type_global = list("trip", "haul")
+type_names_global = c("trip", "haul")
+
+
+# Loop All
+out = list()
+for(i in 1:length(proportion_global)){
+  out[[paste0("proportion_", proportion_global)[i]]] = list()
+  for(j in 1:length(type_global)){
+
+    .proportion = proportion_global[i]
+    .type = type_global[[j]]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = NULL,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = if(.type=="trip") {list(type = "proportion", amount = .proportion, replace = FALSE)} else{NULL},
+                new_haul_N = if(.type=="haul") {list(type = "proportion", amount = .proportion, replace = FALSE)} else{NULL},
+                new_length_N = NULL,
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = FALSE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("proportion_", proportion_global)[i]]][[paste0("type_", type_names_global)[j]]] = .output
+
+  }
+}
+
+saveRDS(out, file = paste0("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-06-10 Rmd/paper_plots/paper_plots_1.6.Rmd
include more scenarios and plot scripts

--- 2025-03-31 Rmd/paper_plots/paper_plots_1.5.Rmd
@@
 ---
-title: "Paper Plots V5"
+title: "Paper Plots V6"
 author: "Brett Stacy"
@@
                                 706))
+
+assessment_2023_iss_FI = tidytable(year = 1999:2023,
+                                iss = c(2078,
+                                        1396,
+                                        1829,
+                                        2159,
+                                        1040,
+                                        1887,
+                                        1164,
+                                        2487,
+                                        270,
+                                        1757,
+                                        908,
+                                        1191,
+                                        1398,
+                                        865,
+                                        909,
+                                        1057,
+                                        2068,
+                                        3149,
+                                        2802,
+                                        2996,
+                                        1230,
+                                        0,
+                                        3167,
+                                        2388,
+                                        1976))
 
@@
 mtext("Year", side = 1, line = 2, cex = 1.5)
-
+```
+
+\newpage
+
+```{r, fig.height=6}
 # compare with and without SS
 par(mfrow = c(1,1))
-plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, type = "o", pch = 19, ylab = "ISSB", ylim = c(0, 15000), cex.lab = 1.3) 
+plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, type = "o", pch = 19, ylab = "ISSB", ylim = c(0, 13000), cex.lab = 1.3) 
 lines(out_1.4.old$length$iss$YEAR, out_1.4.old$length$iss$iss, col = "blue", type = "o", pch = 5)
@@
 ```
+
+\newpage
 
@@
 # par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
-par(mfrow = c(3,1), mar = c(0,3.1,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
+par(mfrow = c(3,1), mar = c(0,3.2,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
 plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, type = "o", pch = 19, ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.5, cex.axis = 1.3)
@@
 legend(1977, 11000, lty = c(1,1,1), col = c("black", "blue", "orange"), pch = c(19, 3, 5), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n", cex = 1.5)
-text(1977, 14000, "A", cex = 1.5)
+text(1977, 14000, "a", cex = 2, font = 2)
 
 plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xaxt = "n", cex.lab = 1.5, cex.axis = 1.3)
-text(1977, 420000, "B", cex = 1.5)
-
-plot(out_5.2$length$iss$YEAR[sub_range], out_5.2$length$iss$iss[sub_range], ylab = "ISSB", cex.lab = 1.5, col = "cyan", ylim = c(0, 27000), xlab = "", xaxt = "n", lwd = 1.5, type = "o", pch= 18, cex.axis = 1.3)
+text(1977, 420000, "b", cex = 2, font = 2)
+
+plot(out_5.2$length$iss$YEAR[sub_range], out_5.2$length$iss$iss[sub_range], ylab = "ISSB", cex.lab = 1.5, col = "cyan", ylim = c(0, 26000), xlab = "", xaxt = "n", lwd = 1.5, type = "o", pch= 18, cex.axis = 1.3)
 axis(side = 1, at = seq(1980, 2020, by = 5), cex.axis = 1.3)
@@
 legend(1977, 20000, title = "Scenario", legend = c("1", "2", "3", "Full"), lty = c(1,1,1,1), pch = c(18, 15, 17, 19), col = c("cyan", "orange3", "magenta", "black"), bty = "n", lwd = rep(1.5, 4), cex = 1.5)
-text(1977, 23000, "C", cex = 1.5)
+text(1977, 23000, "c", cex = 2, font = 2)
 
@@
 
-```{r, fig.height=10}
+```{r, fig.height=9}
 out_1.5$length$og_props %>% 
@@
                      n.breaks = 9) +
-  labs(x = "Length (cm)", y = "Frequency", tag = "A") +
+  labs(x = "Length (cm)", y = "Frequency", tag = "a") +
   theme(legend.position = c(0.8, 0.8),
@@
   scale_y_continuous(limits = c(0, .04), expand = c(0, 0)) +
-  scale_color_viridis_d() +
-  scale_fill_viridis_d()
+  scale_fill_brewer(palette = "Dark2") +
+  scale_color_brewer(palette = "Dark2")
 
@@
 
+p3 = ggplot(data = props.sub, aes(x = rss, colour = Year, shape = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "e") +
+  geom_point(data = props.sub %>%
+               tidytable::left_join(out_1.5$length$iss %>%
+                                      tidytable::select(YEAR, iss)) %>%
+               tidytable::summarise(x = unique(iss), .by = Year) %>%
+               # tidytable::summarise(x = median(rss), .by = Year) %>%
+               tidytable::mutate(y = c(5,6)), aes(x,y, fill = Year, color = Year), size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  scale_shape_manual(values = c(23, 25)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", ""),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_fill_brewer(palette = "Dark2") +
+  scale_color_brewer(palette = "Dark2")
+
+# now do RSS with boot_length only.
+out_5.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year, shape = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "b") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_5.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(7,9)), aes(x,y, fill = Year, color = Year), size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
+  scale_shape_manual(values = c(23, 25)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", ""),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_fill_brewer(palette = "Dark2") +
+  scale_color_brewer(palette = "Dark2")
+
+# now do RSS with boot_length and boot_haul.
+out_9.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year, shape = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "c") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_9.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(5,6)), aes(x,y, fill = Year, color = Year), size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  scale_shape_manual(values = c(23, 25)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", ""),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_fill_brewer(palette = "Dark2") +
+  scale_color_brewer(palette = "Dark2")
+
+# now do RSS with boot all.
+out_4.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year, shape = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "d") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_4.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(2,2)), aes(x,y, fill = Year, color = Year), size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
+  scale_shape_manual(values = c(23, 25)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", ""),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_fill_brewer(palette = "Dark2") +
+  scale_color_brewer(palette = "Dark2")
+
+p1 / p3.2 / p3.3 / p3.4 / p3
+
+```
+
+The comparison shows that fish in 2003 were less similar in length compared to 2004.
+2003 corresponds to a higher ISS even though the sample rate was the same and the number of hauls and nominal sample size were comparable.
+More of the fish sampled in 2003 were required for characterizing the underlying multinomial sampling distribution compared to 2004 because more lengths were represented at a higher rate in 2003 (shorter, wider distribution).
+This is reflected in the RSS (ref figure).
+
+# * 2000 & 2001 Histograms
+
+\newpage
+
+```{r, fig.height=10}
+out_1.5$length$og_props %>% 
+  tidytable::filter(YEAR %in% 2000:2001) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
+  geom_line() +
+  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  # geom_area_pattern(aes(pattern = Year, y = og_FREQ, x = LENGTH), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  scale_x_continuous(limits = c(22, 108),
+                     n.breaks = 9) +
+  labs(x = "Length (cm)", y = "Frequency", tag = "a") +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  scale_y_continuous(limits = c(0, .04), expand = c(0, 0)) +
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+# now do RSS
+out_1.5$length$rss %>% 
+  tidytable::filter(YEAR %in% 2000:2001) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
 p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
-  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 100) +
   theme_classic() +
@@
         plot.tag = element_text(size = 14, face = "bold")) +
-  labs(x = "RSS", y = "Count", tag = "E") + 
+  labs(x = "RSS", y = "Count", tag = "e") + 
   geom_point(data = props.sub %>% 
@@
 out_5.2$length$rss %>% 
-  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::filter(YEAR %in% 2000:2001) %>% 
   tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
@@
         plot.tag = element_text(size = 14, face = "bold")) +
-  labs(x = "RSS", y = "Count", tag = "B") + 
+  labs(x = "RSS", y = "Count", tag = "b") + 
   geom_point(data = props.sub %>% 
@@
 out_9.2$length$rss %>% 
-  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::filter(YEAR %in% 2000:2001) %>% 
   tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
@@
         plot.tag = element_text(size = 14, face = "bold")) +
-  labs(x = "RSS", y = "Count", tag = "C") + 
+  labs(x = "RSS", y = "Count", tag = "c") + 
   geom_point(data = props.sub %>% 
@@
 out_4.2$length$rss %>% 
-  tidytable::filter(YEAR %in% 2003:2004) %>% 
+  tidytable::filter(YEAR %in% 2000:2001) %>% 
   tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
@@
         plot.tag = element_text(size = 14, face = "bold")) +
-  labs(x = "RSS", y = "Count", tag = "D") + 
+  labs(x = "RSS", y = "Count", tag = "d") + 
   geom_point(data = props.sub %>% 
@@
 
-# # now do RSS with boot all + SS
-# out_2.2$length$rss %>% 
-#   tidytable::filter(YEAR %in% 2003:2004) %>% 
-#   tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
-# 
-# p3.5 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
-#   geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
-#   theme_classic() +
-#   theme(legend.position = c(0.8, 0.8),
-#         plot.tag.position = c(0.1, 0.95),
-#         plot.tag = element_text(size = 14, face = "bold")) +
-#   labs(x = "RSS", y = "Count", tag = "E") + 
-#   geom_point(data = props.sub %>% 
-#                tidytable::left_join(out_2.2$length$iss %>% 
-#                                       tidytable::select(YEAR, iss)) %>% 
-#                tidytable::summarise(x = unique(iss), .by = Year) %>% 
-#                # tidytable::summarise(x = median(rss), .by = Year) %>% 
-#                tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
-#   scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
-#   # scale_x_continuous(n.breaks = 8)
-#   scale_x_continuous(breaks = seq(0, 35000, by = 2500),
-#                      labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
-#                      limits = c(0, 35000),
-#                      expand = c(0, 0))
-# 
-#
-
-# 
-# p1 / p3
-# p1 / p3 / p3.2
-
 p1 / p3.2 / p3.3 / p3.4 / p3
@@
 
-The comparison shows that fish in 2003 were less similar in length compared to 2004.
-2003 corresponds to a higher ISS even though the sample rate was the same and the number of hauls and nominal sample size were comparable.
-More of the fish sampled in 2003 were required for characterizing the underlying multinomial sampling distribution compared to 2004 because more lengths were represented at a higher rate in 2003 (shorter, wider distribution).
-This is reflected in the RSS (ref figure).
+# * 1998 & 1999 Histograms
+
+\newpage
+
+```{r, fig.height=10}
+out_1.5$length$og_props %>% 
+  tidytable::filter(YEAR %in% 1998:1999) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
+  geom_line() +
+  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  # geom_area_pattern(aes(pattern = Year, y = og_FREQ, x = LENGTH), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  scale_x_continuous(limits = c(22, 108),
+                     n.breaks = 9) +
+  labs(x = "Length (cm)", y = "Frequency", tag = "a") +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  scale_y_continuous(limits = c(0, .04), expand = c(0, 0)) +
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+# now do RSS
+out_1.5$length$rss %>% 
+  tidytable::filter(YEAR %in% 1998:1999) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 100) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "e") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_1.5$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+# now do RSS with boot_length only.
+out_5.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 1998:1999) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "b") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_5.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+# now do RSS with boot_length and boot_haul.
+out_9.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 1998:1999) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "c") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_9.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+# now do RSS with boot all.
+out_4.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 1998:1999) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "d") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_4.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(2,2)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+p1 / p3.2 / p3.3 / p3.4 / p3
+
+```
+
+# * 2004 & 2005 Histograms
+
+\newpage
+
+```{r, fig.height=10}
+out_1.5$length$og_props %>% 
+  tidytable::filter(YEAR %in% 2004:2005) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p1 = ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
+  geom_line() +
+  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
+  # geom_area_pattern(aes(pattern = Year, y = og_FREQ, x = LENGTH), alpha = 0.5, position = "identity") +
+  theme_classic() +
+  scale_x_continuous(limits = c(22, 108),
+                     n.breaks = 9) +
+  labs(x = "Length (cm)", y = "Frequency", tag = "a") +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  scale_y_continuous(limits = c(0, .04), expand = c(0, 0)) +
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+# now do RSS
+out_1.5$length$rss %>% 
+  tidytable::filter(YEAR %in% 2004:2005) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 100) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "e") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_1.5$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+# now do RSS with boot_length only.
+out_5.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2004:2005) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "b") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_5.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+# now do RSS with boot_length and boot_haul.
+out_9.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2004:2005) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "c") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_9.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(6,6)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+# now do RSS with boot all.
+out_4.2$length$rss %>% 
+  tidytable::filter(YEAR %in% 2004:2005) %>% 
+  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub
+
+p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
+  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
+  theme_classic() +
+  theme(legend.position = c(0.8, 0.8),
+        plot.tag.position = c(0.1, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  labs(x = "RSS", y = "Count", tag = "d") + 
+  geom_point(data = props.sub %>% 
+               tidytable::left_join(out_4.2$length$iss %>% 
+                                      tidytable::select(YEAR, iss)) %>% 
+               tidytable::summarise(x = unique(iss), .by = Year) %>% 
+               # tidytable::summarise(x = median(rss), .by = Year) %>% 
+               tidytable::mutate(y = c(2,2)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
+  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
+  # scale_x_continuous(n.breaks = 8)
+  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
+                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
+                     limits = c(0, 35000),
+                     expand = c(0, 0))+
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+p1 / p3.2 / p3.3 / p3.4 / p3
+
+```
 
 # * Time series Expansion NEW
-```{r, fig.width=9, fig.height=5}
+
+\newpage
+
+```{r, fig.width=9, fig.height=4}
 out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_44.1_ISS_500_iters_2025-03-25.RDS")
@@
 
-# 1999:2023
-df2 %>% 
+# # 1999:2023
+# df2 %>% 
+#   filter(year%in%1999:2023) %>% 
+# ggplot(aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+#   geom_line() +
+#   geom_point() +
+#   scale_shape_manual(values = c(1,2,3)) +
+#   labs(x = "Year", y = "ISSB", color = "Expansion Complexity") +
+#   scale_color_manual(labels = c("None", "Medium: haul only", "Full: haul, area, gear, month"), values = c("blue", "red", "black")) +
+#   geom_point() + 
+#   theme_classic() + 
+#   theme(legend.position = c(0.7, 0.9),
+#         axis.title = element_text(size = 14),
+#         axis.text = element_text(size = 12),
+#         legend.text = element_text(size = 12),
+#         legend.title = element_text(size = 14))
+
+# 1999:2023 for paper
+l1 = df2 %>% 
   filter(year%in%1999:2023) %>%
-ggplot(aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+  mutate(scenario = factor(ifelse(scenario=="none", "None", 
+                           ifelse(scenario=="medium", "Medium", "Full")), levels = c("Full", "Medium", "None"))) %>% 
+  ggplot(aes(x = year, y = ISS, colour = scenario, shape = scenario)) +
   geom_line() +
   geom_point() +
-  scale_shape_manual(values = c(1,2,3)) +
-  labs(x = "Year", y = "ISSB", color = "Expansion Complexity") +
-  scale_color_manual(labels = c("None", "Medium: haul only", "Full: haul, area, gear, month"), values = c("blue", "red", "black")) +
-  geom_point() + 
-  theme_classic() + 
-  theme(legend.position = c(0.7, 0.9),
+  scale_shape_manual(name = "Expansion Complexity", 
+                     labels = c("full", "intermediate", "none"),
+                     values = c(1,2,19)) +
+  scale_color_manual(name = "Expansion Complexity", 
+                     labels = c("full", "intermediate", "none"), 
+                     values = c("black", "orange", "blue")) +
+  labs(x = "", y = "ISSB") +
+  scale_x_continuous(breaks = seq(2000, 2020, by = 5), labels = seq(2000, 2020, by = 5)) +
+  scale_y_continuous(breaks = seq(0, 14000, by = 2000)) +
+  theme_classic() + 
+  theme(legend.position = c(0.55, 0.85),
         axis.title = element_text(size = 14),
@@
         legend.text = element_text(size = 12),
-        legend.title = element_text(size = 14))
+        legend.title = element_text(size = 14),
+        legend.background = element_rect(fill = "transparent"))
+
+l2 = df2 %>% 
+  filter(year%in%1999:2023) %>%
+  mutate(scenario = factor(ifelse(scenario=="none", "n", 
+                           ifelse(scenario=="medium", "i", "f")), levels = c("f", "i", "n"))) %>% 
+  ggplot(aes(x = scenario, y = ISS, fill = scenario)) +
+  geom_boxplot() +
+  stat_summary(fun = median, geom = "point", shape = c(1, 2, 19), color = "white") +
+  scale_fill_manual(values = c("black", "orange", "blue")) +
+  labs(x = "", y = "") +
+  theme_classic() +
+  theme(legend.position = "none",
+        axis.text = element_text(size = 12)) +
+  scale_y_continuous(labels = NULL,
+                     breaks = seq(0, 14000, by = 2000))
+
+l1 + plot_spacer() + l2 + plot_layout(ncol = 3, nrow = 1,
+                           widths = c(7, -.6, 1))
+
+```
+
+\newpage
+
+# Time series Expansion WITH SURVEY ISS
+
+```{r, fig.width=9, fig.height=4}
+out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_44.1_ISS_500_iters_2025-03-25.RDS")
+
+year = out_2.1.1$expansion_NULL$length$iss$YEAR
+
+df = tidytable(year = year,
+               none = out_2.1.1$expansion_NULL$length$iss$iss,
+               medium = out_2.1.1$expansion_haul_numbers$length$iss$iss,
+               full = out_2.1.1$expansion_haul_month_numbers$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+# 
+# # all years
+# ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+#   geom_line() +
+#   labs(x = "", y = "ISSB") +
+#   geom_point() + 
+#   theme_classic() +
+#   theme(legend.position = c(0.84, 0.8),
+#         axis.title.x = element_blank())
+
+# # 1999:2023
+# df2 %>% 
+#   filter(year%in%1999:2023) %>% 
+# ggplot(aes(x = year, y = ISS, group = scenario, colour = scenario)) +
+#   geom_line() +
+#   geom_point() +
+#   scale_shape_manual(values = c(1,2,3)) +
+#   labs(x = "Year", y = "ISSB", color = "Expansion Complexity") +
+#   scale_color_manual(labels = c("None", "Medium: haul only", "Full: haul, area, gear, month"), values = c("blue", "red", "black")) +
+#   geom_point() + 
+#   theme_classic() + 
+#   theme(legend.position = c(0.7, 0.9),
+#         axis.title = element_text(size = 14),
+#         axis.text = element_text(size = 12),
+#         legend.text = element_text(size = 12),
+#         legend.title = element_text(size = 14))
+
+# 1999:2023 for paper
+l1 = df2 %>% 
+  filter(year%in%1999:2023) %>%
+  mutate(scenario = factor(ifelse(scenario=="none", "None", 
+                           ifelse(scenario=="medium", "Medium", "Full")), levels = c("Full", "Medium", "None"))) %>% 
+  tidytable::bind_rows(assessment_2023_iss_FI %>% 
+                         tidytable::mutate(scenario = "survey") %>% 
+                         tidytable::rename(ISS = iss)) %>% 
+  ggplot(aes(x = year, y = ISS, colour = scenario, shape = scenario)) +
+  geom_line() +
+  geom_point() +
+  scale_shape_manual(name = "Expansion Complexity", 
+                     labels = c("full", "intermediate", "none", "survey ISS"),
+                     values = c(1,2,19,3)) +
+  scale_color_manual(name = "Expansion Complexity", 
+                     labels = c("full", "intermediate", "none", "survey ISS"), 
+                     values = c("black", "orange", "blue", "purple")) +
+  labs(x = "", y = "ISSB") +
+  scale_x_continuous(breaks = seq(2000, 2020, by = 5), labels = seq(2000, 2020, by = 5)) +
+  scale_y_continuous(breaks = seq(0, 14000, by = 2000)) +
+  theme_classic() + 
+  theme(legend.position = c(0.55, 0.85),
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12),
+        legend.text = element_text(size = 12),
+        legend.title = element_text(size = 14),
+        legend.background = element_rect(fill = "transparent"))
+
+l2 = df2 %>%
+  filter(year%in%1999:2023) %>%
+  mutate(scenario = factor(ifelse(scenario=="none", "n",
+                           ifelse(scenario=="medium", "i", "f")), levels = c("f", "i", "n"))) %>%
+  tidytable::bind_rows(assessment_2023_iss_FI %>% 
+                         tidytable::mutate(scenario = "s") %>% 
+                         tidytable::rename(ISS = iss)) %>% 
+  ggplot(aes(x = scenario, y = ISS, fill = scenario)) +
+  geom_boxplot() +
+  stat_summary(fun = median, geom = "point", shape = c(1, 2, 19, 3), color = "white") +
+  scale_fill_manual(values = c("black", "orange", "blue", "purple")) +
+  labs(x = "", y = "") +
+  theme_classic() +
+  theme(legend.position = "none",
+        axis.text = element_text(size = 12)) +
+  scale_y_continuous(labels = NULL,
+                     breaks = seq(0, 14000, by = 2000))
+
+l1 + plot_spacer() + l2 + plot_layout(ncol = 3, nrow = 1,
+                           widths = c(7, -.6, 1))
+
+# l1
+
 ```
@@
   tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Enone"])/df2$ISS[df2$scenario=="N20_Enone"],
-                    type = "Enone",
+                    type = "none",
                     .by = scenario) %>% 
@@
   tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Emedium"])/df2$ISS[df2$scenario=="N20_Emedium"],
-                    type = "Emedium",
+                    type = "medium",
                     .by = scenario) %>% 
@@
   tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
-                    type = "Efull",
+                    type = "full",
                     .by = scenario) %>% 
@@
   tidytable::mutate(ISS.error = (ISS - relative.trip)/relative.trip,
-                    type = "trip",
+                    Level = "Trips",
                     .by = scenario) -> df3.1
@@
   tidytable::mutate(ISS.error = (ISS - relative.haul)/relative.haul,
-                    type = "haul",
+                    Level = "Hauls",
                     .by = scenario) -> df3.2
@@
 df3.1 %>% 
-  tidytable::bind_rows(df3.2) -> df4
-
-df4 %>% 
+  tidytable::bind_rows(df3.2) -> df4.prop
+
+df4.prop %>% 
   ggplot(aes(x = scenario, y = ISS.error*100)) +
-  geom_boxplot(aes(fill = type)) +
+  geom_boxplot(aes(fill = Level)) +
   labs(x = "Proportional Change", y = "ISSB % Difference") +
   theme_classic() +
-  theme(legend.position = c(0.8, 0.2)) +
+  theme(legend.position = c(0.8, 0.2),
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12),
+        legend.text = element_text(size = 12),
+        legend.title = element_text(size = 14),
+        legend.background = element_rect(fill = "transparent")) +
   geom_hline(yintercept = 0, linetype = "solid", color = "black") +
   geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
-  scale_y_continuous(breaks = seq(-100, 20, by = 10), limits = c(-100, 20)) +
-  scale_x_discrete(labels = c("0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.7", "0.8", "0.9"))
+  scale_y_continuous(breaks = seq(-100, 20, by = 10), limits = c(-95, 17), expand = c(0, 0)) +
+  scale_x_discrete(labels = c("0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.7", "0.8", "0.9")) +
+  scale_fill_brewer(palette = "Dark2") +
+  scale_color_brewer(palette = "Dark2")
 
@@
 out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_40.3_ISS_500_iters_2025-03-25.RDS")
+# out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_40.4_ISS_500_iters_2025-03-27.RDS")
 
@@
 
+### DATA: Samples VS Trip/haul. Replace=TRUE, including 1.0
+```{r, fig.width=8}
+
+out_25.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_49.1_ISS_500_iters_2025-04-04.RDS")
+# out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_39.8_ISS_500_iters_2025-03-27.RDS")
+
+# year = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$YEAR
+year = out_25.1$samples_1$haul_0.5_trip_0.75$length$iss$YEAR
+
+df = tidytable(year = year,
+               N1_H0.5_T0.5 = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$iss,
+               N5_H0.5_T0.5 = out_25.1$samples_5$haul_0.5_trip_0.5$length$iss$iss,
+               N10_H0.5_T0.5 = out_25.1$samples_10$haul_0.5_trip_0.5$length$iss$iss,
+               N15_H0.5_T0.5 = out_25.1$samples_15$haul_0.5_trip_0.5$length$iss$iss,
+               N20_H0.5_T0.5 = out_25.1$samples_20$haul_0.5_trip_0.5$length$iss$iss,
+
+               N1_H0.5_T0.75 = out_25.1$samples_1$haul_0.5_trip_0.75$length$iss$iss,
+               N5_H0.5_T0.75 = out_25.1$samples_5$haul_0.5_trip_0.75$length$iss$iss,
+               N10_H0.5_T0.75 = out_25.1$samples_10$haul_0.5_trip_0.75$length$iss$iss,
+               N15_H0.5_T0.75 = out_25.1$samples_15$haul_0.5_trip_0.75$length$iss$iss,
+               N20_H0.5_T0.75 = out_25.1$samples_20$haul_0.5_trip_0.75$length$iss$iss,
+
+               N1_H0.75_T0.5 = out_25.1$samples_1$haul_0.75_trip_0.5$length$iss$iss,
+               N5_H0.75_T0.5 = out_25.1$samples_5$haul_0.75_trip_0.5$length$iss$iss,
+               N10_H0.75_T0.5 = out_25.1$samples_10$haul_0.75_trip_0.5$length$iss$iss,
+               N15_H0.75_T0.5 = out_25.1$samples_15$haul_0.75_trip_0.5$length$iss$iss,
+               N20_H0.75_T0.5 = out_25.1$samples_20$haul_0.75_trip_0.5$length$iss$iss,
+
+               N1_H0.75_T0.75 = out_25.1$samples_1$haul_0.75_trip_0.75$length$iss$iss,
+               N5_H0.75_T0.75 = out_25.1$samples_5$haul_0.75_trip_0.75$length$iss$iss,
+               N10_H0.75_T0.75 = out_25.1$samples_10$haul_0.75_trip_0.75$length$iss$iss,
+               N15_H0.75_T0.75 = out_25.1$samples_15$haul_0.75_trip_0.75$length$iss$iss,
+               N20_H0.75_T0.75 = out_25.1$samples_20$haul_0.75_trip_0.75$length$iss$iss,
+
+               N1_H1.0_T1.0 = out_25.1$samples_1$haul_1_trip_1$length$iss$iss,
+               N5_H1.0_T1.0 = out_25.1$samples_5$haul_1_trip_1$length$iss$iss,
+               N10_H1.0_T1.0 = out_25.1$samples_10$haul_1_trip_1$length$iss$iss,
+               N15_H1.0_T1.0 = out_25.1$samples_15$haul_1_trip_1$length$iss$iss,
+               N20_H1.0_T1.0 = out_25.1$samples_20$haul_1_trip_1$length$iss$iss)
+
+df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
+
+scenario_names = c("H0.5_T0.5", "H0.5_T0.75", "H0.75_T0.5", "H0.75_T0.75", "H1.0_T1.0")
+scenario_names.short = c("0.5/0.5", "0.5/0.75", "0.75/0.5", "0.75/0.75", "1.0/1.0")
+
+## 1
+df2[grep(scenario_names[1], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[1],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[1])+2))) -> df3.1
+
+## 2
+df2[grep(scenario_names[2], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[2],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[2])+2))) -> df3.2
+
+## 3
+df2[grep(scenario_names[3], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[3],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[3])+2))) -> df3.3
+
+## 4
+df2[grep(scenario_names[4], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[4],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[4])+2))) -> df3.4
+
+## 5
+df2[grep(scenario_names[5], scenario)] %>% 
+  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0_T1.0"])/df2$ISS[df2$scenario=="N20_H1.0_T1.0"],
+                    type = scenario_names.short[5],
+                    .by = scenario) %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -(nchar(scenario_names[5])+2))) -> df3.5
+
+df3.1 %>% 
+  tidytable::bind_rows(df3.2) %>% 
+  tidytable::bind_rows(df3.3) %>% 
+  tidytable::bind_rows(df3.4) %>% 
+  tidytable::bind_rows(df3.5) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
+df4 -> df4.3.b
+
+```
+
 ### * 2 Panel: Sample Size VS Trip, Haul
@@
 
+# Sampling Rates Together 5 panel
+
+```{r, fig.height=12, fig.width=10}
+
+p1 = df4.a %>%
+  ggplot(aes(x = scenario, y = ISS.error)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "a") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.25), 
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Haul and Port data"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+p2 = df4.b %>%
+  ggplot(aes(x = scenario, y = ISS.error)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "", tag = "b") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.25), 
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Haul only data"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+p3 = df4.1.a %>%
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>%
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "c") +
+  theme_classic() +
+  theme(legend.position = c(0.74, 0.15),
+        legend.direction = "horizontal",
+        legend.box = "horizontal",
+        legend.background = element_rect(fill = "transparent"),
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  guides(fill = guide_legend(title = "Trips",
+                             title.position = "top",
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+p4 = df4.1.b %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Sampling Rate", y = "", tag = "d") +
+  theme_classic() +
+  theme(legend.position = c(0.74, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        legend.background = element_rect(fill = "transparent"),
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Hauls",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+p5 = df4.0 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Sampling Rate", y = "ISSB % Difference", tag = "e") +
+  theme_classic() +
+    theme(legend.position = c(0.7, 0.2), 
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        legend.background = element_rect(fill = "transparent"),
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Expansion Complexity"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_x_discrete(labels = c("1", "5", "10", "15", "20")) +
+  scale_color_viridis_d() +
+  scale_fill_viridis_d()
+
+p1 + 
+p2 + 
+p3 +
+p4 +
+p5 +
+plot_layout(ncol = 2, nrow = 3)
+
+```
+
+# Sampling Rates Together 6 panel
+
+```{r, fig.height=12, fig.width=10}
+
+p1 = df4.a %>%
+  tidytable::mutate(type = ifelse(type=="relative_20", "baseline 20", "baseline full")) %>% 
+  ggplot(aes(x = scenario, y = ISS.error)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "a") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.25), 
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Haul and Port data"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_fill_brewer(palette = "Dark2")
+
+p2 = df4.b %>%
+  tidytable::mutate(type = ifelse(type=="relative_20", "baseline 20", "baseline full")) %>% 
+  ggplot(aes(x = scenario, y = ISS.error)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "ISSB % Difference", tag = "b") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.25), 
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Haul only data"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_fill_brewer(palette = "Dark2")
+
+p3 = df4.1.a %>%
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>%
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "", tag = "d") +
+  theme_classic() +
+  theme(legend.position = c(0.74, 0.15),
+        legend.direction = "horizontal",
+        legend.box = "horizontal",
+        legend.background = element_rect(fill = "transparent"),
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  guides(fill = guide_legend(title = "Trips",
+                             title.position = "top",
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_fill_brewer(palette = "Dark2")
+
+p4 = df4.1.b %>% 
+  tidytable::mutate(scenario = str_sub(scenario, start = 2, end = -1)) %>% 
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "", y = "", tag = "e") +
+  theme_classic() +
+  theme(legend.position = c(0.74, 0.15), 
+        legend.direction = "horizontal", 
+        legend.box = "horizontal",
+        legend.background = element_rect(fill = "transparent"),
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Hauls",
+                             title.position = "top", 
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_fill_brewer(palette = "Dark2")
+
+p5 = df4.3.b %>%
+  tidytable::mutate(scenario = factor(str_sub(scenario, start = 2, end = -1))) %>%
+  # tidytable::filter(type %in% scenario_names.short[c(2,4,5,6,7)]) %>%
+  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) %>%
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Sampling Rate (cod per haul)", y = "", tag = "f") +
+  theme_classic() +
+  theme(legend.position = c(0.7, 0.15),
+        legend.direction = "horizontal",
+        legend.box = "horizontal",
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) +
+  guides(fill = guide_legend(title = "Hauls/Trips",
+                             title.position = "top",
+                             title.hjust = 0.5,
+                             label.position = "bottom"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_fill_brewer(palette = "Dark2")
+
+p6 = df4.0 %>% 
+  ggplot(aes(x = scenario, y = ISS.error*100)) +
+  geom_boxplot(aes(fill = type)) +
+  labs(x = "Sampling Rate (cod per haul)", y = "ISSB % Difference", tag = "c") +
+  theme_classic() +
+    theme(legend.position = c(0.7, 0.25), 
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        legend.background = element_rect(fill = "transparent"),
+        plot.tag.position = c(0.15, 0.95),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  guides(fill = guide_legend(title = "Expansion Complexity"))  +
+  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
+  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-94, 10)) +
+  scale_x_discrete(labels = c("1", "5", "10", "15", "20")) +
+  scale_fill_brewer(palette = "Dark2")
+
+p1 + 
+p3 + 
+p2 +
+p4 +
+p6 +
+p5 +
+plot_layout(ncol = 2, nrow = 3)
+
+```
+
 # SCRATCH
@@
 
-```{r}
+```{r, fig.height=4}
 
 par(mfrow = c(1,1))
-plot(out_37.2$length$iss$YEAR, out_37.2$length$iss$iss, col = "blue", type = "l")
+plot(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss, ylab = "ISSB", type = "l", xlab = "")
+plot(out_37.2$length$iss$YEAR, out_37.2$length$iss$iss, col = "blue", type = "l", ylab = "ISSB", xlab = "")
 lines(out_1.5$length$iss$YEAR, out_1.5$length$iss$iss)
 lines(out_37.3$length$iss$YEAR, out_37.3$length$iss$iss, col = "purple")
-
-```
+legend("topleft", legend = c("Baseline", "Boot Trips Only", "Boot Hauls Only"), col = c("black", "purple", "blue"), lty = rep(1, 3))
+
+```
+
+# Supp Mat Simulation
+
+```{r}
+# Load required packages
+library(MASS)  # For multinomial sampling
+library(ggplot2)  # For visualization
+
+# Define two probability distributions
+narrow_probs <- c(0.7, 0.2, 0.08, 0.02)  # Mostly concentrated in one category
+wide_probs <- c(0.4, 0.3, 0.2, 0.1)  # More evenly spread across categories
+categories <- c("A", "B", "C", "D")  # Labels for categories
+
+# Function to sample from multinomial and estimate proportions
+simulate_multinomial <- function(sample_size, probs) {
+  samples <- rmultinom(1, sample_size, probs)  # Draw samples
+  estimated_probs <- samples / sum(samples)  # Compute proportions
+  return(estimated_probs)
+}
+
+# Compare different sample sizes for both distributions
+set.seed(123)  # Ensure reproducibility
+narrow_sample_small <- simulate_multinomial(100, narrow_probs)
+wide_sample_small <- simulate_multinomial(100, wide_probs)
+narrow_sample_large <- simulate_multinomial(10000, narrow_probs)
+wide_sample_large <- simulate_multinomial(10000, wide_probs)
+
+# Create a data frame for plotting
+df <- data.frame(
+  Category = rep(categories, times = 4),
+  Probability = c(narrow_sample_small, narrow_sample_large, wide_sample_small, wide_sample_large),
+  Sample_Size = rep(c("Small (100)", "Large (10,000)"), each = 8),
+  Distribution = rep(c("Narrow", "Wide"), each = 4, times = 2)
+)
+
+# Plot results
+ggplot(df, aes(x = Category, y = Probability, fill = Sample_Size)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  facet_wrap(~Distribution) +
+  theme_minimal() +
+  labs(title = "Multinomial Probability Estimates by Sample Size",
+       x = "Category",
+       y = "Estimated Probability",
+       fill = "Sample Size") +
+  scale_fill_manual(values = c("#66c2a5", "#fc8d62"))  # Custom colors
+```
+
+# Supp Mat Bimodal
+
+```{r}
+
+df.temp = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS/Rmd/comp_bimodal_expansion.RDS")
+
+ggplot(data=df.temp, aes(x=bin, y=freq, colour=Composition)) + 
+  geom_line() +
+  geom_area(aes(fill=Composition, group=Composition), alpha = 0.5, position = "identity") +
+  scale_x_continuous(limits = c(20, 110)) +
+  labs(x = "Length (cm)", y = "Frequency") +
+  theme_classic() +
+    theme(legend.position = c(0.75, 0.75))
+```

### 2025-06-10 Rmd/paper_plots/paper_plots_assessment_1.Rmd
include more scenarios and plot scripts

@@
 # M
+## ISSA to ISSB single plot
 
@@
 ```
+
+## ISSA to ISSB 2
+
+```{r, fig.height=8}
+profiles = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/Likelihoods_by_fleet.csv")
+
+profiles %>%
+  tidytable::filter(Label=="Length_like", M>=0.300) %>% 
+  mutate(Model_Run = ifelse(MODEL=="Model_23.1.0.d_NEW_FISS_tuned", "ISSB", "ISSA")) -> profiles.2
+
+p1 = profiles.2 %>% 
+  tidytable::filter(Model_Run=="ISSA") %>% 
+  ggplot(aes(x = M, y = Diff, group = variable, color = variable)) +
+  geom_line() +
+  geom_point() +
+  geom_vline(xintercept = 0.3866, linetype = "dashed", color = "black") +
+  geom_text(aes(x = 0.38, label = "Fixed M=0.3866", y = 1.5), colour="blue", angle=90, vjust = 1.2) +
+  geom_hline(yintercept = 0) +
+  labs(x = "Natural Mortality", y = "Change in -LL for Fishery Length Comps") +
+  theme_classic() +
+  theme(legend.position = c(.8, .8)) +
+  scale_y_continuous(limits = c(-.2, 6), expand = c(0, 0))
+
+p2 = profiles.2 %>% 
+  tidytable::filter(Model_Run=="ISSB") %>% 
+  ggplot(aes(x = M, y = Diff, group = variable, color = variable)) +
+  geom_line() +
+  geom_point() +
+  geom_vline(xintercept = 0.3866, linetype = "dashed", color = "black") +
+  geom_text(aes(x = 0.38, label = "Fixed M=0.3866", y = 1.5), colour="blue", angle=90, vjust = 1.2) +
+  geom_hline(yintercept = 0) +
+  labs(x = "M", y = "Change in -LL for Fishery Length Comps") +
+  theme_classic() +
+  theme(legend.position = c(.8, .8)) +
+  scale_y_continuous(limits = c(-.2, 6), expand = c(0, 0))
+
+p1 + p2 + plot_layout(ncol = 1, nrow = 2)
+
+```
+
+#M ISSA to ISSB 3 for paper
+
+```{r, fig.height=6}
+profiles = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/Likelihoods_by_fleet.csv")
+
+profiles %>%
+  tidytable::filter(Label=="Length_like", variable=="Fishery", M>=0.300) %>% 
+  mutate("Fishery Composition ISS" = ifelse(MODEL=="Model_23.1.0.d_NEW_FISS_tuned", "ISSB", "ISSA")) -> profiles.2
+
+profiles.2 %>% 
+  # ggplot(aes(x = M, y = Diff, color = Model_Run, shape = Model_Run)) +
+  ggplot(aes(x = M, y = Diff, color = `Fishery Composition ISS`, shape = `Fishery Composition ISS`)) +
+  geom_line() +
+  scale_shape_manual(values = c(2, 16)) +
+  geom_point(size = 3) +
+  geom_vline(xintercept = 0.3866, linetype = "dashed", color = "black") +
+  geom_text(aes(x = 0.383, label = "Fixed M=0.3866", y = 1.5), colour="black", angle=90, vjust = 1.2) +
+  geom_vline(xintercept = 0.34, linetype = "dotted", color = "black") +
+  geom_text(aes(x = 0.336, label = "Survey M=0.34", y = 1.5), colour="black", angle=90, vjust = 1.2) +
+  geom_hline(yintercept = 0) +
+  labs(x = "Natural Mortality (M)", y = "Change in -log likelihood") +
+  theme_classic() +
+  theme(legend.position = c(.8, .8)) +
+  scale_y_continuous(limits = c(-.1, 2), expand = c(0, 0)) +
+  theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14)) +
+  scale_color_brewer(palette = "Dark2")
+
+```
+notes:
+survey ISS at 0.34 for BOTH ISSA and ISSB. 
+Fixed M is the fixed value for natural mortality specified in the assessment model.
+This is after tuning.
+ISSA min at 0.415, ISSB min at 0.385
+
+caption: "Likelihood profiles of the fishery composition data over natural mortality using ISSA or ISSB in the cod assessment.
+The cod assessment has a fixed value of 0.3866 for natural mortality, and the likelihood profiles of the survey composition data are minimized at 0.34."
+
+say in paper:
+Using ISSB in the assessment suggests a lower value of natural mortality (M) compared to using ISSA.
+The value of M at the minimum negative log likelihood for the fishery composition data using ISSB was 0.385, whereas for ISSA it was 0.415.
+The value of M suggested by ISSB is very close to the fixed value of 0.3866 specified in the cod assessment, and closer to the value suggested by the survey length composition data (0.34 when either ISSA or ISSB is used in the assessment).
+Therefore, using ISSB in the assessment results in less of a data conflict between the fishery and survey length composition information used in the cod assessment.
+
+\newpage
+
+# Bratio for paper
+
+```{r, fig.height=5}
+Bratio = a.out.2 %>% 
+  tidytable::filter(Model_Run == "ISSA tuned", Label%in%Bratio.names) %>% 
+  tidytable::bind_rows(a.out.2 %>% 
+                         tidytable::filter(Model_Run == "ISSB tuned", Label%in%Bratio.names)) %>% 
+  tidytable::mutate(Year = as.numeric(substr(Label, 8, 11))) %>% 
+  tidytable::mutate("Fishery Composition ISS" = ifelse(Model_Run=="ISSA tuned", "ISSA", "ISSB"))
+
+Bratio %>% 
+  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = `Fishery Composition ISS`, linetype = `Fishery Composition ISS`)) +
+  geom_line() +
+  geom_ribbon(alpha = 0.5) +
+  xlab("") +
+  ylab("SSB/SSB unfished") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.85), 
+        legend.direction = "vertical", 
+        legend.box = "vertical") +
+  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = .35, linetype = "dashed", color = "black") +
+  geom_text(aes(x=2032, label="Management Target", y=.33), colour="black", angle=0) +
+  geom_text(aes(x = 2021.6, label = "Assessment Year 2023", y = 0.73), colour="black", angle=90, vjust = 1.2) +
+  scale_x_continuous(breaks = seq(1980, 2040, by = 5), expand = c(0, 0)) +
+  theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14)) +
+  scale_fill_brewer(palette = "Dark2")
+```
+
+caption: "Point estimates and standard deviations of estimated spawning stock biomass (SSB) relative to unfished SSB using ISSA or ISSB in the cod assessment.
+Values past the assessment year of 2023 are projected estimates.
+Horizontal dashed line is the management target of 0.35.
+
+notes:
+After tuning. the point estimates are similar. the uncertainty is comparable prior to the assessment year for most years but is lower for using ISSB compared to ISSA.
+
+say in paper:
+The point estimates of the biomass ratio were similar for most years when using either ISSA or ISSB in the cod assessment.
+However, using ISSB resulted in lower uncertainty for projected estimates (sd = 0.0079 at year 2038) compared to ISSA (sd = 0.0128 at year 2038).
+
+# Plots Together a,b
+
+```{r, fig.height=7}
+
+pa1 = Bratio %>% 
+  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = `Fishery Composition ISS`, linetype = `Fishery Composition ISS`)) +
+  geom_line() +
+  geom_ribbon(alpha = 0.5) +
+  xlab("") +
+  ylab("SSB/SSB unfished") +
+  labs(tag = "a") +
+  theme_classic() +
+  theme(legend.position = c(0.5, 0.85), 
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        plot.tag.position = c(0.15, 0.97),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = .35, linetype = "dashed", color = "black") +
+  geom_text(aes(x=2032, label="Management Target", y=.32), colour="black", angle=0) +
+  geom_text(aes(x = 2021.6, label = "Assessment Year", y = 0.73), colour="black", angle=90, vjust = 1.2) +
+  scale_x_continuous(breaks = seq(1980, 2040, by = 5), expand = c(0, 0)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.25), limits = c(0, 1), expand = c(0, 0)) +
+  theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14)) +
+  scale_fill_brewer(palette = "Dark2")
+
+pa2 = profiles.2 %>% 
+  # ggplot(aes(x = M, y = Diff, color = Model_Run, shape = Model_Run)) +
+  ggplot(aes(x = M, y = Diff, color = `Fishery Composition ISS`, shape = `Fishery Composition ISS`)) +
+  geom_line() +
+  scale_shape_manual(values = c(2, 16)) +
+  geom_point(size = 3) +
+  geom_vline(xintercept = 0.3866, linetype = "dashed", color = "black") +
+  geom_text(aes(x = 0.383, label = "Fixed M", y = 1.5), colour="black", angle=90, vjust = 1.2) +
+  geom_vline(xintercept = 0.34, linetype = "dotted", color = "black") +
+  geom_text(aes(x = 0.336, label = "Survey M", y = 1.5), colour="black", angle=90, vjust = 1.2) +
+  geom_hline(yintercept = 0) +
+  labs(x = "Natural Mortality (M)", y = "Change in -log likelihood", tag = "b") +
+  theme_classic() +
+  theme(legend.position = c(.8, .8),
+        plot.tag.position = c(0.15, 0.97),
+        plot.tag = element_text(size = 14, face = "bold")) + 
+  scale_y_continuous(limits = c(-.1, 2.1), expand = c(0, 0)) +
+  scale_x_continuous(breaks = seq(0.30, 0.44, by = 0.02)) +
+  theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14)) +
+  scale_color_brewer(palette = "Dark2")
+
+pa1 + pa2 + plot_layout(ncol = 1, nrow = 2)
+
+```
+
+CONISDER FULL PARAMETER TABLE IN SUPPLEMENTARY MATERIAL.

### 2025-06-10 run/paper_runs/paper_scenario_25.3.TAS.R

@@ -1,0 +1,67 @@
+
+rm(list = ls())
+run_name = "paper_scenario_25.3.TAS"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy/Downloads/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
+# proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+proportion_global = list(haul = c(.5, .75, 1.25, 1.25), trip = c(.75, .75, .5, .75))
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global$haul)){
+
+    samples = samples_global[i]
+    .proportion_haul = proportion_global$haul[j]
+    .proportion_trip = proportion_global$trip[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = list(type = "proportion", amount = .proportion_trip),
+                new_haul_N = list(type = "proportion", amount = .proportion_haul),
+                new_length_N = list(type = "value", bound = NULL, amount = samples),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = TRUE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0(paste0("haul_", proportion_global$haul)[j], "_", paste0("trip_", proportion_global$trip)[j])]] = .output
+
+  }
+}
+
[…]

### 2025-06-10 run/paper_runs/paper_scenario_40.4.R

@@ -1,0 +1,67 @@
+
+rm(list = ls())
+run_name = "paper_scenario_40.4"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy/Downloads/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20)
+proportion_global = c(0.25, 0.50, 0.75, 1.0)
+
+
+
+
+tictoc::tic()
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global)){
+
+    samples = samples_global[i]
+    .proportion = proportion_global[j]
+
+    # tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = NULL,
+                new_haul_N =list(type = "proportion", amount = .proportion, replace = FALSE),
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = FALSE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    # tictoc::toc()
+    out[[paste0("samples_", samples_global)[i]]][[paste0("haul_", proportion_global)[j]]] = .output
+
+  }
+}
+tictoc::toc()
+
+saveRDS(out, file = paste0("C:/Users/bstacy/baseISS_data/outputs/paper_output/", run_name, "_ISS_", iters_global, "_iters_", Sys.Date(), ".RDS"))
+
+
+
+
+
+
+
+
+
+

### 2025-06-10 run/paper_runs/paper_scenario_50.1.R

@@ -1,0 +1,67 @@
+
+rm(list = ls())
+run_name = "paper_scenario_50.1"
+
+lfreq_data = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_nosex_ebs_pcod_Steve_TRIP_STRATA.RDS")
+library(tidytable)
+library(baseISS)
+
+
+### Global
+iters_global = 500
+samples_global = c(1, 5, 10, 15, 20)
+# proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
+proportion_global = list(haul = c(.5, .5, .75, .75, 1.0), trip = c(.5, .75, .5, .75, 1.0))
+
+
+
+
+# Loop All
+out = list()
+for(i in 1:length(samples_global)){
+  out[[paste0("samples_", samples_global)[i]]] = list()
+  for(j in 1:length(proportion_global$haul)){
+
+    samples = samples_global[i]
+    .proportion_haul = proportion_global$haul[j]
+    .proportion_trip = proportion_global$trip[j]
+
+    tictoc::tic()
+    fishery_iss(species_code = "202",
+                area_code = "EBS",
+                length_based = TRUE,
+                iters = iters_global,
+                freq_data = lfreq_data,
+                yrs = 1999,
+                bin = NULL,
+                plus_len = NULL,
+                post_strata = NULL,
+                minimum_sample_size = list(resolution = "YAGM_SFREQ", size = 30),
+                new_trip_N = list(type = "proportion", amount = .proportion_trip, replace = FALSE),
+                new_haul_N = list(type = "proportion", amount = .proportion_haul, replace = FALSE),
+                new_length_N = list(type = "value", bound = "minimum", amount = samples, replace = FALSE),
+                max_length = 150,
+                boot.trip = TRUE,
+                boot.haul = TRUE,
+                boot.length = TRUE,
+                boot.age = FALSE,
+                expand.by.sampling.strata = FALSE,
+                expansion_factors = c("haul_numbers", "month_numbers"),
+                save_data_frame = FALSE) -> .output
+    tictoc::toc()
[…]
